### 2017-12-18 Draft_Form/saerlp_article_master.tex
Initial commit 18_12_2017
Initital commit

\documentclass[a4paper, 12pt, titlepage]{scrartcl} % tech.report
\usepackage{authblk}

%============================================ Define Titlepage =====================================================%

\author[*$\dag$]{\large Andreas Hill}
\author[*]{\large Daniel Mandallaz}
\author[**]{\large Joachim Langshausen}
\affil[*]{\normalsize Department of Environmental Systems Science, ETH Zurich}
\affil[**]{\normalsize Forest Service Rhineland-Palatinate}       
\renewcommand\Authands{, }

% \date{\vspace{-0.3cm} \large \today \vspace{1.1cm}}
\date{\vspace{-0.8ex}}
\title{\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation of timber volume resources on forest district levels \\ \vspace{2ex}
  \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}}
\subject{\vspace{-1.5cm} Article Draft \vspace{0.2cm} \vspace{-0.5cm}}

% alternative title(s):
% - Implementation of design-based small area estimations on forest district level in Rhineland-Palatinate (Germany) by combining remote sensing information with data of the Third German National Forest Inventory
%
% Large scale implementation of design-based small area estimations on forest district level in Rhineland-Palatinate using data of the Third German National Forest Inventory
% Implementation of design-based small area estimations on forest district level in Rhineland-Paltinate (Germany) by
% combining remote sensing information with data of the Third German National Forest Inventory
%
% Large-scale implementation of design-based small area estimations on forest district level by
% combining remote sensing data with data of the Third German National Forest Inventory
%
% A double-sampling extension of the Third German National Forest Inventory for small area estimations of timber volume resources on forest district level with a large scale application to the federal state of Rhineland-Palatinate
%
%

%============================================ Load Packages ========================================================%
\usepackage{hyperref}
\usepackage{natbib}
 \hypersetup{
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    filecolor=magenta,      
    urlcolor=blue}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}%package zum einbinden von Bildern
\usepackage{fancyhdr}
\usepackage{amsmath} %Paket für erweiterte math. Formeln
\usepackage{amsfonts}
\usepackage{mathptmx}
\usepackage{booktabs}%Weitere Optionen für Tabellen
\usepackage{array} 
\usepackage{float}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{boldline}
\usepackage[explicit]{titlesec}
\usepackage{listings} %für R-Skripte
\usepackage{color}
\usepackage{pdfpages} % to include pdfs
\usepackage{graphicx}
\usepackage[font=footnotesize]{caption} % define font-size for captions
\usepackage[font=footnotesize]{subcaption}
\usepackage{rotating}
\usepackage{longtable} 
\usepackage{dcolumn} 
\usepackage{pictex}
\usepackage{tikz} 
 \usetikzlibrary{external}       % function to externalize tics-graphic buildings
 \tikzset{external/force remake} % overwrites existing externalized pdfs
 \tikzexternalize[prefix=cache/] % All externalized pdf are saved in folder 'cache'
 \tikzexternaldisable % Only externalise on-demand

% comment out to disable line-numbering:
%\usepackage{lineno}
%\linenumbers

%\bibliographystyle{ieeetr}
%\bibliographystyle{apasoft}
\bibliographystyle{spbasic}
%\bibliographystyle{spmpsci}

%============================================ Define Settings ========================================================%

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.2,0.7,0.25}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  %frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=Octave,                 % the language of the code
  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text 
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,                       % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; 
                                   %  also try caption instead of title
}

\titlespacing{\section}{50pt}{2em}{2em} % {left}{before-sep}{after-sep}
\titlespacing{\subsection}{14pt}{2em}{1.5em}
\titlespacing{\subsubsection}{12pt}{2em}{1em}

%\setcounter{page}{1} % Setzt Seitenzahl gleich 1
\setlength{\parindent}{1em} % Einzug bei neuen Absätzen

%============================================ Define personal commands=============================================%

% remind myself of something:
\newcommand{\note}[1]{\color{red}(#1!)\color{black}}
\newcommand{\missref}{\note{[REF]}}
\newcommand{\todo}[1]{\textcolor{blue}{[Todo: #1]}}

% reocurring terms:
\newcommand{\adjrsq}{adjusted $R^2$}
\newcommand{\rmsecv}{RMSE$_{cv}$}
\newcommand{\mha}{m$^3$/ha}
\newcommand{\var}{\mathbb{V}}
\newcommand{\EX}{\mathbb{E}}
\newcommand{\psynth}{\textit{PSYNTH}}
\newcommand{\psmall}{\textit{PSMALL}}
\newcommand{\extpsynth}{\textit{EXTPSYNTH}}

%============================================ Start Document =======================================================%

\begin{document}\sloppy

%============================================ SetUp directories ====================================================%

\maketitle
\thispagestyle{empty}
\newpage

\vspace*{\fill}
\begin{tabular}{lll}

\small Corresponding author$^\dag$: & \small \underline{andreas.hill@usys.ethz.ch} \\
\small Co-authors: & \small \underline{daniel.mandallaz@env.ethz.ch}, \underline{joachim.langshausen@wald-rlp.de} \\
\end{tabular}\\

\begin{tabular}{lll}
\small Publication date: & \small \today \\
\end{tabular}
\newpage

%  Abstract
\input{tex/Abstract}\thispagestyle{empty} \newpage\cleardoublepage

% begin roman pagenumbering
\pagenumbering{Roman}

\tableofcontents
\newpage

\listoffigures
\newpage

\listoftables
\newpage

\pagestyle{fancy} %Kopfzeile und Fusszeile
\fancyfoot[C]{\thepage}
\setlength{\headsep}{15mm}

%============================================ Test temp ===============================================%

%\input{tex/test_temp}\newpage\cleardoublepage

%============================================ Introduction ========================================================%

\pagenumbering{arabic}
\setcounter{page}{1}

\input{tex/Introduction(2)}\newpage\cleardoublepage

%============================================ Materials and Methods ===============================================%

\input{tex/Materials_and_Methods(2)}\newpage\cleardoublepage

%============================================ Results =============================================================%

%\input{tex/Results}\newpage\cleardoublepage

%============================================ Discussion ==========================================================%

%\input{tex/Discussion}\newpage\cleardoublepage

%==================================== Conclusion & Outlook ==========================================================%

%\input{tex/Conclusions}\newpage\cleardoublepage

%============================================ Acknowledgements ==========================================================%

%\input{tex/Acknowledgements}\newpage\cleardoublepage

%============================================ Appendices ==========================================================%

%\input{tex/Appendices}\newpage\cleardoublepage

%============================================ Literature ==========================================================%

\bibliography{bib/literaturerRLPsae}\newpage\cleardoublepage

%==================================================================================================================%
\end{document}

### 2017-12-18 Draft_Form/tex/Abstract.tex
Initial commit 18_12_2017
Initital commit

\section*{Abstract} 
\label{sec:abstract}
The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval. However, the data have scarcely been used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors. In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area estimation procedures that try to overcome the restriction in terrestrial sample size by enlarging the sample by a large set of model predictions. We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (42 and 392 forest district units respectively) in the federal German state of Rhineland-Palatinate. A LiDAR derived canopy height model and a tree species classification map based on satellite data were used as auxiliary information in an ordinary least square regression model to produce the timber volume predictions on the plot level. The results indicate that the suggested double-sampling procedure can significantly increase estimation precision on both management levels compared to estimates based on the simple random sampling (SRS) estimator: on Forstamt-level, the proportion of estimation errors below 6\% could be increased from 10\% to 60\% (90\% were below 7\% estimation error). The increase of estimation precision was even more pronounced on the Revier-level, although the errors were generally higher than on the Forstamt-level: here, the proportion of estimation errors below 10\% could be increased from 15\% to 40\%. The average decrease in variance was ... and ..., and the relative efficiency was ... and ... on Forstamt and Revier-level respectively.

% gain
% relative efficiency
% limiting factors (--> to be solved for the future?)

% Keywords:
\vspace{0.2cm} \noindent \textbf{Keywords.} National forest inventory, small area estimation, double sampling for regression within strata, cluster sampling, LiDAR canopy height model, tree species classification \vspace{-1cm}

% NOTE
% - Problem statement: Large scale inventories, such as the German NFI, provide high accuracies on national as well as federal state level. However, the uncertainty of estimations on smaller scale management levels (destricts) often turns out be unaccepably large.
% - Multi-phase sampling procedures try to overcome the lack of terrestrial information by using an additional large sample of predictions based on remote sensing data. These techniques can particularly be efficient for domains where the terrestrial sample size is considerably small (small area estimation problem).
% - The aim of this article was to 
%
%
%

### 2017-12-18 Draft_Form/tex/Acknowledgements.tex
Initial commit 18_12_2017
Initital commit

\section*{Acknowledgements}
\thispagestyle{plain}

We want to express our gratitude to Prof. H. Heinimann (Chair of Land Use Engineering, ETH Zurich) for supporting this study.

We want to explicitly thank Dr. Johannes Stoffels and Dr. Henning Buddenbaum from the Environmental Sensing and Geoinformatic Group of University of Trier for providing the LiDAR data and tree species classification map.

Special gratitude is owed to the State Forest Service of Rhineland-Palatinate, in particular Jürgen Dietz and Claus-Andreas Lessander, for collaboration and providing the forest inventory- and geodata.

We also want to thank Kai Husmann and Christoph Fischer from the Northwest German Forest Research Institution Göttingen for their advice in processing the terrestrial inventory data.

% people to thank:
% - H.R. Heinimann
% - Johannes und Henning
% - Thomas Riedel (Thuenen-Institute) for providing the densified sample grid
% - Kai Husmann & Christoph Fischer

### 2017-12-18 Draft_Form/tex/Appendices.tex
Initial commit 18_12_2017
Initital commit

%\appendix
%\addcontentsline{toc}{section}{Appendices}
%\section*{Appendices}
%\section{First appendix}
%\section{Second appendix}

\appendix
\section{Appendix}

% ----------------------------------------------------------------------- %
% A.1
% ----------------------------------------------------------------------- %
%\subsection{Model accuracies for $CHM$ variables}

%\input{tab/mod_chm_table.tex}\newpage

### 2017-12-18 Draft_Form/tex/Discussion.tex
Initial commit 18_12_2017
Initital commit

\section{Discussion} %article
\label{sec:Dis}

%\subsection{Stratification according to Tree Species and LiDAR Acquisitions}
%\label{sec:strat_dis}

% NOTES:
%
% - Kuliesis et al.:  --> "NFI [provide reliable estimates for the most important attributes and] can be used 
%                          as a tool for validation of all other inventories", i.e. stand-wise inventories
%                     ==> in our case, we can say that we illustrated how the German NFI data can now be used
%                         for this purpose, i.e. providing of reliable data to validate the stand-wise inventories
%
%
% --> Extension to at least partially exhaustive estimator (three-phase non-exhaustive) if auxiliary data are really exhaustively
%     available
%
%
%
%
%
%
%
%
%
%

### 2017-12-18 Draft_Form/tex/Introduction(2).tex
Initial commit 18_12_2017
Initital commit

\section{Introduction} % article
\label{sec:intro}

The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germanys forest over time. The NFI thereby has to satisfy various information needs and amongst others reports to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}. At the current time, the inventory design of the German NFI solely rests upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany. As this implies covering a large area of 114'191 ha \citep{bwi3}, the sample size has been chosen according to satisfy high estimation accuracies for forest attributes on the national and federal state level. This however leads to very low sampling intensities and consequently, sample sizes often drop dramatically when entering spatial units below the federal state level. This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out be unacceptably large due to the very limited number of sample plots within these units. For this reason, the German NFI data have not yet been extensively incorporated in operational forest planning on forest district management levels. In most German federal states, management strategies are thus still based on expert judgements from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par

Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to base their regional management strategies on quantitative and accurate information \citep{bockmann1998}. However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonluepke2013}. One method which has proven to be efficient is double-or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}. Double sampling incorporates inexpensive auxiliary information and can be used to either increase estimation precision under given terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size. A double sampling for stratification procedure has e.g. been used in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} lately illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs. Recent studies have lately extended double-sampling to triple-sampling estimation methods using auxiliary information in two different sampling intensities. An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories. An other example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par

Two-phase and three-phase samplings techniques have also been used in the service of small area estimation (SAE). SAE techniques particular address the situation where the number of samples within a subunit, so-called small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit. A broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics. A commonly applied SAE method is thereby known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not available in the small area. The statistical models are thereby often developed by "borrowing strength" from data outside the small area. There are numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, and most of the studies use unit-level models, i.e. the statistical models are fitted using data from inventory plots. Especially unit-level models for timber volume estimation under the use of various remote sensing data have been intensively investigated with respect to timber volume prediction \citep{koch2010, naesset2014inmaltamo}. There are also few studies that have investigated area level-models, where the auxiliary information is only provided on the SA-level \citep{magnussen2017}. Some studies have illustrated that even NFI data of low sampling densities can be used in small area estimation procedures to provide estimations of acceptable accuracy on much smaller management levels. One example is \citet{breidenbach2012} who used data from the Norwegian NFI for SAE estimations of standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35. Estimation errors under the applied model-based and design-based SAE estimators turned to be markedly smaller than achieved under simple random sampling (SRS). Another example is \citet{magnussen2014} who recently used the Swiss NFI data for SAE estimation of timber volume within 108 Swiss forest districts with sample sizes between 9 and 206. Despite these promising results, a similar study in Germany using the German NFI data for SAE estimation has not yet been conducted.\par

The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels when incorporated in small area estimation procedures. We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 42 and 392 forest districts respectively. The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a, mandallaz2013b}. Auxiliary information were obtained from a countrywide airborne Laser scanning (LiDAR) canopy height model (CHM) and a tree species classification map and used for regression within tree species strata. The estimation accuracies were compared to those achieved under SRS sampling. The chosen double-sampling estimators were favoured for several reasons: \textbf{(i)} the design-based frame considerably relaxes requirements on the regression model which seemed appropriate facing severe quality restrictions in the LiDAR data; \textbf{(ii)} the estimators can consider \textit{non-exhaustive}, i.e. non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for the design-dependency of the regression coefficients on the sample (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals.\par

The results from this study were considered to provide valuable information whether the suggested procedure a) might be a cost-saving alternative to a regional FDI and b) can be used as a reliable validation for SDI data. A secondary objective was to address the potential effects of auxiliary data quality on estimation precision, and to identify challenges when transferring the existing German NFI design into the suggested double sampling estimation procedure.

%
%
%
%
%Most SA estimators applied in these studies are model-based (model-dependent), i.e. the reliability of the estimates rely on the fact the statistical model adequately specifies the underlying stochastic process that determines the realized distribution of the target variable over the forest area. This can lead to high requirements on the model and imply extensive modelling techniques of correlation structures.
%
%Few SA estimators that have been a
%
%All applied SAE-estimators have in common that they use the so-called finite population approach which implies that the inventory area consists of a well-defined finite population of sample units. 
%
%
%A difference to most SA-estimators that have so far been applied is a) ours are design-based, b) ours use the infinite population
%approach, c) ours are also specified for the special case of cluster sampling. The advantage of the design-based approach is that ..., whereas ...
%
%
%
%
% As SAE methods coming from official statistics are commonly based on list-sampling, the underlying population are considered to be finite which can arise some ambiguities when applied to forest inventories. \citet{mandallaz2013a, mandallaz2013b, mandallaz2013c} recently provided a comprehensive set of small area estimators especially developed for forest inventories under both double- and triple sampling designs in the infinite population approach which is well suited for forest inventories \citep{saborowski2010}.\par
%
%- area-level or unit-level SAE (most are unit-level, i.e. based on plot-observation), but also example of area-level
%  studies (johannes, steen).
%- borrowing strength method
%
%
%
%- classification of sae-methodology not consistent: in Rao, we read about
%  a) direct estimation:
%     o estimation is purely based on data, either yi or auxiliary data, within the small area
%     o 3 types: 1) only yi data, 2) yi data and aux.data that are available in entire population (GREG),
%                3) auxdata only available in small area
%     o assumes / requires a sufficiently large sample size in the small area
%     o in Rao, "borrowing strength" for the reg-coefficients ("survey estimator") is classified as
%       a direct estimator as it does not increase sample size in the sa
%  b) indirect estimation:
%     o becomes necessary if the direct estimators lead to unacceptably large standard errors
%       due to too small sample sizes in the sa
%     o increase the effective sample size in the small area (Rao, p.20)
%     o largely based on sample survey data in combination with auxiliary information
%     o 1) synthetic estimation (with or without auxiliary information) 
%          - uses an direct estimator for a large area AS an indirect estimator for the small area,
%            assumes that small area has the same characteristics as large area, if not -> design-biased
%     o 2) composite estimators: weighted average between synthetic estimator and direct estimator 
%     o choice of models, that provide a link to the small area through additional auxiliary data
%       - mixed models that can consider between area variation by including random area-specific effects
%       - the aim of the modelling is to find the EBLUP, i.e. the best linear unbiased prediction(s). This
%         is done by using the frame of linear mixed models that can e.g. consider spatial dependence random sa effects ...
%         (e.g. gls, ...) 
%       - 2 kind of models: 1) area level models, 2) unit level models 
%       - EBLUP-estimator is a composite estimator (see Breidenbach) that uses a bias correction term
%
%- sae in forest inventory studies:
%  o numerous applications of SAE in forestry: 
%  o most of the studies use unit level models, i.e. the linking models are fitted using data from inventory plots
%    - especially unit-level models for timber volume estimation have been intensively investigated, and the
%      rapidly increasing availability of remote sensing data has made their application also possible for
%      large areas
%  o there are also few studies that use area level models: e.g. \cite{magnussen2017}
%  o some studies have illustrated that the value of NFI data can be increased by using them in sae techniques to provide
%    estimations of acceptable accuracy on much smaller management levels. ... \cite{breidenbach2012}, \cite{magnussen2014},
%    \cite{steinmann2013},...
%
%          
%- differences:
%  o most indirect sae estimators applied in forest inventory are model-based (model-dependent), i.e. relies on the fact
%    the model adequately specifies the underlying stochastic process that determines the realized distribution of the
%    target variable over the forest area. Additionally, most estimators use the finite population framework
%  o Daniel: sae estimators derived in the design-based framework. Advantage: Design-unbiasedness does not depend on the correct
%    specification of the model. This can particularly be an advantage if the auxiliary data are of medium to low quality and
%    a good model fit might be infeasible (?). The estimators are also derived in the infinite population approach. Also, we do
%    have the estimators for cluster sampling.
%  o design-based sae estimator have scarcely been used in forest inventory, no example for application to cluster sampling 
%    until now

%       
%
%
%There are numerous studies that have used the sparse grid of NFI data in small area estimation procedures to provide estimations of acceptable accuracy on much smaller management levels. One example is \citet{breidenbach2012} who use data from the Norwegian NFI and applied the synthetic and generalized regression estimator as well as the EBLUP for SAE estimations of standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35. Two recent studies by \citet{magnussen2014} and \citet{steinmann2013} used the Swiss NFI data for SAE estimation of timber volume and proportion of forest on Forest District level, with terrestrial sample sizes ranging between .... . In all three studies, the most valuable auxiliary information was derived from LiDAR- or photogrammetrical height models.
%
%Despite these promising results, a similar study in Germany using the German NFI data for SAE estimation has not yet been conducted.
%
%The aim of this study was 
%
%--> We will do this: ....
%
%--> Estimators: We will use the 3 SAE estimators

%
%
%
%
%
%
%

% Especially the increasing availability of high quality auxiliary data (LiDAR- or photogrammetrical height information, satellite)

%
%There exist a broad range of literature covering SAE estimation methods in official statistics \cite{rao2015} as well as forest inventory \citep{kohl2006}.
%
%
%
%Mandallaz recently provided a comprehensive set of small area estimators especially developed for forest inventories under both double- and triple sampling designs in the infinite population approach (citations) which has frequently stated to be very well suited for forest inventories (saborowski2010).
%
%
%There has been an extensive literature covering SAE estimation procedures in official statistics (Rao) which have also been adjusted and applied to small area estimation problems in forest inventories (Breidenbach). As these methods are based on list-sampling, the underlying population are considered to be finite which can arise some .... when applied to forest inventories. 
%
%Mandallaz recently provided a comprehensive set of small area estimators particularly developed for forest inventories under both double- and triple sampling designs in the infinite population approach (citations) which has often been stated to be better suited for forest inventories (saborowski2010).
%
%
%
%
%A method which has gained much attention is double-sampling and there is a broad range of literature describing double-sampling estimation in official statistics as well as forest inventory \citep{sarndal2003, gregoire2007, kohl2006, schreuder1993}. Double sampling procedures use inexpensive auxiliary information, often provided by spatially exhaustive remote sensing data, in order optimise the terrestrial sample design \citep{grafstrom2017a} or to create a large sample of predictions of the terrestrial target variable additional to the terrestrial observations
%
%
%
%
%
%An alternative way to approach the SAE problem if a densified regional inventory is not feasible is the application of Small Area Estimation procedures. In this case, 
%
%Double and triple sampling methods can also be used to tackle the small area estimation problem. 
%
%There has been an extensive literature covering SAE estimation procedures in official statistics (Rao) which have also been adjusted and applied to small area estimation problems in forest inventories (Breidenbach). As these methods are based on list-sampling, the underlying population are considered to be finite which can arise some .... when applied to forest inventories. Mandallaz recently provided a comprehensive set of small area estimators especially developed for forest inventories under both double- and triple sampling designs in the infinite population approach (citations) which has frequently stated to be very well suited for forest inventories (saborowski2010).
%
%There are few studies that used the sparse grid of NFI data in small area estimation procedures to provide estimations of acceptable accuracy on much smaller management levels. One example is Breidenbach (2012) who applied ... for 14 municipalities where the number of NFI samples within these areas were between 1 and 35.
%
%
%
%
%
%
%
%

### 2017-12-18 Draft_Form/tex/Introduction.tex
Initial commit 18_12_2017
Initital commit

\section{Introduction} % article
\label{sec:intro}

The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germanys forest over time. The NFI thereby has to satisfy various information needs and amongst others reports to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}. At the current time, the inventory design of the German NFI solely rests upon a terrestrial inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany. As this implies covering a large area of 114'191 ha \citep{bwi3}, the sample size has been chosen according to satisfy high estimation accuracies for forest attributes on the national and federal state level. This however leads to very low sampling intensities and consequently, sample sizes often drop dramatically when entering spatial units below the federal state level. This is particularly true for forest management levels such as forest districts for which the estimations uncertainties often turn out be unacceptably large due to the limitation of available inventory data. For this reason, the German NFI data have not yet been extensively used for operational forest planning on these management levels. As a consequence, the management strategies in most German federal states are based on expert judgements from time-consuming standwise inventories (SFI). As such ocular SFI estimates are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty, some German federal states (e.g. Lower-Saxony) have established a regional Forest District Inventory (FDI) carried out independently from the NFI \citep{bockmann1998} in order base their decisions also on quantitative and precise inventory information.\par

However, due to high financial costs of FDIs on the one hand, and limited financial and staff resources on the other hand, there has been an increasing need for alternative, more efficient inventory methods that increase estimation precision at identical costs, or maintain estimation precision at lower costs \citep{vonluepke2013}. The incorporation of additional inexpensive auxiliary information, e.g. from remote sensing data, stand maps or past inventory data, via data assimilation approaches has frequently been addressed as a key to improve information precision and thus the quality of forest planning results \citep{saad2017}. A data assimilation method which has become particular attractive with respect to forest inventories is multi-phase sampling. Multi-phase sampling methods use auxiliary information in two basic ways, i.e. either to create a balanced terrestrial sample design \citep{grafstrom2017a} or to predict the terrestrial target variable by the use of some prediction model. The basic idea of the latter is to boost the sample size in the inventory area by creating an additional large sample of predictions at locations where the terrestrial information has not been gathered.\par

Estimators using multi-phase sampling designs consider either one additional sample of auxiliary information, so called two-phase or double sampling \citep{gregoire2007, mandallaz2008}, or even two nested samples of auxiliary information with different sample sizes, so called three-phase or triple-sampling \citep{mandallaz2013c}. Recent studies have already illustrated that the extension of existing terrestrial inventories to double-or triple sampling designs can lead to an enormous increase in efficiency in terms of cost-saving and estimation precision. \citet{bockmann1998, saborowski2010} optimized the FDI of Lower Saxony (Germany) to a double-sampling for stratification inventory that uses aerial images as auxiliary information for strata-classification in the large inventory phase. \citet{vonLuepke2012} recently suggested an extension of to a three-phase design that indicated a possible reduction of terrestrial sample sizes for intermediate inventories when using updates of past inventory data as additional auxiliary information. \citet{massey2014a}

suggested an extension of the Swiss National Forest Inventory

% -- SAE with NFI data:
% have demonstrated the huge potential of double- and triple sampling 
%
%There are few studies were NFI data have been used in multi-phase sampling procedures in order to provide small area estimations. (Breidenbach, Magnussen)
%

% -- What we doin this article:
%
%
%

% NOTES:
%
% overall focus (how to set iz up): -> make efficient use of the German NFI data on local forest management levels
% 
% -> limited resources --> need for more efficient methods in terms of cost reduction while mainntaining or increasing
%                          the amount and quality of information
%
% -> switch to "attractive" methods: incorporation of auxiliary information (DA-assimilation -> Saad et al.), explain method with respect of sae estimation
%    
% -> review of studies, where mphase-methods have been applied to:
%    - regional forest inventories:
%      o v.Lübke: changing the FDI Lower-Saxony to a three-phase design 
%    
%   - national forest inventories:
%     o Breidenbach (sae-estimation!)
%     o Grafström 
%
% -> what do we do (New)?
%
%    o we will demonstrate how the German NFI data can be combined with auxiliary information for design-based two-phase sae estimators
%      in order to produce estimations of the standing timber volume within two important management (FD-)levels
%
%    o we will therefore extend the German NFI to a two-phase sampling design, where the German NFI data are used as 
%      the terrestrial phase information
%
%   o we will use double-sampling for regression within strata
%
%    o we will illustrate the implementation and evaluate the potential of the proposed estimation method
%      in the federal German state of Rhineland-Palatinate (sae estiamtions for 42 and 392 forest district units respectively)
%
%    o we will compare the performance of different sae design-based estimators (psmall, extpsynth, psynth)
%
% -> what unanswered questions do we address:
%    o adress strength and weaknessess of the implementation (quality requirements / restrictions of auxiliary data, ...)
%    o which estimation accuracies on FD-levels can be achieved by using the German NFI data within two-phase sae estimators ?
%
% - 1) Niki: three-phase sampling for regression within strata applied in the FDI in Lower-Saxony
%
% - 2) Massey: three-phase sampling for the Swiss NFI under the new annual sampling design
%
% - 3) Breidenbach: 
%
%

% - Problem statement: Large scale inventories, such as the German NFI, provide high accuracies on national as well as federal state level. However, the uncertainty of estimations on smaller scale management levels (destricts) often turns out be unaccepably large due to limited sample size. Thus, the NFI data have not yet been extensively used in and for operational forest planning
%
% - Promising solution: Multi-phase sampling procedures try to overcome the lack of terrestrial information by using an additional large sample of predictions based on remote sensing data. These techniques can particularly be efficient for domains where the terrestrial sample size is considerably small (small area estimation problem).
%
% - Review: Whats has practically, i.e. implementation of such procedures in practice, been done in this frame internationally, especially in terms of large scale applications? Switzerland: [Alex], Norway: [...], Germany: [has it been done on federal state level?; if not, then we are the first to implement and "test" such a procdure]
%
% - gap of knowledge: 
%   a) (locally in RLP): are mphase-procedures an alternative of enlarging the terrestrial sample
%      (Betriebsinventur)? (general question)
%   b) (locally in RLP): Can mp-estimations support the "waldbegang"? (specific question in RLP)
%   c) (internationally): Is an evaluation from large scale implementations missing?
%      (i.e. challenges regarding implementation & data availability; effects that occur; ...)
%
% - The aim of this article was (thus) to:
% a) investigate whether the German NFI data can provide accectable estimation precision for small domains (i.e. forest districts) when incorporated in multi-phase estimation procedures using the example of timber volume estimation
% b) integrate available remote sensing data sources
% c) address challenges that occure when transferring the methodology of mutli-phase estimators to large scale real world inventories [...]
%
% - compare the performance of different design-based estimators (psmall, extpsynth, psynth)
%   (adress differences between psmall and extpsynth under cluster sampling)
%

%Forest inventory methods have long been an integral instrument to investigate the current state and the development of forests within reoccurring time periods. They provide reliable and evidence based information when it comes to define and locate management actions and to adapt forest management strategies according to guidelines on national- and international level. Methods that have recently become particularly attractive are so called \textit{double-sampling} \citep{mandallaz2008} and \textit{mapping} \citep{beaudoin2014} procedures. The core concept of these methods is to use predictions of the terrestrial target variable at additional sample locations where the terrestrial information has not been gathered. These predictions are produced by models that use explanatory variables derived from \textit{auxiliary information}, mostly spatially exhaustive remote sensing data, in the inventory area. The specific scope of double-sampling methods is to enlarge the terrestrial sample size by a much larger sample of predictions of the target variable in order to gain higher estimation precision without performing additional expensive terrestrial measurements. Among a broad range of concepts and methods for double sampling procedures \citep{gregoire2007, kohl2006, schreuder1993}, model-based and model-assisted regression estimators have been widely used \citep{breidenbach2012, mandallaz2013b, magnussen2014, massey2014a}. While double-sampling methods provide reliable estimations for a given spatial unit, e.g. a forest district, they do not provide information about the spatial distribution of the estimated quantity within this area. For this reason, the same modelling technique as used in the double-sampling procedures have also been intensively used to produce exhaustive prediction maps that provide pixelwise estimations of a target variable in high spatial resolution \citep{vanaardt2008, latifi2010, hill2014, nink2015}.\par
%
%To allow for an area-wide application of the prediction model, both double sampling- and mapping methods require that the remote sensing data are available over the entire inventory area. This is usually not a limiting factor in \textit{small-scale} applications. In an optimal case, the remote sensing data are in principle collected in accordance to the specific study objective. Quality standards that have often been addressed are that \textit{a)} the remote sensing data should be acquired close to or even at the time of the terrestrial inventory in order to ensure best possible comparability between the target variable on the ground and the remote sensing derived variables \citep{mcroberts2015}; \textit{b)} the remote sensing technology and its spectral and spatial resolution should specifically been chosen according to the modelling purpose \citep{kohl2006}; and \textit{c)} the variation in quality of the remote sensing data over the inventory area should be minimized in order to avoid artificial noise in the data \citep{naesset2014inmaltamo}. Despite the increasing availability and decreasing costs of remote sensing data \citep{white2016}, these quality standards of the remote sensing data can often not be guaranteed for \textit{large-scale} applications \citep{maack2016}, and trade-offs must be coped with \citep{jakubowski2013}. The prime objective is then to produce the best possible prediction model given the restrictions imposed by the actually available remote sensing information. The exploration of scarcely used remote sensing products and the optimization of prediction models under severe quality restrictions in the remote sensing data are thus one of the challenges in large-scale model-supported inventory applications.\par
%
%Among the still rarely used remote sensing data in large scale applications, the use of tree species information in prediction models - especially for timber volume estimation - has been stated as one of the most promising but often missing information \citep{koch2010, white2016}. As timber volume estimations on single tree level in forest inventories are often based on species-specific biomass and volume equations \citep{zianis2005}, the application of species specific models is expected to be a key factor for improving estimation precision \citep{white2016}. \citet{straub2009} and \citet{latifi2012} already reported a notable gain in model performances when they used a stratification according to broadleaf and coniferous tree species on sample plot level in addition to canopy height metrics for timber volume estimations. One of the rare examples for using more species specific information is \citep{packalen2006} who applied a separate prediction of the sample plot timber volume for Scots pine, Norway spruce and a deciduous-species group. However, studies are necessary especially for countries whose forests are characterized by a larger variety of tree species that may also occur in mixed and uneven-aged stands \citep{mcroberts2010}. The area-wide tree species information in most studies were obtained from satellite- and airborne remote sensing sensors based on automatic classifcation methods. Whereas the presence of misclassifications has already been addressed \citep{latifi2012}, an issue that has so far been neglected is how misclassifications actually affect the prediction model \citep{gustafson2003}.\par
%
%A frequently encountered problem in large scale forest inventories is the lack of temporal synchronicity between the remote sensing acquisition and the terrestrial survey. As a result, the available remote sensing data might exhibit notable time-lags to the date of the terrestrial inventory. This has often been addressed as a major drawback, especially for the application of model-assisted change estimation \citep{massey2015b}.\\
%
%Our study is embedded in the current implementation of model-assisted regression estimators \citep{mandallaz2013a, mandallaz2013b, mandallaz2013c} for estimating the standing timber volume within various forest management units over the entire state of Rhineland-Palatinate (RLP, Germany). With respect to this overall objective, the aim of this study was to derive an ordinary least square regression model to generate predictions of the standing timber volume associated to a sample location of the Third German National Forest Inventory (BWI3) over the entire federal state forest area (6155 km$^2$). Both a merged LiDAR dataset from different acquisition years and a satellite-based tree species classification map (which predicts the five major tree species of RLP), was available for the entire inventory area and consequently used to derive predictor variables. The major limiting factors for using these data in a regression analysis are \textbf{(i)} variation in the LiDAR data quality as well as time-lags of up to 10 years between the LiDAR acquisitions and the terrestrial survey, \textbf{(ii)} misclassifications in the tree species classification map and \textbf{(iii)} the ambiguous choice of a suitable extraction area (\textit{support}) for each remote sensing information under angle count sampling in the terrestrial survey (variable sample plot sizes).\par
%
%For this reason, we address the following specific research questions:
%
%\begin{enumerate}
% \item How can tree species map information be optimally used within a timber volume regression model? Which effects do misclassifications have on the model properties and how can these effects be minimized?
% \item What is the effect of quality restrictions and substantial time-lags between the LiDAR- and terrestrial data acquisition on the regression model, and can we account for the this type of noise in the data?
% \item Does support-size influence model accuracy? What is the optimal support size for each remote sensing information and what are the determining factors?
%\end{enumerate}

### 2017-12-18 Draft_Form/tex/Materials_and_Methods(2).tex
Initial commit 18_12_2017
Initital commit

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %

\section{Terrestrial sampling design of the German NFI}
\label{sec:germanNFI}

The German National Forest Inventory (German NFI) is a periodic inventory that is carried out every 10 years over the entire forest area of Germany. The most recent inventory (BWI3) was conducted in the years 2011 and 2012. While information was originally gathered at a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid. The German NFI uses a cluster sampling design, which means that a sample unit consists of maximal four sample locations (also referred to as \textit{sample plots}) that are arranged in a square (so called \textit{cluster}) with a side length of 150 metres (Picture). The number of plots per cluster can however vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}. In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the tree-individual inclusion circle \citep{bwi3_aufn}. A further inventory threshold for a tree to be recorded is a diameter at breast height ($dbh$) of at least 7 cm. For each sample tree that is selected by this procedure, the dbh, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to calculate a volume estimation on the tree level. These volume estimations are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.

% ++++++++++++ %
\section{Double sampling in the infinite population approach}
\label{sec:inf_pop}

% \subsubsection{One- and Two-Phase Sampling in the Infinite Population Approach}

The estimators used in this study have been proposed by \citep{mandallaz2013a,mandallaz2013b} and build upon the so called infinite population approach (IPA) in order to bridge the inventory procedure and the derived information to the mathematics behind the estimators. Therefore, we shall first provide a short introduction into this general estimation frame. We start by assuming that the population $P$ of trees $i \in 1,2, ..., N$ within a forest of interest $F$ is exactly defined, and each tree $i$ has a directly or indirectly observable response variable $Y_i$ (e.g. its timber volume) that allows to specify the population mean $Y$ (e.g., the average timber volume per unit area) over $F$. If a full census of all tree population individuals is not possible, $Y$ has to be estimated by the conduction of an inventory.  The infinite population approach assumes that the spatial distribution of the local density $Y(x)$ (e.g., the timber volume per unit area) at each point or location $x$ in the forest $F$ is given by a fixed (i.e. non stochastic) piecewise constant function. The population mean $Y$ is thus mathematically equivalent to the integral of the density function surface divided by the forest area $\lambda(F)$, i.e. $Y=\frac{1}{\lambda(F)} \sum_{i=1}^{N}Y_i=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$, and thus the population mean $Y$ corresponds to a spatial mean. Since the local density function is in practice always unknown, one estimates $Y$ by collecting a sample $s_2$ of all local density values by the conduction of a terrestrial inventory at $n_2$ uniformly and independently distributed sample points over $F$. This procedure is often referred to as \textit{one-phase sampling} (OPS). Opposed to the one-phase approach, \textit{two-phase} or \textit{double-sampling} procedures use information from two nested samples (phases). Practically speaking, the terrestrial inventory $s_2$ is embedded in a large phase $s_1$ comprising $n_1$ sample locations that each provide a set of explanatory variables described by the column vector $\pmb{Z}(x)=(z(x)_1, z(x)_2,...,z(x)_p)^{\top}$ at each point $x \in s_1$. These explanatory variables are derived from auxiliary information that is available in high quantity within the forest $F$. For every $x \in s_1$, $\pmb{Z}(x)$ is transformed into a prediction $\hat{Y}(x)$ of $Y(x)$ using the choice of some prediction model. The basic idea of this method is to boost the sample size by providing a large sample of less precise but cheaper predictions of $Y(x)$ in $s_1$ and to correct any possible model bias, i.e., $\EX{(Y(x)-\hat{Y}(x))}$, using the subsample of terrestrial inventory units where the value of $Y(x)$ is observed.

% which in \pkg{forestinventory} is always a linear model fit in $s_2$ using ordinary least squares (OLS).
%The one-phase and two-phase estimators applied in this study have been implemented in the software-package \textit{forestinventory} \cite{forestinventory} 
% The local density $Y(x)$ is in practice derived by ...
% extend the approach to collecting auxiliary information ...
% say that we also assume that the forest area is well-defined ...

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\section{Estimators}
\label{sec:estimators}

% ++++++++++++ %
\subsection{Design-based SRS estimator for cluster sampling}
\label{sec:srs_estimator}

The simple random sampling (SRS) estimator for cluster sampling constitutes the \textit{status quo} that is currently applied under the existing one-phase sampling design of the German NFI in order to obtain a point and variance estimate for the mean timber volume of a given estimation unit. In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator that is applied in the BWI3 algorithms \citep{bwi3_ausw} in the form given in \citet{mandallaz2008, mandallaz2016}.\par 
In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M=4$ ) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$. The actual number of plots per cluster, $M(x)$, is a random variable due to the uniform distribution of $x_l$ ($l=1, ..., M$) in the forest $F$ and forest/non-forest decision for each sample location $x_l$:

\begin{equation}\label{eq:Mx}
M(x)=\sum_{l=1}^{M}I_{F}(x_l) \hspace{3ex} \text{where} \hspace{3ex} I_F(x_l)=\begin{cases}&1 \text{ if $x_l \in F$}\\
&0 \text{ if $x_l\not\in F$}
\end{cases}
\end{equation}

The local density on cluster level $Y_{c}(x)$, in our case the timber volume per hectare, is then defined as the average of the individual sample plot densities $Y(x_l)$:

\begin{equation}\label{eq:locdens_clust}
Y_{c}(x) = \frac{\sum_{l=1}^{M} I_{F}(x_{l}) Y(x_l)}{M(x)}
\end{equation}

The local density $Y(x_l)$ on individual sample plot level was calculated according to the description in \citet{mandallaz2008}, which can be rewritten for angle-count sampling technique applied in the BWI3. The general form of $Y(x)$ in \citet{mandallaz2008} is given as the Horwitz-Thompson estimator

%\begin{equation}\label{locdens_plot}
%Y(x)= \sum_{i=1}^{F}\frac{I_{i}(x)Y_i}{\varPi_{i}\lambda(F)} = \sum_{i \in s_{2}(x)}\frac{Y_i}{\varPi_{i}\lambda(F)}
%\end{equation}

\begin{equation}\label{eq:locdens_plot}
Y(x_l)=\sum_{i \in s_{2}(x_l)}\frac{Y_i}{\pi_{i}\lambda(F)}
\end{equation}

where $Y_i$ is in our case the predicted timber volume of the tree $i$ recorded at sample location $x$ in m$^3$. Each tree has an inclusion probability $\pi_{i}$ that is well defined as the proportion of its inclusion circle area $\lambda(K_i)$ within the forest area $\lambda(F)$, i.e. via their geometric intersection:

%with the binary indicator variable $Ii$ for the $i$th tree defined as
%
%\begin{equation}\label{1stage}
%I_i(x)=\begin{cases}&1 \text{ if $x \in K_i$}\\
%&0 \text{ if $x\not\in K_i$}
%\end{cases}
%\end{equation}

\begin{equation}\label{locdens_plot_1}
\pi_{i} = \frac{\lambda(K_i \cap F)}{\lambda(F)}
\end{equation}

The radius $R_i$ of the tree-individual inclusion circle $K_i$ is given by $R_i = bhd_{i}/cf_{i,corr}$ (also referred to as \textit{limiting distance}), where $cf_{i,corr}$ is the counting factor corrected for potential boundary effects at the forest border. In case of angle-count sampling, we can rewrite $\pi_{i}$ as

\begin{equation}\label{eq:locdens_plot_2}
\pi_{i} = \frac{G_i}{cf_{i,corr}\lambda(F)}
	\end{equation}

since the intersection area $\lambda(K_i \cap F)/\lambda(F)$ can be expressed using the trees basal area $G_i$ (in m$^2$) and the corrected counting factor:

\begin{equation}\label{eq:locdens_plot_3}
\lambda(K_i \cap F) = \frac{G_i}{cf_{i, corr}} \hspace{3ex} \text{where} \hspace{3ex} cf_{i,corr} = cf\frac{\lambda(K_i)}{\lambda(K_i \cap F)}
\end{equation}

Using Eq. \ref{eq:locdens_plot_2} in Eq. \ref{eq:locdens_plot} yields the rewritten form of $Y(x_l)$ for angle count sampling that conforms to the definition used in the BWI3 algorithms \citep{bwi3_ausw}:

\begin{equation}\label{eq:locdens_plot_4}
Y(x_l)= \sum_{i \in s_{2}(x_l)} \frac{cf_{i, corr}Y_i}{G_i} = \sum_{i \in s_{2}(x_l)} nha_{i}{Y_i}
\end{equation}

where $nha_i$ is the number of trees per hectare represented by tree $i$. The local densities on cluster level can then be used to derive the estimated spatial mean $\hat{Y}_c$ and its estimated variance $\hat{\var}(\hat{Y}_c)$ for any given spatial unit for which $n_2 \geq 2$ ($n_2$ denoting the number of sample units, i.e. clusters):

\begin{subequations}\label{eq:srs_est_cluster}
	\begin{align}
\hat{Y}_c &= \frac{\sum_{x \in s_2} M(x) Y_{c}(x)}{\sum_{x \in s_2} M(x)} \\
\hat{\var}(\hat{Y}_c) &= \frac{1}{n_2(n_2 - 1)}\sum_{x \in s_2}\Big(\frac{M(x)}{\bar{M_2}}\Big)^2(Y_{c}(x) - \hat{Y}_c)^2
	\end{align}
\end{subequations}

\newpage

% +++++++++++++++++++++++++++++ %
\subsection{Design-based small area regression estimators for cluster sampling}
\label{sec:SAestimators}

All three considered small area estimators have in common that they use ordinary least square (OLS) regression models to produce the predictions of the local density $Y_{c}(x)$ directly on the cluster level $c$. We consider the \textit{internal model approach}, where the vector of estimated regression coefficients on the cluster level is found by "borrowing strength" from the entire terrestrial sample $s_2$ of the current inventory:

\begin{subequations}\label{normequ_simple_cluster}
	\begin{align}
\hat{\pmb{\beta}}_{c,s_2} &= \pmb{A}_{c,s_2}^{-1} \Big(\frac{1}{n_2}\sum_{x\in{s_2}}M(x)Y_{c}(x)\pmb{Z}_{c}(x)\Big) \\
\pmb{A}_{c,s_2} &=\frac{1}{n_2}\sum_{x\in{s_2}}M(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)
	\end{align}
\end{subequations}

\noindent $\pmb{Z}_{c}(x)$ is the vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Eq.\ref{eq:Zc(x)}). The weight $w(x_l)$ is the proportion of the support-area within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.

\begin{equation}\label{eq:Zc(x)}
\pmb{Z}_{c}(x)=\frac{\sum_{l=1}^{M}I_{F}(x_l)w(x_l)\pmb{Z}(x_l)}{\sum_{l=1}^{M}I_{F}(x_l)w(x_l)}
\end{equation}

\noindent The estimated design-based variance-covariance matrix $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}$ accounts for the fact that the regression model is internal by reflecting the dependency of the estimated regression coefficients on the realized sample $s_2$. It is defined as

\begin{equation}\label{eq:varcovarbeta}
\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}=\pmb{A}_{c,s_2}^{-1}
\Big(\frac{1}{n_2^2}\sum_{x\in{s_2}}M^{2}(x)\hat{R}_{c}^2(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)\Big)
\pmb{A}_{c,s_2}^{-1}
\end{equation}

\noindent with $\hat{R}_{c}=Y_{c}(x)-\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2}$ being the empirical model residuals at the cluster level, which by construction of OLS satisfy the important \textit{zero mean residual property}, i.e. $\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$.\\

 In the following, we will give a short description of each small area estimator and refer to \citet{mandallaz2013a, mandallaz2016, mandallaz2013b} if the reader requires additional details or proofs. The estimators have also been implemented in the R-package \textit{forestinventory} \citep{forestinventory} which was used to compute all estimates in this study.\\

% ----------------------------- %
% PSMALL estimator:
\subsubsection{Pseudo Small Area Estimator (\psmall{})}
% \textbf{Pseudo Small Area Estimator (\psmall{})}\\

All point information used for small area estimation is now restricted to that available at the sample locations $s_{1,G}$ or $s_{2,G}$ in the small area $G$, with exception of $\hat{\pmb{\beta}}_{c,s_2}$ and $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}$ which are always based on the entire sample $s_2$. We thus first define the following quantities on the small area level:

\begin{subequations}\label{eq:compsG}
	\begin{align}
	\hat{\bar{\pmb{Z}}}_{c,G} &= \frac{\sum_{x \in s_{1,G}} M_{G}(x) \pmb{Z}_{c,G}(x)}{\sum_{x \in s_{1,G}} M_{G}(x)} \label{eq:meanZcG} \hspace{3ex} &\text{where} \hspace{3ex}
	\pmb{Z}_{c,G}(x) =  \frac{\sum_{l=1}^{L} I_{G}(x_l)\pmb{Z}(x_l)}{M_{G}(x)}\\		
	Y_{c,G}(x) &= \frac{\sum_{l=1}^{L} I_{G}(x_l)\pmb{Y}(x_l)}{M_{G}(x)}  &\text{and} \hspace{3ex}
	\hat{Y}_{c,G}(x)=\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2}\\
	\bar{\hat{R}}_{2,G} &= \frac{\sum_{x \in s_{2,G}} M_{G}(x) \hat{R}_{c,G}(x)}{\sum_{x \in s_{2,G}} M_{G}(x)} \hspace{3ex} &\text{where} \hspace{3ex}
	\hat{R}_{c,G}(x) = Y_{c,G}(x)-\hat{Y}_{c,G}(x)
	\end{align}
\end{subequations}

Note that the restriction to $G$, i.e. $I_{G}(x_l)=\{0,1\}$, is made on the individual sample plot level $x_l$, and $M_{G}(x) = \sum_{l=1}^{L}I_{G}(x_l)$ thus is the number of sample plots per cluster within the small area. The asymptotically design-unbiased point estimate of \textit{PSMALL} is then defined according to Eq. \ref{eq:psmall_pest}. The first term estimates the small area population mean of $G$ by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$. The second term then corrects for a potential bias of the regression model predictions in the small area $G$ by adding the mean of the empirical residuals $\bar{\hat{R}}_{2,G}$ in $G$. This correction insures that the \textit{zero mean residual property} in $F$ also holds within the small area $G$, which is per se not ensured by fitting the regression coefficients with data outside $G$.

\begin{subequations}\label{eq:psmall}
	\begin{align}
	\hat{Y}_{c,G,PSMALL} &= \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} + \bar{\hat{R}}_{2,G} \label{eq:psmall_pest} \\
	\hat{\var}(\hat{Y}_{c,G,PSMALL}) & = \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}\hat{\bar{\pmb{Z}}}_{c,G}
	+ \hat{\pmb{\beta}}_{c,s_2}^{\top}\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}\hat{\pmb{\beta}}_{c,s_2} \nonumber \\
	& + \frac{1}{n_{2,G}(n_{2,G}-1)}\sum_{x \in s_{2,G}}\Big(\frac{M_{G}(x)}{\bar{M}_{2,G}}\Big)^2(\hat{R}_{c,G}(x) - \bar{\hat{R}}_{2,G})^2
	\label{eq:psmall_var}
	\end{align}
\end{subequations}

The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Eq. \ref{eq:psmall_var}. Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean in $G$ using a non-exhaustive sample $s_{1,G}$. The third term is the variance of the model residuals and thus accounts for the inaccuracies of the model predictions. Note that the first term can also be rewritten using g-weights \cite[pg.14]{mandallaz2016} which ensure calibration properties of the auxiliary variables on the terrestrial sample.\\

The variance-covariance matrix of the auxiliary vector $\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}$ is thereby defined as

\begin{equation}\label{estvarcovaux_G}
\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}} = \frac{1}{n_{1,G}(n_{1,G}-1)} \sum_{i \in s_{1,G}} \big(\frac{M_{G}(x)}{\bar{M}_{1,G}}\big)^2 (\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})(\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})^{\top}
\end{equation}

with $\bar{M}_{1,G}=\frac{\sum_{i \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.\\

% ----------------------------- %
% PSYNTH estimator:
\subsubsection{Pseudo Synthetic Estimator (\psynth{})}
% \textbf{Pseudo Synthetic Estimator (\psynth{})}\\

The \psynth{} estimator is commonly applied when no terrestrial sample is available within the small area $G$ (i.e. $n_{2,G}=0$). The point estimate (Eq. \ref{eq:psynth_pest}) is thus only based on the predictions generated by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$. Note that the bias correction term using the empirical residuals (Eq. \ref{eq:psmall_pest}) can no longer be applied. The \psynth{} estimator thus has a potential unobservable design-based bias.

\begin{subequations}\label{eq:psynth}
	\begin{align}
	\hat{Y}_{c,G,PSYNTH} & =\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} \label{eq:psynth_pest} \\
	\hat{\var}(\hat{Y}_{c,G,PSYNTH})& =
	\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}
	\hat{\bar{\pmb{Z}}}_{c,G}
	+ \hat{\pmb{\beta}}^{\top}_{c,s_2}\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}\hat{\pmb{\beta}}_{c,s_2} \label{eq:psynth_var}
	\end{align}
\end{subequations}

The uncertainty of the model predictions can also no longer be considered in the variance estimation (Eq. \ref{eq:psynth_var}). The synthetic estimator will therefore usually have a smaller variance than estimators incorporating the model uncertainties, but at the cost of a potential bias. Note that the \psynth{} estimator is still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.\\

% ----------------------------- %
% EXTPSYNTH estimator:
\subsubsection{Extended Pseudo Synthetic Estimator (\extpsynth{})}
% \textbf{Extended Pseudo Synthetic Estimator (\extpsynth{})}\\

The \extpsynth{} estimator (Eq. \ref{eq:extpsynth}) has been proposed by \cite{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased. It has the advantage that the mean of the empirical model residuals of the OLS regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e. $\bar{\hat{R}}_{c} = \bar{\hat{R}}_{c,G} = 0$. This is realized by \textit{extending} the auxiliary vector $\pmb{Z}_{c}(x)$ by the indicator variable $I_{c,G}$ which takes the value 1 if the entire cluster lies within the small area $G$ and 0 if the entire cluster is outside $G$, i.e. $I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$. The extended auxiliary vector thus becomes $\pmb{\mathbb{Z}}_{c}^{\top}(x)= (\pmb{Z}_{c}^{\top}(x),I_{c,G}(x))$ and the new regression coefficient using $\pmb{\mathbb{Z}}_{c}(x)$ instead of $\pmb{Z}_{c}(x)$ in Eq. \ref{normequ_simple_cluster} is denoted as $\hat{\pmb{\theta}}_{s_2}$. All remaining components are calculated by plugging in $\pmb{\mathbb{Z}}_{c}(x)$ in Eq. \ref{eq:compsG}. A decomposition of $\hat{\pmb{\theta}}_{s_2}$ reveals that the residual correction term is now included in the regression coefficient $\hat{\pmb{\theta}}_{s_2}$.

\begin{subequations}\label{eq:extpsynth}
	\begin{align}
	\hat{Y}_{c,G,EXTPSYNTH} & =\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}^{\top}\hat{\pmb{\theta}}_{c,s_2} \label{eq:extpsynth_pest} \\
	\hat{\var}(\hat{Y}_{c,G,EXTPSYNTH})& =
	\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\theta}}_{c,s_2}}
	\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}
	+ \hat{\pmb{\theta}}^{\top}_{c,s_2}\hat{\pmb{\Sigma}}_{\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}}\hat{\pmb{\theta}}_{c,s_2} \label{eq:extpsynth_var}
	\end{align}
\end{subequations}

However, it is important to note that $\bar{\hat{R}}_{c,G} = 0$ under the extended regression model only holds if the sample plots $x_1, ..., x_l$ of a cluster are \textit{all} either inside our outside the small area, i.e. $M_G(x)\equiv M(x)$, and thus $I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$ can only take the values 1 or 0. \citet{mandallaz2016} assumed that the effects on the estimates should be negligible as the number of occasions where $M_{G}(x) < M(x)$ was considered to be small in practical implementations. It was thus a further objective of this study to investigate the actual occurrences and effects of this phenomenon by comparing the estimates of \extpsynth{} to those of \psmall{}. % where the estimates stay unaffected

% ----------------------------- %
\subsection{Measures of estimation accuracy}

The estimation accuracies were quantified by the \textit{estimation error}, which is the ratio of the standard error and the point estimate:

\begin{equation}\label{eq:error}
error(\hat{Y})_{[\%]}=\frac{\sqrt{\var(\hat{Y})}}{\hat{Y}}*100
\end{equation}

We further calculated the 95\% confidence interval for each estimate for visualization purpose. The confidence intervals can also be used for hypothesis testing whether the point estimates of the three estimators for a given small area are statistically different. The confidence intervals under SRS can be obtained as:

\begin{equation}\label{ci_1phase}
CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
\hat{Y}+t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
\end{equation}

The confidence intervals for the \psmall{} and \extpsynth{} estimates are calculated as:

\begin{equation}\label{ci_2phase_sae}
CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
\hat{Y}+t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
\end{equation}

For the \psynth{} estimates, the confidence intervals are

\begin{equation}\label{ci_2phase_global}
CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
\hat{Y}+t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
\end{equation}

In order to address the potential benefits of the small area estimators compared with the SRS approach, we calculated the \textit{relative efficiency} (Eq. \ref{eq:releff}) which can be interpreted as the relative sample size under SRS needed to achieve the variance under the double sampling estimators.

\begin{equation}\label{eq:releff}
rel.eff_{[\%]}=\frac{\hat{\var}_{SRS}(\hat{Y})}{\hat{\var}_{SAE_{2phase}}(\hat{Y})}\cdot100
\end{equation}

\newpage

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\section{Case study}
\label{sec:CaseStudy}

%This section describes the actual implementation of the proposed small area estimators (Section \ref{sec:estimators}) under the cluster design of the German NFI (Section \ref{sec:germanNFI}) in the federal state Rhineland-Palatinate.

\subsection{Study area and small area units}
\label{sec:studyarea}

The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium. With 42.3\% (appr. 8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}. The forests of RLP are further characterized by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterized by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a. Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech. Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure. The forest area of RLP are divided into 3 ownership classes, i.e. state forest (27\%), communal forest (46\%) and privately owned forest (27\%). The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}. For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArea}). On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 426 Forstreviere (\textit{FR}). The next level are the actual forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5- to 10 year period in order to set up management strategies for the upcoming 10 years. The FAs and FRs constituted the small area (SA) units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}. The average area of the SA units were 43'777 ha on the FA-level, and 4624 ha on the FR level.

% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
%   FA                43'777 ha  (17367 - 125423)     46 (128)         11 (36)            64 (198)
%   FR                4624 ha   (0.68 - 43284)         5  (14)          0 (0)             13 (34)
%   stand level       6 ha     (0.03 ha - 73)          0 (0)            0 (0)             2 (4)

% Add Graphic 1:
% - Graphic of RLP with "zoom" in the 3 managament units (or later all together in Graphic

% Add in text:
% - add information on the (average) spatial area of each sae-level

% ----------------------------------------------------------------------- %
\subsection{Terrestrial sample}

Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI. In the last inventory (BWI3) conducted in the year 2013, timber volume information was derived for 2810 cluster (8092 plots) in the field survey. The local timber volume density on the plot and cluster level for this sample was consequently calculated according to Section \ref{sec:srs_estimator}. In the frame of this survey, the plot center coordinates have been re-measured with differential global satellite navigation system (DGPS) technique. Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrially observations and the information derived from the auxiliary information. A comparison of the DGPS coordinates with the so-far used target coordinates revealed that 90\% of all horizontal deviations lay in the range of 25 meters. A detailed analysis of horizontal DGPS errors in RLP by \citet{lambrecht2017} indicated that 80\% of the plots should not exceed horizontal DGPS errors of 8 meters. For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.

% NOTE:
% - add table with overview of terrestrial dta attributes (like Johannes)
%

% ----------------------------------------------------------------------- %
\subsection{Extension to double sampling design}

In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a 500x500 m sample grid that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}). The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ cluster by the terrestrially measured DGPS coordinates. For our study, we restricted the \textit{sampling frame} to the communal and state forest. The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service. The terrestrial sample size was thus reduced to 2055 cluster (5791 plots). Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.

\begin{figure}[H]
	\centering
	\resizebox{0.63\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
	\caption{\textit{Left}: Study Area with delineated FA forest management units. \textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit with overlayed the extended double sampling cluster design. \textit{Green}: Forest stand polygon layer defining the forest area of this study.}
	\label{fig:StudyArea}
\end{figure}

% NOTES:
%
% Add Table:
% provide table of "forest characteristics" in RLP
% adress sample sizes before and after extension (table?)
%
% move this to discussion:
% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$. This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer. For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$. The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e. by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par
%
%  "This extension led to a considerable increase of the sample size $n_{1,G}$ in the small area units of both, the FA and FR level."
% - Show (theoretical) increase in sample sizes by extension to 2phase scheme 
%   --> these sample sizes are in the following reduced by missing rs-info
%
% - Add Graphik showing RLP, zoom into 3 management levels including 2-phase sample
%   (big graphic, can take 1/2 page later)

% ----------------------------------------------------------------------- %
% Table xx provides an overview of the terrestrial sample sizes on these management levels for the state and communal forest areas.

% \input{terrSamplsizeFoaFuWa.tex}

% average no. plots / clusters; average area of all three units (divided by state + communal forest & entire forest area)

% --> this is only for communal & state forest area:
% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
%   FA                43'777 ha  (17367 - 125423)     46 (128)         11 (36)            64 (198)
%   FR                4624 ha   (0.68 - 43284)         5  (14)          0 (0)             13 (34)
%   stand level       6 ha     (0.03 ha - 73)          0 (0)            0 (0)             2 (4)

% - Verwaltungsebenen: management levels (Forstamt, Revier, Bestände) -> durschnittliche Flächengrössen (für die sollen die sae schätzungen gemacht werden)
% - evtl bereits Stichprobenzahlen generell und innerhalb der Managementenheiten nennen (das ginge dirket hinsichltich des eigentlichen Themas)
%   (das generelle Problem der Stichprobenanzahl in diesen Einheiten wurde ja schon in der Einleitung angesprochen, also könnte man
%    hier direkt ein Beispiel geben) --> hier noch getrennt nach gesamter Wald und nur Woefis-Wald (Tabelle, Grpahik)
% - warum RLP ? (neues Informationssystem, Interesse an effizienteren Methoden)
% wir nennen Fortamt einfach 'FA-level' und Forstrevier einfach 'FR-level' :-)
% Info: 45 Forstämter without Bundesforstamt; 426 Reviere without Bundesforstamt
% mention that the boundaries of all these management units are well-defined by polygon masks (that were used to extract the sampling
% frame)
% ----------------------------------------------------------------------- %

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Auxiliary information}
\label{sec:auxinfo}

% ----------------------------------------- %
\subsubsection{LiDAR canopy height model}
\label{sec:chm}

A prerequisite for the application of the suggested two-phase small area estimators was the identification of suitable auxiliary information that is available over the entire study area. Between the year 2003 and 2013, the topographic survey institution of RLP conducted an airborne laser scanning (LiDAR) acquisition over the entire federal state at leaf-off condition in order to derive a countrywide digital terrain and surface model. For this study, the recorded LiDAR data was used to create a canopy height model (CHM) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters (Figure \ref{fig:Auxvars}, \textit{top}). The CHM was calculated as the difference between the digital terrain model (DTM) and the digital surface model (DSM) that were derived by a Delauney interpolation of the two separated LiDAR point clouds (ground pulses and first pulses from non-ground objects). Based on numerous studies (e.g. \cite{maack2016}), the CHM was considered to provide the most valuable information to be used in the OLS regression model for predicting the timber volume on sample plot level. However, during the extended acquisition period, airborne laser scanning technology evolved significantly, which lead to severe quality variations in the CHM. In particular, the LiDAR acquisition recorded in 2002 and 2003 exhibited a rather poor quality with about only 1 point per 5x5 m$^2$, while more recently acquired datasets contained more than 125 points per 5x5 m$^2$ raster cell. Furthermore, due to sensor failures, CHM information was not available at 16 sample locations (none of them considered terrestrial sample plots of the $s_2$ phase though). These plots were deleted from the sampling frame and its non-available information thus treated as missing at random. This assumption was considered to be reasonable as the respective sample locations did not exclude specific forest structures.

%As explanatory variables, the mean canopy height (\textit{meanheight}) and the standard deviation ($stddev$) were calculated as the mean and standard deviation of all raster values within a predefined square around each sample plot center. The square (i.e. \textit{support} of the explanatory variable, see section \ref{sec:supp}) was previously intersected with the state and communal forest area defined by a polygon mask and thereby corrected for edge effects at the forest border. The tree height is one prominent predictor variable in the taper functions of the \bwi{} that are used to calculate a timber volume value for each sample tree \citep{kublin2003, kublin2013}. A visual inspection of the tree volumes of all sample trees collected in the \bwi{} within RLP against their tree heights also revealed the characteristic shape of an allometric relationship between these variables (Online Resource 1). It was hypothesized that this relationship on single-tree level is also apparent on the aggregated level of a sample plot and cluster, and can be used within the frame of regression modeling.\par
%
%The strength of correlation between \textit{meanheight} and timber volume on plot level was expected to show high variation according to the mentioned time-lag up to 10 years between LiDAR acquisition and terrestrial survey. The quality of the height information was also expected to vary according to changing sensor technologies and different point densities used over the years. For these reasons, the LiDAR acquisition year (\textit{lidaryear}) for each sample plot was considered as a potential categorical explanatory variable to explain the variation in the data introduced by these factors. For this purpose, the acquisition year \textit{2008} was further divided into \textit{2008} and \textit{2008\_1}. In the latter, the data quality turned out to be very poor due to sensor failures during the acquisition. Additionally, the years \textit{2006} and \textit{2007} as well as \textit{2012} and \textit{2013} were pooled in order to increase the number of observations per factor level for modelling reasons. As a result, the \textit{lidaryear} variable comprised nine categories (\textit{2002}, \textit{2003}, \textit{2007}, \textit{2008}, \textit{2008\_1}, \textit{2009}, \textit{2010}, \textit{2011} and \textit{2012}).

% ---------------------------------------------- %
\subsubsection{Tree species map}
\label{sec:tspecclass}

The second source of auxiliary information was a countrywide satellite-based classification map of the five main tree species (European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir, Scots pine) described in \citet{stoffels2015} (Figure \ref{fig:Auxvars}, \textit{bottom}). The classified tree species map has a grid size of 5 meters and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) by application of the spatially adaptive classification algorithm described in \citet{stoffels2012}.  As timber volume estimations on the tree level are often based on species-specific biomass and volume equations, the use of tree species information - especially for timber volume estimation - has often been stated as a key factor for improving the estimation precision \cite{white2016}. In this respect, incorporating the tree species map information was particularly attractive as it predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree. However, due to unavailable satellite data for the classification, the tree species map excluded one large patch with an area of 415 km$^2$ in the south-west part of RLP covering an entire FA-unit (10 FR units respectively). In 9 additional FR units, the tree species information was also missing for a subset of the sample locations due to two additional patches with an area of 76 km$^2$ and 100 km$^2$ in the northern part of RLP. For these parts, small area estimation was thus restricted to using only the available CHM information in the regression model. With respect to model fitting, the tree species information was missing for 407 (7\%) of the 5791 sample locations. A summary of the sample sizes and missing auxiliary information is again provided in Table \ref{tab:ssize}.

% Graphik:
\begin{figure}[H]
	\centering
	\resizebox{0.8\hsize}{!}{\includegraphics*{fig/AuxvarsLOWRES.png}}
	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information. Right: Magnified illustration of the rectangular supports used to derive the explanatory variables from the auxiliary information.}
	\label{fig:Auxvars}
\end{figure}

\begin{table}[H]
	\begin{center}
		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plots}$: number of plots. $n_{\{1,2\}}$: number of cluster}
		\vspace{0.2cm}
		\label{tab:ssize}
		{\small %
		\begin{tabular}{l|r|r|r|r}
			\hline
			\multicolumn{1}{c|}{\textit{Sampling frame}} & \multicolumn{1}{c|}{\textbf{$n_{1,plot}$}}  & \multicolumn{1}{c|}{\textbf{$n_1$}}  & \multicolumn{1}{c|}{\textbf{$n_{2,plot}$}}  & \multicolumn{1}{c}{\textbf{$n_2$}} \\ % <-- added & and content for each column
			\hline \hline
			communal and state forest & 96'854 & 33'365 & 5791 & 2055\\ % <--
			\hspace{5mm} \footnotesize missing CHM & \footnotesize 16 & \footnotesize 9 & \footnotesize 0 & \footnotesize 0\\ % <--
			\hspace{5mm} \footnotesize missing TSPEC & \footnotesize 6910  & \footnotesize 3465 & \footnotesize 407 & \footnotesize 380\\ % <--
			\hspace{5mm} \footnotesize missing CHM \textit{and} TSPEC & \footnotesize 2 & \footnotesize 1 & \footnotesize 0 & \footnotesize 0\\ % <--
			\hspace{5mm} \footnotesize missing CHM \textit{or} TSPEC & \footnotesize 6924 & \footnotesize 3473 & \footnotesize 407 & \footnotesize 380\\ % <--
			\hline \hline
		\end{tabular}
	} %
	\end{center}
\end{table}

%\begin{table}[H]
%	\begin{center}
%		\caption{Sample size for each phase in entire study area.}
%		\label{tab:ssize}
%		\begin{tabular}{l|r|r|r|r}
%			\hline
%			\textit{Sampling frame} & \textbf{$n_{1,plot}$} & \textbf{$n_1$} & \textbf{$n_{2,plot}$} & \textbf{$n_2$}\\ % <-- added & and content for each column
%			\hline \hline
%			communal and state forest & 96'854 & 33'365 & 5791 & 2055\\ % <--
%			\hspace{5mm} \small missing CHM & \small 16 & \small 9 & \small 0 & \small 0\\ % <--
%			\hspace{5mm} \small missing TSPEC & \small 6910  & \small 3465 & \small 407 & \small 380\\ % <--
%			\hspace{5mm} \small missing CHM \textit{and} TSPEC & \small 2 & \small 1 & \small 0 & \small 0\\ % <--
%			\hspace{5mm} \small missing CHM \textit{or} TSPEC & \small 6924 & \small 3473 & \small 407 & \small 380\\ % <--
%			\hline
%			Total for estimation & 89'930 & 29'892 & 5384 & 1675\\ % <--			
%		\end{tabular}
%	\end{center}
%\end{table}

% ---------------------------------------------- %
\subsection{Calculation of the auxiliary variables}
\label{sec:expvarcalc}

\subsubsection{LiDAR canopy height model}

From the CHM, the mean canopy height (\textit{meanheight}) and the standard deviation (\textit{stddev}) was calculated by evaluating the raster values around each sample location within a predefined rectangular square (support) with a side length of 12 meters that was centered around the sample plot centers. Each support was previously intersected with the forest polygon layer in order to evaluate auxiliary information only within the forest definition. The percentage of the non-intersected support within the forest layer was used as the weight $w(x_l)$ introduced in  Eq. \ref{eq:Zc(x)}. Furthermore, the year of the LiDAR acquisition (\textit{lidaryear}) was derived as an additional categorical variable to account for the time-lag between the CHM information and the terrestrial survey as well as to explain heterogeneity in the data introduced by the varying LiDAR quality. Adjustments were made to the original acquisition years by introducing an additional factor level \textit{2008\_1} for a subset of the 2008 acquisition where the quality turned out to be considerably poor due to a sensor error. In addition, the years 2006 and 2007 as well as 2012 and 2013 were pooled in order to increase the number of observations per factor level, resulting in nine categories in total (\textit{2002}, \textit{2003}, \textit{2007}, \textit{2008\_1}, \textit{2008}, \textit{2009}, \textit{2010}, \textit{2011} and \textit{2012}).

\subsubsection{Tree species map}

The tree species map information was used to predict the main tree species of a sample plot (\textit{treespecies}). This implied two consecutive processing steps. In the \textit{first} step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the same support as used for the CHM were classified as that species. Otherwise, the sample location was assigned the value 'mixed'. It should be mentioned that the support size and the percentage threshold are parameters that can be optimised in order to achieve the best variance decomposition and thus improvement in model accuracy when using the categorical \textit{treespecies} variable in a regression model. \citet{hill2017a} conducted a detailed analysis of how to optimally derive the auxiliary variables for the present data set and identified the above described settings as the most suitable. It was additionally shown that using the random forest algorithm by \citet{breiman2001} for a calibration of the predicted main plot species on the actual main taper-function species derived from the terrestrial inventory data could boost the classification accuracy in the classes \textit{Scots pine} and \textit{Douglas Fir}, which performed considerably worse than the remaining species (Table \ref{tab:classacc}). The calibration was able to considerably mitigate the effects of misclassification on the regression coefficients and thus allowed for an increase in model accuracy. In a \textit{second} step, we thus provided the random forest algorithm in the statistical software R \citep{R} with the actual main taper-function species derived from the terrestrial inventory data as response variable as well as a full set of $p$ predictor variables that comprised the initial prediction of the main plot tree species (\textit{treespecies}), the mean canopy height (\textit{meanheight}) and standard deviation ($stddev$) derived from the CHM, the proportion of coniferous trees estimated from the tree species classification map ($prop.conif$) and the bioclimatic growing region ($wgb$) at the sample location. The algorithm was grown with 2000 trees, considering $\sqrt{p} \approx$ 3 of the predictors for each split. The resulting random forest model was consequently applied at all sample locations $s_1$ to provide the \textit{treespecies} variable.

\begin{table}[H]
	\begin{center}
	\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
	\vspace{0.2cm}
	\label{tab:classacc}
 {\small %
	\begin{tabular}{c|c|c|c|c|c|c|c} %8cols
		\hlineB{1}
		\multirow{2}{*}{Main plot species} & \multicolumn{2}{c|}{Producer's accuracy[\%]} & \multicolumn{2}{c|}{User's accuracy[\%]} & \multirow{2}{*}{nref} & \multicolumn{2}{c}{nclass} \\ 
		\cline{2-3} \cline{4-5} \cline{7-8} & uncalib & calib & uncalib & calib & & uncalib & calib \\
		\hline \hline	
		 Beech       & 29.56 & 22.31 & 46.11 & 47.02 & 883 & 566 & 419 \\
		 Douglas Fir & 33.04 & 24.78 & 47.50 & 48.72 & 230 & 160 & 117 \\
		 Oak         & 47.75 & 11.07 & 24.34 & 48.48 & 289 & 567 & 66 \\
		 Spruce      & 43.63 & 53.15 & 60.81 & 61.13 & 651 & 467 & 566 \\
		 Scots Pine  & 55.87 & 22.91 & 29.59 & 46.07 & 179 & 338 & 89 \\
		 Mixed       & 66.40 & 84.49 & 63.69 & 64.53 & 3152 & 3286 & 4127 \\
		\hline
		 & \multicolumn{4}{l|}{Overall accuracy: 54.83\% (61.96\%)} & 5384 & \multicolumn{2}{c}{5384} \\
		 \hline \hline
	\end{tabular}
}%
	\end{center}
\end{table}

% ---------------------------------------------- %
\subsection{Regression Model}
\label{sec:regmod}

% NOTES:
% - model formulation was based on the following considerations: a) The mean canopy height has the heighest explanatory power. Since the strength of correlation between meanheight and the timber volume on plot level showed high variation according to the time-lag of up to 10 years between the LiDAR acquisition and the BWI3 terrestrial inventory. and the varying LiDAR quality, the 
%
%
%
%
%

% MENTION:
% - objective: find regression model (formula) to be applied in the sae estimators
% - Specialty here: in the sae estimators, the predictions are generated on the cluster level (thus the regression coefficients are found on the cluster level)
%   (--> and even more important: the residuals considered in the variance est. are also on the cluster level)
%  ==> so for model selection, we looked at the global model performance on the plot as well as the cluster level
%  ==> we also performed individual paramater t-test for each variable on the plot and cluster level. In order to  
%
% - important to recall that the design-based estimators, in which the regression model is used, do not impose any assumptions on the regression model as is the case in the model-dependent estimation framework.
%
% - no terrestrial data removed from the dataset for modelling, as all terrestrial data are used in the internal model (no choice, its specified by the estimators) 
%
% - mention sample sizes here: Due to missingness in the rs-data, the auxiliary variables were calculated for 89'930 sample plots (5384 terrestrial ...)
%
% - Model Validation (compare several models in table --> Alex)
%
% - Design-based Model Inference (new, use design-based var-covar-matrix)
%
% - idea: make a design-based inference of the regression coefficients on cluster level on the robust reg.coef-matrix
%   "whereas the regression analysis in hill et al. 2017a" was carried out on the sample plot level, we here extend
%    the analysis to the cluster level, as this is actually the level the estimators use the regression model predictions"
%

% ---------------------------------------------- %
\subsubsection{Design-Based Model Inference}
\label{sec:edbinf}

\newpage

% ======================================================================================================================== %
% NOTES:
% - Study Area **
%   o characteristics of forests, e.g. structural & species diversity
%   o introduce forest districts, show example and quickly mention their reasoning  
% 
% - The German NFI *
%   o cluster sampling, angle-cound sampling, CF-correction at the forest border
%     no. of plots (clusters) original according to BWI-survey
%   o plot locations by DGPS, and expected accuracy and pre-processing (plausibility analyses
%     and replacing by old coordinates if necessary)
%
% - Estimators **
%   o one-phase estimator: write down estimator in HT-style (evtl. Derivation of CF-correction in
%     Appendix)
%   o two-phase psmall cluster
%   o two-phase psynth extended cluster
%   o two-phase psynth cluster
%   (briefly explain:
%    o the estimator like in jss-article, pronounce difference between psmall
%      and psynthext in case of cluster sampling --> special case and research question:
%      how often does it occur and does it make a difference?
%    o explain difference between external and internal model --> this can be the reasoning for
%      using Daniels estimators for our objective: a) "db" --> we do not depent on the model which
%      is a huge advantage if we have medium-level quality data; b) "cluster" --> provided by Daniels
%      estimators in combination with c) "iternal" model building --> g-weight property and
%      considering dependency of regression coefs on the sample 
%
% - Extension of terrestrial sample grid **
%   o rules (?), new sample sizes globally and within saes
%
%
% - Auxililary information and variable derivation **
%   o document missing data at 1-phase grid (separate into s1 and s2) 
%   o maybe: "due to missing remote sensing information at some sample points, the original sample sizes (s2, s1) 
%             were shrinked down to the numbers shwn in table XX" (-> table showing the actual sample sizes)
%  
% - Model building **
%   o refer to calibration method in previous article
%   o refer to comprehensice model evaluations in previous article
%   o present final model
%
%
% 1) Preprocessing of terrestrial inventory data
% 2) Preprocessing of auxiliary information
% 3) Extention to 2-phase sample grid
% 4) Model building
%
%

### 2017-12-18 Draft_Form/tex/Materials_and_Methods.tex
Initial commit 18_12_2017
Initital commit

--- 2017-12-18 Draft_Form/tex/Materials_and_Methods(2).tex
@@
+\section{Methods}
+\label{sec:Meth}
+
 % ----------------------------------------------------------------------- %
@@
 
-\section{Terrestrial sampling design of the German NFI}
+\subsection{Terrestrial Sampling Design of the German NFI}
 \label{sec:germanNFI}
@@
 
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+\subsection{Estimators}
+\label{sec:estimators}
+
 % ++++++++++++ %
-\section{Double sampling in the infinite population approach}
+\subsubsection{Double Sampling in the Infinite Population Approach}
 \label{sec:inf_pop}
@@
 
-% ----------------------------------------------------------------------- %
-% ----------------------------------------------------------------------- %
-\section{Estimators}
-\label{sec:estimators}
-
 % ++++++++++++ %
-\subsection{Design-based SRS estimator for cluster sampling}
+\subsubsection{SRS Estimator for Cluster Sampling}
 \label{sec:srs_estimator}
 
-The simple random sampling (SRS) estimator for cluster sampling constitutes the \textit{status quo} that is currently applied under the existing one-phase sampling design of the German NFI in order to obtain a point and variance estimate for the mean timber volume of a given estimation unit.
-In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator that is applied in the BWI3 algorithms \citep{bwi3_ausw} in the form given in \citet{mandallaz2008, mandallaz2016}.\par
+The simple random sampling (SRS) estimator for cluster sampling was applied under the existing one-phase sampling design of the German NFI in order to obtain a point and variance estimate for the mean timber volume in each small area unit (Section \ref{sec:studyarea}).
+In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator in the form given in \citet{mandallaz2008, mandallaz2016}.
 In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M=4$ ) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$.
@@
 % +++++++++++++++++++++++++++++ %
-\subsection{Design-based small area regression estimators for cluster sampling}
+\subsubsection{Design-Based Small Area Regression Estimators for Cluster Sampling}
 \label{sec:SAestimators}
@@
 % PSMALL estimator:
-\subsubsection{Pseudo Small Area Estimator (\psmall{})}
-% \textbf{Pseudo Small Area Estimator (\psmall{})}\\
+\textbf{Pseudo Small Area Estimator (\psmall{})}\\
 
@@
 \ref{eq:psmall_var}.
-Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean in $G$ using a non-exhaustive sample $s_{1,G}$.
+Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean using the sample $s_{1,G}$.
 The third term is the variance of the model residuals and thus accounts for the inaccuracies of the model predictions.
@@
 % PSYNTH estimator:
-\subsubsection{Pseudo Synthetic Estimator (\psynth{})}
-% \textbf{Pseudo Synthetic Estimator (\psynth{})}\\
+\newpage
+\textbf{Pseudo Synthetic Estimator (\psynth{})}\\
 
@@
 % EXTPSYNTH estimator:
-\subsubsection{Extended Pseudo Synthetic Estimator (\extpsynth{})}
-% \textbf{Extended Pseudo Synthetic Estimator (\extpsynth{})}\\
+\textbf{Extended Pseudo Synthetic Estimator (\extpsynth{})}\\
 
@@
 \ref{eq:extpsynth}) has been proposed by \cite{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased.
-It has the advantage that the mean of the empirical model residuals of the OLS regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e.
+It has the advantage that the mean of the empirical model residuals of the regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e.
 $\bar{\hat{R}}_{c} = \bar{\hat{R}}_{c,G} = 0$.
@@
 
-% ----------------------------- %
-\subsection{Measures of estimation accuracy}
+\subsubsection{Measures of Estimation Accuracy}
 
@@
 % ----------------------------------------------------------------------- %
-\section{Case study}
-\label{sec:CaseStudy}
+\section{Materials}
+\label{sec:Mat}
 
@@
 
-\subsection{Study area and small area units}
+\subsection{Study Area and Small Area Units}
 \label{sec:studyarea}
 
-The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium.
+The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium (figure \ref{fig:Study Area}).
 With 42.3\% (appr.
@@
 The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}.
-For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArea}).
+For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (figure xx).
 On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 426 Forstreviere (\textit{FR}).
@@
 The FAs and FRs constituted the small area (SA) units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}.
-The average area of the SA units were 43'777 ha on the FA-level, and 4624 ha on the FR level.
+The average area of the SA units were 43'777 ha on the FA-level, and 4624 ha on the FR level.\\
 
@@
 % ----------------------------------------------------------------------- %
-\subsection{Terrestrial sample}
+% ----------------------------------------------------------------------- %
+\subsection{Extension to Double Sampling Design}
 
-Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI.
-In the last inventory (BWI3) conducted in the year 2013, timber volume information was derived for 2810 cluster (8092 plots) in the field survey.
+Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI, where timber volume information was derived for 2810 cluster (8092 plots) in the field survey of the latest inventory.
 The local timber volume density on the plot and cluster level for this sample was consequently calculated according to Section \ref{sec:srs_estimator}.
-In the frame of this survey, the plot center coordinates have been re-measured with differential global satellite navigation system (DGPS) technique.
+In the frame of the last inventory (BWI3), the plot center coordinates have been re-measured with differential global satellite navigation system (DGPS) technique.
 Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrially observations and the information derived from the auxiliary information.
@@
 A detailed analysis of horizontal DGPS errors in RLP by \citet{lambrecht2017} indicated that 80\% of the plots should not exceed horizontal DGPS errors of 8 meters.
-For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.
+For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.\par
 
-% NOTE:
-% - add table with overview of terrestrial dta attributes (like Johannes)
-%
-
-% ----------------------------------------------------------------------- %
-\subsection{Extension to double sampling design}
-
-In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a 500x500 m sample grid that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}).
+In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a 500x500 m sample grid that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure xx).
 The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ cluster by the terrestrially measured DGPS coordinates.
@@
 The terrestrial sample size was thus reduced to 2055 cluster (5791 plots).
-Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.
+Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.\par
 
@@
 	\centering
-	\resizebox{0.63\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
-	\caption{\textit{Left}: Study Area with delineated FA forest management units.
-\textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit with overlayed the extended double sampling cluster design.
-\textit{Green}: Forest stand polygon layer defining the forest area of this study.}
+	\resizebox{0.75\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
+	\caption{Forest management units in Rhineland-Palatinate, overlayed with the extended double sampling cluster design.}
 	\label{fig:StudyArea}
@@
 % ----------------------------------------------------------------------- %
-\subsection{Auxiliary information}
+\subsection{Auxiliary Information}
 \label{sec:auxinfo}
 
+% ! Mention Missingness in the data and resulting reduction of the sample size (s1, s2)
+
 % ----------------------------------------- %
-\subsubsection{LiDAR canopy height model}
+\subsubsection{LiDAR Canopy Height Model}
 \label{sec:chm}
 
-A prerequisite for the application of the suggested two-phase small area estimators was the identification of suitable auxiliary information that is available over the entire study area.
-Between the year 2003 and 2013, the topographic survey institution of RLP conducted an airborne laser scanning (LiDAR) acquisition over the entire federal state at leaf-off condition in order to derive a countrywide digital terrain and surface model.
-For this study, the recorded LiDAR data was used to create a canopy height model (CHM) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters (Figure \ref{fig:Auxvars}, \textit{top}).
+In order to derive a countrywide digital terrain and surface model, the topographic survey institution of RLP conducted an airborne laser scanning (LiDAR) acquisition over the entire federal state at leaf-off condition between the year 2003 and 2013.
+For this study, these data was used to create a canopy height model (\textit{CHM}) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters.
 The CHM was calculated as the difference between the digital terrain model (DTM) and the digital surface model (DSM) that were derived by a Delauney interpolation of the two separated LiDAR point clouds (ground pulses and first pulses from non-ground objects).
-Based on numerous studies (e.g.
-\cite{maack2016}), the CHM was considered to provide the most valuable information to be used in the OLS regression model for predicting the timber volume on sample plot level.
-However, during the extended acquisition period, airborne laser scanning technology evolved significantly, which lead to severe quality variations in the CHM.
-In particular, the LiDAR acquisition recorded in 2002 and 2003 exhibited a rather poor quality with about only 1 point per 5x5 m$^2$, while more recently acquired datasets contained more than 125 points per 5x5 m$^2$ raster cell.
-Furthermore, due to sensor failures, CHM information was not available at 16 sample locations (none of them considered terrestrial sample plots of the $s_2$ phase though).
-These plots were deleted from the sampling frame and its non-available information thus treated as missing at random.
-This assumption was considered to be reasonable as the respective sample locations did not exclude specific forest structures.
+During the extended acquisition period, airborne laser scanning technology and data quality evolved significantly, which lead to severe variations in the data quality.
+In particular, the LiDAR acquisition recorded in 2002 and 2003 exhibited a rather poor quality with about only 1 point per 5x5 m$^2$, while more recently acquired datasets of contain more than 125 points per 5x5 m$^2$ raster cell.
+Due to sensor failures, CHM information was not available at 16 $s_1$ (0 $s_2$) sample points.
 
@@
 % ---------------------------------------------- %
-\subsubsection{Tree species map}
+\subsubsection{Tree Species Classification Map}
 \label{sec:tspecclass}
 
-The second source of auxiliary information was a countrywide satellite-based classification map of the five main tree species (European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir, Scots pine) described in \citet{stoffels2015} (Figure \ref{fig:Auxvars}, \textit{bottom}).
-The classified tree species map has a grid size of 5 meters and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) by application of the spatially adaptive classification algorithm described in \citet{stoffels2012}.
-As timber volume estimations on the tree level are often based on species-specific biomass and volume equations, the use of tree species information - especially for timber volume estimation - has often been stated as a key factor for improving the estimation precision \cite{white2016}.
-In this respect, incorporating the tree species map information was particularly attractive as it predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree.
-However, due to unavailable satellite data for the classification, the tree species map excluded one large patch with an area of 415 km$^2$ in the south-west part of RLP covering an entire FA-unit (10 FR units respectively).
-In 9 additional FR units, the tree species information was also missing for a subset of the sample locations due to two additional patches with an area of 76 km$^2$ and 100 km$^2$ in the northern part of RLP.
-For these parts, small area estimation was thus restricted to using only the available CHM information in the regression model.
-With respect to model fitting, the tree species information was missing for 407 (7\%) of the 5791 sample locations.
-A summary of the sample sizes and missing auxiliary information is again provided in Table \ref{tab:ssize}.
+A countrywide satellite-based classification map of the five main tree species (European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir, Scots pine) described in \citet{stoffels2015} was used to derive tree species information on sample plot level.
+The classified tree species map has a grid size of 5 meters and predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree.
+Due to unavailable satellite data for the classification, the tree species map excluded one patch with an area of 415 km$^2$ in the south-west part of RLP, and two further patches with an area of 76 km$^2$ and 100 km$^2$ in the northern part \citep{stoffels2015}.
+The tree species information was consequently missing for 407 (7\%) of the 5791 sample locations.
 
-% Graphik:
-\begin{figure}[H]
-	\centering
-	\resizebox{0.8\hsize}{!}{\includegraphics*{fig/AuxvarsLOWRES.png}}
-	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information.
-Right: Magnified illustration of the rectangular supports used to derive the explanatory variables from the auxiliary information.}
-	\label{fig:Auxvars}
-\end{figure}
-
-\begin{table}[H]
-	\begin{center}
-		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plots}$: number of plots. $n_{\{1,2\}}$: number of cluster}
-		\vspace{0.2cm}
-		\label{tab:ssize}
-		{\small %
-		\begin{tabular}{l|r|r|r|r}
-			\hline
-			\multicolumn{1}{c|}{\textit{Sampling frame}} & \multicolumn{1}{c|}{\textbf{$n_{1,plot}$}}  & \multicolumn{1}{c|}{\textbf{$n_1$}}  & \multicolumn{1}{c|}{\textbf{$n_{2,plot}$}}  & \multicolumn{1}{c}{\textbf{$n_2$}} \\ % <-- added & and content for each column
-			\hline \hline
-			communal and state forest & 96'854 & 33'365 & 5791 & 2055\\ % <--
-			\hspace{5mm} \footnotesize missing CHM & \footnotesize 16 & \footnotesize 9 & \footnotesize 0 & \footnotesize 0\\ % <--
-			\hspace{5mm} \footnotesize missing TSPEC & \footnotesize 6910  & \footnotesize 3465 & \footnotesize 407 & \footnotesize 380\\ % <--
-			\hspace{5mm} \footnotesize missing CHM \textit{and} TSPEC & \footnotesize 2 & \footnotesize 1 & \footnotesize 0 & \footnotesize 0\\ % <--
-			\hspace{5mm} \footnotesize missing CHM \textit{or} TSPEC & \footnotesize 6924 & \footnotesize 3473 & \footnotesize 407 & \footnotesize 380\\ % <--
-			\hline \hline
-		\end{tabular}
-	} %
-	\end{center}
-\end{table}
-
-%\begin{table}[H]
-%	\begin{center}
-%		\caption{Sample size for each phase in entire study area.}
-%		\label{tab:ssize}
-%		\begin{tabular}{l|r|r|r|r}
-%			\hline
-%			\textit{Sampling frame} & \textbf{$n_{1,plot}$} & \textbf{$n_1$} & \textbf{$n_{2,plot}$} & \textbf{$n_2$}\\ % <-- added & and content for each column
-%			\hline \hline
-%			communal and state forest & 96'854 & 33'365 & 5791 & 2055\\ % <--
-%			\hspace{5mm} \small missing CHM & \small 16 & \small 9 & \small 0 & \small 0\\ % <--
-%			\hspace{5mm} \small missing TSPEC & \small 6910  & \small 3465 & \small 407 & \small 380\\ % <--
-%			\hspace{5mm} \small missing CHM \textit{and} TSPEC & \small 2 & \small 1 & \small 0 & \small 0\\ % <--
-%			\hspace{5mm} \small missing CHM \textit{or} TSPEC & \small 6924 & \small 3473 & \small 407 & \small 380\\ % <--
-%			\hline
-%			Total for estimation & 89'930 & 29'892 & 5384 & 1675\\ % <--			
-%		\end{tabular}
-%	\end{center}
-%\end{table}
-
-% ---------------------------------------------- %
-\subsection{Calculation of the auxiliary variables}
-\label{sec:expvarcalc}
-
-\subsubsection{LiDAR canopy height model}
-
-From the CHM, the mean canopy height (\textit{meanheight}) and the standard deviation (\textit{stddev}) was calculated by evaluating the raster values around each sample location within a predefined rectangular square (support) with a side length of 12 meters that was centered around the sample plot centers.
-Each support was previously intersected with the forest polygon layer in order to evaluate auxiliary information only within the forest definition.
-The percentage of the non-intersected support within the forest layer was used as the weight $w(x_l)$ introduced in  Eq.
-\ref{eq:Zc(x)}.
-Furthermore, the year of the LiDAR acquisition (\textit{lidaryear}) was derived as an additional categorical variable to account for the time-lag between the CHM information and the terrestrial survey as well as to explain heterogeneity in the data introduced by the varying LiDAR quality.
-Adjustments were made to the original acquisition years by introducing an additional factor level \textit{2008\_1} for a subset of the 2008 acquisition where the quality turned out to be considerably poor due to a sensor error.
-In addition, the years 2006 and 2007 as well as 2012 and 2013 were pooled in order to increase the number of observations per factor level, resulting in nine categories in total (\textit{2002}, \textit{2003}, \textit{2007}, \textit{2008\_1}, \textit{2008}, \textit{2009}, \textit{2010}, \textit{2011} and \textit{2012}).
-
-\subsubsection{Tree species map}
-
-The tree species map information was used to predict the main tree species of a sample plot (\textit{treespecies}).
-This implied two consecutive processing steps.
-In the \textit{first} step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the same support as used for the CHM were classified as that species.
-Otherwise, the sample location was assigned the value 'mixed'.
-It should be mentioned that the support size and the percentage threshold are parameters that can be optimised in order to achieve the best variance decomposition and thus improvement in model accuracy when using the categorical \textit{treespecies} variable in a regression model.
-\citet{hill2017a} conducted a detailed analysis of how to optimally derive the auxiliary variables for the present data set and identified the above described settings as the most suitable.
-It was additionally shown that using the random forest algorithm by \citet{breiman2001} for a calibration of the predicted main plot species on the actual main taper-function species derived from the terrestrial inventory data could boost the classification accuracy in the classes \textit{Scots pine} and \textit{Douglas Fir}, which performed considerably worse than the remaining species (Table \ref{tab:classacc}).
-The calibration was able to considerably mitigate the effects of misclassification on the regression coefficients and thus allowed for an increase in model accuracy.
-In a \textit{second} step, we thus provided the random forest algorithm in the statistical software R \citep{R} with the actual main taper-function species derived from the terrestrial inventory data as response variable as well as a full set of $p$ predictor variables that comprised the initial prediction of the main plot tree species (\textit{treespecies}), the mean canopy height (\textit{meanheight}) and standard deviation ($stddev$) derived from the CHM, the proportion of coniferous trees estimated from the tree species classification map ($prop.conif$) and the bioclimatic growing region ($wgb$) at the sample location.
-The algorithm was grown with 2000 trees, considering $\sqrt{p} \approx$ 3 of the predictors for each split.
-The resulting random forest model was consequently applied at all sample locations $s_1$ to provide the \textit{treespecies} variable.
-
-\begin{table}[H]
-	\begin{center}
-	\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
-	\vspace{0.2cm}
-	\label{tab:classacc}
- {\small %
-	\begin{tabular}{c|c|c|c|c|c|c|c} %8cols
-		\hlineB{1}
-		\multirow{2}{*}{Main plot species} & \multicolumn{2}{c|}{Producer's accuracy[\%]} & \multicolumn{2}{c|}{User's accuracy[\%]} & \multirow{2}{*}{nref} & \multicolumn{2}{c}{nclass} \\ 
-		\cline{2-3} \cline{4-5} \cline{7-8} & uncalib & calib & uncalib & calib & & uncalib & calib \\
-		\hline \hline	
-		 Beech       & 29.56 & 22.31 & 46.11 & 47.02 & 883 & 566 & 419 \\
-		 Douglas Fir & 33.04 & 24.78 & 47.50 & 48.72 & 230 & 160 & 117 \\
-		 Oak         & 47.75 & 11.07 & 24.34 & 48.48 & 289 & 567 & 66 \\
-		 Spruce      & 43.63 & 53.15 & 60.81 & 61.13 & 651 & 467 & 566 \\
-		 Scots Pine  & 55.87 & 22.91 & 29.59 & 46.07 & 179 & 338 & 89 \\
-		 Mixed       & 66.40 & 84.49 & 63.69 & 64.53 & 3152 & 3286 & 4127 \\
-		\hline
-		 & \multicolumn{4}{l|}{Overall accuracy: 54.83\% (61.96\%)} & 5384 & \multicolumn{2}{c}{5384} \\
-		 \hline \hline
-	\end{tabular}
-}%
-	\end{center}
-\end{table}
-
-% ---------------------------------------------- %
-\subsection{Regression Model}
-\label{sec:regmod}
-
-% NOTES:
-% - model formulation was based on the following considerations: a) The mean canopy height has the heighest explanatory power.
-Since the strength of correlation between meanheight and the timber volume on plot level showed high variation according to the time-lag of up to 10 years between the LiDAR acquisition and the BWI3 terrestrial inventory.
-and the varying LiDAR quality, the
+%
 %
@@
 
-% MENTION:
-% - objective: find regression model (formula) to be applied in the sae estimators
-% - Specialty here: in the sae estimators, the predictions are generated on the cluster level (thus the regression coefficients are found on the cluster level)
-%   (--> and even more important: the residuals considered in the variance est. are also on the cluster level)
-%  ==> so for model selection, we looked at the global model performance on the plot as well as the cluster level
-%  ==> we also performed individual paramater t-test for each variable on the plot and cluster level. In order to  
-%
-% - important to recall that the design-based estimators, in which the regression model is used, do not impose any assumptions on the regression model as is the case in the model-dependent estimation framework.
-%
-% - no terrestrial data removed from the dataset for modelling, as all terrestrial data are used in the internal model (no choice, its specified by the estimators) 
-%
-% - mention sample sizes here: Due to missingness in the rs-data, the auxiliary variables were calculated for 89'930 sample plots (5384 terrestrial ...)
-%
-% - Model Validation (compare several models in table --> Alex)
-%
-% - Design-based Model Inference (new, use design-based var-covar-matrix)
-%
-% - idea: make a design-based inference of the regression coefficients on cluster level on the robust reg.coef-matrix
-%   "whereas the regression analysis in hill et al. 2017a" was carried out on the sample plot level, we here extend
-%    the analysis to the cluster level, as this is actually the level the estimators use the regression model predictions"
-%
+% ---------------------------------------------- %
+\subsubsection{Calculation of Explanatory Variables}
+\label{sec:tspecclass}
 
-% ---------------------------------------------- %
-\subsubsection{Design-Based Model Inference}
-\label{sec:edbinf}
+% Graphik:
+
+%\begin{figure}[H]
+%	\centering
+%	\resizebox{0.8\hsize}{!}{\includegraphics*{fig/Auxvars.png}}
+%	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information.
+Right: Magnified illustration of the rectangular supports used to derive the explanatory variables from the auxiliary information.}
+%	\label{fig:Auxvars}
+%\end{figure}
+
+\newpage
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+\subsection{Regression Model}
+\label{sec:regmod}
 

### 2017-12-18 Draft_Form/tex/Notes_preprocessing.tex
Initial commit 18_12_2017
Initital commit

%% Preprocessing:

% -------------------------------------------- %
% BWI Daten:
% -------------------------------------------- %

------------------------------------------------------------------------
------ 1) Auswahl der wzp4-Plots: ------

 --> an 8092 Plots (2810 Cluster) in RLP wurde die wzp4 durchgeführt.
 Es wurden Plots ausgewählt welche:
# 1) - zur BWI3 gehoeren --> inve3 = 1 & 
# 2) -  auf bestocktem Holzboden liegen --> wa = 5 & 
# 3) - im begehbaren Wald liegen --> begehbar = 1 &
# ---> 8092 Plots

------------------------------------------------------------------------
------ 2) Auswahl der wzp4-Bäume pro Plot: ------

Für diese 8092 Plots wurden jene Probebäume ausgewählt, welche
# 4) - in der wzp4 aufgenommen wurden (wzp4-Baeume) --> av = 0
# 5) - ! alle "bestandesinternen Bäume"* (bz = 1) !

--> 56149 wzp4-Bäume in RLP aufgenommen (bestandesinterne Bäume), verteilt auf 8092 Plots
    (Info: weicht von  # Bäumen in Modellierungspaper ab --> hier habe ich wohl best.übergreifend ausgewertet --> 56561)

------------------------------------------------------------------------
------ 3) Berechnung der Vorratsdichte pro Plot: ------
-> Nach Winkelzählprobe (Formel geben?) Waldrand (Bestandes)-Edge-Korrektur erwähnen
-> von den 8092 Plots sind 317 sog. "zero-plots" für welche das Plotvolumen 0 ist

------------------------------------------------------------------------
------ 4) Lagekoordinaten für Plots: ------

Erwähnen weil:
-> wichtig für Vergleichbarkeit von expl. Variablen und Plotvorratsdichte
-> erwähnen: nicht wichtig für einphasige Auswertung, aber wichtig bei Erweiterung

Aufn.methode und fehlende Messungen:
-> Im Rahmen der 3. BWI (? korrekt) alle Plots in RLP mit DGPS vermessen (Median über 100 Messungen).
-> für 375 der 8092 Plots (ca. 5\%) waren die GPS Messungen leider nicht berfügbar und werden in den
   Folgeinventuren neu vermessen. Für unsere Auswertungen wurden für diese Plots die "alten" Soll-Koordinaten" übernommen

Abweichungen zwischen alten Soll-Positionen und neuen GPS-Positionen:
-> ein Vergleich der alten Soll-Koordinaten und der DGPS IST-Koordinaten ergibt, dass
   eine Abweichung von maximal 25m für 90\% der Plots (das sagt aber noch nichts über
   die Genauigkeit der DGPS-Koordinaten aus).

Genauigkeit der DGPS-Messung:  
-> schwierig abzuschätzen
->  90\% der DGPS vermessenen Plots haben einen "Idealen" oder "Exzellenten" HDOP-Wert (HDOP aufgezeichnet
    bei Messung, aber keine Metadaten zur Lagegenauigkeit in [m])
-> Lambrecht et. al schätzen aufgrund ihrer Koregistrierung im Nationalpark HHW, dass 80\% der DGPS-Messungen 
   eine Abweichung zwischen 1.4 und 8.7 m haben
-> eigene Analyse für ganz RLP ergibt, dass die Abweichungen zwischen Soll- und IST-Koordinaten unabhängig von
   vom HDOP und der Anzahl Messungen ist

Plausibilitätsprüfung(en):
1) Fehlerhafte Datenablage: für 2 Plots ändert sich fälschlicherweise die Trakt-ID
2) Trakstruktur: für 4 Plots ist die Traktstruktur nicht stimmig --> siehe Slides
 --> 6 unplausible Plots wenn man DGPS-Messung vertraut --> diese wurden durch die alten Soll-Koordinaten ersetzt

==> insgesamt wurden also für 375 + 6 = 381 der 8092 Plots die alten Soll-Koordinaten verwendet (4.7\%)

% ------------------------------------------------ %
% Erweiterung des terrestrischen Stichprobennetzes:
% ------------------------------------------------ %

Das terrestrische Stichprobennetz (2x2km) wurde auf 500x500 meter (4-fach) verdichtet

Regeln:
1) Alle Punkte müssen innerhalb der obersten definierten Management-Fläche (Forstämter) liegen
2) Der Wald-Nichtwald-Entscheid muss bei Anwendung des mehrphasigen Verfahrens sowohl auf die terrestrischen als auch
   die "synthetischen" Inventurpunkte (sprich: ALLE Punkte) angewendet werden können. Daher werden alle Punkte anhand der
   Geodatenlayer (Woefis, Atkis) maskiert. --> führt zu variabler Anzahl Plots pro Trakt (entspricht Theorie)

Restriktion auf Wald-Layer:

aufgetretene Effekte:
 -> 2 terrestrische Plots ("63718_3", "60767_4") liegen ausserhalb der foa-geometry --> Datensatz von 8092 auf 8090 reduziert
 -> es liegen zusätzlich 179 terrestrische Proben ausserhalb der beachteten Gesamtwalddefinition union(Atkis, woefis)-Waldlayers 
    (179 / 8092 = 2\%)
 -> für unsere Woefis"wald"-Auswertung: 5791 terrestrische Plots (2055 Cluster) fallen in den Woefis-Wald (5791/8090 = 71.5\%, entspricht ziemlich gut des von der BWI angegebenen Anteils an Gemeinde- und Staatswald:73\%)

 -> Stichpobenzahl insgesamt für woefis-wald: 96854 plots (33365 Cluster)

% -------------------------------------------- %
% Aufbereitung der Fernerkundungsdaten
% -------------------------------------------- %

--> folgt Beschrieb im Modellierungsartikel

--> missing data erwähnen

--> Erwähnen: Im Gegensatz zur Modellierungs-Studie, in der wir die 'zero-plots' wegggelassen haben, schliessen wir diese hier ein 
     (Grund: bei Berechnung der Punktschätzungen in der angewendeten Software (Verweis) wird die 'zero-mean-property' (zmp) der Residuen 
             in F und G vorrausgesetzt (dadurch entfällt der Residuenterm). Die zmp wäre ist hier dann aber nur gewährleistet, wenn wir das Modell
             mit ALLEN terrestrischen Daten fitten, welche später auch in die Schätzungen eingehen)
      das Weglassen der zero-plots in der Schätzung kommt aber natürlich nicht in Frage! Also ist das Vorgehen hier die einzige Möglichkeit

    ==> es ergibt sich durch Einbeziehung der zero-plots ein ganz leicht anderes adjusted R2 (0.49 anstatt 0.48), lustigerweise sogar etwas höher als vorher.
        Erwähnen, dass die Aussagen aus dem Modellierungspaper davon nicht betroffen sind.

% -------------------------------------------- %
% Reg.Modell und Ableitung Hilfsvariablen
% -------------------------------------------- %

Berechnungszeiten für Woefis-Wald: (96854 plots)
-> Berechnung Supports: Berechnungszeit für woefis-wald: 67 Minuten
-> Berechnung CHM-Metriken: 1 Minute
-> Berechnung TREESPECIES-Metriken: 6 Minute
-> Berechnung FRACCOVER-Metriken: 4 Minuten
-> Berechnung wgbz-Metriken: 610.96 Minuten

### 2017-12-18 Draft_Form/tex/Results.tex
Initial commit 18_12_2017
Initital commit

--- 2017-12-18 Draft_Form/tex/Materials_and_Methods.tex
@@
-\section{Methods}
-\label{sec:Meth}
+\section{Results} %techreport
+\label{sec:Res}
 
@@
 % ----------------------------------------------------------------------- %
-
-\subsection{Terrestrial Sampling Design of the German NFI}
-\label{sec:germanNFI}
-
-The German National Forest Inventory (German NFI) is a periodic inventory that is carried out every 10 years over the entire forest area of Germany.
-The most recent inventory (BWI3) was conducted in the years 2011 and 2012.
-While information was originally gathered at a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid.
-The German NFI uses a cluster sampling design, which means that a sample unit consists of maximal four sample locations (also referred to as \textit{sample plots}) that are arranged in a square (so called \textit{cluster}) with a side length of 150 metres (Picture).
-The number of plots per cluster can however vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}.
-In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the tree-individual inclusion circle \citep{bwi3_aufn}.
-A further inventory threshold for a tree to be recorded is a diameter at breast height ($dbh$) of at least 7 cm.
-For each sample tree that is selected by this procedure, the dbh, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to calculate a volume estimation on the tree level.
-These volume estimations are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.
-
-% ----------------------------------------------------------------------- %
-% ----------------------------------------------------------------------- %
-\subsection{Estimators}
-\label{sec:estimators}
-
-% ++++++++++++ %
-\subsubsection{Double Sampling in the Infinite Population Approach}
-\label{sec:inf_pop}
-
-% \subsubsection{One- and Two-Phase Sampling in the Infinite Population Approach}
-
-The estimators used in this study have been proposed by \citep{mandallaz2013a,mandallaz2013b} and build upon the so called infinite population approach (IPA) in order to bridge the inventory procedure and the derived information to the mathematics behind the estimators.
-Therefore, we shall first provide a short introduction into this general estimation frame.
-We start by assuming that the population $P$ of trees $i \in 1,2, ..., N$ within a forest of interest $F$ is exactly defined, and each tree $i$ has a directly or indirectly observable response variable $Y_i$ (e.g.
-its timber volume) that allows to specify the population mean $Y$ (e.g., the average timber volume per unit area) over $F$.
-If a full census of all tree population individuals is not possible, $Y$ has to be estimated by the conduction of an inventory.
-The infinite population approach assumes that the spatial distribution of the local density $Y(x)$ (e.g., the timber volume per unit area) at each point or location $x$ in the forest $F$ is given by a fixed (i.e.
-non stochastic) piecewise constant function.
-The population mean $Y$ is thus mathematically equivalent to the integral of the density function surface divided by the forest area $\lambda(F)$, i.e.
-$Y=\frac{1}{\lambda(F)} \sum_{i=1}^{N}Y_i=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$, and thus the population mean $Y$ corresponds to a spatial mean.
-Since the local density function is in practice always unknown, one estimates $Y$ by collecting a sample $s_2$ of all local density values by the conduction of a terrestrial inventory at $n_2$ uniformly and independently distributed sample points over $F$.
-This procedure is often referred to as \textit{one-phase sampling} (OPS).
-Opposed to the one-phase approach, \textit{two-phase} or \textit{double-sampling} procedures use information from two nested samples (phases).
-Practically speaking, the terrestrial inventory $s_2$ is embedded in a large phase $s_1$ comprising $n_1$ sample locations that each provide a set of explanatory variables described by the column vector $\pmb{Z}(x)=(z(x)_1, z(x)_2,...,z(x)_p)^{\top}$ at each point $x \in s_1$.
-These explanatory variables are derived from auxiliary information that is available in high quantity within the forest $F$.
-For every $x \in s_1$, $\pmb{Z}(x)$ is transformed into a prediction $\hat{Y}(x)$ of $Y(x)$ using the choice of some prediction model.
-The basic idea of this method is to boost the sample size by providing a large sample of less precise but cheaper predictions of $Y(x)$ in $s_1$ and to correct any possible model bias, i.e., $\EX{(Y(x)-\hat{Y}(x))}$, using the subsample of terrestrial inventory units where the value of $Y(x)$ is observed.
-
-% which in \pkg{forestinventory} is always a linear model fit in $s_2$ using ordinary least squares (OLS).
-%The one-phase and two-phase estimators applied in this study have been implemented in the software-package \textit{forestinventory} \cite{forestinventory} 
-% The local density $Y(x)$ is in practice derived by ...
-% extend the approach to collecting auxiliary information ...
-% say that we also assume that the forest area is well-defined ...
-
-% ++++++++++++ %
-\subsubsection{SRS Estimator for Cluster Sampling}
-\label{sec:srs_estimator}
-
-The simple random sampling (SRS) estimator for cluster sampling was applied under the existing one-phase sampling design of the German NFI in order to obtain a point and variance estimate for the mean timber volume in each small area unit (Section \ref{sec:studyarea}).
-In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator in the form given in \citet{mandallaz2008, mandallaz2016}.
-In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M=4$ ) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$.
-The actual number of plots per cluster, $M(x)$, is a random variable due to the uniform distribution of $x_l$ ($l=1, ..., M$) in the forest $F$ and forest/non-forest decision for each sample location $x_l$:
-
-\begin{equation}\label{eq:Mx}
-M(x)=\sum_{l=1}^{M}I_{F}(x_l) \hspace{3ex} \text{where} \hspace{3ex} I_F(x_l)=\begin{cases}&1 \text{ if $x_l \in F$}\\
-&0 \text{ if $x_l\not\in F$}
-\end{cases}
-\end{equation}
-
-The local density on cluster level $Y_{c}(x)$, in our case the timber volume per hectare, is then defined as the average of the individual sample plot densities $Y(x_l)$:
-
-\begin{equation}\label{eq:locdens_clust}
-Y_{c}(x) = \frac{\sum_{l=1}^{M} I_{F}(x_{l}) Y(x_l)}{M(x)}
-\end{equation}
-
-The local density $Y(x_l)$ on individual sample plot level was calculated according to the description in \citet{mandallaz2008}, which can be rewritten for angle-count sampling technique applied in the BWI3.
-The general form of $Y(x)$ in \citet{mandallaz2008} is given as the Horwitz-Thompson estimator
-
-%\begin{equation}\label{locdens_plot}
-%Y(x)= \sum_{i=1}^{F}\frac{I_{i}(x)Y_i}{\varPi_{i}\lambda(F)} = \sum_{i \in s_{2}(x)}\frac{Y_i}{\varPi_{i}\lambda(F)}
-%\end{equation}
-
-\begin{equation}\label{eq:locdens_plot}
-Y(x_l)=\sum_{i \in s_{2}(x_l)}\frac{Y_i}{\pi_{i}\lambda(F)}
-\end{equation}
-
-where $Y_i$ is in our case the predicted timber volume of the tree $i$ recorded at sample location $x$ in m$^3$.
-Each tree has an inclusion probability $\pi_{i}$ that is well defined as the proportion of its inclusion circle area $\lambda(K_i)$ within the forest area $\lambda(F)$, i.e.
-via their geometric intersection:
-
-%with the binary indicator variable $Ii$ for the $i$th tree defined as
-%
-%\begin{equation}\label{1stage}
-%I_i(x)=\begin{cases}&1 \text{ if $x \in K_i$}\\
-%&0 \text{ if $x\not\in K_i$}
-%\end{cases}
-%\end{equation}
-
-\begin{equation}\label{locdens_plot_1}
-\pi_{i} = \frac{\lambda(K_i \cap F)}{\lambda(F)}
-\end{equation}
-
-The radius $R_i$ of the tree-individual inclusion circle $K_i$ is given by $R_i = bhd_{i}/cf_{i,corr}$ (also referred to as \textit{limiting distance}), where $cf_{i,corr}$ is the counting factor corrected for potential boundary effects at the forest border.
-In case of angle-count sampling, we can rewrite $\pi_{i}$ as
-
-\begin{equation}\label{eq:locdens_plot_2}
-\pi_{i} = \frac{G_i}{cf_{i,corr}\lambda(F)}
-	\end{equation}
-
-since the intersection area $\lambda(K_i \cap F)/\lambda(F)$ can be expressed using the trees basal area $G_i$ (in m$^2$) and the corrected counting factor:
-
-\begin{equation}\label{eq:locdens_plot_3}
-\lambda(K_i \cap F) = \frac{G_i}{cf_{i, corr}} \hspace{3ex} \text{where} \hspace{3ex} cf_{i,corr} = cf\frac{\lambda(K_i)}{\lambda(K_i \cap F)}
-\end{equation}
-
-Using Eq.
-\ref{eq:locdens_plot_2} in Eq.
-\ref{eq:locdens_plot} yields the rewritten form of $Y(x_l)$ for angle count sampling that conforms to the definition used in the BWI3 algorithms \citep{bwi3_ausw}:
-
-\begin{equation}\label{eq:locdens_plot_4}
-Y(x_l)= \sum_{i \in s_{2}(x_l)} \frac{cf_{i, corr}Y_i}{G_i} = \sum_{i \in s_{2}(x_l)} nha_{i}{Y_i}
-\end{equation}
-
-where $nha_i$ is the number of trees per hectare represented by tree $i$.
-The local densities on cluster level can then be used to derive the estimated spatial mean $\hat{Y}_c$ and its estimated variance $\hat{\var}(\hat{Y}_c)$ for any given spatial unit for which $n_2 \geq 2$ ($n_2$ denoting the number of sample units, i.e.
-clusters):
-
-\begin{subequations}\label{eq:srs_est_cluster}
-	\begin{align}
-\hat{Y}_c &= \frac{\sum_{x \in s_2} M(x) Y_{c}(x)}{\sum_{x \in s_2} M(x)} \\
-\hat{\var}(\hat{Y}_c) &= \frac{1}{n_2(n_2 - 1)}\sum_{x \in s_2}\Big(\frac{M(x)}{\bar{M_2}}\Big)^2(Y_{c}(x) - \hat{Y}_c)^2
-	\end{align}
-\end{subequations}
-
-\newpage
-
-% +++++++++++++++++++++++++++++ %
-\subsubsection{Design-Based Small Area Regression Estimators for Cluster Sampling}
-\label{sec:SAestimators}
-
-All three considered small area estimators have in common that they use ordinary least square (OLS) regression models to produce the predictions of the local density $Y_{c}(x)$ directly on the cluster level $c$.
-We consider the \textit{internal model approach}, where the vector of estimated regression coefficients on the cluster level is found by "borrowing strength" from the entire terrestrial sample $s_2$ of the current inventory:
-
-\begin{subequations}\label{normequ_simple_cluster}
-	\begin{align}
-\hat{\pmb{\beta}}_{c,s_2} &= \pmb{A}_{c,s_2}^{-1} \Big(\frac{1}{n_2}\sum_{x\in{s_2}}M(x)Y_{c}(x)\pmb{Z}_{c}(x)\Big) \\
-\pmb{A}_{c,s_2} &=\frac{1}{n_2}\sum_{x\in{s_2}}M(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)
-	\end{align}
-\end{subequations}
-
-\noindent $\pmb{Z}_{c}(x)$ is the vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Eq.\ref{eq:Zc(x)}).
-The weight $w(x_l)$ is the proportion of the support-area within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.
-
-\begin{equation}\label{eq:Zc(x)}
-\pmb{Z}_{c}(x)=\frac{\sum_{l=1}^{M}I_{F}(x_l)w(x_l)\pmb{Z}(x_l)}{\sum_{l=1}^{M}I_{F}(x_l)w(x_l)}
-\end{equation}
-
-\noindent The estimated design-based variance-covariance matrix $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}$ accounts for the fact that the regression model is internal by reflecting the dependency of the estimated regression coefficients on the realized sample $s_2$.
-It is defined as
-
-\begin{equation}\label{eq:varcovarbeta}
-\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}=\pmb{A}_{c,s_2}^{-1}
-\Big(\frac{1}{n_2^2}\sum_{x\in{s_2}}M^{2}(x)\hat{R}_{c}^2(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)\Big)
-\pmb{A}_{c,s_2}^{-1}
-\end{equation}
-
-\noindent with $\hat{R}_{c}=Y_{c}(x)-\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2}$ being the empirical model residuals at the cluster level, which by construction of OLS satisfy the important \textit{zero mean residual property}, i.e.
-$\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$.\\
-
- In the following, we will give a short description of each small area estimator and refer to \citet{mandallaz2013a, mandallaz2016, mandallaz2013b} if the reader requires additional details or proofs.
-The estimators have also been implemented in the R-package \textit{forestinventory} \citep{forestinventory} which was used to compute all estimates in this study.\\
-
-% ----------------------------- %
-% PSMALL estimator:
-\textbf{Pseudo Small Area Estimator (\psmall{})}\\
-
-All point information used for small area estimation is now restricted to that available at the sample locations $s_{1,G}$ or $s_{2,G}$ in the small area $G$, with exception of $\hat{\pmb{\beta}}_{c,s_2}$ and $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}$ which are always based on the entire sample $s_2$.
-We thus first define the following quantities on the small area level:
-
-\begin{subequations}\label{eq:compsG}
-	\begin{align}
-	\hat{\bar{\pmb{Z}}}_{c,G} &= \frac{\sum_{x \in s_{1,G}} M_{G}(x) \pmb{Z}_{c,G}(x)}{\sum_{x \in s_{1,G}} M_{G}(x)} \label{eq:meanZcG} \hspace{3ex} &\text{where} \hspace{3ex}
-	\pmb{Z}_{c,G}(x) =  \frac{\sum_{l=1}^{L} I_{G}(x_l)\pmb{Z}(x_l)}{M_{G}(x)}\\		
-	Y_{c,G}(x) &= \frac{\sum_{l=1}^{L} I_{G}(x_l)\pmb{Y}(x_l)}{M_{G}(x)}  &\text{and} \hspace{3ex}
-	\hat{Y}_{c,G}(x)=\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2}\\
-	\bar{\hat{R}}_{2,G} &= \frac{\sum_{x \in s_{2,G}} M_{G}(x) \hat{R}_{c,G}(x)}{\sum_{x \in s_{2,G}} M_{G}(x)} \hspace{3ex} &\text{where} \hspace{3ex}
-	\hat{R}_{c,G}(x) = Y_{c,G}(x)-\hat{Y}_{c,G}(x)
-	\end{align}
-\end{subequations}
-
-Note that the restriction to $G$, i.e.
-$I_{G}(x_l)=\{0,1\}$, is made on the individual sample plot level $x_l$, and $M_{G}(x) = \sum_{l=1}^{L}I_{G}(x_l)$ thus is the number of sample plots per cluster within the small area.
-The asymptotically design-unbiased point estimate of \textit{PSMALL} is then defined according to Eq.
-\ref{eq:psmall_pest}.
-The first term estimates the small area population mean of $G$ by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$.
-The second term then corrects for a potential bias of the regression model predictions in the small area $G$ by adding the mean of the empirical residuals $\bar{\hat{R}}_{2,G}$ in $G$.
-This correction insures that the \textit{zero mean residual property} in $F$ also holds within the small area $G$, which is per se not ensured by fitting the regression coefficients with data outside $G$.
-
-\begin{subequations}\label{eq:psmall}
-	\begin{align}
-	\hat{Y}_{c,G,PSMALL} &= \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} + \bar{\hat{R}}_{2,G} \label{eq:psmall_pest} \\
-	\hat{\var}(\hat{Y}_{c,G,PSMALL}) & = \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}\hat{\bar{\pmb{Z}}}_{c,G}
-	+ \hat{\pmb{\beta}}_{c,s_2}^{\top}\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}\hat{\pmb{\beta}}_{c,s_2} \nonumber \\
-	& + \frac{1}{n_{2,G}(n_{2,G}-1)}\sum_{x \in s_{2,G}}\Big(\frac{M_{G}(x)}{\bar{M}_{2,G}}\Big)^2(\hat{R}_{c,G}(x) - \bar{\hat{R}}_{2,G})^2
-	\label{eq:psmall_var}
-	\end{align}
-\end{subequations}
-
-The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Eq.
-\ref{eq:psmall_var}.
-Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean using the sample $s_{1,G}$.
-The third term is the variance of the model residuals and thus accounts for the inaccuracies of the model predictions.
-Note that the first term can also be rewritten using g-weights \cite[pg.14]{mandallaz2016} which ensure calibration properties of the auxiliary variables on the terrestrial sample.\\
-
-The variance-covariance matrix of the auxiliary vector $\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}$ is thereby defined as
-
-\begin{equation}\label{estvarcovaux_G}
-\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}} = \frac{1}{n_{1,G}(n_{1,G}-1)} \sum_{i \in s_{1,G}} \big(\frac{M_{G}(x)}{\bar{M}_{1,G}}\big)^2 (\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})(\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})^{\top}
-\end{equation}
-
-with $\bar{M}_{1,G}=\frac{\sum_{i \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.\\
-
-% ----------------------------- %
-% PSYNTH estimator:
-\newpage
-\textbf{Pseudo Synthetic Estimator (\psynth{})}\\
-
-The \psynth{} estimator is commonly applied when no terrestrial sample is available within the small area $G$ (i.e.
-$n_{2,G}=0$).
-The point estimate (Eq.
-\ref{eq:psynth_pest}) is thus only based on the predictions generated by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$.
-Note that the bias correction term using the empirical residuals (Eq.
-\ref{eq:psmall_pest}) can no longer be applied.
-The \psynth{} estimator thus has a potential unobservable design-based bias.
-
-\begin{subequations}\label{eq:psynth}
-	\begin{align}
-	\hat{Y}_{c,G,PSYNTH} & =\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} \label{eq:psynth_pest} \\
-	\hat{\var}(\hat{Y}_{c,G,PSYNTH})& =
-	\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}
-	\hat{\bar{\pmb{Z}}}_{c,G}
-	+ \hat{\pmb{\beta}}^{\top}_{c,s_2}\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}\hat{\pmb{\beta}}_{c,s_2} \label{eq:psynth_var}
-	\end{align}
-\end{subequations}
-
-The uncertainty of the model predictions can also no longer be considered in the variance estimation (Eq.
-\ref{eq:psynth_var}).
-The synthetic estimator will therefore usually have a smaller variance than estimators incorporating the model uncertainties, but at the cost of a potential bias.
-Note that the \psynth{} estimator is still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.\\
-
-% ----------------------------- %
-% EXTPSYNTH estimator:
-\textbf{Extended Pseudo Synthetic Estimator (\extpsynth{})}\\
-
-The \extpsynth{} estimator (Eq.
-\ref{eq:extpsynth}) has been proposed by \cite{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased.
-It has the advantage that the mean of the empirical model residuals of the regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e.
-$\bar{\hat{R}}_{c} = \bar{\hat{R}}_{c,G} = 0$.
-This is realized by \textit{extending} the auxiliary vector $\pmb{Z}_{c}(x)$ by the indicator variable $I_{c,G}$ which takes the value 1 if the entire cluster lies within the small area $G$ and 0 if the entire cluster is outside $G$, i.e.
-$I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$.
-The extended auxiliary vector thus becomes $\pmb{\mathbb{Z}}_{c}^{\top}(x)= (\pmb{Z}_{c}^{\top}(x),I_{c,G}(x))$ and the new regression coefficient using $\pmb{\mathbb{Z}}_{c}(x)$ instead of $\pmb{Z}_{c}(x)$ in Eq.
-\ref{normequ_simple_cluster} is denoted as $\hat{\pmb{\theta}}_{s_2}$.
-All remaining components are calculated by plugging in $\pmb{\mathbb{Z}}_{c}(x)$ in Eq.
-\ref{eq:compsG}.
-A decomposition of $\hat{\pmb{\theta}}_{s_2}$ reveals that the residual correction term is now included in the regression coefficient $\hat{\pmb{\theta}}_{s_2}$.
-
-\begin{subequations}\label{eq:extpsynth}
-	\begin{align}
-	\hat{Y}_{c,G,EXTPSYNTH} & =\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}^{\top}\hat{\pmb{\theta}}_{c,s_2} \label{eq:extpsynth_pest} \\
-	\hat{\var}(\hat{Y}_{c,G,EXTPSYNTH})& =
-	\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\theta}}_{c,s_2}}
-	\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}
-	+ \hat{\pmb{\theta}}^{\top}_{c,s_2}\hat{\pmb{\Sigma}}_{\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}}\hat{\pmb{\theta}}_{c,s_2} \label{eq:extpsynth_var}
-	\end{align}
-\end{subequations}
-
-However, it is important to note that $\bar{\hat{R}}_{c,G} = 0$ under the extended regression model only holds if the sample plots $x_1, ..., x_l$ of a cluster are \textit{all} either inside our outside the small area, i.e.
-$M_G(x)\equiv M(x)$, and thus $I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$ can only take the values 1 or 0.
-\citet{mandallaz2016} assumed that the effects on the estimates should be negligible as the number of occasions where $M_{G}(x) < M(x)$ was considered to be small in practical implementations.
-It was thus a further objective of this study to investigate the actual occurrences and effects of this phenomenon by comparing the estimates of \extpsynth{} to those of \psmall{}.
-% where the estimates stay unaffected
-
-\subsubsection{Measures of Estimation Accuracy}
-
-The estimation accuracies were quantified by the \textit{estimation error}, which is the ratio of the standard error and the point estimate:
-
-\begin{equation}\label{eq:error}
-error(\hat{Y})_{[\%]}=\frac{\sqrt{\var(\hat{Y})}}{\hat{Y}}*100
-\end{equation}
-
-We further calculated the 95\% confidence interval for each estimate for visualization purpose.
-The confidence intervals can also be used for hypothesis testing whether the point estimates of the three estimators for a given small area are statistically different.
-The confidence intervals under SRS can be obtained as:
-
-\begin{equation}\label{ci_1phase}
-CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
-\hat{Y}+t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
-\end{equation}
-
-The confidence intervals for the \psmall{} and \extpsynth{} estimates are calculated as:
-
-\begin{equation}\label{ci_2phase_sae}
-CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
-\hat{Y}+t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
-\end{equation}
-
-For the \psynth{} estimates, the confidence intervals are
-
-\begin{equation}\label{ci_2phase_global}
-CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
-\hat{Y}+t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
-\end{equation}
-
-In order to address the potential benefits of the small area estimators compared with the SRS approach, we calculated the \textit{relative efficiency} (Eq.
-\ref{eq:releff}) which can be interpreted as the relative sample size under SRS needed to achieve the variance under the double sampling estimators.
-
-\begin{equation}\label{eq:releff}
-rel.eff_{[\%]}=\frac{\hat{\var}_{SRS}(\hat{Y})}{\hat{\var}_{SAE_{2phase}}(\hat{Y})}\cdot100
-\end{equation}
-
-\newpage
-
-% ----------------------------------------------------------------------- %
-% ----------------------------------------------------------------------- %
-\section{Materials}
-\label{sec:Mat}
-
-%This section describes the actual implementation of the proposed small area estimators (Section \ref{sec:estimators}) under the cluster design of the German NFI (Section \ref{sec:germanNFI}) in the federal state Rhineland-Palatinate.
-
-\subsection{Study Area and Small Area Units}
-\label{sec:studyarea}
-
-The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium (figure \ref{fig:Study Area}).
-With 42.3\% (appr.
-8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}.
-The forests of RLP are further characterized by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterized by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a.
-Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech.
-Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure.
-The forest area of RLP are divided into 3 ownership classes, i.e.
-state forest (27\%), communal forest (46\%) and privately owned forest (27\%).
-The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}.
-For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (figure xx).
-On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 426 Forstreviere (\textit{FR}).
-The next level are the actual forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5- to 10 year period in order to set up management strategies for the upcoming 10 years.
-The FAs and FRs constituted the small area (SA) units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}.
-The average area of the SA units were 43'777 ha on the FA-level, and 4624 ha on the FR level.\\
-
-% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
-%   FA                43'777 ha  (17367 - 125423)     46 (128)         11 (36)            64 (198)
-%   FR                4624 ha   (0.68 - 43284)         5  (14)          0 (0)             13 (34)
-%   stand level       6 ha     (0.03 ha - 73)          0 (0)            0 (0)             2 (4)
-
-% Add Graphic 1:
-% - Graphic of RLP with "zoom" in the 3 managament units (or later all together in Graphic
-
-% Add in text:
-% - add information on the (average) spatial area of each sae-level
-
-% ----------------------------------------------------------------------- %
-% ----------------------------------------------------------------------- %
-\subsection{Extension to Double Sampling Design}
-
-Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI, where timber volume information was derived for 2810 cluster (8092 plots) in the field survey of the latest inventory.
-The local timber volume density on the plot and cluster level for this sample was consequently calculated according to Section \ref{sec:srs_estimator}.
-In the frame of the last inventory (BWI3), the plot center coordinates have been re-measured with differential global satellite navigation system (DGPS) technique.
-Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrially observations and the information derived from the auxiliary information.
-A comparison of the DGPS coordinates with the so-far used target coordinates revealed that 90\% of all horizontal deviations lay in the range of 25 meters.
-A detailed analysis of horizontal DGPS errors in RLP by \citet{lambrecht2017} indicated that 80\% of the plots should not exceed horizontal DGPS errors of 8 meters.
-For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.\par
-
-In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a 500x500 m sample grid that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure xx).
-The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ cluster by the terrestrially measured DGPS coordinates.
-For our study, we restricted the \textit{sampling frame} to the communal and state forest.
-The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service.
-The terrestrial sample size was thus reduced to 2055 cluster (5791 plots).
-Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.\par
-
-\begin{figure}[H]
-	\centering
-	\resizebox{0.75\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
-	\caption{Forest management units in Rhineland-Palatinate, overlayed with the extended double sampling cluster design.}
-	\label{fig:StudyArea}
-\end{figure}
-
-% NOTES:
-%
-% Add Table:
-% provide table of "forest characteristics" in RLP
-% adress sample sizes before and after extension (table?)
-%
-% move this to discussion:
-% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$.
-This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer.
-For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$.
-The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e.
-by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par
-%
-%  "This extension led to a considerable increase of the sample size $n_{1,G}$ in the small area units of both, the FA and FR level."
-% - Show (theoretical) increase in sample sizes by extension to 2phase scheme 
-%   --> these sample sizes are in the following reduced by missing rs-info
-%
-% - Add Graphik showing RLP, zoom into 3 management levels including 2-phase sample
-%   (big graphic, can take 1/2 page later)
-
-% ----------------------------------------------------------------------- %
-% Table xx provides an overview of the terrestrial sample sizes on these management levels for the state and communal forest areas.
-
-% \input{terrSamplsizeFoaFuWa.tex}
-
-% average no. plots / clusters; average area of all three units (divided by state + communal forest & entire forest area)
-
-% --> this is only for communal & state forest area:
-% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
-%   FA                43'777 ha  (17367 - 125423)     46 (128)         11 (36)            64 (198)
-%   FR                4624 ha   (0.68 - 43284)         5  (14)          0 (0)             13 (34)
-%   stand level       6 ha     (0.03 ha - 73)          0 (0)            0 (0)             2 (4)
-
-% - Verwaltungsebenen: management levels (Forstamt, Revier, Bestände) -> durschnittliche Flächengrössen (für die sollen die sae schätzungen gemacht werden)
-% - evtl bereits Stichprobenzahlen generell und innerhalb der Managementenheiten nennen (das ginge dirket hinsichltich des eigentlichen Themas)
-%   (das generelle Problem der Stichprobenanzahl in diesen Einheiten wurde ja schon in der Einleitung angesprochen, also könnte man
-%    hier direkt ein Beispiel geben) --> hier noch getrennt nach gesamter Wald und nur Woefis-Wald (Tabelle, Grpahik)
-% - warum RLP ? (neues Informationssystem, Interesse an effizienteren Methoden)
-% wir nennen Fortamt einfach 'FA-level' und Forstrevier einfach 'FR-level' :-)
-% Info: 45 Forstämter without Bundesforstamt; 426 Reviere without Bundesforstamt
-% mention that the boundaries of all these management units are well-defined by polygon masks (that were used to extract the sampling
-% frame)
-% ----------------------------------------------------------------------- %
-
-\newpage
-% ----------------------------------------------------------------------- %
-% ----------------------------------------------------------------------- %
-\subsection{Auxiliary Information}
-\label{sec:auxinfo}
-
-% ! Mention Missingness in the data and resulting reduction of the sample size (s1, s2)
-
-% ----------------------------------------- %
-\subsubsection{LiDAR Canopy Height Model}
-\label{sec:chm}
-
-In order to derive a countrywide digital terrain and surface model, the topographic survey institution of RLP conducted an airborne laser scanning (LiDAR) acquisition over the entire federal state at leaf-off condition between the year 2003 and 2013.
-For this study, these data was used to create a canopy height model (\textit{CHM}) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters.
-The CHM was calculated as the difference between the digital terrain model (DTM) and the digital surface model (DSM) that were derived by a Delauney interpolation of the two separated LiDAR point clouds (ground pulses and first pulses from non-ground objects).
-During the extended acquisition period, airborne laser scanning technology and data quality evolved significantly, which lead to severe variations in the data quality.
-In particular, the LiDAR acquisition recorded in 2002 and 2003 exhibited a rather poor quality with about only 1 point per 5x5 m$^2$, while more recently acquired datasets of contain more than 125 points per 5x5 m$^2$ raster cell.
-Due to sensor failures, CHM information was not available at 16 $s_1$ (0 $s_2$) sample points.
-
-%As explanatory variables, the mean canopy height (\textit{meanheight}) and the standard deviation ($stddev$) were calculated as the mean and standard deviation of all raster values within a predefined square around each sample plot center.
-The square (i.e.
-\textit{support} of the explanatory variable, see section \ref{sec:supp}) was previously intersected with the state and communal forest area defined by a polygon mask and thereby corrected for edge effects at the forest border.
-The tree height is one prominent predictor variable in the taper functions of the \bwi{} that are used to calculate a timber volume value for each sample tree \citep{kublin2003, kublin2013}.
-A visual inspection of the tree volumes of all sample trees collected in the \bwi{} within RLP against their tree heights also revealed the characteristic shape of an allometric relationship between these variables (Online Resource 1).
-It was hypothesized that this relationship on single-tree level is also apparent on the aggregated level of a sample plot and cluster, and can be used within the frame of regression modeling.\par
-%
-%The strength of correlation between \textit{meanheight} and timber volume on plot level was expected to show high variation according to the mentioned time-lag up to 10 years between LiDAR acquisition and terrestrial survey.
-The quality of the height information was also expected to vary according to changing sensor technologies and different point densities used over the years.
-For these reasons, the LiDAR acquisition year (\textit{lidaryear}) for each sample plot was considered as a potential categorical explanatory variable to explain the variation in the data introduced by these factors.
-For this purpose, the acquisition year \textit{2008} was further divided into \textit{2008} and \textit{2008\_1}.
-In the latter, the data quality turned out to be very poor due to sensor failures during the acquisition.
-Additionally, the years \textit{2006} and \textit{2007} as well as \textit{2012} and \textit{2013} were pooled in order to increase the number of observations per factor level for modelling reasons.
-As a result, the \textit{lidaryear} variable comprised nine categories (\textit{2002}, \textit{2003}, \textit{2007}, \textit{2008}, \textit{2008\_1}, \textit{2009}, \textit{2010}, \textit{2011} and \textit{2012}).
-
-% ---------------------------------------------- %
-\subsubsection{Tree Species Classification Map}
-\label{sec:tspecclass}
-
-A countrywide satellite-based classification map of the five main tree species (European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir, Scots pine) described in \citet{stoffels2015} was used to derive tree species information on sample plot level.
-The classified tree species map has a grid size of 5 meters and predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree.
-Due to unavailable satellite data for the classification, the tree species map excluded one patch with an area of 415 km$^2$ in the south-west part of RLP, and two further patches with an area of 76 km$^2$ and 100 km$^2$ in the northern part \citep{stoffels2015}.
-The tree species information was consequently missing for 407 (7\%) of the 5791 sample locations.
-
-%
-%
-%
-%
-%
-%
-
-% ---------------------------------------------- %
-\subsubsection{Calculation of Explanatory Variables}
-\label{sec:tspecclass}
-
-% Graphik:
-
-%\begin{figure}[H]
-%	\centering
-%	\resizebox{0.8\hsize}{!}{\includegraphics*{fig/Auxvars.png}}
-%	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information.
-Right: Magnified illustration of the rectangular supports used to derive the explanatory variables from the auxiliary information.}
-%	\label{fig:Auxvars}
-%\end{figure}
-
-\newpage
-% ----------------------------------------------------------------------- %
-% ----------------------------------------------------------------------- %
-\subsection{Regression Model}
-\label{sec:regmod}
-
-\newpage
-
-% ======================================================================================================================== %
-% NOTES:
-% - Study Area **
-%   o characteristics of forests, e.g. structural & species diversity
-%   o introduce forest districts, show example and quickly mention their reasoning  
-% 
-% - The German NFI *
-%   o cluster sampling, angle-cound sampling, CF-correction at the forest border
-%     no. of plots (clusters) original according to BWI-survey
-%   o plot locations by DGPS, and expected accuracy and pre-processing (plausibility analyses
-%     and replacing by old coordinates if necessary)
-%
-% - Estimators **
-%   o one-phase estimator: write down estimator in HT-style (evtl. Derivation of CF-correction in
-%     Appendix)
-%   o two-phase psmall cluster
-%   o two-phase psynth extended cluster
-%   o two-phase psynth cluster
-%   (briefly explain:
-%    o the estimator like in jss-article, pronounce difference between psmall
-%      and psynthext in case of cluster sampling --> special case and research question:
-%      how often does it occur and does it make a difference?
-%    o explain difference between external and internal model --> this can be the reasoning for
-%      using Daniels estimators for our objective: a) "db" --> we do not depent on the model which
-%      is a huge advantage if we have medium-level quality data; b) "cluster" --> provided by Daniels
-%      estimators in combination with c) "iternal" model building --> g-weight property and
-%      considering dependency of regression coefs on the sample 
-%
-% - Extension of terrestrial sample grid **
-%   o rules (?), new sample sizes globally and within saes
-%
-%
-% - Auxililary information and variable derivation **
-%   o document missing data at 1-phase grid (separate into s1 and s2) 
-%   o maybe: "due to missing remote sensing information at some sample points, the original sample sizes (s2, s1) 
-%             were shrinked down to the numbers shwn in table XX" (-> table showing the actual sample sizes)
-%  
-% - Model building **
-%   o refer to calibration method in previous article
-%   o refer to comprehensice model evaluations in previous article
-%   o present final model
-%
-%
-% 1) Preprocessing of terrestrial inventory data
-% 2) Preprocessing of auxiliary information
-% 3) Extention to 2-phase sample grid
-% 4) Model building
-%
-%
+%\subsection{Model Validations}
+%\label{sec:modval_res}

### 2018-01-25 Draft_Form/tex/Results.tex
update 25_01_2018
update 25_01_2018 (begin Results)

@@
 % ----------------------------------------------------------------------- %
-%\subsection{Model Validations}
-%\label{sec:modval_res}
+\subsection{Feasibility of estimations}
+\label{sec:feasest}
+
+% Alternative section title: General estimation results
+
+% NOTES:
+% - 1) address feasibility of estimations for each estimator
+% - 2) give general overview about estimation results (see Breidenbach) before going into more detail
+%
+%
+
+\newpage
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+\subsection{Estimation errors}
+\label{sec:esterr}
+
+\begin{figure}[H]
+	\centering
+	\resizebox{1\hsize}{!}{\includegraphics{fig/error_distr_foa_fu.png}}
+	\caption{Cumulative distribution of estimation errors under the simple random sampling (SRS), the pseudo small (PSMALL), the extended pseudo synthetic (EXTPSYNTH) and the pseudo synthetic (SYNTH) estimator.
+\textit{Left}: Results for the 45 FA units.
+\textit{Right}: Results for the 388 (SRS), 321 (PSMALL / EXTPSYNTH) and 403 (PSYNTH) FR units.}
+	\label{fig:disterrors}
+\end{figure}
+
+\newpage
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+\subsection{Gain and Relative Efficiency}
+\label{sec:gain_releff}
+
+\begin{figure}[H]
+	\centering
+	\resizebox{0.7\hsize}{!}{\includegraphics{fig/compare_onephase_psmall.png}}
+	\caption{Cumulative distribution of variance reduction by the PSMALL compared to the SRS estimator for the  45 FA and 321 FR units.}
+	\label{fig:gain}
+\end{figure}
+
+\newpage
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+\subsection{Comparison of PSMALL and EXTPSYNTH}
+\label{sec:comp}
+
+\begin{figure}[H]
+	\centering
+	\resizebox{1\hsize}{!}{\includegraphics{fig/psmall_vs_extpsynth_fu.png}}
+	\caption{\textit{Left}: Comparison of the g-weight variance between the PSMALL and the EXTPSYNTH estimator for the 321 FR units.
+		      \textit{Right}: Difference in g-weight variance between the PSMALL and the EXTPSYNTH estimator in dependence of the terrestrial data ($n2G$) in the FR unit.}
+	\label{fig:compvar}
+\end{figure}
+
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+%\subsection{Effect of Model Accuracy}
+%\label{sec:modacc_eff}

### 2018-01-28 Draft_Form/tex/Results.tex
update 26_01_2018
update 26_01_2018
update 28_01_2018
update 28_01_2018

@@
-\section{Results} %techreport
+\section{Results}
 \label{sec:Res}
@@
 % ----------------------------------------------------------------------- %
-\subsection{Estimation errors}
+\subsection{Comparison of estimation errors}
 \label{sec:esterr}
+
+On both small area levels, the design-unbiased estimators \psmall{} and \extpsynth{} led to a substantial reduction in the estimation errors compared to the SRS estimator (fig.
+\ref{fig:disterrors}).
+On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under the \extpsynth{} and \psmall{} estimator.
+The cumulative error distribution (fig.
+\ref{fig:disterrors}, left) reveals that under the SRS estimator, errors $\leq$ 5\% were achieved for 17\% of the FA units (8 of 45).
+This proportion could be increased to 62\% (28 FA units) and 73\% (33 FA units) by application of \psmall{} and \extpsynth{}.
+95\% of all estimates exhibited errors $\leq$ 9.5\% under the SRS estimator and $\leq$ 6.6\% when using \psmall{} or \extpsynth{}.
+Estimation errors higher than 10\% only appeared twice for each of the unbiased estimators.\par
+
+The error reduction by the unbiased double sampling estimators was even more pronounced on the FR level (fig.
+\ref{fig:disterrors}, right), although the overall error niveau was substantially higher than on FA level.
+The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under the \psmall{} and \extpsynth{} estimator.
+95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors $\leq$ 20\%.
+In comparion, the SRS estimates resulted in errors $\leq$ 36.6\% for 95\% of the 388 FR units and exceeded an error of 20\% in 30\% of the cases.\par
+
+On both small area levels, the \psynth{} estimator resulted in much smaller estimation errors compared to \psmall{} and \extpsynth{}.
+This was as expected, since the \psynth{} variance estimate does not take the residual variation in each small area unit into account (section \ref{sec:psynth}).
+Compared to the error distribution of the asymptotically design-unbiased estimators \psmall{} and \extpsynth{}, the estimation errors of \psynth{} might thus be to optimistic.
 
@@
 	\resizebox{1\hsize}{!}{\includegraphics{fig/error_distr_foa_fu.png}}
-	\caption{Cumulative distribution of estimation errors under the simple random sampling (SRS), the pseudo small (PSMALL), the extended pseudo synthetic (EXTPSYNTH) and the pseudo synthetic (SYNTH) estimator.
+	\caption{Cumulative distribution of estimation errors under the simple random sampling (SRS), the pseudo small (\psmall{}), the extended pseudo synthetic (\extpsynth{}) and the pseudo synthetic (\psynth{}) estimator.
 \textit{Left}: Results for the 45 FA units.
-\textit{Right}: Results for the 388 (SRS), 321 (PSMALL / EXTPSYNTH) and 403 (PSYNTH) FR units.}
+\textit{Right}: Results for the 388 (SRS), 321 (\psmall{} / \extpsynth{}) and 403 (\psynth{}) FR units.}
 	\label{fig:disterrors}
+\end{figure}
+
+%% NOTES
+ %Estimation errors smaller than 10\% were achieved for only 15\% (xx) of all FR units under SRS, while this proportion could be increased to 38\% and 46\% by PSMALL and EXTPSYNTH.
+
+% Whereas the estimation errors under PSMALL and PSYNTH were limited to maximum of 41 and 45\%, The SRS estimates exceeded this value in 11 FR units.
+%
+% AS obvious from figure \ref{fig:disterrors} (right), the major improvement 
+%
+%
+%
+%
+% The PSYNTH estimator always resulted in much smaller estiamtion errors compared to PSMALL and PSYNTH. This is because ...
+%
+% As obvious from figure \ref{fig:disterrors}, the error distribution of PSMALL and EXTPSYNTH were found to be very similar and suggested that the two estimator performed very similar.
+In section \ref{sec:comp}, we analysed the differences between the two estimators in more detail.
+%
+%The highest observed estimation error was 14\% for the SRS, PSMALL and EXTPSYNTH estimator.
+
+\newpage
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+\subsection{Comparison of \psmall{} and \extpsynth{}}
+\label{sec:comp}
+
+As obvious from figure \ref{fig:disterrors}, the error distribution of \psmall{} and \extpsynth{} were found to be very similar, with \psmall{} showing marginally higher estimation errors.
+In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (fig.
+\ref{fig:compvar}, left).
+As obvious, \psmall{} yielded slightly larger variances for the vast majority of the estimates.
+As addressed in section \ref{sec:extpsynth}, one possible explanation for such differences was the effect of one or more cluster not entirely being included in a small area unit, as this would constitute a violation of the \extpsynth{} estimator.
+This violation was actually observed in 155 of the 312 FR units (48\%).
+However, the affected FR units (depicted in red color, fig.
+\ref{fig:compvar}) did not show a significant divergence from the \psmall{} variances with respect to the remaining unaffected FR units.
+For this reason, the variance differences between the two estimators were expected to occur for the following reasons: as depicted in \citet[pp.17--18]{mandallaz2016}, the mathematical formulations of the \psmall{} and \extpsynth{} estimator are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area.
+An additional comparison of the absolute differences in the g-weight variance (fig.
+\ref{fig:compvar}, right) revealed that large differences in fact particularly occurred for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$).
+The differences decreased with increasing sample size and thus confirmed the asymptotic relationship between the two estimators.
+A comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par
+
+%As obvious from figure \ref{fig:disterrors}, the error distribution of \psmall{} and \extpsynth{} were found to be very similar, with \psmall{} showing marginally higher estimation errors.
+Differences between the two estimators were expected to occur for the following reasons: 1) as depicted in \citet[pp.17--18]{mandallaz2016}, the mathematical formulations of the \psmall{} and \extpsynth{} estimator are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area.
+Therefore, differences between the estimators were particularly expected for small area units with low terrestrial sampling intensities.
+2) As addressed in section \ref{sec:extpsynth}, the case of one or more cluster not entirely being included in a small area unit would constitute a violation of the \extpsynth{} estimator.
+Effects of this violation on the estimates had yet not been investigated and also lead to a divergence between \psmall{} and \extpsynth{}.\par
+%
+%In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (fig.
+\ref{fig:compvar}, left).
+As obvious, \psmall{} yielded slightly larger variances for the vast majority of the estimates.
+A violation of the \extpsynth{} assumption by one or more cluster not entirely included in a small area unit was observed in 155 of the 312 FR units (48\%).
+However, the affected FR units (depicted in red color, fig.
+\ref{fig:compvar}) did not show a significant divergence from the \psmall{} variances with respect to the remaining unaffected FR units.
+An additional comparison of the absolute differences in the g-weight variance (fig.
+\ref{fig:compvar}, right) revealed that large differences particularly occurred for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$).
+The differences decreased with increasing sample size and thus confirmed the asymptotic relationship between the two estimators.
+A comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par
+
+% NOTES:
+% - Section \ref{sec:comp} provides a more detailed analysis of the differences between the two estimators.
+% - DM-explanation: The model residuals and thus the residual variance for extpsynth should in general be a bit better than those of psmall, since we additionally adjust the regression
+%                   to the small area data by introducing the sae-indicator variable (even if this is strictly speaken only a means to cause zero-mean-residuals)
+%                   ==> we even can relate the differences to the residual variation, since the first and second term of extpsynth and psmall area identical with exception 
+%                       of the adjusted regression coefficient
+% - we can see the asymptotic of psmall and extpsynth: with increasing n2G, psmall and extpsynth are mathematically identical
+% ==> so differences will particularly concern sae units with small n2G (threshold seems to be around n2G < 10)
+%
+% for Discussion:
+% - our analyses 
+%   a) suggest that the differences between \psmall{} and \extpsynth{} become negligible for sample sizes $n_{2,G}$ larger than 10 due to the asymptotic relationship between these estimators 
+%   b) showed that violation of the '\extpsynth{}'-assumption had only minor effects on the variance estimates that did not lead to statistically different point estimates 
+%   c) indicate that \extpsynth{} will in general have slightly smaller est.variances due to a slightly better model fit through the data in the small area, which is caused by the 
+%      adjusted intercept (which however is mainly a means to insure the zero-mean-residual assumption in the \extpsynth{}-estimator
+
+\begin{figure}[H]
+	\centering
+	\resizebox{1\hsize}{!}{\includegraphics{fig/psmall_vs_extpsynth_fu.png}}
+	\caption{\textit{Left}: Comparison of the g-weight variance between the PSMALL and the EXTPSYNTH estimator for the 321 FR units.
+		\textit{Right}: Difference in g-weight variance between the PSMALL and the EXTPSYNTH estimator in dependence of the terrestrial data ($n2G$) in the FR unit.}
+	\label{fig:compvar}
 \end{figure}
@@
 
+\begin{figure}[H]
+	\centering
+	\resizebox{0.7\hsize}{!}{\includegraphics{fig/eval_2phase_fail.png}}
+	\caption{}
+	\label{fig:fail}
+\end{figure}
+
 \newpage
+
 % ----------------------------------------------------------------------- %
 % ----------------------------------------------------------------------- %
-\subsection{Comparison of PSMALL and EXTPSYNTH}
-\label{sec:comp}
+\subsection{Effect of regression model accuracy}
+\label{sec:modacc_eff}
 
@@
 	\centering
-	\resizebox{1\hsize}{!}{\includegraphics{fig/psmall_vs_extpsynth_fu.png}}
-	\caption{\textit{Left}: Comparison of the g-weight variance between the PSMALL and the EXTPSYNTH estimator for the 321 FR units.
-		      \textit{Right}: Difference in g-weight variance between the PSMALL and the EXTPSYNTH estimator in dependence of the terrestrial data ($n2G$) in the FR unit.}
-	\label{fig:compvar}
+	\resizebox{1\hsize}{!}{\includegraphics{fig/modcom_errors_fu.png}}
+	\caption{}
+	\label{fig:compmods}
 \end{figure}
-
-% ----------------------------------------------------------------------- %
-% ----------------------------------------------------------------------- %
-%\subsection{Effect of Model Accuracy}
-%\label{sec:modacc_eff}

### 2018-02-02 Draft_Form/tex/Results.tex
update_02_02_2018
update_02_02_2018

@@
 As addressed in section \ref{sec:extpsynth}, one possible explanation for such differences was the effect of one or more cluster not entirely being included in a small area unit, as this would constitute a violation of the \extpsynth{} estimator.
-This violation was actually observed in 155 of the 312 FR units (48\%).
+This violation was actually observed in 155 of the 321 FR units (48\%).
 However, the affected FR units (depicted in red color, fig.
@@
 % ----------------------------------------------------------------------- %
-\subsection{Gain and Relative Efficiency}
-\label{sec:gain_releff}
+\subsection{Variance reduction of SRS estimator}
+\label{sec:gain_eval}
 
@@
 	\centering
-	\resizebox{0.7\hsize}{!}{\includegraphics{fig/compare_onephase_psmall.png}}
-	\caption{Cumulative distribution of variance reduction by the PSMALL compared to the SRS estimator for the  45 FA and 321 FR units.}
+	\resizebox{0.7\hsize}{!}{\includegraphics{fig/compare_onephase_extpsynth_psmall.png}}
+	\caption{Cumulative distribution of variance reduction by the PSMALL and EXTPSYNTH compared to the SRS estimator for the  45 FA and 321 FR units.}
 	\label{fig:gain}
@@
 
+%% NOTES:
+% - 
+%
+%
+%
+%
+%
+%
+%
+
 \newpage
-
 % ----------------------------------------------------------------------- %

### 2018-02-02 Draft_Form/tex/Materials_and_Methods(2).tex
update 28_01_2018
update 28_01_2018
update 02_02_2018(evening)
update 02_02_2018(evening)

@@
 \subsubsection{Pseudo Synthetic Estimator (\psynth{})}
+\label{sec:psynth}
 % \textbf{Pseudo Synthetic Estimator (\psynth{})}\\
@@
 \subsubsection{Extended Pseudo Synthetic Estimator (\extpsynth{})}
+\label{sec:extpsynth}
 % \textbf{Extended Pseudo Synthetic Estimator (\extpsynth{})}\\
@@
 \begin{equation}\label{eq:releff}
-rel.eff_{[\%]}=\frac{\hat{\var}_{SRS}(\hat{Y})}{\hat{\var}_{SAE_{2phase}}(\hat{Y})}\cdot100
+rel.eff=\frac{\hat{\var}_{SRS}(\hat{Y})}{\hat{\var}_{SAE_{2phase}}(\hat{Y})}
 \end{equation}
@@
 For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArea}).
-On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 426 Forstreviere (\textit{FR}).
-The next level are the actual forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5- to 10 year period in order to set up management strategies for the upcoming 10 years.
+On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 405 Forstreviere (\textit{FR}).
+The next level are the forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5- to 10 year period in order to set up management strategies for the upcoming 10 years.
 The FAs and FRs constituted the small area (SA) units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}.
@@
 
+% Notes to myself:
+% - in the original forstrevier layer, we have 427 FR units but 21 of them are not covered by woefis-layer (so no state- and communal forest), and 1 is the "Bundesforstamt" not considered by us
+
 % ----------------------------------------------------------------------- %
@@
 The local timber volume density on the plot and cluster level for this sample was consequently calculated according to Section \ref{sec:srs_estimator}.
-In the frame of this survey, the plot center coordinates have been re-measured with differential global satellite navigation system (DGPS) technique.
+In the frame of this survey, the plot center coordinates were re-measured with differential global satellite navigation system (DGPS) technique.
 Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrially observations and the information derived from the auxiliary information.
@@
 For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.
-
-% NOTE:
-% - add table with overview of terrestrial dta attributes (like Johannes)
-%
-
-% ----------------------------------------------------------------------- %
-\subsection{Extension to double sampling design}
-
-In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a 500x500 m sample grid that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}).
-The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ cluster by the terrestrially measured DGPS coordinates.
-For our study, we restricted the \textit{sampling frame} to the communal and state forest.
-The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service.
-The terrestrial sample size was thus reduced to 2055 cluster (5791 plots).
-Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.
+The terrestrial sample size $n_{2,G}$ within the FA units was 46 cluster on average and ranged between 11 and 64.
+Within the FR units, $n_{2,G}$ was considerably smaller with an average of 5 cluster and a range between 0 and 13.
 
@@
 	\centering
-	\resizebox{0.63\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
+	\resizebox{0.8\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
 	\caption{\textit{Left}: Study Area with delineated FA forest management units.
@@
 \end{figure}
+
+% ----------------------------------------------------------------------- %
+\subsection{Extension to double sampling design}
+
+In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 kilometer grid to a grid size of 500x500 meters that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}).
+The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ cluster by the terrestrially measured DGPS coordinates.
+For our study, we restricted the \textit{sampling frame} to the communal and state forest.
+The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service.
+Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.
+The terrestrial sample size $n_2$ was thus reduced to 2055 cluster (5791 plots).
+Table \ref{tab:fieldata} provides a short descriptive summary about the volume densities and the main attributes of the NFI plots located in the state and communal forest sampling frame.
+The densification led to an average sample size $n_{1,G}$ of 759  cluster (range: 246 -- 1022) in the FA units, and 88 cluster (range: 1 -- 194) in the FR units.
+
+\input{tab/table_fieldmeasuredvals.tex}
 
@@
 
-\newpage
 % ----------------------------------------------------------------------- %
@@
 The second source of auxiliary information was a countrywide satellite-based classification map of the five main tree species (European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir, Scots pine) described in \citet{stoffels2015} (Figure \ref{fig:Auxvars}, \textit{bottom}).
-The classified tree species map has a grid size of 5 meters and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) by application of the spatially adaptive classification algorithm described in \citet{stoffels2012}.
+The classified tree species map has a grid size of 5 meters and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) by application of a spatially adaptive classification algorithm described in \citet{stoffels2012}.
 As timber volume estimations on the tree level are often based on species-specific biomass and volume equations, the use of tree species information - especially for timber volume estimation - has often been stated as a key factor for improving the estimation precision \cite{white2016}.
@@
 
-% Graphik:
-\begin{figure}[H]
-	\centering
-	\resizebox{0.8\hsize}{!}{\includegraphics*{fig/AuxvarsLOWRES.png}}
-	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information.
-Right: Magnified illustration of the rectangular supports used to derive the explanatory variables from the auxiliary information.}
-	\label{fig:Auxvars}
-\end{figure}
-
+% neu:
 \begin{table}[H]
@@
 				communal and state forest & 96'854 & 33'365 & 5791 & 2055\\ % <--
-			\hspace{5mm} \footnotesize missing CHM & \footnotesize 16 & \footnotesize 9 & \footnotesize 0 & \footnotesize 0\\ % <--
-			\hspace{5mm} \footnotesize missing TSPEC & \footnotesize 6910  & \footnotesize 3465 & \footnotesize 407 & \footnotesize 380\\ % <--
-			\hspace{5mm} \footnotesize missing CHM \textit{and} TSPEC & \footnotesize 2 & \footnotesize 1 & \footnotesize 0 & \footnotesize 0\\ % <--
-			\hspace{5mm} \footnotesize missing CHM \textit{or} TSPEC & \footnotesize 6924 & \footnotesize 3473 & \footnotesize 407 & \footnotesize 380\\ % <--
+				\hspace{5mm} \footnotesize missing CHM & \footnotesize 18 & \footnotesize 10 & \footnotesize 0 & \footnotesize 0\\ % <--
+				\hspace{5mm} \footnotesize missing TSPEC & \footnotesize 7060  & \footnotesize 3587 & \footnotesize 414 & \footnotesize 385\\ % <--
+				\hspace{5mm} \footnotesize missing CHM \textit{and} TSPEC & \footnotesize 3 & \footnotesize 2 & \footnotesize 0 & \footnotesize 0\\ % <--
+				\hspace{5mm} \footnotesize missing CHM \textit{or} TSPEC & \footnotesize 7075 & \footnotesize 3595 & \footnotesize 414 & \footnotesize 385\\ % <--
 				\hline \hline
@@
 
-%\begin{table}[H]
-%	\begin{center}
-%		\caption{Sample size for each phase in entire study area.}
-%		\label{tab:ssize}
-%		\begin{tabular}{l|r|r|r|r}
-%			\hline
-%			\textit{Sampling frame} & \textbf{$n_{1,plot}$} & \textbf{$n_1$} & \textbf{$n_{2,plot}$} & \textbf{$n_2$}\\ % <-- added & and content for each column
-%			\hline \hline
-%			communal and state forest & 96'854 & 33'365 & 5791 & 2055\\ % <--
-%			\hspace{5mm} \small missing CHM & \small 16 & \small 9 & \small 0 & \small 0\\ % <--
-%			\hspace{5mm} \small missing TSPEC & \small 6910  & \small 3465 & \small 407 & \small 380\\ % <--
-%			\hspace{5mm} \small missing CHM \textit{and} TSPEC & \small 2 & \small 1 & \small 0 & \small 0\\ % <--
-%			\hspace{5mm} \small missing CHM \textit{or} TSPEC & \small 6924 & \small 3473 & \small 407 & \small 380\\ % <--
-%			\hline
-%			Total for estimation & 89'930 & 29'892 & 5384 & 1675\\ % <--			
-%		\end{tabular}
-%	\end{center}
-%\end{table}
+% Graphik:
+\begin{figure}[H]
+	\centering
+	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/AuxvarsLOWRES.png}}
+	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information.
+Right: Magnified illustration of the rectangular supports used to derive the explanatory variables from the auxiliary information.}
+	\label{fig:Auxvars}
+\end{figure}
 

### 2018-02-02 Draft_Form/tex/Results.tex
update 02_02_2018(evening)
update 02_02_2018(evening)

@@
 % ----------------------------------------------------------------------- %
-\subsection{Feasibility of estimations}
+\subsection{General estimation results}
 \label{sec:feasest}
 
-% Alternative section title: General estimation results
+On FA level,
 
@@
 % - 2) give general overview about estimation results (see Breidenbach) before going into more detail
+%
+
+% Feasibility: 
+% FA-level: for 44 out of 45 FA-units, the full model could be applied. For one remaining, only the model without tree species was applied.
+% 
+% FR-level: 
+%
+% mathemat. feasibility:
+% - op-estimation feasible for 388 of the 405 fu-units. --> for 17 fus not possible due to n2G < 2
+% - psmall / extpsynth possible for 386 of the 405 units (for 19 fus not possible). Reason: for 19 fus we have n2G < 2
+% - psynth not possible for 403 of 405. For 2 units not possible due to n1G < 2 (these two are included in the 19 above).
+%    -> basically, for these 2 fu-units, none of the estimators could produce estimations due to n1G < 2
+%  
+%  restriction of unbiased estimtors to n2G >= 4: 
+% - psmall / extpsynth: 65 of the 386 fu-units have n2G < 4, so theyx cancel out. Thus we have 19 + 65 = 84 fu-units for which no psmall & extpsynth estimations were deliverable.
+%   ==> Thus, we have unbiase estimations for 321 of 405 fu units (79%)
+
+% Some stats:
+%
+%
+%
 %
@@
 % ----------------------------------------------------------------------- %
-\subsection{Comparison of estimation errors}
+\subsection{Estimation errors}
 \label{sec:esterr}
@@
 \ref{fig:compvar}) did not show a significant divergence from the \psmall{} variances with respect to the remaining unaffected FR units.
-For this reason, the variance differences between the two estimators were expected to occur for the following reasons: as depicted in \citet[pp.17--18]{mandallaz2016}, the mathematical formulations of the \psmall{} and \extpsynth{} estimator are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area.
+The variance differences between the two estimators were expected to occur for the following reason: as depicted in \citet[pp.17--18]{mandallaz2016}, the mathematical formulations of the \psmall{} and \extpsynth{} estimator are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area.
 An additional comparison of the absolute differences in the g-weight variance (fig.
-\ref{fig:compvar}, right) revealed that large differences in fact particularly occurred for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$).
+\ref{fig:compvar}, right) revealed that large differences did in fact particularly occur for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$).
 The differences decreased with increasing sample size and thus confirmed the asymptotic relationship between the two estimators.
-A comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par
+However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par
 
@@
 % ----------------------------------------------------------------------- %
-\subsection{Variance reduction of SRS estimator}
+\subsection{Reduction of variance by two-phase estimators}
+% \subsection{Variance reduction of SRS estimator}
 \label{sec:gain_eval}
@@
 %
-
-\newpage
-% ----------------------------------------------------------------------- %
-% ----------------------------------------------------------------------- %
-\subsection{Effect of regression model accuracy}
-\label{sec:modacc_eff}
-
-\begin{figure}[H]
-	\centering
-	\resizebox{1\hsize}{!}{\includegraphics{fig/modcom_errors_fu.png}}
-	\caption{}
-	\label{fig:compmods}
-\end{figure}

### 2018-02-03 Draft_Form/tex/Abstract.tex
update 03_02_2018
update 03_02_2018

@@
 The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval.
-However, the data have scarcely been used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors.
+However, the data have yet been scarcely used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors.
+In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area regression estimators.
+We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (45 and 405 forest district units respectively) in the federal German state of Rhineland-Palatinate.
+An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions on the plot level.
+The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the SRS estimator by 43\% and 25\% on average for the two management levels respectively.
+
+%The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval.
+However, the data have yet been scarcely used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors.
 In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area estimation procedures that try to overcome the restriction in terrestrial sample size by enlarging the sample by a large set of model predictions.

### 2018-02-03 Draft_Form/tex/Introduction(2).tex
update 03_02_2018
update 03_02_2018

@@
 The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels when incorporated in small area estimation procedures.
-We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 42 and 392 forest districts respectively.
+We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 45 and 405 forest districts respectively.
 The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a, mandallaz2013b}.
-Auxiliary information were obtained from a countrywide airborne Laser scanning (LiDAR) canopy height model (CHM) and a tree species classification map and used for regression within tree species strata.
+Auxiliary data were obtained from a countrywide airborne Laser scanning (LiDAR) canopy height model (CHM) and a tree species classification map and used for regression within tree species strata.
 The estimation accuracies were compared to those achieved under SRS sampling.

### 2018-02-03 Draft_Form/tex/Results.tex
update 03_02_2018
update 03_02_2018

@@
 
-On FA level,
+An application of the SRS, \psmall{} and \extpsynth{} estimator was not feasible for 17 of all 405 FR-units due to an insufficient terrestrial sample size of $n_{2,G} < 2$.
+We further restricted the calculation of \psmall{} and \extpsynth{} to small area units with a minimum terrestrial sample size of $n_{2,G} \geq 4$ to avoid unstable estimates.
+This affected 65 additional FR units and limited unbiased two-phase estimations to 321 (79\%) of the 405 FR units.
+It should be noted that also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 1$.
+Due to substantial larger sample sizes, all estimators could however be applied in all small area units on the FA level.
+The average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (table \ref{tab:estres}).
+An additional pairwise comparison of the 95\% confidence intervals for all FA- and FR-units revealed that the four estimators did in fact not produce statistically different point estimates.
+This confirmed that the differences between the estimators are solely found in the precision which they provide for the point estimates.
 
-% NOTES:
-% - 1) address feasibility of estimations for each estimator
-% - 2) give general overview about estimation results (see Breidenbach) before going into more detail
+%% NOTES
 %
-
 % Feasibility: 
@@
 % FR-level: 
-%
-% mathemat. feasibility:
+% o mathemat. feasibility:
 %    - op-estimation feasible for 388 of the 405 fu-units. --> for 17 fus not possible due to n2G < 2
-% - psmall / extpsynth possible for 386 of the 405 units (for 19 fus not possible). Reason: for 19 fus we have n2G < 2
+%    - psmall / extpsynth possible for 388 of the 405 units (for 17 fus not possible). Reason: n2G < 2 (identical with op)
 %    - psynth not possible for 403 of 405. For 2 units not possible due to n1G < 2 (these two are included in the 19 above).
 %    -> basically, for these 2 fu-units, none of the estimators could produce estimations due to n1G < 2
-%  
-%  restriction of unbiased estimtors to n2G >= 4: 
+%  o restriction of unbiased estimtors to n2G >= 4: 
 %    - psmall / extpsynth: 65 of the 386 fu-units have n2G < 4, so theyx cancel out. Thus we have 19 + 65 = 84 fu-units for which no psmall & extpsynth estimations were deliverable.
@@
 
-% Some stats:
-%
-%
-%
-%
-%
+% Mention: a comparison of the confidence intervals between revealed that the
 
-\newpage
+\begin{table}[H]
+	\begin{center}
+		\caption{Descriptive summary of point estimates and estimation errors on the two forest district levels. $N_u$: number of evaluated small area units.}
+		\vspace{0.2cm}
+		\label{tab:estres}
+		{\small %
+			\begin{tabular}{c|l c|c|c|c|c|c|c} %8cols
+				\hlineB{1}
+				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Point estimates} & \multicolumn{3}{c}{Errors [\%]} \\
+				\cline{4-9} & & & mean & min & max & mean & min & max \\
+				\hline \hline
+				\multirow{4}{*}{FA} & SRS       & ($N_u$=45)  & 300.16 & 215.91 & 392.84 &  6.69 & 3.87 & 13.21 \\
+				                    & PSMALL    & ($N_u$=45)  & 307.29 & 209.26 & 417.10 &  5.16 & 3.46 & 14.33 \\
+				                    & EXTPSYNTH & ($N_u$=45)  & 307.27 & 209.01 & 415.02 &  4.78 & 3.25 & 13.88 \\
+				                    & PSYNTH    & ($N_u$=45)  & 306.90 & 223.51 & 409.92 &  2.34 & 1.54 &  3.95 \\
+				\hlineB{2}          
+				\multirow{4}{*}{FR} & SRS       & ($N_u$=388) & 301.83 &  99.89 & 612.13 & 18.32 & 0.34 & 104.97 \\
+				                    & PSMALL    & ($N_u$=321) & 308.15 & 159.64 & 568.67 & 12.24 & 3.48 &  44.94 \\
+				                    & EXTPSYNTH & ($N_u$=321) & 308.38 & 154.07 & 544.34 & 11.34 & 3.60 &  40.91 \\
+				                    & PSYNTH    & ($N_u$=403) & 307.82 & 166.01 & 444.29 & 4.65  & 2.56 &  62.51 \\
+				\hline \hline
+			\end{tabular}
+		}%
+	\end{center}
+\end{table}
+
 % ----------------------------------------------------------------------- %
@@
 \ref{fig:disterrors}).
-On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under the \extpsynth{} and \psmall{} estimator.
+On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under the \extpsynth{} and \psmall{} estimator (table \ref{tab:estres}).
 The cumulative error distribution (fig.
@@
 Estimation errors higher than 10\% only appeared twice for each of the unbiased estimators.\par
-
 The error reduction by the unbiased double sampling estimators was even more pronounced on the FR level (fig.
 \ref{fig:disterrors}, right), although the overall error niveau was substantially higher than on FA level.
-The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under the \psmall{} and \extpsynth{} estimator.
+The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under the \psmall{} and \extpsynth{} estimator (table \ref{tab:estres}).
+Errors smaller than 10\% were achieved in 15\% by the SRS estimator and 46\% by the \psmall{} and \psynth{} estimator.
 95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors $\leq$ 20\%.
-In comparion, the SRS estimates resulted in errors $\leq$ 36.6\% for 95\% of the 388 FR units and exceeded an error of 20\% in 30\% of the cases.\par
-
-On both small area levels, the \psynth{} estimator resulted in much smaller estimation errors compared to \psmall{} and \extpsynth{}.
-This was as expected, since the \psynth{} variance estimate does not take the residual variation in each small area unit into account (section \ref{sec:psynth}).
-Compared to the error distribution of the asymptotically design-unbiased estimators \psmall{} and \extpsynth{}, the estimation errors of \psynth{} might thus be to optimistic.
+In comparion, the SRS estimates resulted in errors $\leq$ 36.6\% for 95\% of the 388 FR units.
 
@@
 
+On both small area levels, the \psynth{} estimator resulted in much smaller estimation errors compared to \psmall{} and \extpsynth{}.
+This was as expected, since the \psynth{} variance estimate does not take the residual variation in each small area unit into account (section \ref{sec:psynth}).
+Compared to the error distribution of the asymptotically design-unbiased estimators \psmall{} and \extpsynth{}, the estimation errors of \psynth{} might thus be to optimistic.
+
 %% NOTES
@@
 
-% Whereas the estimation errors under PSMALL and PSYNTH were limited to maximum of 41 and 45\%, The SRS estimates exceeded this value in 11 FR units.
-%
-% AS obvious from figure \ref{fig:disterrors} (right), the major improvement 
-%
-%
-%
-%
-% The PSYNTH estimator always resulted in much smaller estiamtion errors compared to PSMALL and PSYNTH. This is because ...
-%
-% As obvious from figure \ref{fig:disterrors}, the error distribution of PSMALL and EXTPSYNTH were found to be very similar and suggested that the two estimator performed very similar.
-In section \ref{sec:comp}, we analysed the differences between the two estimators in more detail.
-%
-%The highest observed estimation error was 14\% for the SRS, PSMALL and EXTPSYNTH estimator.
-
-\newpage
 % ----------------------------------------------------------------------- %
@@
 
-As obvious from figure \ref{fig:disterrors}, the error distribution of \psmall{} and \extpsynth{} were found to be very similar, with \psmall{} showing marginally higher estimation errors.
+Figure \ref{fig:disterrors} revealed that the error distribution of \psmall{} and \extpsynth{} are very similar, with \psmall{} showing marginally higher estimation errors.
 In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (fig.
@@
 However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par
-
-%As obvious from figure \ref{fig:disterrors}, the error distribution of \psmall{} and \extpsynth{} were found to be very similar, with \psmall{} showing marginally higher estimation errors.
-Differences between the two estimators were expected to occur for the following reasons: 1) as depicted in \citet[pp.17--18]{mandallaz2016}, the mathematical formulations of the \psmall{} and \extpsynth{} estimator are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area.
-Therefore, differences between the estimators were particularly expected for small area units with low terrestrial sampling intensities.
-2) As addressed in section \ref{sec:extpsynth}, the case of one or more cluster not entirely being included in a small area unit would constitute a violation of the \extpsynth{} estimator.
-Effects of this violation on the estimates had yet not been investigated and also lead to a divergence between \psmall{} and \extpsynth{}.\par
-%
-%In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (fig.
-\ref{fig:compvar}, left).
-As obvious, \psmall{} yielded slightly larger variances for the vast majority of the estimates.
-A violation of the \extpsynth{} assumption by one or more cluster not entirely included in a small area unit was observed in 155 of the 312 FR units (48\%).
-However, the affected FR units (depicted in red color, fig.
-\ref{fig:compvar}) did not show a significant divergence from the \psmall{} variances with respect to the remaining unaffected FR units.
-An additional comparison of the absolute differences in the g-weight variance (fig.
-\ref{fig:compvar}, right) revealed that large differences particularly occurred for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$).
-The differences decreased with increasing sample size and thus confirmed the asymptotic relationship between the two estimators.
-A comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par
 
@@
 
-\newpage
+% \newpage
 % ----------------------------------------------------------------------- %
 % ----------------------------------------------------------------------- %
-\subsection{Reduction of variance by two-phase estimators}
-% \subsection{Variance reduction of SRS estimator}
+\subsection{Reduction of SRS variance by \psmall{} and \extpsynth{}}
 \label{sec:gain_eval}
+
+We further evaluated how much the variance of the SRS estimator in each FA and FR unit was reduced by alternative application of the \psmall{} and \extpsynth{} estimator.
+For all FA-units, the application of \psmall{} and \extpsynth{} led to a reduction of the SRS variance that was up to 54.1\% and 49.7\% in 75\% of the FA-units (fig.
+\ref{fig:gain}).
+The differences between \psmall{} and \extpsynth{} were again due to the slightly smaller variances produced by the \extpsynth{} estimator.
+The reduction in variance was also expressed in the relative efficiency, which was 2.02 on average and ranged between 1.18 and 4.13 for the \extpsynth{} estimator.
+On FR-level, the achieved reduction in variance and the relative efficiencies reached even higher values than on FA-level (table \ref{tab:gain}).
+However, cases also occurred where one or both two-phase estimators produced partly substantially larger variance values than under the SRS estimator.
+This particularly happened in 18\% (61) of the FR-units under the \extpsynth{}, and in 23\% (76) of the FR-units under the \psmall{} estimator.
 
@@
 
+\begin{table}[H]
+	\begin{center}
+		\caption{Descriptive summary of SRS variance reduction and relative efficiencies on the two forest district levels. $N_u$: number of evaluated small area units.}
+		\vspace{0.2cm}
+		\label{tab:gain}
+		{\small %
+			\begin{tabular}{c|l c|c|c|c|c|c|c} %8cols
+				\hlineB{1}
+				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Reduction of SRS variance [\%]} & \multicolumn{3}{c}{relative efficiency} \\
+				\cline{4-9} & & & mean & min & max & mean & min & max \\
+				\hline \hline
+				\multirow{2}{*}{FA} & PSMALL    & ($N_u$=45)  & 33.51 & 0 & 72.5 & 1.74 & 1.03 & 3.64 \\
+				& EXTPSYNTH & ($N_u$=45)  & 43.30 & 0 & 75.8 & 2.03  & 1.18 & 4.13 \\
+				\hlineB{2}          
+				\multirow{2}{*}{FR} & PSMALL    & ($N_u$=321) & 12.48 & 0 & 96.8 & 2.54 & 0.08 & 31.61  \\
+				& EXTPSYNTH & ($N_u$=321) & 24.75 & 0 & 97.0 & 2.95 & 0.10 & 33.70 \\
+				\hline \hline
+			\end{tabular}
+		}%
+	\end{center}
+\end{table}
+
+Here comes some detective work ...
+
 \begin{figure}[H]
@@
 \end{figure}
-
-%% NOTES:
-% - 
-%
-%
-%
-%
-%
-%
-%

### 2018-02-04 Draft_Form/tex/Results.tex
update 04_02_2018
update 04_02_2018

@@
 An application of the SRS, \psmall{} and \extpsynth{} estimator was not feasible for 17 of all 405 FR-units due to an insufficient terrestrial sample size of $n_{2,G} < 2$.
-We further restricted the calculation of \psmall{} and \extpsynth{} to small area units with a minimum terrestrial sample size of $n_{2,G} \geq 4$ to avoid unstable estimates.
+We further restricted the calculation of \psmall{} and \extpsynth{} estimator to small area units with a minimum terrestrial sample size of $n_{2,G} \geq 4$ to avoid unstable estimates.
 This affected 65 additional FR units and limited unbiased two-phase estimations to 321 (79\%) of the 405 FR units.
-It should be noted that also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 1$.
+It should be noted that also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 2$.
 Due to substantial larger sample sizes, all estimators could however be applied in all small area units on the FA level.
 The average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (table \ref{tab:estres}).
-An additional pairwise comparison of the 95\% confidence intervals for all FA- and FR-units revealed that the four estimators did in fact not produce statistically different point estimates.
+An additional pairwise comparison of the 95\% confidence intervals revealed that the four estimators did in fact not produce statistically different point estimates for all FA and FR units.
 This confirmed that the differences between the estimators are solely found in the precision which they provide for the point estimates.
@@
 \ref{fig:disterrors}, left) reveals that under the SRS estimator, errors $\leq$ 5\% were achieved for 17\% of the FA units (8 of 45).
-This proportion could be increased to 62\% (28 FA units) and 73\% (33 FA units) by application of \psmall{} and \extpsynth{}.
+This proportion could be increased to 62\% (28 FA units) and 73\% (33 FA units) by application of the \psmall{} and \extpsynth{} estimator.
 95\% of all estimates exhibited errors $\leq$ 9.5\% under the SRS estimator and $\leq$ 6.6\% when using \psmall{} or \extpsynth{}.
-Estimation errors higher than 10\% only appeared twice for each of the unbiased estimators.\par
-The error reduction by the unbiased double sampling estimators was even more pronounced on the FR level (fig.
+Estimation errors higher than 10\% only appeared twice for each of the three estimators.\par
+The error reduction by the \psmall{} and \extpsynth{} estimator was even more pronounced on the FR level (fig.
 \ref{fig:disterrors}, right), although the overall error niveau was substantially higher than on FA level.
 The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under the \psmall{} and \extpsynth{} estimator (table \ref{tab:estres}).
-Errors smaller than 10\% were achieved in 15\% by the SRS estimator and 46\% by the \psmall{} and \psynth{} estimator.
+Errors smaller than 10\% were achieved for 15\% of the FR units by the SRS estimator, and for 46\% by the \psmall{} and \psynth{} estimator.
 95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors $\leq$ 20\%.
@@
 This was as expected, since the \psynth{} variance estimate does not take the residual variation in each small area unit into account (section \ref{sec:psynth}).
-Compared to the error distribution of the asymptotically design-unbiased estimators \psmall{} and \extpsynth{}, the estimation errors of \psynth{} might thus be to optimistic.
+Compared to the asymptotically design-unbiased estimators \psmall{} and \extpsynth{}, the estimation errors produced by \psynth{} seem to be too optimistic.
+One should also recall that the estimates of the \psynth{} estimator are potentially design-biased.
 
@@
 
-Figure \ref{fig:disterrors} revealed that the error distribution of \psmall{} and \extpsynth{} are very similar, with \psmall{} showing marginally higher estimation errors.
+Figure \ref{fig:disterrors} reveals that the error distribution of \psmall{} and \extpsynth{} are very similar, with \psmall{} showing marginally higher estimation errors.
 In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (fig.
@@
 This violation was actually observed in 155 of the 321 FR units (48\%).
-However, the affected FR units (depicted in red color, fig.
+However, the affected FR units (depicted in red diamonds, fig.
 \ref{fig:compvar}) did not show a significant divergence from the \psmall{} variances with respect to the remaining unaffected FR units.
-The variance differences between the two estimators were expected to occur for the following reason: as depicted in \citet[pp.17--18]{mandallaz2016}, the mathematical formulations of the \psmall{} and \extpsynth{} estimator are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area.
+The variance differences between the two estimators were thus due to the mathematical formulations of the \psmall{} and \extpsynth{} estimator, which are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area \citep[pp.17--18]{mandallaz2016}.
 An additional comparison of the absolute differences in the g-weight variance (fig.
-\ref{fig:compvar}, right) revealed that large differences did in fact particularly occur for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$).
+\ref{fig:compvar}, right) revealed that large divergences did in fact particularly occur for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$).
 The differences decreased with increasing sample size and thus confirmed the asymptotic relationship between the two estimators.
-However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par
+However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.
+The results indicate that the adjustment of the intercept term of the \extpsynth{} estimator to the data within a small area will in general yield slightly smaller variances than the \psmall{} estimator.\par
 
@@
 
-% \newpage
 % ----------------------------------------------------------------------- %
 % ----------------------------------------------------------------------- %
-\subsection{Reduction of SRS variance by \psmall{} and \extpsynth{}}
+\subsection{Reduction of SRS variance by double sampling procedure}
 \label{sec:gain_eval}
 
-We further evaluated how much the variance of the SRS estimator in each FA and FR unit was reduced by alternative application of the \psmall{} and \extpsynth{} estimator.
-For all FA-units, the application of \psmall{} and \extpsynth{} led to a reduction of the SRS variance that was up to 54.1\% and 49.7\% in 75\% of the FA-units (fig.
+A direct comparison of the achieved variances within the small area units revealed that the application of the design-unbiased estimators (\psmall{} and \extpsynth{}) led to a reduction of the SRS variance in all FA units.
+In 75\% of the FA units, the \extpsynth{} estimator was able to reduce the SRS variance by up to 54.1\% (fig.
 \ref{fig:gain}).
-The differences between \psmall{} and \extpsynth{} were again due to the slightly smaller variances produced by the \extpsynth{} estimator.
-The reduction in variance was also expressed in the relative efficiency, which was 2.02 on average and ranged between 1.18 and 4.13 for the \extpsynth{} estimator.
-On FR-level, the achieved reduction in variance and the relative efficiencies reached even higher values than on FA-level (table \ref{tab:gain}).
-However, cases also occurred where one or both two-phase estimators produced partly substantially larger variance values than under the SRS estimator.
-This particularly happened in 18\% (61) of the FR-units under the \extpsynth{}, and in 23\% (76) of the FR-units under the \psmall{} estimator.
+The reduction in variance was also expressed in the relative efficiency values, which were 2.02 on average and ranged between 1.18 and 4.13 on the FA level.
+On FR-level, the achieved reduction in variance and the relative efficiencies reached even higher values (table \ref{tab:gain}).
+The \psmall{} estimator again yielded slightly lower variance reductions and relative efficiencies due to the smaller variances produced by the \extpsynth{} estimator (section \ref{sec:comp}).
+However, cases also occurred where one or both two-phase estimators produced substantially larger variance values than under the SRS estimator.
+This particularly happened in 19\% (61) of the FR units under the \extpsynth{}, and in 24\% (76) of the FR units under the \psmall{} estimator.
 
@@
 \end{figure}
+
+One possible reason for an increased variance by the two-phase estimators was supposed to be a poor performance of the regression model within the small area unit.
+In order to investigate this hypothesis, we analyzed the three variance terms of the  \psmall{} estimator (eq.
+\ref{eq:psmall_var}), i.e.
+the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residuals that expresses the model performance within the small area (term 3).
+Figure \ref{fig:fail1} illustrates the reduction or increase of the SRS variance for all FR units in dependence of the proportion of the residual variance term (term 3) on the g-weight variance.
+Two issues become obvious: firstly, the residual term generally constitutes the dominating part of the g-weight variance (around 84\% on average).
+FR units for which the \psmall{} estimator produced an increase of the SRS variance did not differ distinctly from the pattern of the remaining FR units.
+The same was also found when looking at the absolute residual terms (fig.
+\ref{fig:fail2}).
+Secondly, FR units with the highest increases of the SRS variance were particularly observed under small terrestrial sample sizes $n_{2,G} = 4$.
+The average increase in variance for $n_{2,G} = 4$ was 272\% compared to 62\% for $n_{2,G} > 4$.
+In comparison, the average reduction in SRS variances was around 50\% for both sampling sizes $n_{2,G} = 4$ and $n_{2,G} > 4$.
+These findings suggest that moderate or poor model fits within a small area can cause the \psmall{} and \extpsynth{} estimator to produce higher variances than the SRS estimator particularly under small terrestrial sample sizes.
+However, small terrestrial sample sizes can also have the effect that the SRS estimator might not reflect the actual variation of the local density within a small area.
+In this case, the two-phase variance estimate might be larger but more realistic.
+Whereas a visual analysis of aerial images, remote sensing data or stand maps might give some evidence for this hypothesis, a definite proof is practically infeasible.
 
@@
 				\hline \hline
-				\multirow{2}{*}{FA} & PSMALL    & ($N_u$=45)  & 33.51 & 0 & 72.5 & 1.74 & 1.03 & 3.64 \\
-				& EXTPSYNTH & ($N_u$=45)  & 43.30 & 0 & 75.8 & 2.03  & 1.18 & 4.13 \\
+				\multirow{2}{*}{FA} & PSMALL    & ($N_u$=45)  & 33.51 &  2.6 & 72.5 & 1.74 & 1.03 & 3.64 \\
+				                    & EXTPSYNTH & ($N_u$=45)  & 43.30 & 15.7 & 75.8 & 2.03  & 1.18 & 4.13 \\
 				\hlineB{2}          
-				\multirow{2}{*}{FR} & PSMALL    & ($N_u$=321) & 12.48 & 0 & 96.8 & 2.54 & 0.08 & 31.61  \\
-				& EXTPSYNTH & ($N_u$=321) & 24.75 & 0 & 97.0 & 2.95 & 0.10 & 33.70 \\
+				\multirow{2}{*}{FR} & PSMALL    & ($N_u$=321) & 12.48 & -1203.9 & 96.8 & 2.54 & 0.08 & 31.61  \\
+				                    & EXTPSYNTH & ($N_u$=321) & 24.75 & -892.7  & 97.0 & 2.95 & 0.10 & 33.70 \\
 				\hline \hline
@@
 
-Here comes some detective work ...
+\begin{figure}[H]
+	\centering
+	\resizebox{0.8\hsize}{!}{\includegraphics{fig/eval_2phase_fail_1.png}}
+	\caption{}
+	\label{fig:fail1}
+\end{figure}
 
@@
 	\centering
-	\resizebox{0.7\hsize}{!}{\includegraphics{fig/eval_2phase_fail.png}}
+	\resizebox{0.8\hsize}{!}{\includegraphics{fig/eval_2phase_fail_2.png}}
 	\caption{}
-	\label{fig:fail}
+	\label{fig:fail2}
 \end{figure}

### 2018-02-05 Draft_Form/tex/Results.tex
update 05_02_2018
update 05_02_2018

@@
 An application of the SRS, \psmall{} and \extpsynth{} estimator was not feasible for 17 of all 405 FR-units due to an insufficient terrestrial sample size of $n_{2,G} < 2$.
-We further restricted the calculation of \psmall{} and \extpsynth{} estimator to small area units with a minimum terrestrial sample size of $n_{2,G} \geq 4$ to avoid unstable estimates.
+We further restricted the calculation of the \psmall{} and \extpsynth{} estimator to small area units with a minimum terrestrial sample size of $n_{2,G} \geq 4$ to avoid unstable estimates.
 This affected 65 additional FR units and limited unbiased two-phase estimations to 321 (79\%) of the 405 FR units.
 It should be noted that also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 2$.
-Due to substantial larger sample sizes, all estimators could however be applied in all small area units on the FA level.
+Due to substantial larger sample sizes, all estimators could however be applied to all 45 FA units.
 The average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (table \ref{tab:estres}).
@@
 This was as expected, since the \psynth{} variance estimate does not take the residual variation in each small area unit into account (section \ref{sec:psynth}).
-Compared to the asymptotically design-unbiased estimators \psmall{} and \extpsynth{}, the estimation errors produced by \psynth{} seem to be too optimistic.
+Compared to the asymptotically design-unbiased estimators \psmall{} and \extpsynth{}, the estimation errors produced by \psynth{} thus seem to be too optimistic.
 One should also recall that the estimates of the \psynth{} estimator are potentially design-biased.
@@
 However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.
-The results indicate that the adjustment of the intercept term of the \extpsynth{} estimator to the data within a small area will in general yield slightly smaller variances than the \psmall{} estimator.\par
+The results indicate that the adjustment of the intercept term to the data within a small area used in the \extpsynth{} estimator will in general yield slightly smaller variances than the \psmall{} estimator.\par
 
@@
 % ----------------------------------------------------------------------- %
-\subsection{Reduction of SRS variance by double sampling procedure}
+\subsection{Reduction of SRS variance by \psmall{} and \extpsynth{}}
 \label{sec:gain_eval}
@@
 The reduction in variance was also expressed in the relative efficiency values, which were 2.02 on average and ranged between 1.18 and 4.13 on the FA level.
-On FR-level, the achieved reduction in variance and the relative efficiencies reached even higher values (table \ref{tab:gain}).
+On FR-level, the reduction in variance and the relative efficiencies reached even higher values (table \ref{tab:gain}).
 The \psmall{} estimator again yielded slightly lower variance reductions and relative efficiencies due to the smaller variances produced by the \extpsynth{} estimator (section \ref{sec:comp}).
-However, cases also occurred where one or both two-phase estimators produced substantially larger variance values than under the SRS estimator.
+However, cases also occurred on the FR level where one or both two-phase estimators produced larger variance values than under the SRS estimator.
 This particularly happened in 19\% (61) of the FR units under the \extpsynth{}, and in 24\% (76) of the FR units under the \psmall{} estimator.
@@
 the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residuals that expresses the model performance within the small area (term 3).
-Figure \ref{fig:fail1} illustrates the reduction or increase of the SRS variance for all FR units in dependence of the proportion of the residual variance term (term 3) on the g-weight variance.
-Two issues become obvious: firstly, the residual term generally constitutes the dominating part of the g-weight variance (around 84\% on average).
-FR units for which the \psmall{} estimator produced an increase of the SRS variance did not differ distinctly from the pattern of the remaining FR units.
-The same was also found when looking at the absolute residual terms (fig.
+Figure \ref{fig:fail1} illustrates the reduction or increase of the SRS variance by \psmall{} for all FR units in dependence of the residual variance term proportion on the g-weight variance.
+Two issues become obvious: firstly, the residual term generally constitutes the dominating part of the g-weight variance for all \psmall{} estimates (around 84\% on average).
+FR units for which the \psmall{} estimator produced larger variances than the SRS estimator did not differ distinctly from the pattern of the remaining FR units.
+The same was also found when looking at the absolute residual term values (fig.
 \ref{fig:fail2}).
-Secondly, FR units with the highest increases of the SRS variance were particularly observed under small terrestrial sample sizes $n_{2,G} = 4$.
+Secondly, FR units with the highest variance increases compared to SRS were particularly observed under small terrestrial sample sizes $n_{2,G} = 4$.
 The average increase in variance for $n_{2,G} = 4$ was 272\% compared to 62\% for $n_{2,G} > 4$.

### 2018-02-06 Draft_Form/tab/modacc_modterms.tex
update 06_02_2018
update 06_02_2018

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Sun Jan 07 17:11:26 2018
\begin{table*}[!htbp]
	\begin{center}
	\caption{Accuracy metrics for submodels of final OLS regression model. Interaction terms are indicated by ':'. () give the respective values on the cluster level.} 
	\label{tab:modacc_modterms}
    {\small %
	\begin{tabular}{llccc}
  \hline
model terms & model & $R^2_{adj}$ & $RMSE_{cv}$ & $RMSE_{cv}\%$ \\ 
  \hline
meanheight + stddev + meanheight$^2$ +  & full model &  0.48 & 140.62  & 46.69 \\
treespecies + ALSyear + & & (0.53) &  (101.61) & (33.57) \\ 
meanheight:treespecies + \\ meanheight:ALSyear + meanheight:stddev + \\ stddev:ALSyear &&& \\ \\
meanheight + stddev + meanheight$^2$ + & reduced model  & 0.45  & 145.62 & 48.35 \\
ALSyear + meanheight:ALSyear + & & (0.49) & (106.08) & (35.40) \\
meanheight:stddev + stddev:ALSyear &&& \\ \\
\hline
\hline
\end{tabular}
}%
\end{center}
\end{table*}
%\endgroup

### 2018-02-07 Draft_Form/tex/Introduction(2).tex
update 07_02_2018
update 07_02_2018

@@
 The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a, mandallaz2013b}.
-Auxiliary data were obtained from a countrywide airborne Laser scanning (LiDAR) canopy height model (CHM) and a tree species classification map and used for regression within tree species strata.
+Auxiliary data were obtained from a countrywide airborne Laser scanning (ALS) canopy height model (CHM) and a tree species classification map and used for regression within tree species strata.
 The estimation accuracies were compared to those achieved under SRS sampling.
-The chosen double-sampling estimators were favoured for several reasons: \textbf{(i)} the design-based frame considerably relaxes requirements on the regression model which seemed appropriate facing severe quality restrictions in the LiDAR data; \textbf{(ii)} the estimators can consider \textit{non-exhaustive}, i.e.
+The chosen double-sampling estimators were favoured for several reasons: \textbf{(i)} the design-based frame considerably relaxes requirements on the regression model which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can consider \textit{non-exhaustive}, i.e.
 non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for the design-dependency of the regression coefficients on the sample (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals.\par

### 2018-02-07 Draft_Form/tex/Materials_and_Methods(2).tex
update 03_02_2018
update 03_02_2018
update 05_02_2018
update 05_02_2018
update 06_02_2018
update 06_02_2018
update 07_02_2018
update 07_02_2018

@@
 
-\newpage
+% \newpage
 
@@
 \begin{equation}\label{estvarcovaux_G}
-\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}} = \frac{1}{n_{1,G}(n_{1,G}-1)} \sum_{i \in s_{1,G}} \big(\frac{M_{G}(x)}{\bar{M}_{1,G}}\big)^2 (\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})(\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})^{\top}
+\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}} = \frac{1}{n_{1,G}(n_{1,G}-1)} \sum_{x \in s_{1,G}} \big(\frac{M_{G}(x)}{\bar{M}_{1,G}}\big)^2 (\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})(\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})^{\top}
 \end{equation}
 
-with $\bar{M}_{1,G}=\frac{\sum_{i \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.\\
+with $\bar{M}_{1,G}=\frac{\sum_{x \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.\\
 
@@
 	\centering
-	\resizebox{0.8\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
+	\resizebox{0.85\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
 	\caption{\textit{Left}: Study Area with delineated FA forest management units.
@@
 \subsection{Extension to double sampling design}
+\label{ext_to_2phase}
 
@@
 % ----------------------------------------------------------------------- %
-\subsection{Auxiliary information}
+\subsection{Auxiliary data}
 \label{sec:auxinfo}
@@
 
-A prerequisite for the application of the suggested two-phase small area estimators was the identification of suitable auxiliary information that is available over the entire study area.
-Between the year 2003 and 2013, the topographic survey institution of RLP conducted an airborne laser scanning (LiDAR) acquisition over the entire federal state at leaf-off condition in order to derive a countrywide digital terrain and surface model.
+A prerequisite for the application of the suggested two-phase small area estimators was the identification of suitable auxiliary data available over the entire study area.
+Between the year 2003 and 2013, the topographic survey institution of RLP conducted an airborne laser scanning (ALS) acquisition over the entire federal state at leaf-off condition in order to derive a countrywide digital terrain and surface model.
 For this study, the recorded LiDAR data was used to create a canopy height model (CHM) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters (Figure \ref{fig:Auxvars}, \textit{top}).
-The CHM was calculated as the difference between the digital terrain model (DTM) and the digital surface model (DSM) that were derived by a Delauney interpolation of the two separated LiDAR point clouds (ground pulses and first pulses from non-ground objects).
-Based on numerous studies (e.g.
-\cite{maack2016}), the CHM was considered to provide the most valuable information to be used in the OLS regression model for predicting the timber volume on sample plot level.
-However, during the extended acquisition period, airborne laser scanning technology evolved significantly, which lead to severe quality variations in the CHM.
-In particular, the LiDAR acquisition recorded in 2002 and 2003 exhibited a rather poor quality with about only 1 point per 5x5 m$^2$, while more recently acquired datasets contained more than 125 points per 5x5 m$^2$ raster cell.
-Furthermore, due to sensor failures, CHM information was not available at 16 sample locations (none of them considered terrestrial sample plots of the $s_2$ phase though).
+The CHM (Fig.
+\ref{fig:Auxvars}, \textit{top}) was calculated as the difference between the digital terrain model (DTM) and the digital surface model (DSM) that were derived by a Delauney interpolation of the ground and first ALS pulses respectively.
+A more detailed description of the procedure can be found in \citet{hill2017a}.
+The CHM was considered to provide the most valuable information to be used in the OLS regression model for predicting the timber volume on sample plot and cluster level.
+However, the extended acquisition period of the ALS campaign led to substantial time gaps to the BWI3 survey of up to 10 years.
+In addition, the CHM exhibited severe quality variations in the CHM du to evolving ALS technology over the years.
+LiDAR acquisition recorded in 2002 and 2003 particularly showed a rather poor quality with about only 0.04 point per m$^2$, while more recently acquired datasets contained more than 5 points per m$^2$.
+Furthermore CHM information was not available at 16 sample locations due to sensor failures.
 These plots were deleted from the sampling frame and its non-available information thus treated as missing at random.
 This assumption was considered to be reasonable as the respective sample locations did not exclude specific forest structures.
-
-%As explanatory variables, the mean canopy height (\textit{meanheight}) and the standard deviation ($stddev$) were calculated as the mean and standard deviation of all raster values within a predefined square around each sample plot center.
-The square (i.e.
-\textit{support} of the explanatory variable, see section \ref{sec:supp}) was previously intersected with the state and communal forest area defined by a polygon mask and thereby corrected for edge effects at the forest border.
-The tree height is one prominent predictor variable in the taper functions of the \bwi{} that are used to calculate a timber volume value for each sample tree \citep{kublin2003, kublin2013}.
-A visual inspection of the tree volumes of all sample trees collected in the \bwi{} within RLP against their tree heights also revealed the characteristic shape of an allometric relationship between these variables (Online Resource 1).
-It was hypothesized that this relationship on single-tree level is also apparent on the aggregated level of a sample plot and cluster, and can be used within the frame of regression modeling.\par
-%
-%The strength of correlation between \textit{meanheight} and timber volume on plot level was expected to show high variation according to the mentioned time-lag up to 10 years between LiDAR acquisition and terrestrial survey.
-The quality of the height information was also expected to vary according to changing sensor technologies and different point densities used over the years.
-For these reasons, the LiDAR acquisition year (\textit{lidaryear}) for each sample plot was considered as a potential categorical explanatory variable to explain the variation in the data introduced by these factors.
-For this purpose, the acquisition year \textit{2008} was further divided into \textit{2008} and \textit{2008\_1}.
-In the latter, the data quality turned out to be very poor due to sensor failures during the acquisition.
-Additionally, the years \textit{2006} and \textit{2007} as well as \textit{2012} and \textit{2013} were pooled in order to increase the number of observations per factor level for modelling reasons.
-As a result, the \textit{lidaryear} variable comprised nine categories (\textit{2002}, \textit{2003}, \textit{2007}, \textit{2008}, \textit{2008\_1}, \textit{2009}, \textit{2010}, \textit{2011} and \textit{2012}).
 
@@
 
-The second source of auxiliary information was a countrywide satellite-based classification map of the five main tree species (European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir, Scots pine) described in \citet{stoffels2015} (Figure \ref{fig:Auxvars}, \textit{bottom}).
-The classified tree species map has a grid size of 5 meters and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) by application of a spatially adaptive classification algorithm described in \citet{stoffels2012}.
-As timber volume estimations on the tree level are often based on species-specific biomass and volume equations, the use of tree species information - especially for timber volume estimation - has often been stated as a key factor for improving the estimation precision \cite{white2016}.
-In this respect, incorporating the tree species map information was particularly attractive as it predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree.
-However, due to unavailable satellite data for the classification, the tree species map excluded one large patch with an area of 415 km$^2$ in the south-west part of RLP covering an entire FA-unit (10 FR units respectively).
+Additional auxiliary data was derived from a countrywide satellite-based classification map predicting the five main tree species \citep{stoffels2015}, i.e.
+European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir and Scots pine (Fig.
+\ref{fig:Auxvars}, \textit{bottom}).
+The tree species map has a grid size of 5 meters and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) by application of a spatially adaptive classification algorithm \citep{stoffels2012}.
+As timber volume estimations on the tree level are often based on species-specific biomass and volume equations, the use of tree species information has often been stated as a key factor for improving the precision of timber volume estimates \cite{white2016}.
+In this respect, incorporating the tree species map was particularly attractive as it predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree.
+However, due to unavailable satellite data, the tree species map excluded one large patch with an area of 415 km$^2$ in the south-west part of RLP covering an entire FA unit (10 FR units respectively).
 In 9 additional FR units, the tree species information was also missing for a subset of the sample locations due to two additional patches with an area of 76 km$^2$ and 100 km$^2$ in the northern part of RLP.
-For these parts, small area estimation was thus restricted to using only the available CHM information in the regression model.
-With respect to model fitting, the tree species information was missing for 407 (7\%) of the 5791 sample locations.
-A summary of the sample sizes and missing auxiliary information is again provided in Table \ref{tab:ssize}.
+For these 19 FR units, small area estimation was thus restricted to using only the available CHM information in the regression model.
+With respect to fitting the internal model for estimation, the tree species information was missing for 411 (7\%) of the 5791 sample locations.
+A summary of the sample sizes and missing auxiliary data for both the CHM and the tree species map is provided in Table \ref{tab:ssize}.
 
@@
 				\hline \hline
-				communal and state forest & 96'854 & 33'365 & 5791 & 2055\\ % <--
+				communal and state forest & 96'854 & 33'365 & 5791 & 2055\\
 				\hspace{5mm} \footnotesize missing CHM & \footnotesize 18 & \footnotesize 10 & \footnotesize 0 & \footnotesize 0\\ % <--
@@
 	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information.
-Right: Magnified illustration of the rectangular supports used to derive the explanatory variables from the auxiliary information.}
+Right: Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.}
 	\label{fig:Auxvars}
@@
 % ---------------------------------------------- %
-\subsection{Calculation of the auxiliary variables}
+\subsection{Calculation of the explanatory variables}
 \label{sec:expvarcalc}
 
-\subsubsection{LiDAR canopy height model}
+\subsubsection{ALS canopy height model}
 
-From the CHM, the mean canopy height (\textit{meanheight}) and the standard deviation (\textit{stddev}) was calculated by evaluating the raster values around each sample location within a predefined rectangular square (support) with a side length of 12 meters that was centered around the sample plot centers.
-Each support was previously intersected with the forest polygon layer in order to evaluate auxiliary information only within the forest definition.
-The percentage of the non-intersected support within the forest layer was used as the weight $w(x_l)$ introduced in  Eq.
-\ref{eq:Zc(x)}.
-Furthermore, the year of the LiDAR acquisition (\textit{lidaryear}) was derived as an additional categorical variable to account for the time-lag between the CHM information and the terrestrial survey as well as to explain heterogeneity in the data introduced by the varying LiDAR quality.
+Continuous explanatory variables derived from the CHM were the mean canopy height (\textit{meanheight}) and the standard deviation (\textit{stddev}).
+The quantities were calculated by evaluating the raster values around each sample location within a predefined circle (\textit{support}) with a radius of 12 meters.
+In order to correct for edge effects at the forest border, each support area was previously intersected with the state and communal forest area, which was defined by a polygon mask provided by the state forest service.
+The percentage of the support within the forest layer was used as the weight $w(x_l)$ introduced in Eq.
+\ref{eq:Zc(x)} in order to derive the weighted mean of the explanatory variables on the cluster level.
+Restricting the auxiliary data evaluation to the forest area was primarily a means to optimize the coherence between explanatory variables computed at the forest boundary and the corresponding local density, but also supports the consistency with the sampling frame (section \ref{ext_to_2phase}).
+In particular, the BWI3 survey applies an edge correction at the forest border at the individual tree level by intersection of the trees' inclusion circle with the forest border.
+An adjustment for the fact that part of a trees' inclusion circle is outside the forest area is then realized by increasing its counting factor, which would otherwise lead to an underestimation of the local density.
+Since the ALS height values will usually drop to around zero outside the forest area, neglecting the edge correction of the support attenuates the mean canopy height value towards zero and thus increases the discrepancy to the local density.\par
+We further derived the year of the ALS acquisition (\textit{ALSyear}) as an additional categorical variable which was used to account for the time-lag between the CHM information and the terrestrial survey as well as to explain heterogeneity in the data introduced by the varying ALS quality.
 Adjustments were made to the original acquisition years by introducing an additional factor level \textit{2008\_1} for a subset of the 2008 acquisition where the quality turned out to be considerably poor due to a sensor error.
@@
 
-The tree species map information was used to predict the main tree species of a sample plot (\textit{treespecies}).
+The tree species map information was used to predict the main tree species of the sample trees at each sample plot (\textit{treespecies}) as an additional categorical variable.
 This implied two consecutive processing steps.
-In the \textit{first} step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the same support as used for the CHM were classified as that species.
+In the \textit{first} step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the edge-corrected support were classified as that species.
 Otherwise, the sample location was assigned the value 'mixed'.
-It should be mentioned that the support size and the percentage threshold are parameters that can be optimised in order to achieve the best variance decomposition and thus improvement in model accuracy when using the categorical \textit{treespecies} variable in a regression model.
-\citet{hill2017a} conducted a detailed analysis of how to optimally derive the auxiliary variables for the present data set and identified the above described settings as the most suitable.
-It was additionally shown that using the random forest algorithm by \citet{breiman2001} for a calibration of the predicted main plot species on the actual main taper-function species derived from the terrestrial inventory data could boost the classification accuracy in the classes \textit{Scots pine} and \textit{Douglas Fir}, which performed considerably worse than the remaining species (Table \ref{tab:classacc}).
-The calibration was able to considerably mitigate the effects of misclassification on the regression coefficients and thus allowed for an increase in model accuracy.
-In a \textit{second} step, we thus provided the random forest algorithm in the statistical software R \citep{R} with the actual main taper-function species derived from the terrestrial inventory data as response variable as well as a full set of $p$ predictor variables that comprised the initial prediction of the main plot tree species (\textit{treespecies}), the mean canopy height (\textit{meanheight}) and standard deviation ($stddev$) derived from the CHM, the proportion of coniferous trees estimated from the tree species classification map ($prop.conif$) and the bioclimatic growing region ($wgb$) at the sample location.
-The algorithm was grown with 2000 trees, considering $\sqrt{p} \approx$ 3 of the predictors for each split.
-The resulting random forest model was consequently applied at all sample locations $s_1$ to provide the \textit{treespecies} variable.
+Likewise for the CHM variables, the support radius was 12 meters although the use of different support sizes for each explanatory variable would be in agreement with the two-phase estimators presented in section \ref{sec:SAestimators}.
+When using the \textit{treespecies} variable in a regression model, the support size and the percentage threshold particularly constitute parameters to be optimized in order to achieve an optimal variance decomposition of the data that subsequently leads to the best possible model accuracy.
+A detailed analysis and description of the optimal processing parameters for the explanatory variables of the present data set is provided in \citet{hill2017a}.
+In this study, the authors also applied a calibration model to the initially derived \textit{treespecies} variable that successfully removed the effects of misclassification errors on the regression model coefficients and increased the model accuracy.
+The calibration model consists of a decision tree from a random forest algorithm \citet{breiman2001} that was trained to predict the actual main plot tree species (known for all terrestrial plots) based on available auxiliary variables.
+These variables were the predicted \textit{treespecies} variable, the mean canopy height and standard deviation of the CHM, as well as the proportion of coniferous trees estimated from the classification map and the growing region derived from a polygon map.
+The algorithm was grown with 2000 trees considering $\sqrt{p} \approx$ 3 of the predictors for each split.
+In a \textit{second} step, we thus applied this calibration model to the \textit{treespecies} variable derived at all sample locations $s_1$.
+Table \ref{tab:classacc} gives the classification accuracies of the \textit{treespecies} variable before and after calibration.
 
@@
  {\small %
-	\begin{tabular}{c|c|c|c|c|c|c|c} %8cols
+	\begin{tabular}{l|c|c|c|c|c|c|c} %8cols
 		\hlineB{1}
@@
 
-% NOTES:
-% - model formulation was based on the following considerations: a) The mean canopy height has the heighest explanatory power.
-Since the strength of correlation between meanheight and the timber volume on plot level showed high variation according to the time-lag of up to 10 years between the LiDAR acquisition and the BWI3 terrestrial inventory.
-and the varying LiDAR quality, the
+The model selection constituted a major part of the current study, especially because several issues such as a) the heterogeneity in the remote sensing data, b) the identification of the optimal support sizes under angle count sampling and c) the incorporation of tree species information had to be addressed and investigated in order to identify the most accurate regression model realizable under the given data.
+We will here thus only provide a shortened summary of the extensive analysis carried out and refer to the study of \citet{hill2017a} if the reader is interested in more detailed information on the subjects.\par
+
+The model with highest \adjrsq{} and lowest RMSE was achieved with the variables \meanheight{}, \meanheight{}$^2$, \stddev{} and \alsyear{} from the ALS data as well as the \treespecies{} variable from the classification map as main effect terms.
+Additionally, interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{} , \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{} were included.
+The model yielded an \adjrsq{} of 0.48 and an RMSE of 140.62 \mha{} (46.7\%) on the plot level (table \ref{tab:modacc_modterms}, full model).
+While the study of \citet{hill2017a} only provide the model evaluations on the plot level, the two-phase estimators described in section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level.
+We thus re-evaluated the model as used in the estimators also on the cluster level and found the model accuracies to be higher than on the plot level (\adjrsq{} of 0.53 and RMSE of 101.61 \mha{} and 33.6\%).
+A substantial improvement of the model accuracy was achieved by the stratification to ALS acquisition years, which otherwise considerably lowered the \adjrsq{} due to increased unexplained variation in the data.
+An additional evaluation of the model residuals within each ALS acquisition year stratum (table \ref{tab:adj_r2_within}) revealed that a) the model accuracy substantially varied between the strata and b) high \adjrsq{} values of 0.59 even up to 0.66 on the cluster level were particularly achieved in acquisition year strata close to the date of the terrestrial survey (2010--2012).
+This effect was substantially diminished when dropping the \alsyear{} variable from the model.\par
+
+As depicted in section \ref{sec:tspecclass}, the information of the tree species classification map was missing within 1 FA and 19 FR units.
+For these small area units, we applied the regression model without the \treespecies{} variable (table \ref{tab:modacc_modterms}, reduced model).
+However, the model accuracy of the full and reduced model were found to be very similar on both the plot and cluster level.
+We thus assumed that the application of the reduced model would not cause substantially larger estimation errors as compared to the full model and subsequently performed a joint evaluation of the estimation results in section \ref{sec:Res}.
+
+% Table 1:
+\input{tab/modacc_modterms.tex}
+
+Discuss outliers etc. here ...
+
+% Table 2:
+\input{tab/mod_r2_lyearstrata_table.tex}
+
+%% NOTES:
 %
+% - we will here thus only provide a shortened summary of the regression model and refer to the study of \citet{hill2017a} if the reader is interested in more detailed information on the subjects.
 %
+% - 
+% - differences: zero-plots included (basically, we here HAVE to use ALL plots for the regression model calibration --> because we use an internal model)
+%   --> comment on the (non) removal of outliers / leverage plots: see review-answers --> plots stay in dataset with exception of truly erroneous local density variables
+%       'plots kept in the sampling frame (i.e. they are used as x e s2 in the estimators) MUST also be kept in the modelling frame --> to insure the zero-mean-residual assumption'
+%       (important: also leverage plots or "outliers" might have a good reason to be kept in the sampling / modelling frame --> think of sherman tree)
 %
-%
-%
-
-% MENTION:
-% - objective: find regression model (formula) to be applied in the sae estimators
-% - Specialty here: in the sae estimators, the predictions are generated on the cluster level (thus the regression coefficients are found on the cluster level)
-%   (--> and even more important: the residuals considered in the variance est. are also on the cluster level)
-%  ==> so for model selection, we looked at the global model performance on the plot as well as the cluster level
-%  ==> we also performed individual paramater t-test for each variable on the plot and cluster level. In order to  
-%
-% - important to recall that the design-based estimators, in which the regression model is used, do not impose any assumptions on the regression model as is the case in the model-dependent estimation framework.
-%
-% - no terrestrial data removed from the dataset for modelling, as all terrestrial data are used in the internal model (no choice, its specified by the estimators) 
-%
-% - mention sample sizes here: Due to missingness in the rs-data, the auxiliary variables were calculated for 89'930 sample plots (5384 terrestrial ...)
-%
-% - Model Validation (compare several models in table --> Alex)
-%
-% - Design-based Model Inference (new, use design-based var-covar-matrix)
-%
-% - idea: make a design-based inference of the regression coefficients on cluster level on the robust reg.coef-matrix
-%   "whereas the regression analysis in hill et al. 2017a" was carried out on the sample plot level, we here extend
-%    the analysis to the cluster level, as this is actually the level the estimators use the regression model predictions"
-%
-
-% ---------------------------------------------- %
-\subsubsection{Design-Based Model Inference}
-\label{sec:edbinf}
+% for discussion: better than removing plots would be the the use of disturbance classes (Massey --> change estimation) in order to decrease the impact on plots where major cuttings took place
+% between the ALS acquisition and the terrestrial survey. However, this is not possible if one height acquisition is available
 
 \newpage
-
 % ======================================================================================================================== %
@@
 %
+
+% NOTES:
+% - model formulation was based on the following considerations: a) The mean canopy height has the heighest explanatory power.
+Since the strength of correlation between meanheight and the timber volume on plot level showed high variation according to the time-lag of up to 10 years between the LiDAR acquisition and the BWI3 terrestrial inventory.
+and the varying LiDAR quality, the
+%
+%
+%
+%
+%
+
+% MENTION:
+% - objective: find regression model (formula) to be applied in the sae estimators
+% - Specialty here: in the sae estimators, the predictions are generated on the cluster level (thus the regression coefficients are found on the cluster level)
+%   (--> and even more important: the residuals considered in the variance est. are also on the cluster level)
+%  ==> so for model selection, we looked at the global model performance on the plot as well as the cluster level
+%  ==> we also performed individual paramater t-test for each variable on the plot and cluster level. In order to  
+%
+% - important to recall that the design-based estimators, in which the regression model is used, do not impose any assumptions on the regression model as is the case in the model-dependent estimation framework.
+%
+% - no terrestrial data removed from the dataset for modelling, as all terrestrial data are used in the internal model (no choice, its specified by the estimators) 
+%
+% - mention sample sizes here: Due to missingness in the rs-data, the auxiliary variables were calculated for 89'930 sample plots (5384 terrestrial ...)
+%
+% - Model Validation (compare several models in table --> Alex)
+%
+% - Design-based Model Inference (new, use design-based var-covar-matrix)
+%
+% - idea: make a design-based inference of the regression coefficients on cluster level on the robust reg.coef-matrix
+%   "whereas the regression analysis in hill et al. 2017a" was carried out on the sample plot level, we here extend
+%    the analysis to the cluster level, as this is actually the level the estimators use the regression model predictions"
+%
+
+% Feasibility: 
+% FA-level: for 44 out of 45 FA-units, the full model could be applied. For one remaining, only the model without tree species was applied.
+% FR-level: for xx out of the 405 FR-units, the full model could be applied. For one remaining, only the model without tree species was applied.
+%
+% ==> show specs for both regression models

### 2018-02-08 Draft_Form/tab/modacc_modterms.tex
update 07_02_2018
update 07_02_2018
update_08_02_2018
update_08_02_2018

@@
 	\begin{center}
-	\caption{Accuracy metrics for submodels of final OLS regression model. Interaction terms are indicated by ':'. () give the respective values on the cluster level.} 
+	\caption{Accuracy metrics for the two OLS regression models. Interaction terms are indicated by ':'. () give the respective values on the cluster level.} 
 	\label{tab:modacc_modterms}
@@
   \hline
-model terms & model & $R^2_{adj}$ & $RMSE_{cv}$ & $RMSE_{cv}\%$ \\ 
+model terms & model & $R^2_{adj}$ & RMSE & RMSE\% \\ 
   \hline
-meanheight + stddev + meanheight$^2$ +  & full model &  0.48 & 140.62  & 46.69 \\
+meanheight + stddev + meanheight$^2$ +  & full model &  0.48 & 139.22  & 45.98 \\
 treespecies + ALSyear + & & (0.53) &  (101.61) & (33.57) \\ 
 meanheight:treespecies + \\ meanheight:ALSyear + meanheight:stddev + \\ stddev:ALSyear &&& \\ \\
-meanheight + stddev + meanheight$^2$ + & reduced model  & 0.45  & 145.62 & 48.35 \\
+
+meanheight + stddev + meanheight$^2$ + & reduced model  & 0.45  & 144.13 & 47.60 \\
 ALSyear + meanheight:ALSyear + & & (0.49) & (106.08) & (35.40) \\

### 2018-02-08 Draft_Form/tex/Materials_and_Methods(2).tex
update_08_02_2018
update_08_02_2018

@@
 \subsubsection{Pseudo Small Area Estimator (\psmall{})}
+\label{sec:psmall}
 % \textbf{Pseudo Small Area Estimator (\psmall{})}\\
@@
 
-The model selection constituted a major part of the current study, especially because several issues such as a) the heterogeneity in the remote sensing data, b) the identification of the optimal support sizes under angle count sampling and c) the incorporation of tree species information had to be addressed and investigated in order to identify the most accurate regression model realizable under the given data.
+The model selection constituted a major part of the current study, especially because sophisticated challenges such as a) the heterogeneity in the remote sensing data, b) the identification of the optimal support sizes under angle count sampling and c) the incorporation of tree species information had to be addressed and investigated in order to identify the most accurate regression model realizable under the given data.
 We will here thus only provide a shortened summary of the extensive analysis carried out and refer to the study of \citet{hill2017a} if the reader is interested in more detailed information on the subjects.\par
 
-The model with highest \adjrsq{} and lowest RMSE was achieved with the variables \meanheight{}, \meanheight{}$^2$, \stddev{} and \alsyear{} from the ALS data as well as the \treespecies{} variable from the classification map as main effect terms.
+The model with highest \adjrsq{} and lowest RMSE was achieved with the variables \meanheight{}, \meanheight{}$^2$, \stddev{} and \alsyear{} derived from the ALS data as well as the \treespecies{} variable derived from the classification map as main effect terms.
 Additionally, interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{} , \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{} were included.
@@
 We thus re-evaluated the model as used in the estimators also on the cluster level and found the model accuracies to be higher than on the plot level (\adjrsq{} of 0.53 and RMSE of 101.61 \mha{} and 33.6\%).
-A substantial improvement of the model accuracy was achieved by the stratification to ALS acquisition years, which otherwise considerably lowered the \adjrsq{} due to increased unexplained variation in the data.
-An additional evaluation of the model residuals within each ALS acquisition year stratum (table \ref{tab:adj_r2_within}) revealed that a) the model accuracy substantially varied between the strata and b) high \adjrsq{} values of 0.59 even up to 0.66 on the cluster level were particularly achieved in acquisition year strata close to the date of the terrestrial survey (2010--2012).
-This effect was substantially diminished when dropping the \alsyear{} variable from the model.\par
+A stratification to the ALS acquisition years substantially improved the model accuracy and thus proved to be an effective means in accounting for the artificially introduced noise in the data set due to ALS quality variations and time-gaps between the ALS and the terrestrial survey.
+However, the stratification led to highly unbalanced datasets when stratifying according to the \treespecies{} variable.
+For this reason, a species individual modelling within each \alsyear{} stratum remained infeasible, but might have further improved the model accuracy.
+An additional evaluation of the model residuals within each ALS acquisition year stratum (table \ref{tab:adj_r2_within}) revealed that the model accuracies substantially varied between the strata (table \ref{tab:adj_r2_within}).
+\adjrsq{} values above the average  were particularly achieved in ALS acquisition years close to the terrestrial survey date (0.59 even up to 0.66 on the cluster level).
+This effect was substantially diminished when dropping the \alsyear{} variable from the model term.\par
 
@@
 
-Discuss outliers etc. here ...
+It should be mentioned that there is a major difference between the external and internal model approach concerning the treatment of outliers or leverage points for model fitting.
+In order to ensure the zero-mean-residual property of the \psmall{} and \extpsynth{} estimator under the internal model approach (section \ref{sec:psmall} and \ref{sec:extpsynth}), all observations of the terrestrial sample locations $x \in s_2$ used for estimation must also be included in the modelling frame.
+Excluding an observation from the model fit thus requires deleting it also from the sampling frame, which has to be regarded as an interference with the random sampling process the design-based inference relies on.
+For this reason, a removal of potential outliers or leverage points is, strictly speaking, only justified if the terrestrial response value or the explanatory variable value turns out to be truly erroneous (e.g.
+typos or erroneous measurements).
+If this is not the case, the removal of outliers or influential data points might increase the model fit, but to the cost of possible bias for the estimates (bias-variance trade-off).
+
+We conducted a leverage and outlier detection on the plot level for the full regression model applying the usual criteria of \textit{Leverages} and \textit{Cook's Distance} as amongst others described in \citet{fahrmeir2013}.
+The Cook's Distance values $D_i$ did not exceed a value of 0.019, and thus were far apart from the often cited critical threshold of $D_i > 0.5$.
+However, the critical threshold of $2p/n$ for the leverage values (i.e.
+twice the average of the hat matrix' diagonal entries) was exceeded by 10\% (568) of the (5377) observations.
+
+We conducted an Influence Analysis, i.e.
+leverage / outlier detection, for the 'final model'.
+We here considered the usually applied criteria of \textit{Leverages} and \textit{Cook's Distance} as amongst others described in Fahrmeir 2013 \{Regression: models, methods and applications.
+\textit{Springer Science \& Business Media}.
+page 164-167\}.
+The critical threshold of $2p/n$ (i.e.
+twice the average of the hat matrix' diagonal entries), was exceeded by 10\% of the observations.
+However, only 3\% of these leverage points were assigned to studentized residuals > 1 or < -1.
+Leaving these 3\% of points out and recalculating the final model lead to a $R^{2}_{adj}$ of 0.494 compared to 0.485 when including them in the regression.
+The Cook's Distance values $D_i$ did not exceed a value of 0.019, and thus were far apart from the often cited critical threshold of $D_i > 0.5$.
+Based on these findings, we decided not to remove observations from the modelling data set.
+We added a paragraph commenting on this issue of influential data points in section 3.3 'Final Regression Model', page 9 RHS line 690-707.
 
@@
 %
-% - we will here thus only provide a shortened summary of the regression model and refer to the study of \citet{hill2017a} if the reader is interested in more detailed information on the subjects.
-%
-% - 
-% - differences: zero-plots included (basically, we here HAVE to use ALL plots for the regression model calibration --> because we use an internal model)
+% - differences: zero-plots included !!! (basically, we here HAVE to use ALL plots for the regression model calibration --> because we use an internal model)
 %   --> comment on the (non) removal of outliers / leverage plots: see review-answers --> plots stay in dataset with exception of truly erroneous local density variables

### 2018-02-08 Draft_Form/tex/Materials_and_Methods(2).tex
update 08_02_2018(2)
update 08_02_2018(2)

@@
 		{\small %
-	\begin{tabular}{l|c|c|c|c|c|c|c} %8cols
+			\begin{tabular}{l|c|c|c|c} %8cols
 				\hlineB{1}
-		\multirow{2}{*}{Main plot species} & \multicolumn{2}{c|}{Producer's accuracy[\%]} & \multicolumn{2}{c|}{User's accuracy[\%]} & \multirow{2}{*}{nref} & \multicolumn{2}{c}{nclass} \\ 
-		\cline{2-3} \cline{4-5} \cline{7-8} & uncalib & calib & uncalib & calib & & uncalib & calib \\
+				Main plot species & Producer's accuracy[\%] & User's accuracy[\%] & nref & nclass \\
 				\hline \hline	
-		 Beech       & 29.56 & 22.31 & 46.11 & 47.02 & 883 & 566 & 419 \\
-		 Douglas Fir & 33.04 & 24.78 & 47.50 & 48.72 & 230 & 160 & 117 \\
-		 Oak         & 47.75 & 11.07 & 24.34 & 48.48 & 289 & 567 & 66 \\
-		 Spruce      & 43.63 & 53.15 & 60.81 & 61.13 & 651 & 467 & 566 \\
-		 Scots Pine  & 55.87 & 22.91 & 29.59 & 46.07 & 179 & 338 & 89 \\
-		 Mixed       & 66.40 & 84.49 & 63.69 & 64.53 & 3152 & 3286 & 4127 \\
+				Beech       & 22.31 & 47.02 & 883 & 419 \\
+				Douglas Fir & 24.78 & 48.72 & 230 & 117 \\
+				Oak         & 11.07 & 48.48 & 289 & 66 \\
+				Spruce      & 53.15 & 61.13 & 651 & 566 \\
+				Scots Pine  & 22.91 & 46.07 & 179 & 89 \\
+				Mixed       & 84.49 & 64.53 & 3152 & 4127 \\
 				\hline
-		 & \multicolumn{4}{l|}{Overall accuracy: 54.83\% (61.96\%)} & 5384 & \multicolumn{2}{c}{5384} \\
+				& \multicolumn{2}{l|}{Overall accuracy: 61.96\%} & 5384 & 5384 \\
 				\hline \hline
@@
 \end{table}
+
+%\begin{table}[H]
+%	\begin{center}
+%	\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
+%	\vspace{0.2cm}
+%	\label{tab:classacc}
+% {\small %
+%	\begin{tabular}{l|c c|c c|c|c c} %8cols
+%		\hlineB{1}
+%		\multirow{2}{*}{Main plot species} & \multicolumn{2}{c|}{Producer's accuracy[\%]} & \multicolumn{2}{c|}{User's accuracy[\%]} & \multirow{2}{*}{nref} & \multicolumn{2}{c}{nclass} \\ 
+%		\cline{2-3} \cline{4-5} \cline{7-8} & uncalib & calib & uncalib & calib & & uncalib & calib \\
+%		\hline \hline	
+%		 Beech       & 29.56 & 22.31 & 46.11 & 47.02 & 883 & 566 & 419 \\
+%		 Douglas Fir & 33.04 & 24.78 & 47.50 & 48.72 & 230 & 160 & 117 \\
+%		 Oak         & 47.75 & 11.07 & 24.34 & 48.48 & 289 & 567 & 66 \\
+%		 Spruce      & 43.63 & 53.15 & 60.81 & 61.13 & 651 & 467 & 566 \\
+%		 Scots Pine  & 55.87 & 22.91 & 29.59 & 46.07 & 179 & 338 & 89 \\
+%		 Mixed       & 66.40 & 84.49 & 63.69 & 64.53 & 3152 & 3286 & 4127 \\
+%		\hline
+%		 & \multicolumn{4}{l|}{Overall accuracy: 54.83\% (61.96\%)} & 5384 & \multicolumn{2}{c}{5384} \\
+%		 \hline \hline
+%	\end{tabular}
+%}%
+%	\end{center}
+%\end{table}
 
@@
 The model with highest \adjrsq{} and lowest RMSE was achieved with the variables \meanheight{}, \meanheight{}$^2$, \stddev{} and \alsyear{} derived from the ALS data as well as the \treespecies{} variable derived from the classification map as main effect terms.
-Additionally, interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{} , \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{} were included.
+Additionally, interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{}, \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{} were included.
 The model yielded an \adjrsq{} of 0.48 and an RMSE of 140.62 \mha{} (46.7\%) on the plot level (table \ref{tab:modacc_modterms}, full model).
@@
 A stratification to the ALS acquisition years substantially improved the model accuracy and thus proved to be an effective means in accounting for the artificially introduced noise in the data set due to ALS quality variations and time-gaps between the ALS and the terrestrial survey.
-However, the stratification led to highly unbalanced datasets when stratifying according to the \treespecies{} variable.
-For this reason, a species individual modelling within each \alsyear{} stratum remained infeasible, but might have further improved the model accuracy.
-An additional evaluation of the model residuals within each ALS acquisition year stratum (table \ref{tab:adj_r2_within}) revealed that the model accuracies substantially varied between the strata (table \ref{tab:adj_r2_within}).
-\adjrsq{} values above the average  were particularly achieved in ALS acquisition years close to the terrestrial survey date (0.59 even up to 0.66 on the cluster level).
+However, the stratification led to a highly unbalanced dataset when stratifying according to the \treespecies{} variable.
+For this reason, a species individual modeling within each \alsyear{} stratum remained infeasible, but might have further improved the model accuracy.
+An additional evaluation of the model residuals within each ALS acquisition year stratum revealed that the model accuracies substantially varied between the strata (table \ref{tab:adj_r2_within}).
+Values above the overall \adjrsq{} were particularly achieved in ALS acquisition years close to the terrestrial survey date (0.59 to 0.66 on the cluster level).
 This effect was substantially diminished when dropping the \alsyear{} variable from the model term.\par
@@
 
-It should be mentioned that there is a major difference between the external and internal model approach concerning the treatment of outliers or leverage points for model fitting.
-In order to ensure the zero-mean-residual property of the \psmall{} and \extpsynth{} estimator under the internal model approach (section \ref{sec:psmall} and \ref{sec:extpsynth}), all observations of the terrestrial sample locations $x \in s_2$ used for estimation must also be included in the modelling frame.
-Excluding an observation from the model fit thus requires deleting it also from the sampling frame, which has to be regarded as an interference with the random sampling process the design-based inference relies on.
+Concerning the treatment of outliers or leverage points for model fitting, it should be noted that there is a major difference between the external and internal model approach.
+In order to ensure the zero-mean-residual property of the \psmall{} and \extpsynth{} estimator under the internal model approach (section \ref{sec:psmall} and \ref{sec:extpsynth}), all observations of the terrestrial sample $s_2$ used for estimation must also be included in the modeling frame.
+Thus, excluding an observation from the model fit does also require its deletion from the sampling frame, which has to be regarded as an interference with the random sampling process the design-based inference relies on.
 For this reason, a removal of potential outliers or leverage points is, strictly speaking, only justified if the terrestrial response value or the explanatory variable value turns out to be truly erroneous (e.g.
-typos or erroneous measurements).
-If this is not the case, the removal of outliers or influential data points might increase the model fit, but to the cost of possible bias for the estimates (bias-variance trade-off).
+typos or measurement errors).
+If this is not the case, the removal of outliers or influential data points might increase the model fit, but to the cost of possible bias for the estimates.
+With respect to these considerations, we conducted an analysis of influential observations \citep[pp.
+160--167]{fahrmeir2013} on the plot level for the full regression model.
+In order to identify implausible observations in the explanatory data, we calculated the \textit{leverage} values and found that the critical threshold of $2p/n$ (i.e.
+twice the average of the hat matrix' diagonal entries) was exceeded by 10\% of all observations.
+Further investigation revealed that several leverage points showed unusually large \meanheight{} values associated to their respective timber volume density values.
+These implausible height values particularly occured in ALSyear acquisition years differing from the terrestrial survey date and were thus much more likely caused by harvesting activities in the sample plot area than erroneous ALS data.
+A deletion of these plots from the sampling frame was thus not justified due to the reasons given before.
+Also the remaining leverage points could not be definitely attributed to erroneous auxiliary data and were kept in the data set.
+The same was true for 10 observation with exceptionally large local density values that were identified as \textit{outliers}.
 
-We conducted a leverage and outlier detection on the plot level for the full regression model applying the usual criteria of \textit{Leverages} and \textit{Cook's Distance} as amongst others described in \citet{fahrmeir2013}.
-The Cook's Distance values $D_i$ did not exceed a value of 0.019, and thus were far apart from the often cited critical threshold of $D_i > 0.5$.
-However, the critical threshold of $2p/n$ for the leverage values (i.e.
-twice the average of the hat matrix' diagonal entries) was exceeded by 10\% (568) of the (5377) observations.
+% Table 2:
+\input{tab/mod_r2_lyearstrata_table.tex}
 
-We conducted an Influence Analysis, i.e.
+%% Notes on leverages:
+%
+% - 568 plots exceed the critical threshold of 2p/n
+% - 1/5 (20\%) 
+% - leverages that can indeed be assumed to have a significant influence on the regression coefficients particularly were 
+%   a) per se small \meanheight{} values associated to small timber volume densities
+%   b) unusually large \meanheight{} values associated to small timber volume values.
+These implausible height values particularly occured in ALSyear acquisition years differing from the terrestrial survey.
+These leverage points were thus much more likely caused by harvesting activities in the sample plot area than erroneous ALS data.
+A deletion of these plots from the sampling / modelling frame was thus not justified due to the reasons given before.
+However, fitting the model without these plots turned out not to have any influence on the regression coefficients and the overall model accuracy.
+
+% x-values at the boundaries (small and large values) usually have a high leverage. It does not mean that they are invalid / erroneous.
+
+%We conducted an Influence Analysis, i.e.
 leverage / outlier detection, for the 'final model'.
@@
 We added a paragraph commenting on this issue of influential data points in section 3.3 'Final Regression Model', page 9 RHS line 690-707.
-
-% Table 2:
-\input{tab/mod_r2_lyearstrata_table.tex}
 

### 2018-02-09 Draft_Form/tex/Acknowledgements.tex
update 09_02_2018
update 09_02_2018

@@
 \thispagestyle{plain}
-
-We want to express our gratitude to Prof. H. Heinimann (Chair of Land Use Engineering, ETH Zurich) for supporting this study.
-
-We want to explicitly thank Dr.
-Johannes Stoffels and Dr.
-Henning Buddenbaum from the Environmental Sensing and Geoinformatic Group of University of Trier for providing the LiDAR data and tree species classification map.
-
-Special gratitude is owed to the State Forest Service of Rhineland-Palatinate, in particular Jürgen Dietz and Claus-Andreas Lessander, for collaboration and providing the forest inventory- and geodata.
-
-We also want to thank Kai Husmann and Christoph Fischer from the Northwest German Forest Research Institution Göttingen for their advice in processing the terrestrial inventory data.
-
-% people to thank:
-% - H.R. Heinimann
-% - Johannes und Henning
-% - Thomas Riedel (Thuenen-Institute) for providing the densified sample grid
-% - Kai Husmann & Christoph Fischer
+We want to express our gratitude to Prof.
+H.
+Heinimann (Chair of Land Use Engineering, ETH Zurich) for supporting this study.
+We also want to explicitly thank Johannes Stoffels and Henning Buddenbaum from the Environmental Sensing and Geoinformatic Group of University of Trier for providing the ALS data and tree species classification map, and Kai Husmann and Christoph Fischer from the Northwest German Forest Research Institution Göttingen for their advice in processing the terrestrial inventory data.
+Special gratitude is also owed to Thomas Riedel from the Th{\"u}nen Institute for supporting this study and providing the densified NFI sample grid and Alexander Massey for proofreading.

### 2018-02-09 Draft_Form/tex/Results.tex
update 06_02_2018
update 06_02_2018
update 08_02_2018(2)
update 08_02_2018(2)
update 09_02_2018
update 09_02_2018

@@
 		{\small %
-			\begin{tabular}{c|l c|c|c|c|c|c|c} %8cols
+			\begin{tabular}{c|l c|c c c|c c c} %8cols
 				\hlineB{1}
@@
 
-A direct comparison of the achieved variances within the small area units revealed that the application of the design-unbiased estimators (\psmall{} and \extpsynth{}) led to a reduction of the SRS variance in all FA units.
+A direct comparison of the realized variances within the small area units revealed that the application of the design-unbiased estimators (\psmall{} and \extpsynth{}) led to a reduction of the respective SRS variance in all FA units.
 In 75\% of the FA units, the \extpsynth{} estimator was able to reduce the SRS variance by up to 54.1\% (fig.
@@
 The reduction in variance was also expressed in the relative efficiency values, which were 2.02 on average and ranged between 1.18 and 4.13 on the FA level.
-On FR-level, the reduction in variance and the relative efficiencies reached even higher values (table \ref{tab:gain}).
-The \psmall{} estimator again yielded slightly lower variance reductions and relative efficiencies due to the smaller variances produced by the \extpsynth{} estimator (section \ref{sec:comp}).
-However, cases also occurred on the FR level where one or both two-phase estimators produced larger variance values than under the SRS estimator.
-This particularly happened in 19\% (61) of the FR units under the \extpsynth{}, and in 24\% (76) of the FR units under the \psmall{} estimator.
+On FR-level, the reduction in variance and the relative efficiencies reached even higher values (table \ref{tab:gain} and fig.
+\ref{fig:gain}).
+The \psmall{} estimator again yielded slightly lower variance reductions and relative efficiencies due to the generally smaller variances of the \extpsynth{} estimator (section \ref{sec:comp}).
 
@@
 
-One possible reason for an increased variance by the two-phase estimators was supposed to be a poor performance of the regression model within the small area unit.
-In order to investigate this hypothesis, we analyzed the three variance terms of the  \psmall{} estimator (eq.
-\ref{eq:psmall_var}), i.e.
-the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residuals that expresses the model performance within the small area (term 3).
-Figure \ref{fig:fail1} illustrates the reduction or increase of the SRS variance by \psmall{} for all FR units in dependence of the residual variance term proportion on the g-weight variance.
-Two issues become obvious: firstly, the residual term generally constitutes the dominating part of the g-weight variance for all \psmall{} estimates (around 84\% on average).
-FR units for which the \psmall{} estimator produced larger variances than the SRS estimator did not differ distinctly from the pattern of the remaining FR units.
-The same was also found when looking at the absolute residual term values (fig.
-\ref{fig:fail2}).
-Secondly, FR units with the highest variance increases compared to SRS were particularly observed under small terrestrial sample sizes $n_{2,G} = 4$.
-The average increase in variance for $n_{2,G} = 4$ was 272\% compared to 62\% for $n_{2,G} > 4$.
-In comparison, the average reduction in SRS variances was around 50\% for both sampling sizes $n_{2,G} = 4$ and $n_{2,G} > 4$.
-These findings suggest that moderate or poor model fits within a small area can cause the \psmall{} and \extpsynth{} estimator to produce higher variances than the SRS estimator particularly under small terrestrial sample sizes.
-However, small terrestrial sample sizes can also have the effect that the SRS estimator might not reflect the actual variation of the local density within a small area.
-In this case, the two-phase variance estimate might be larger but more realistic.
-Whereas a visual analysis of aerial images, remote sensing data or stand maps might give some evidence for this hypothesis, a definite proof is practically infeasible.
-
 \begin{table}[H]
@@
 
-\begin{figure}[H]
-	\centering
-	\resizebox{0.8\hsize}{!}{\includegraphics{fig/eval_2phase_fail_1.png}}
-	\caption{}
-	\label{fig:fail1}
-\end{figure}
+However, cases also occurred on the FR level where one or both two-phase estimators produced larger variance values than under the SRS estimator.
+This particularly happened in 19\% (61) of the FR units under the \extpsynth{}, and in 24\% (76) of the FR units under the \psmall{} estimator.
+One possible reason for this was supposed to be a large residual variance due to a poor performance of the regression model within the small area unit.
+In order to investigate this hypothesis, we analyzed the three variance terms of the \psmall{} estimator (eq.
+\ref{eq:psmall_var}), i.e.
+the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residual (term 3).
+The latter particularly expresses the model performance within the small area unit.
+Figure \ref{fig:fail} illustrates the percentage reduction or increase of the SRS variance when compared to the \psmall{} variance for all FR units in dependence on a) the impact of residual variance on the g-weight variance, and b) the terrestrial sample size $n_{2,G}$.\par
+
+Obviously, the residual term generally constitutes the dominating part of the \psmall{} g-weight variance (around 84\% on average).
+However, a high proportion of the residual variance term seems not to be the driver for large \psmall{} variances, as apparent from Fig.
+\ref{fig:fail} (\textit{right}).
+The FR units where the \psmall{} estimator produced larger variances than the SRS estimator did not systematically differ from the majority of the FR units where \psmall{} performed better than SRS.
+However, FR units with exceptionally large variance increases compared to SRS particularly occurred under small terrestrial sample sizes of $n_{2,G} = 4$ (fig.
+\ref{fig:fail}, \textit{left}).
+These FR units exhibited a 272\% average increase of the SRS variance, compared to 62\% for the critical FR units with $n_{2,G} > 4$.
+In comparison, the achievable reduction in SRS variances compared to SRS were not considerably impacted by the terrestrial sample size (fig.
+\ref{fig:fail}, \textit{right}).
+The average reduction of these units was around 50\% under sampling sizes of both $n_{2,G} = 4$ and $n_{2,G} > 4$.
 
@@
 	\centering
-	\resizebox{0.8\hsize}{!}{\includegraphics{fig/eval_2phase_fail_2.png}}
+	\resizebox{1\hsize}{!}{\includegraphics{fig/eval_2phase_fail_11.png}}
 	\caption{}
-	\label{fig:fail2}
+	\label{fig:fail}
 \end{figure}
+
+% discussion: This also underlined why the \psynth{} estimator, which does not take the residual variation into account, produced substantially smaller variances than the design-unbiased estimator. 
+% These findings suggest that moderate or poor model fits within a small area can cause the \psmall{} and \extpsynth{} estimator to produce higher variances than the SRS estimator particularly under small terrestrial sample sizes.
+
+%\begin{figure}[H]
+%	\centering
+%	\resizebox{1\hsize}{!}{\includegraphics{fig/eval_2phase_fail.png}}
+%	\caption{}
+%	\label{fig:fail1}
+%\end{figure}
+
+% However, small terrestrial sample sizes can also have the effect that the SRS estimator might not reflect the actual variation of the local density within a small area.
+In this case, the two-phase variance estimate might be larger but more realistic.
+Whereas a visual analysis of aerial images, remote sensing data or stand maps might give some evidence for this hypothesis, a definite proof is practically infeasible.

### 2018-02-10 Draft_Form/tex/Acknowledgements.tex
update 10_02_2018
update 10_02_2018

@@
 We also want to explicitly thank Johannes Stoffels and Henning Buddenbaum from the Environmental Sensing and Geoinformatic Group of University of Trier for providing the ALS data and tree species classification map, and Kai Husmann and Christoph Fischer from the Northwest German Forest Research Institution Göttingen for their advice in processing the terrestrial inventory data.
-Special gratitude is also owed to Thomas Riedel from the Th{\"u}nen Institute for supporting this study and providing the densified NFI sample grid and Alexander Massey for proofreading.
+Special gratitude is also owed to Thomas Riedel from the Th{\"u}nen Institute for providing the densified NFI sample grid, and Alexander Massey for proofreading.

### 2018-02-10 Draft_Form/tex/Discussion.tex
update 09_02_2018
update 09_02_2018
update 10_02_2018
update 10_02_2018

@@
 
-%\subsection{Stratification according to Tree Species and LiDAR Acquisitions}
-%\label{sec:strat_dis}
+The aim of this study was to investigate the performance of design-based estimators for small area estimation of mean standing timber volume on two spatial forest management levels in Germany.
+It was of particular interest to gather information about the estimation error levels that can be realized using the German NFI data, characterized by low sampling intensities in the area of interests, as terrestrial phase information in the two-phase estimators.
+To address these research questions, we applied the simple random sampling (SRS), the pseudo-small (\psmall{}) and the extended pseudo-synthetic (\extpsynth{}) estimator to 45 and 405 small area units in the German state of Rhineland-Palatinate.\par
 
+Our study showed that on both small area levels, the \psmall{} and the \extpsynth{} estimator generally leads to a substantial reduction of the estimation errors produced by the SRS estimator.
+On the upper management level (FA districts), \psmall{} and \extpsynth{} allowed to provide estimation errors smaller than 5\% for 73\% of the small areas compared to only 17\% under the SRS estimator.
+This level of estimation accuracy could not be achieved on the subsequent management level (FR districts).
+The reason for this were primarily the substantially smaller terrestrial sample sizes.
+However, in most FR units (95\%), the estimation errors could be limited to 20\% compared to 40\% under SRS.
+A pairwise comparison of the confidence intervals revealed that the estimators did thereby not produce significantly different point estimates.
+The much smaller estimation errors of the \psynth{} estimator suggested that the neglection of the regression model accuracies in the small area units leads to overoptimistic estimation accuracies and confidence intervals.
+If possible, one should thus prefer the unbiased estimates of \psmall{} or \extpsynth{}.\par
+
+For several FR units, it was observed that the \psmall{} and the \extpsynth{} estimator can produce larger variances than the SRS estimator.
+It is important to note that this is in perfect agreement with the theory of both two-phase estimators and can theoretically appear if the residual variance in the small area, which generally constitutes the dominating part of the two-phase variance, turns out to be much higher than the variance of the terrestrial data in the small area.
+The empirical findings of our study suggest that such cases can particularly occur if moderate or poor model fits within a small area are combined with small terrestrial sample sizes ($\leq 5$) in the small area.
+Nonetheless, it should be kept in mind that small terrestrial sample sizes can also cause the SRS estimator to not reflect the actual variation of the local density within a small area.
+In this case, the two-phase variance estimate might be larger but more realistic.
+Whereas a visual analysis of aerial images, remote sensing data or stand maps might give some further evidence for or against this hypothesis, a definite proof is practically infeasible.\par
+
+We were able to empirically confirm that the \extpsynth{} estimator generally produces slightly smaller variances and estimation errors than the \psmall{}.
+This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero-mean-residual property of the \extpsynth{}.
+Our analysis also indicated that the difference between the two estimators are negligible for sample sizes $\geq$ 10 due to their asymptotic relationship.
+Furthermore, one or more clusters not entirely included in the small area unit did reassuringly not have a systematic impact on the estimates of \extpsynth{}.
+This empirical evidence can however not be generalized to any application of \extpsynth{} under cluster sampling.
+It thus seems recommendable to calculate both \psmall{} and \extpsynth{}, and subsequently compare their results.
+If no suspicious deviations occur, one can favor the \extpsynth{} as the estimator of choice.\par
+
+%% auxiliary information:
+% - realistically represent current state of ALS availability (see BW), but also tspec info as a specialty
+% - still missingness in the auxililary data
+% - future perspective (BDOM, tspec)
+% - conclusion for estimators: 
+%   o a) using exhaustive aux. variable info in estimators
+%   o b) increase in model accuracies due to more flexible OLS models (*) *: this might also solve the problem of hight residual variations in some FR units (SRS <-> 2p)
+%   o c) demonstrated procedures can then also be used for change esitmation (without the inconvenience of time gaps)
+
+%% conistency of sampling frame:
+% - (**)
+
+% ---------------------------------------------------------------------- %
 % NOTES:
+%
+% begin with general results:
+%
+% - extension to change estimation
+%   o BDOM more frequently updated, max. 1 year time gap between CHM and BWI3 survey
+%   o also treespecies classific. frequently updated using sentinel 2 data
+%   o the gain in model accuracy will certainly considerably increase if the ALSyear stratification becomes unnecessary Value increase also in combination with
+%     further explanatory variables such as growing conditions
+%
+% - CONCLIUSION: transfer of the suggested procedure to FDI inventories: maybe possible to get qunatified data for stands with acceptable estimation errors? (would be of high interest)
+%
+% - recommendation: treat \psynth estimation with extreme caution (residuals not considered, thus provides overoptimistic errors and CIs)
+%
+%
+% - the decision wether the errors are acceptable cannot be answered here but (in our opinion) depend on the question whether ... decisions can be made based on the provided Confidence Intervals.
+% - in a next step, we will investigate whether the derived confidence intervals are sufficient to be used as a validation for the stand-wise inventories (Kuliesis et al.)
+% 
+%
+%
+% - loss of some n1 and n2 due to missing information in remote sensing data.
+If really exhaustively available, one could also use the true means of the auxiliary variables (exhaustive estimators), which
+%   will further decrease the estimation errors.
+Previous studies of Mandallaz, Breschan, Hill (2013) however showed that given a reasonable large sample size n_{1,G} the differences in the est.
+errors
+%   are usually small. This migth also be due to the fact that the largest proportion of the two-phase variance comes from the residual term, which is independent of an exhuastive or non-exhaustive
+%   evaluation of the auxiliary data. ( --> maybe here lead to future improvement of the data availability)
+%
+%
 %
@@
 %
-%
-% --> Extension to at least partially exhaustive estimator (three-phase non-exhaustive) if auxiliary data are really exhaustively
-%     available
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
+% (**):
+% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$.
+This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer.
+For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$.
+The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e.
+by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par

### 2018-02-10 Draft_Form/tex/Results.tex
update 10_02_2018
update 10_02_2018

@@
 The differences decreased with increasing sample size and thus confirmed the asymptotic relationship between the two estimators.
-However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.
-The results indicate that the adjustment of the intercept term to the data within a small area used in the \extpsynth{} estimator will in general yield slightly smaller variances than the \psmall{} estimator.\par
+However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par
+
+% The results indicate that the adjustment of the intercept term to the data within a small area used in the \extpsynth{} estimator will in general yield slightly smaller variances than the \psmall{} estimator.
 
@@
 % ==> so differences will particularly concern sae units with small n2G (threshold seems to be around n2G < 10)
-%
-% for Discussion:
-% - our analyses 
-%   a) suggest that the differences between \psmall{} and \extpsynth{} become negligible for sample sizes $n_{2,G}$ larger than 10 due to the asymptotic relationship between these estimators 
-%   b) showed that violation of the '\extpsynth{}'-assumption had only minor effects on the variance estimates that did not lead to statistically different point estimates 
-%   c) indicate that \extpsynth{} will in general have slightly smaller est.variances due to a slightly better model fit through the data in the small area, which is caused by the 
-%      adjusted intercept (which however is mainly a means to insure the zero-mean-residual assumption in the \extpsynth{}-estimator
 
@@
 	\resizebox{1\hsize}{!}{\includegraphics{fig/eval_2phase_fail_11.png}}
-	\caption{}
+	\caption{Increase or reduction of the SRS variance by application of the \psmall{} estimator for all 321 FR units in dependence of a) the terrestrial sample size in the FR units (\textit{x-axis}) and b) the residual term proportion of the \psmall{} g-weight variance (\textit{y-axis}).}
 	\label{fig:fail}

### 2018-02-11 Draft_Form/tex/Conclusions.tex
update 11_02_2018
update 11_02_2018

\section{Conclusion}
\label{sec:concl}

The study led to two major conclusions: (1) the \extpsynth{} and \psmall{} estimator generally achieved substantially smaller estimation errors on the two investigated forest district levels compared to the SRS estimator. The demonstrated double-sampling procedure thus constitutes a major contribution to an increase in value of the existing German NFI data on the federal state level. However, it is not possible to conclude from our study results alone whether the realized error levels are already acceptable in order to support forest planning decisions. Thus, further investigations are necessary in close cooperation with the forest authorities. A first study will concentrate on testing the \extpsynth{} and \psmall{} confidence intervals as a validation source for the stand-wise inventories. (2) Despite the quality restrictions in the ALS data and the tree species map, the two data sources were found to be well suited to model the mean timber volume on plot and cluster level. With respect to frequently updated aerial canopy height models and tree species maps, it will thus be of hight interest to investigate the model and estimation accuracies that can be expected for future applications. In this framework, the incorporation of additional auxiliary data and the extension to change estimation seem the reasonable next steps to be explored towards an operational implementation of the demonstrated double-sampling procedure.

%The application of the design-unbiased \extpsynth{} and \psmall{} estimator should be preferred over synthetic estimations whenever possible, since they also account for the model inaccuracies and thus provide unbiased estimates as well as more realistic confidence intervals.
%
%
%
%
%We draw three major conclusions from our study: (1) our analyses strongly indicated that the acquisition of auxiliary data close to the date of the terrestrial survey is a key factor to achieve good model accuracies. Particularly for large-scale inventory applications, this requirement is often difficult to meet. In such cases, we consider that the proposed method of including quality information about the auxiliary data in a prediction model can be an effective technique for improving the prediction accuracy. Ongoing studies investigate whether this modelling technique can also lead to smaller estimation errors of design-based estimators. (2) Our study also indicated that the relationship between the field measured timber volume and remote-sensing derived height information is tree species specific. We expect that using the tree species information in a timber volume model would even lead to higher prediction accuracies when combined with explanatory variables that can further explain the variation within each tree species group, such as bioclimatic growing conditions, soil properties and stand density on the plot level. (3) We consider the demonstrated calibration technique to be a valuable method for future studies where an external tree species map (i.e. the map was not created for the specific study objective) is used in prediction models. The application of a calibration model can also be transferred to any error-prone explanatory variable and be a simple means to clean the data set from noise and thus increase the model accuracy.

% - CONCLIUSION: 
%   o transfer of the suggested procedure to FDI inventories: maybe possible to get qunatified data for stands with acceptable estimation errors? (would be of high interest)
%   o the decision wether the errors are acceptable cannot be answered here but (in our opinion) depend on the question whether ... decisions can be made based on the provided Confidence Intervals.
%   o in a next step, we will investigate whether the derived confidence intervals are sufficient to be used as a validation for the stand-wise inventories (Kuliesis et al.)

% - The existing German NFI data can provide substantially smaller estimation errors on forest district levels when used in the proposed double-sampling estimators. However, the question which errors are acceptable to support operational forest planning cannot be answered purely based on the absolute error values. In our opinion, it depends on the question whether the derived confidence intervals a) allow for more profound decisions between forest planning alternatives.

% - prefer model-assisted estimators to synthetic estimators if one can afford --> because design-unbiased, they take the model inaccuracies into account and thus provide unbiased point estimates and more realsitic confidence intervals.

### 2018-02-11 Draft_Form/tex/Discussion.tex
update 11_02_2018
update 11_02_2018

@@
 \label{sec:Dis}
+
+% ------------------------ %
+\subsection{Performance of estimators}
 
@@
 The empirical findings of our study suggest that such cases can particularly occur if moderate or poor model fits within a small area are combined with small terrestrial sample sizes ($\leq 5$) in the small area.
+A closer look on these small areas thus might reveal the reason for the poor prediction performance and help to improve the model fit.
 Nonetheless, it should be kept in mind that small terrestrial sample sizes can also cause the SRS estimator to not reflect the actual variation of the local density within a small area.
@@
 
-We were able to empirically confirm that the \extpsynth{} estimator generally produces slightly smaller variances and estimation errors than the \psmall{}.
+We were also able to empirically confirm that the \extpsynth{} estimator generally produces slightly smaller variances and estimation errors than the \psmall{}.
 This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero-mean-residual property of the \extpsynth{}.
-Our analysis also indicated that the difference between the two estimators are negligible for sample sizes $\geq$ 10 due to their asymptotic relationship.
-Furthermore, one or more clusters not entirely included in the small area unit did reassuringly not have a systematic impact on the estimates of \extpsynth{}.
+However, our analysis indicated that the difference between the two estimators are negligible for sample sizes $\geq$ 10 due to their asymptotic relationship.
+Furthermore, one or more clusters not entirely included in the small area unit did reassuringly not have a notable impact on the estimates of \extpsynth{}.
 This empirical evidence can however not be generalized to any application of \extpsynth{} under cluster sampling.
 It thus seems recommendable to calculate both \psmall{} and \extpsynth{}, and subsequently compare their results.
-If no suspicious deviations occur, one can favor the \extpsynth{} as the estimator of choice.\par
+If no suspicious deviations occur, we consider the \extpsynth{} as the estimator of choice.\par
+
+% ------------------------ %
+\subsection{Auxiliary data}
+
+The auxiliary data used in our study were derived from two remote sensing sources, i.e.
+an ALS canopy height model and a tree species classification map.
+Likewise in many similar studies, the ALS mean canopy height proved to be the explanatory variable with highest predictive power.
+However, the large time-gaps of up to 10 years between the ALS acquisition and the terrestrial survey date caused a substantial introduction of artificial noise in the data.
+Whereas a stratification to the ALS acquisition years was an effective means to counteract the implied residual inflation, several leverage points were unambiguously caused by the temporal asynchronicity.
+As opposed to the ALS data, the availability of a country-wide tree species classification map has yet been unique among all German federal states.
+Whereas the study of \citet{hill2017a} already showed that the tree species information was able to improve the model accuracy, it has yet not been used to its full potential.
+One reason for this was the impossibility of a tree species individual modeling within each ALS acquisition year, which we consider to add further explanatory power.
+Another reason was the lack of available satellite data for classification in some parts of the country, which led to missingness in the inventory data and restricted 19 FR units to a simpler regression model.
+Promising steps with respect to more up-to-date canopy height information have already been made, as the topographic survey institution of RLP will from this year on provide a country-wide canopy height model derived from aerial imagery acquisitions.
+These campaigns will in the future be conducted in a two-year period and allow to derive canopy height information matching the dates of terrestrial forest inventories.
+A study of \citet{kirchhoefer2017} recently indicated that similar model accuracies for German NFI data can be achieved using such imagery-based canopy height models.
+Due to the improved coverage and repetition rate of the Sentinel-2 satellite, also the tree species classification map will in the future be updated each year.
+We consider these alternative auxiliary data sources to also solve the problem of missing explanatory variables at inventory plots.
+Thus, one could also make use of the exhaustive information within the two-phase estimators by using the true the auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which theoretically leads to a further decrease of the estimation errors.
+Previous studies of \citet{mandallaz2013b} however showed that given a reasonable large sample size of the first phase, the differences in the estimation error are usually small.
+With respect to the substantial improvements in the temporal synchronicity between auxiliary and terrestrial inventory data, we consider the demonstrated double-sampling approach also to be very efficient for change estimation \citep{massey2015b}.\par
 
@@
 %   o b) increase in model accuracies due to more flexible OLS models (*) *: this might also solve the problem of hight residual variations in some FR units (SRS <-> 2p)
-%   o c) demonstrated procedures can then also be used for change esitmation (without the inconvenience of time gaps)
+%   o c) demonstrated procedures can then also be used for change estimation (without the inconvenience of time gaps)
 
@@
 %
-% - CONCLIUSION: transfer of the suggested procedure to FDI inventories: maybe possible to get qunatified data for stands with acceptable estimation errors? (would be of high interest)
 %
-% - recommendation: treat \psynth estimation with extreme caution (residuals not considered, thus provides overoptimistic errors and CIs)
-%
-%
-% - the decision wether the errors are acceptable cannot be answered here but (in our opinion) depend on the question whether ... decisions can be made based on the provided Confidence Intervals.
-% - in a next step, we will investigate whether the derived confidence intervals are sufficient to be used as a validation for the stand-wise inventories (Kuliesis et al.)
-% 
-%
-%
-% - loss of some n1 and n2 due to missing information in remote sensing data.
-If really exhaustively available, one could also use the true means of the auxiliary variables (exhaustive estimators), which
-%   will further decrease the estimation errors.
-Previous studies of Mandallaz, Breschan, Hill (2013) however showed that given a reasonable large sample size n_{1,G} the differences in the est.
-errors
-%   are usually small. This migth also be due to the fact that the largest proportion of the two-phase variance comes from the residual term, which is independent of an exhuastive or non-exhaustive
-%   evaluation of the auxiliary data. ( --> maybe here lead to future improvement of the data availability)
-%
+% (**):
+% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$.
+This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer.
+For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$.
+The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e.
+by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par
+
+% - CONCLIUSION: 
+%   o transfer of the suggested procedure to FDI inventories: maybe possible to get qunatified data for stands with acceptable estimation errors? (would be of high interest)
+%   o the decision wether the errors are acceptable cannot be answered here but (in our opinion) depend on the question whether ... decisions can be made based on the provided Confidence Intervals.
+%   o in a next step, we will investigate whether the derived confidence intervals are sufficient to be used as a validation for the stand-wise inventories (Kuliesis et al.)
 % 
@@
 %
-% (**):
-% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$.
-This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer.
-For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$.
-The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e.
-by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par

### 2018-02-11 Draft_Form/tex/Introduction(2).tex
update 11_02_2018
update 11_02_2018

@@
 The chosen double-sampling estimators were favoured for several reasons: \textbf{(i)} the design-based frame considerably relaxes requirements on the regression model which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can consider \textit{non-exhaustive}, i.e.
-non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for the design-dependency of the regression coefficients on the sample (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals.\par
+non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for the design-dependency of the regression coefficients on the sample (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals.
+The results from this study were considered to provide valuable information whether the suggested procedure might be a cost-saving alternative to a regional FDI.\par
 
-The results from this study were considered to provide valuable information whether the suggested procedure a) might be a cost-saving alternative to a regional FDI and b) can be used as a reliable validation for SDI data.
+%% old
+% The results from this study were considered to provide valuable information whether the suggested procedure a) might be a cost-saving alternative to a regional FDI and b) can be used as a reliable validation for SDI data.
 A secondary objective was to address the potential effects of auxiliary data quality on estimation precision, and to identify challenges when transferring the existing German NFI design into the suggested double sampling estimation procedure.

### 2018-02-12 Draft_Form/tab/modacc_modterms.tex
update 12_02_2018
update 12_02_2018

@@
 	\begin{center}
-	\caption{Accuracy metrics for the two OLS regression models. Interaction terms are indicated by ':'. () give the respective values on the cluster level.} 
+	\caption{Accuracy metrics for the two OLS regression models on the cluster level. Interaction terms are indicated by ':'. () give the respective values on the plot level.} 
 	\label{tab:modacc_modterms}
@@
 model terms & model & $R^2_{adj}$ & RMSE & RMSE\% \\ 
-  \hline
-meanheight + stddev + meanheight$^2$ +  & full model &  0.48 & 139.22  & 45.98 \\
-treespecies + ALSyear + & & (0.53) &  (101.61) & (33.57) \\ 
+  \hline \hline
+meanheight + stddev + meanheight$^2$ +  & full model &  0.59 & 101.62  & 33.57 \\
+treespecies + ALSyear + & & (0.48) &  (139.22) & (45.98) \\ 
 meanheight:treespecies + \\ meanheight:ALSyear + meanheight:stddev + \\ stddev:ALSyear &&& \\ \\
 
-meanheight + stddev + meanheight$^2$ + & reduced model  & 0.45  & 144.13 & 47.60 \\
-ALSyear + meanheight:ALSyear + & & (0.49) & (106.08) & (35.40) \\
+meanheight + stddev + meanheight$^2$ + & reduced model  & 0.56  & 106.08 & 35.4 \\
+ALSyear + meanheight:ALSyear + & & (0.45) & (144.13) & (47.60) \\
 meanheight:stddev + stddev:ALSyear &&& \\ \\

### 2018-02-12 Draft_Form/tex/Materials_and_Methods(2).tex
update 10_02_2018
update 10_02_2018
update 12_02_2018
update 12_02_2018

@@
 %
-% - Add Graphik showing RLP, zoom into 3 management levels including 2-phase sample
-%   (big graphic, can take 1/2 page later)
 
@@
 	\centering
-	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/AuxvarsLOWRES.png}}
+	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/Auxvars_100dpi.png}}
 	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information.
@@
 			\begin{tabular}{l|c|c|c|c} %8cols
-				\hlineB{1}
+				\hline
 				Main plot species & Producer's accuracy[\%] & User's accuracy[\%] & nref & nclass \\
@@
 				Mixed       & 84.49 & 64.53 & 3152 & 4127 \\
-				\hline
+				\hlineB{2}
 				& \multicolumn{2}{l|}{Overall accuracy: 61.96\%} & 5384 & 5384 \\
@@
 
+%% Here is the table with calibrated and uncalibrated values:
 %\begin{table}[H]
@@
 While the study of \citet{hill2017a} only provide the model evaluations on the plot level, the two-phase estimators described in section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level.
-We thus re-evaluated the model as used in the estimators also on the cluster level and found the model accuracies to be higher than on the plot level (\adjrsq{} of 0.53 and RMSE of 101.61 \mha{} and 33.6\%).
+We thus re-evaluated the model as used in the estimators also on the cluster level and found the model accuracies to be higher than on the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%).
 A stratification to the ALS acquisition years substantially improved the model accuracy and thus proved to be an effective means in accounting for the artificially introduced noise in the data set due to ALS quality variations and time-gaps between the ALS and the terrestrial survey.
@@
 An additional evaluation of the model residuals within each ALS acquisition year stratum revealed that the model accuracies substantially varied between the strata (table \ref{tab:adj_r2_within}).
-Values above the overall \adjrsq{} were particularly achieved in ALS acquisition years close to the terrestrial survey date (0.59 to 0.66 on the cluster level).
+Values above the overall \adjrsq{} were particularly achieved in ALS acquisition years close to the terrestrial survey date (0.60 to 0.65 on the cluster level).
 This effect was substantially diminished when dropping the \alsyear{} variable from the model term.\par
@@
 
+%\begin{equation}\label{eq:R_squared_clust}
+%R^2 =  \frac{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(\hat{Y}_{c}(x)-\bar{Y}_c(x)\Big)^2}{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(Y_{c}(x)-\bar{Y}_c(x)\Big)^2}
+%\end{equation}
+
 %% Notes on leverages:
@@
 % x-values at the boundaries (small and large values) usually have a high leverage. It does not mean that they are invalid / erroneous.
-
-%We conducted an Influence Analysis, i.e.
-leverage / outlier detection, for the 'final model'.
-We here considered the usually applied criteria of \textit{Leverages} and \textit{Cook's Distance} as amongst others described in Fahrmeir 2013 \{Regression: models, methods and applications.
-\textit{Springer Science \& Business Media}.
-page 164-167\}.
-The critical threshold of $2p/n$ (i.e.
-twice the average of the hat matrix' diagonal entries), was exceeded by 10\% of the observations.
-However, only 3\% of these leverage points were assigned to studentized residuals > 1 or < -1.
-Leaving these 3\% of points out and recalculating the final model lead to a $R^{2}_{adj}$ of 0.494 compared to 0.485 when including them in the regression.
-The Cook's Distance values $D_i$ did not exceed a value of 0.019, and thus were far apart from the often cited critical threshold of $D_i > 0.5$.
-Based on these findings, we decided not to remove observations from the modelling data set.
-We added a paragraph commenting on this issue of influential data points in section 3.3 'Final Regression Model', page 9 RHS line 690-707.
 

### 2018-02-13 Draft_Form/tab/modacc_modterms.tex
update 13_02_2018
update 13_02_2018

@@
   \hline \hline
-meanheight + stddev + meanheight$^2$ +  & full model &  0.59 & 101.62  & 33.57 \\
+meanheight + stddev + meanheight$^2$ +  & full model &  0.58 & 90.11  & 29.76 \\
 treespecies + ALSyear + & & (0.48) &  (139.22) & (45.98) \\ 
@@
 
-meanheight + stddev + meanheight$^2$ + & reduced model  & 0.56  & 106.08 & 35.4 \\
+meanheight + stddev + meanheight$^2$ + & reduced model  & 0.55  & 95.23 & 31.65 \\
 ALSyear + meanheight:ALSyear + & & (0.45) & (144.13) & (47.60) \\

### 2018-02-13 Draft_Form/tex/Appendices.tex
update 13_02_2018
update 13_02_2018

@@
-%\appendix
-%\addcontentsline{toc}{section}{Appendices}
-%\section*{Appendices}
-%\section{First appendix}
-%\section{Second appendix}
-
 \appendix
 \section{Appendix}
+\label{sec:appendix_saerlp}
 
-% ----------------------------------------------------------------------- %
-% A.1
-% ----------------------------------------------------------------------- %
-%\subsection{Model accuracies for $CHM$ variables}
+% -------------------------------------- %
+\subsection*{R-squared on cluster level}
 
-%\input{tab/mod_chm_table.tex}\newpage
+The R$^2$ on the cluster level is calculated using the number of plots $M(x)$ of each cluster in order to weight for the varying number of plots on which $Y_c(x)$ and $\hat{Y}_{c}(x)$ are based on.
+
+\begin{equation*}\label{eq:R_squared_clust}
+R^2 =  \frac{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(\hat{Y}_{c}(x)-\hat{\bar{Y}}_c\Big)^2}{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(Y_{c}(x)-\hat{\bar{Y}}_c\Big)^2}
+\end{equation*}
+
+\noindent $Y_c(x)$ and $\hat{Y}_{c}(x)$ are the predicted and observed local densities on the cluster level calculated according to equations \ref{eq:locdens_clust} and \ref{eq:globresids}.
+$\hat{\bar{Y}}_c$ is the estimated sample mean corresponding to the weighted mean over all observed local densities on the cluster level (equ.
+\ref{eq:srs_est_clusters}).\par
+
+% -------------------------------------- %
+\subsection*{RMSE on cluster level}
+
+The same weights $M(x)$ are also applied to calculate the RMSE on the cluster level. $n_2$ is the number of clusters used in the modeling frame.
+
+\begin{equation*}\label{eq:RMSE_clust}
+RMSE= \sqrt{\frac{1}{n_{2}}  \sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M}_2}\Big)^2 \Big(\hat{Y}_{c}(x)-Y_c(x)\Big)^2}
+\end{equation*}
+
+\noindent The \textit{relative} or \textit{normalized} RMSE is calculated by setting the absolute RMSE in relation to the estimated sample mean $\hat{\bar{Y}}_c$:
+
+\begin{equation*}\label{eq:NRMSE_clust}
+RMSE[\%] = \frac{RMSE}{\hat{\bar{Y}}_c}
+\end{equation*}
+
+\noindent Generally note that the weights $\frac{M(x)}{\bar{M_2}} \equiv 1$ if the number of plots per cluster is constant.

### 2018-02-13 Draft_Form/tex/Discussion.tex
update 13_02_2018
update 13_02_2018

@@
 It was of particular interest to gather information about the estimation error levels that can be realized using the German NFI data, characterized by low sampling intensities in the area of interests, as terrestrial phase information in the two-phase estimators.
-To address these research questions, we applied the simple random sampling (SRS), the pseudo-small (\psmall{}) and the extended pseudo-synthetic (\extpsynth{}) estimator to 45 and 405 small area units in the German state of Rhineland-Palatinate.\par
+To address these research questions, we applied the simple random sampling (SRS), the pseudo-small (\psmall{}) and the extended pseudo-synthetic (\extpsynth{}) estimator for cluster sampling to 45 and 405 small area units in the German state of Rhineland-Palatinate.\par
 
@@
 
-For several FR units, it was observed that the \psmall{} and the \extpsynth{} estimator can produce larger variances than the SRS estimator.
+For several FR units, it was observed that the \psmall{} and the \extpsynth{} estimator can occasionally produce larger variances than the SRS estimator.
 It is important to note that this is in perfect agreement with the theory of both two-phase estimators and can theoretically appear if the residual variance in the small area, which generally constitutes the dominating part of the two-phase variance, turns out to be much higher than the variance of the terrestrial data in the small area.
@@
 This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero-mean-residual property of the \extpsynth{}.
-However, our analysis indicated that the difference between the two estimators are negligible for sample sizes $\geq$ 10 due to their asymptotic relationship.
+However, our analysis indicated that the difference between the two estimators are negligible for sample sizes $\geq$ 10 due to their asymptotic equivalency.
 Furthermore, one or more clusters not entirely included in the small area unit did reassuringly not have a notable impact on the estimates of \extpsynth{}.

### 2018-02-13 Draft_Form/tex/Materials_and_Methods(2).tex
update 13_02_2018
update 13_02_2018

@@
 where $nha_i$ is the number of trees per hectare represented by tree $i$.
-The local densities on cluster level can then be used to derive the estimated spatial mean $\hat{Y}_c$ and its estimated variance $\hat{\var}(\hat{Y}_c)$ for any given spatial unit for which $n_2 \geq 2$ ($n_2$ denoting the number of sample units, i.e.
+The local densities on cluster level can then be used to derive the estimated spatial mean $\hat{\bar{Y}}_c$ and its estimated variance $\hat{\var}(\hat{Y}_c)$ for any given spatial unit for which $n_2 \geq 2$ ($n_2$ denoting the number of sample units, i.e.
 clusters):
 
-\begin{subequations}\label{eq:srs_est_cluster}
+\begin{subequations}\label{eq:srs_est_clusters}
 	\begin{align}
-\hat{Y}_c &= \frac{\sum_{x \in s_2} M(x) Y_{c}(x)}{\sum_{x \in s_2} M(x)} \\
-\hat{\var}(\hat{Y}_c) &= \frac{1}{n_2(n_2 - 1)}\sum_{x \in s_2}\Big(\frac{M(x)}{\bar{M_2}}\Big)^2(Y_{c}(x) - \hat{Y}_c)^2
+\hat{\bar{Y}}_c &= \frac{\sum_{x \in s_2} M(x) Y_{c}(x)}{\sum_{x \in s_2} M(x)} \\
+\hat{\var}(\hat{\bar{Y}}_c) &= \frac{1}{n_2(n_2 - 1)}\sum_{x \in s_2}\Big(\frac{M(x)}{\bar{M_2}}\Big)^2(Y_{c}(x) - \hat{\bar{Y}}_c)^2
 	\end{align}
@@
 
-\noindent with $\hat{R}_{c}=Y_{c}(x)-\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2}$ being the empirical model residuals at the cluster level, which by construction of OLS satisfy the important \textit{zero mean residual property}, i.e.
+with
+
+\begin{equation}\label{eq:globresids}
+\hat{R}_{c}=Y_{c}(x)-\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2} = Y_{c}(x) - \hat{Y}_{c}(x)
+\end{equation}
+
+\noindent being the empirical model residuals at the cluster level, which by construction of OLS satisfy the important \textit{zero mean residual property}, i.e.
 $\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$.\\
@@
 	\pmb{Z}_{c,G}(x) =  \frac{\sum_{l=1}^{L} I_{G}(x_l)\pmb{Z}(x_l)}{M_{G}(x)}\\		
-	Y_{c,G}(x) &= \frac{\sum_{l=1}^{L} I_{G}(x_l)\pmb{Y}(x_l)}{M_{G}(x)}  &\text{and} \hspace{3ex}
+	Y_{c,G}(x) &= \frac{\sum_{l=1}^{L} I_{G}(x_l)Y(x_l)}{M_{G}(x)}  &\text{and} \hspace{3ex}
 	\hat{Y}_{c,G}(x)=\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2}\\
@@
 While the study of \citet{hill2017a} only provide the model evaluations on the plot level, the two-phase estimators described in section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level.
-We thus re-evaluated the model as used in the estimators also on the cluster level and found the model accuracies to be higher than on the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%).
+We thus re-evaluated the model as used in the estimators also on the cluster level (formulas given in Appendix) and found the model accuracies to be higher than on the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%).
 A stratification to the ALS acquisition years substantially improved the model accuracy and thus proved to be an effective means in accounting for the artificially introduced noise in the data set due to ALS quality variations and time-gaps between the ALS and the terrestrial survey.

### 2018-02-14 Draft_Form/tex/Materials_and_Methods(2).tex
update 14_02_2018
update 14_02_2018

@@
 While information was originally gathered at a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid.
-The German NFI uses a cluster sampling design, which means that a sample unit consists of maximal four sample locations (also referred to as \textit{sample plots}) that are arranged in a square (so called \textit{cluster}) with a side length of 150 metres (Picture).
+The German NFI uses a cluster sampling design, which means that a sample unit consists of maximal four sample locations (also referred to as \textit{sample plots}) that are arranged in a square (so called \textit{cluster}) with a side length of 150 metres.
 The number of plots per cluster can however vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}.
@@
 In a \textit{second} step, we thus applied this calibration model to the \textit{treespecies} variable derived at all sample locations $s_1$.
-Table \ref{tab:classacc} gives the classification accuracies of the \textit{treespecies} variable before and after calibration.
+Table \ref{tab:classacc} gives the classification accuracies of the \textit{treespecies} variable after calibration.
 

### 2018-02-27 Draft_Form/saerlp_article_master.tex
update 25_01_2018
update 25_01_2018 (begin Results)
update 03_02_2018
update 03_02_2018
update 04_02_2018
update 04_02_2018
update 07_02_2018
update 07_02_2018
update 09_02_2018
update 09_02_2018
update 11_02_2018
update 11_02_2018
update 12_02_2018
update 12_02_2018
update 13_02_2018
update 13_02_2018
update 15_02_2018
update 15_02_2018
update 27_02_2018
update 27_02_2018 (Alex review)

@@
 \date{\vspace{-0.8ex}}
-\title{\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation of timber volume resources on forest district levels \\ \vspace{2ex}
+\title{\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation on forest district levels \\ \vspace{2ex}
   \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}}
@@
 % comment out to disable line-numbering:
-%\usepackage{lineno}
-%\linenumbers
+\usepackage{lineno}
+\linenumbers
 
@@
 \newcommand{\EX}{\mathbb{E}}
-\newcommand{\psynth}{\textit{PSYNTH}}
-\newcommand{\psmall}{\textit{PSMALL}}
-\newcommand{\extpsynth}{\textit{EXTPSYNTH}}
+\newcommand{\psynth}{PSYNTH}
+\newcommand{\psmall}{PSMALL}
+\newcommand{\extpsynth}{EXTPSYNTH}
+\newcommand{\meanheight}{\textit{meanheight}}
+\newcommand{\stddev}{\textit{stddev}}
+\newcommand{\treespecies}{\textit{treespecies}}
+\newcommand{\alsyear}{\textit{ALSyear}}
 
@@
 
-\input{tex/Introduction(2)}\newpage\cleardoublepage
+\input{tex/Introduction(2)}% \newpage\cleardoublepage
 
@@
 
-%\input{tex/Results}\newpage\cleardoublepage
+\input{tex/Results}\newpage\cleardoublepage
 
@@
 
-%\input{tex/Discussion}\newpage\cleardoublepage
+\input{tex/Discussion}%\newpage\cleardoublepage
 
@@
 
-%\input{tex/Conclusions}\newpage\cleardoublepage
+\input{tex/Conclusions}% \newpage\cleardoublepage
 
@@
 
-%\input{tex/Acknowledgements}\newpage\cleardoublepage
+\input{tex/Acknowledgements}\newpage\cleardoublepage
 
@@
 
-%\input{tex/Appendices}\newpage\cleardoublepage
+\input{tex/Appendices}\newpage\cleardoublepage
 

### 2018-02-27 Draft_Form/tex/Appendices.tex
update 27_02_2018
update 27_02_2018 (Alex review)

@@
 
-\noindent $Y_c(x)$ and $\hat{Y}_{c}(x)$ are the predicted and observed local densities on the cluster level calculated according to equations \ref{eq:locdens_clust} and \ref{eq:globresids}.
-$\hat{\bar{Y}}_c$ is the estimated sample mean corresponding to the weighted mean over all observed local densities on the cluster level (equ.
+\noindent $Y_c(x)$ and $\hat{Y}_{c}(x)$ are the predicted and observed local densities on the cluster level calculated according to Equations \ref{eq:locdens_clust} and \ref{eq:globresids}.
+$\hat{\bar{Y}}_c$ is the estimated sample mean corresponding to the weighted mean over all observed local densities on the cluster level (Eq.
 \ref{eq:srs_est_clusters}).\par
@@
 
-\noindent The \textit{relative} or \textit{normalized} RMSE is calculated by setting the absolute RMSE in relation to the estimated sample mean $\hat{\bar{Y}}_c$:
+\noindent The \textit{relative} or \textit{normalized} RMSE is calculated by dividing the RMSE by the estimated sample mean $\hat{\bar{Y}}_c$:
 
@@
 
-\noindent Generally note that the weights $\frac{M(x)}{\bar{M_2}} \equiv 1$ if the number of plots per cluster is constant.
+\noindent Note that the weights $\frac{M(x)}{\bar{M_2}} \equiv 1$ if the number of plots per cluster is constant.

### 2018-02-27 Draft_Form/tex/Conclusions.tex
update 14_02_2018
update 14_02_2018
update 27_02_2018
update 27_02_2018 (Alex review)

@@
 The demonstrated double-sampling procedure thus constitutes a major contribution to an increase in value of the existing German NFI data on the federal state level.
-However, it is not possible to conclude from our study results alone whether the realized error levels are already acceptable in order to support forest planning decisions.
+However, it is not possible to conclude from our study results alone whether the realized error levels are already sufficient enough in order to support forest planning decisions.
 Thus, further investigations are necessary in close cooperation with the forest authorities.
 A first study will concentrate on testing the \extpsynth{} and \psmall{} confidence intervals as a validation source for the stand-wise inventories.
-(2) Despite the quality restrictions in the ALS data and the tree species map, the two data sources were found to be well suited to model the mean timber volume on plot and cluster level.
-With respect to frequently updated aerial canopy height models and tree species maps, it will thus be of hight interest to investigate the model and estimation accuracies that can be expected for future applications.
+(2) Despite the quality restrictions in the ALS data and the tree species map, the two data sources were found to be well suited to model the mean timber volume on plot and cluster levels.
+With respect to frequently updated aerial canopy height models and tree species maps, it will thus be of interest to investigate the model and estimation performances that can be expected for future applications.
 In this framework, the incorporation of additional auxiliary data and the extension to change estimation seem the reasonable next steps to be explored towards an operational implementation of the demonstrated double-sampling procedure.
-
-%The application of the design-unbiased \extpsynth{} and \psmall{} estimator should be preferred over synthetic estimations whenever possible, since they also account for the model inaccuracies and thus provide unbiased estimates as well as more realistic confidence intervals.
-%
-%
-%
-%
-%We draw three major conclusions from our study: (1) our analyses strongly indicated that the acquisition of auxiliary data close to the date of the terrestrial survey is a key factor to achieve good model accuracies.
-Particularly for large-scale inventory applications, this requirement is often difficult to meet.
-In such cases, we consider that the proposed method of including quality information about the auxiliary data in a prediction model can be an effective technique for improving the prediction accuracy.
-Ongoing studies investigate whether this modelling technique can also lead to smaller estimation errors of design-based estimators.
-(2) Our study also indicated that the relationship between the field measured timber volume and remote-sensing derived height information is tree species specific.
-We expect that using the tree species information in a timber volume model would even lead to higher prediction accuracies when combined with explanatory variables that can further explain the variation within each tree species group, such as bioclimatic growing conditions, soil properties and stand density on the plot level.
-(3) We consider the demonstrated calibration technique to be a valuable method for future studies where an external tree species map (i.e.
-the map was not created for the specific study objective) is used in prediction models.
-The application of a calibration model can also be transferred to any error-prone explanatory variable and be a simple means to clean the data set from noise and thus increase the model accuracy.
-
-% - CONCLIUSION: 
-%   o transfer of the suggested procedure to FDI inventories: maybe possible to get qunatified data for stands with acceptable estimation errors? (would be of high interest)
-%   o the decision wether the errors are acceptable cannot be answered here but (in our opinion) depend on the question whether ... decisions can be made based on the provided Confidence Intervals.
-%   o in a next step, we will investigate whether the derived confidence intervals are sufficient to be used as a validation for the stand-wise inventories (Kuliesis et al.)
-
-% - The existing German NFI data can provide substantially smaller estimation errors on forest district levels when used in the proposed double-sampling estimators.
-However, the question which errors are acceptable to support operational forest planning cannot be answered purely based on the absolute error values.
-In our opinion, it depends on the question whether the derived confidence intervals a) allow for more profound decisions between forest planning alternatives.
-
-% - prefer model-assisted estimators to synthetic estimators if one can afford --> because design-unbiased, they take the model inaccuracies into account and thus provide unbiased point estimates and more realsitic confidence intervals.

### 2018-02-27 Draft_Form/tex/Discussion.tex
update 27_02_2018
update 27_02_2018 (Alex review)

@@
 The aim of this study was to investigate the performance of design-based estimators for small area estimation of mean standing timber volume on two spatial forest management levels in Germany.
-It was of particular interest to gather information about the estimation error levels that can be realized using the German NFI data, characterized by low sampling intensities in the area of interests, as terrestrial phase information in the two-phase estimators.
-To address these research questions, we applied the simple random sampling (SRS), the pseudo-small (\psmall{}) and the extended pseudo-synthetic (\extpsynth{}) estimator for cluster sampling to 45 and 405 small area units in the German state of Rhineland-Palatinate.\par
+It was of particular interest to gather information about the estimation error levels that can be attained using German NFI data that is characterized by low sampling intensities in the area of interests.
+To address these research questions, we applied the SRS, the \psmall{} and the \extpsynth{} estimators for cluster sampling to two forest management levels consisting of 45 and 405 small area units respectively in the German state of Rhineland-Palatinate.\par
 
-Our study showed that on both small area levels, the \psmall{} and the \extpsynth{} estimator generally leads to a substantial reduction of the estimation errors produced by the SRS estimator.
-On the upper management level (FA districts), \psmall{} and \extpsynth{} allowed to provide estimation errors smaller than 5\% for 73\% of the small areas compared to only 17\% under the SRS estimator.
-This level of estimation accuracy could not be achieved on the subsequent management level (FR districts).
+Our study showed that on both small area levels, the \psmall{} and the \extpsynth{} estimators generally led to a substantial reduction in estimation error compared to the standard one-phase SRS estimator.
+On the upper management level (FA districts), \psmall{} and \extpsynth{} produced estimation errors smaller than 5\% for 73\% of the small areas compared to only 17\% under the SRS estimator.
+The same level of precision could not be achieved on the lower management level (FR districts) primarily due to substantially smaller terrestrial sample sizes.
 The reason for this were primarily the substantially smaller terrestrial sample sizes.
-However, in most FR units (95\%), the estimation errors could be limited to 20\% compared to 40\% under SRS.
-A pairwise comparison of the confidence intervals revealed that the estimators did thereby not produce significantly different point estimates.
-The much smaller estimation errors of the \psynth{} estimator suggested that the neglection of the regression model accuracies in the small area units leads to overoptimistic estimation accuracies and confidence intervals.
-If possible, one should thus prefer the unbiased estimates of \psmall{} or \extpsynth{}.\par
+However, in 95\% of the FR units, the estimation errors could be limited to 20\% compared to 40\% under SRS.
+A pairwise comparison of the confidence intervals revealed that the estimators did not produce significantly different point estimates.
+The much smaller estimation errors of the \psynth{} estimator
+reflected the fact that it does not try to correct for potential bias in the point estimate which can lead to overly optimistic estimation errors and confidence intervals.
+One should thus prefer the unbiased estimates of \psmall{} or \extpsynth{}.\par
 
@@
 This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero-mean-residual property of the \extpsynth{}.
-However, our analysis indicated that the difference between the two estimators are negligible for sample sizes $\geq$ 10 due to their asymptotic equivalency.
-Furthermore, one or more clusters not entirely included in the small area unit did reassuringly not have a notable impact on the estimates of \extpsynth{}.
-This empirical evidence can however not be generalized to any application of \extpsynth{} under cluster sampling.
+However, our analysis indicated that the difference between the two estimators is negligible for sample sizes $\geq$ 10 due to their asymptotic equivalency.
+Furthermore, one or more clusters not entirely included in the small area unit did not have a notable impact on the estimates of \extpsynth{} when the terrestrial sample size was more than 6.
+However, there was a slight but statistically significant tendency to be over-optimistic for sample sizes between 4 and 6.
+More empirical evidence must be gathered before generalizing this as a rule of thumb for the application of the \extpsynth{} under cluster sampling.
 It thus seems recommendable to calculate both \psmall{} and \extpsynth{}, and subsequently compare their results.
@@
 Likewise in many similar studies, the ALS mean canopy height proved to be the explanatory variable with highest predictive power.
-However, the large time-gaps of up to 10 years between the ALS acquisition and the terrestrial survey date caused a substantial introduction of artificial noise in the data.
-Whereas a stratification to the ALS acquisition years was an effective means to counteract the implied residual inflation, several leverage points were unambiguously caused by the temporal asynchronicity.
+However, the large time-gaps of up to 10 years between the ALS acquisition and the terrestrial survey date caused the substantial introduction of artificial noise in the data.
+Whereas a post-stratification to the ALS acquisition years was an effective means to counteract the implied residual inflation, several leverage points were unambiguously caused by the temporal asynchronicity.
 As opposed to the ALS data, the availability of a country-wide tree species classification map has yet been unique among all German federal states.
-Whereas the study of \citet{hill2017a} already showed that the tree species information was able to improve the model accuracy, it has yet not been used to its full potential.
-One reason for this was the impossibility of a tree species individual modeling within each ALS acquisition year, which we consider to add further explanatory power.
-Another reason was the lack of available satellite data for classification in some parts of the country, which led to missingness in the inventory data and restricted 19 FR units to a simpler regression model.
+Whereas the study of \citet{hill2017a} already showed that the tree species information was able to improve the model fit, it has yet not been used to its full potential.
+One reason for this was the impossibility of modeling individual tree species within each ALS acquisition year, which would add further explanatory power.
+Another reason was the lack of available satellite data for classification in some parts of the country, which led to missing values in the inventory data and restricted 19 FR units to a simpler regression model.
 Promising steps with respect to more up-to-date canopy height information have already been made, as the topographic survey institution of RLP will from this year on provide a country-wide canopy height model derived from aerial imagery acquisitions.
 These campaigns will in the future be conducted in a two-year period and allow to derive canopy height information matching the dates of terrestrial forest inventories.
-A study of \citet{kirchhoefer2017} recently indicated that similar model accuracies for German NFI data can be achieved using such imagery-based canopy height models.
-Due to the improved coverage and repetition rate of the Sentinel-2 satellite, also the tree species classification map will in the future be updated each year.
+A study of \citet{kirchhoefer2017} recently indicated that similar model performance for German NFI data can be achieved using such imagery-based canopy height models.
+Due to the improved coverage and repetition rate of the Sentinel-2 satellite \citep{sentinel2}, the tree species classification map will in the future be updated each year.
 We consider these alternative auxiliary data sources to also solve the problem of missing explanatory variables at inventory plots.
-Thus, one could also make use of the exhaustive information within the two-phase estimators by using the true the auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which theoretically leads to a further decrease of the estimation errors.
+One could also make use of the exhaustive information within the two-phase estimators by using the true the auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which could further decrease of the estimation errors.
 Previous studies of \citet{mandallaz2013b} however showed that given a reasonable large sample size of the first phase, the differences in the estimation error are usually small.

### 2018-02-27 Draft_Form/tex/Introduction(2).tex
update 27_02_2018
update 27_02_2018 (Alex review)

@@
 
-The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germanys forest over time.
-The NFI thereby has to satisfy various information needs and amongst others reports to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}.
-At the current time, the inventory design of the German NFI solely rests upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany.
-As this implies covering a large area of 114'191 ha \citep{bwi3}, the sample size has been chosen according to satisfy high estimation accuracies for forest attributes on the national and federal state level.
-This however leads to very low sampling intensities and consequently, sample sizes often drop dramatically when entering spatial units below the federal state level.
-This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out be unacceptably large due to the very limited number of sample plots within these units.
-For this reason, the German NFI data have not yet been extensively incorporated in operational forest planning on forest district management levels.
-In most German federal states, management strategies are thus still based on expert judgements from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par
+The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germany's forest over time.
+The NFI thereby has the responsibility to satisfy various information needs including reporting to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and to the United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}.
+The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany.
+In order to cover a large area of 114'191 ha \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels.
+However, sample sizes often drop dramatically when entering spatial units below the federal state level.
+This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out to be unacceptably large due to the very limited number of sample plots within these units.
+For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels.
+In most German federal states, management strategies are thus still based on expert judgments from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par
 
-Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to base their regional management strategies on quantitative and accurate information \citep{bockmann1998}.
+Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}.
 However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonluepke2013}.
-One method which has proven to be efficient is double-or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}.
-Double sampling incorporates inexpensive auxiliary information and can be used to either increase estimation precision under given terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size.
-A double sampling for stratification procedure has e.g.
-been used in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} lately illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs.
-Recent studies have lately extended double-sampling to triple-sampling estimation methods using auxiliary information in two different sampling intensities.
-An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories.
-An other example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par
+One method which has proven to be efficient is double- or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}.
+Double sampling incorporates less expensive auxiliary information and can be used to either increase estimation precision under a fixed terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size.
+Double-sampling procedures have already been used for stratification in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs.
+Recent studies have extended double-sampling to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities.
+An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI of Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories.
+Another example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par
 
-Two-phase and three-phase samplings techniques have also been used in the service of small area estimation (SAE).
-SAE techniques particular address the situation where the number of samples within a subunit, so-called small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit.
+Two-phase and three-phase samplings techniques have also been applied to small area estimation (SAE).
+SAE techniques address the situation where the number of samples within a subunit, or small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit.
 A broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics.
-A commonly applied SAE method is thereby known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not available in the small area.
-The statistical models are thereby often developed by "borrowing strength" from data outside the small area.
-There are numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, and most of the studies use unit-level models, i.e.
-the statistical models are fitted using data from inventory plots.
-Especially unit-level models for timber volume estimation under the use of various remote sensing data have been intensively investigated with respect to timber volume prediction \citep{koch2010, naesset2014inmaltamo}.
-There are also few studies that have investigated area level-models, where the auxiliary information is only provided on the SA-level \citep{magnussen2017}.
-Some studies have illustrated that even NFI data of low sampling densities can be used in small area estimation procedures to provide estimations of acceptable accuracy on much smaller management levels.
-One example is \citet{breidenbach2012} who used data from the Norwegian NFI for SAE estimations of standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35.
-Estimation errors under the applied model-based and design-based SAE estimators turned to be markedly smaller than achieved under simple random sampling (SRS).
-Another example is \citet{magnussen2014} who recently used the Swiss NFI data for SAE estimation of timber volume within 108 Swiss forest districts with sample sizes between 9 and 206.
-Despite these promising results, a similar study in Germany using the German NFI data for SAE estimation has not yet been conducted.\par
+One such method that is commonly applied is known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not observed in the small area.
+These models are trained using data from outside the small area in order to "borrow strength" from areas where information is available.
+Of numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, most use unit-level models, i.e.
+the inventory plot is the unit of the response variable in the training data used for the model fit.
+Such unit-level models have been intensively investigated for timber volume estimation using various remote sensing auxiliary data \citep{koch2010, naesset2014inmaltamo}.
+Other studies have investigated area-level models, where the auxiliary information is only provided on the SA level \citep{magnussen2017}.
+Some studies have illustrated that even NFI data derived under low sampling densities can still be used to provide acceptable precision of small area estimates on much smaller management levels.
+One example is \citet{breidenbach2012} who used data from the Norwegian NFI to make small area estimation for standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35.
+The estimation errors under the applied model-based and design-based small area estimators turned to be markedly smaller than under the standard one-phase estimator.
+Another example is \citet{magnussen2014} who recently used the Swiss NFI data to estimate timber volume within 108 Swiss forest districts with sample sizes between 9 and 206.
+Similar studies using German NFI data for small area estimation have been lacking.\par
 
-The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels when incorporated in small area estimation procedures.
+The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels using the latest small area estimation procedures.
 We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 45 and 405 forest districts respectively.
 The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a, mandallaz2013b}.
-Auxiliary data were obtained from a countrywide airborne Laser scanning (ALS) canopy height model (CHM) and a tree species classification map and used for regression within tree species strata.
-The estimation accuracies were compared to those achieved under SRS sampling.
-The chosen double-sampling estimators were favoured for several reasons: \textbf{(i)} the design-based frame considerably relaxes requirements on the regression model which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can consider \textit{non-exhaustive}, i.e.
-non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for the design-dependency of the regression coefficients on the sample (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals.
+Auxiliary data consisted of a canopy height model (CHM) obtained from a countrywide airborne laser scanning (ALS) and a tree species classification map to be used for regression within tree species strata.
+The estimation precisions were compared to those obtained by the standard one-phase estimator for cluster sampling under simple random sampling.
+The chosen double-sampling estimators were selected for several reasons: \textbf{(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can be used with \textit{non-exhaustive}, i.e.
+non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals.
 The results from this study were considered to provide valuable information whether the suggested procedure might be a cost-saving alternative to a regional FDI.\par

### 2018-02-27 Draft_Form/tex/Materials_and_Methods(2).tex
update 27_02_2018
update 27_02_2018 (Alex review)

@@
 
-The German National Forest Inventory (German NFI) is a periodic inventory that is carried out every 10 years over the entire forest area of Germany.
-The most recent inventory (BWI3) was conducted in the years 2011 and 2012.
-While information was originally gathered at a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid.
-The German NFI uses a cluster sampling design, which means that a sample unit consists of maximal four sample locations (also referred to as \textit{sample plots}) that are arranged in a square (so called \textit{cluster}) with a side length of 150 metres.
-The number of plots per cluster can however vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}.
+The German NFI is a periodic inventory that is carried out every 10 years over the entire forest area of Germany.
+The most recent inventory (BWI3) was conducted in 2011 and 2012.
+While information was originally gathered on a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid.
+The German NFI uses a cluster sampling design, which means that a sample unit consists of at most four sample locations (also referred to as \textit{sample plots}) that are arranged in a square, called \textit{cluster}), with a side length of 150 metres.
+The number of plots per cluster can vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}.
 In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the tree-individual inclusion circle \citep{bwi3_aufn}.
-A further inventory threshold for a tree to be recorded is a diameter at breast height ($dbh$) of at least 7 cm.
-For each sample tree that is selected by this procedure, the dbh, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to calculate a volume estimation on the tree level.
-These volume estimations are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.
+A further inventory threshold for a tree to be recorded is a diameter at breast height ($DBH$) of at least 7 cm.
+For each sample tree that is selected by this procedure, the DBH, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to estimate the volume at the tree level.
+These volume estimates are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.
 
@@
 
-The estimators used in this study have been proposed by \citep{mandallaz2013a,mandallaz2013b} and build upon the so called infinite population approach (IPA) in order to bridge the inventory procedure and the derived information to the mathematics behind the estimators.
-Therefore, we shall first provide a short introduction into this general estimation frame.
-We start by assuming that the population $P$ of trees $i \in 1,2, ..., N$ within a forest of interest $F$ is exactly defined, and each tree $i$ has a directly or indirectly observable response variable $Y_i$ (e.g.
-its timber volume) that allows to specify the population mean $Y$ (e.g., the average timber volume per unit area) over $F$.
-If a full census of all tree population individuals is not possible, $Y$ has to be estimated by the conduction of an inventory.
-The infinite population approach assumes that the spatial distribution of the local density $Y(x)$ (e.g., the timber volume per unit area) at each point or location $x$ in the forest $F$ is given by a fixed (i.e.
+The estimators used in this study have been proposed by \citep{mandallaz2013a,mandallaz2013b} and derive their mathematical properties under the so-called infinite population approach (IPA).
+Therefore, we shall first provide a short introduction into this general estimation framework.
+We start by assuming that the population $P$ of trees $i \in 1,2, ..., N$ within a forest of interest $F$ is exactly defined, and each tree $i$ has a response variable $Y_i$ (e.g.
+its timber volume) that can be used to define the population mean $Y$ (e.g., the average timber volume per unit area) over $F$.
+Since a full census of all tree population individuals is almost never feasible, $Y$ has to be estimated based on a sample.
+In the infinite population approach this sample is a set of points or locations $x$ distributed independently and uniformly over the set of all possible points in $F$.
+Each point $x$ has an associated local density $Y(x)$ (e.g., the timber volume per unit area) whose spatial distribution is given by a fixed (i.e.
 non stochastic) piecewise constant function.
-The population mean $Y$ is thus mathematically equivalent to the integral of the density function surface divided by the forest area $\lambda(F)$, i.e.
-$Y=\frac{1}{\lambda(F)} \sum_{i=1}^{N}Y_i=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$, and thus the population mean $Y$ corresponds to a spatial mean.
-Since the local density function is in practice always unknown, one estimates $Y$ by collecting a sample $s_2$ of all local density values by the conduction of a terrestrial inventory at $n_2$ uniformly and independently distributed sample points over $F$.
-This procedure is often referred to as \textit{one-phase sampling} (OPS).
-Opposed to the one-phase approach, \textit{two-phase} or \textit{double-sampling} procedures use information from two nested samples (phases).
+The population mean $Y$ is mathematically equivalent to the integral of the local density function surface divided by the surface area of $F$, $\lambda(F)$, i.e.
+$Y=\frac{1}{N} \sum_{i=1}^{N}Y_i=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$, and thus the population mean $Y$ corresponds to a spatial mean.
+Since the actual local density function is unobserved in its entirety, one estimates $Y$ by taking a sample $s_2$ consisting of $n_2$ points and measuring each of their respective local densities.
+This sampling procedure is often referred to as \textit{one-phase sampling} (OPS) and $s_2$ is referred to as the terrestrial inventory.
+In contrast to the one-phase approach, \textit{two-phase} or \textit{double-sampling} procedures use information from two nested samples (phases).
 Practically speaking, the terrestrial inventory $s_2$ is embedded in a large phase $s_1$ comprising $n_1$ sample locations that each provide a set of explanatory variables described by the column vector $\pmb{Z}(x)=(z(x)_1, z(x)_2,...,z(x)_p)^{\top}$ at each point $x \in s_1$.
@@
 % ++++++++++++ %
-\subsection{Design-based SRS estimator for cluster sampling}
+\subsection{Design-based one-phase estimator for cluster sampling (SRS)}
 \label{sec:srs_estimator}
 
-The simple random sampling (SRS) estimator for cluster sampling constitutes the \textit{status quo} that is currently applied under the existing one-phase sampling design of the German NFI in order to obtain a point and variance estimate for the mean timber volume of a given estimation unit.
+The one-phase estimator for cluster sampling (SRS) constitutes the \textit{status quo} that is currently applied under the existing one-phase sampling design of the German NFI in order to obtain point and variance estimates for the mean timber volume of a given estimation unit.
 In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator that is applied in the BWI3 algorithms \citep{bwi3_ausw} in the form given in \citet{mandallaz2008, mandallaz2016}.\par
 In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M=4$ ) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$.
-The actual number of plots per cluster, $M(x)$, is a random variable due to the uniform distribution of $x_l$ ($l=1, ..., M$) in the forest $F$ and forest/non-forest decision for each sample location $x_l$:
+The actual number of plots per cluster, $M(x)$, is a random variable due to the uniform distribution of $x_l$ ($l=1, ..., M$) in the forest $F$ and to the forest/non-forest decision for each sample location $x_l$:
 
@@
 
-The local density on cluster level $Y_{c}(x)$, in our case the timber volume per hectare, is then defined as the average of the individual sample plot densities $Y(x_l)$:
+The local density on cluster level $Y_{c}(x)$, which in our case the timber volume per hectare, is then defined as the average of the individual sample plot densities $Y(x_l)$:
 
@@
 
-where $Y_i$ is in our case the predicted timber volume of the tree $i$ recorded at sample location $x$ in m$^3$.
+\noindent where $Y_i$ is in our case the timber volume of the tree $i$ recorded at sample location $x$ in m$^3$.
 Each tree has an inclusion probability $\pi_{i}$ that is well defined as the proportion of its inclusion circle area $\lambda(K_i)$ within the forest area $\lambda(F)$, i.e.
@@
 
-The radius $R_i$ of the tree-individual inclusion circle $K_i$ is given by $R_i = bhd_{i}/cf_{i,corr}$ (also referred to as \textit{limiting distance}), where $cf_{i,corr}$ is the counting factor corrected for potential boundary effects at the forest border.
+The radius $R_i$ of the tree's inclusion circle $K_i$ is given by $R_i = DBH_{i}/cf_{i,corr}$ (also referred to as \textit{limiting distance}), where $cf_{i,corr}$ is the original counting factor $cf$ corrected for potential boundary effects at the forest border.
 In case of angle-count sampling, we can rewrite $\pi_{i}$ as
@@
 
-since the intersection area $\lambda(K_i \cap F)/\lambda(F)$ can be expressed using the trees basal area $G_i$ (in m$^2$) and the corrected counting factor:
+\noindent since the intersection area $\lambda(K_i \cap F)/\lambda(F)$ can be expressed using the trees basal area $G_i$ (in m$^2$) and the corrected counting factor:
 
@@
 
-Using Eq.
-\ref{eq:locdens_plot_2} in Eq.
-\ref{eq:locdens_plot} yields the rewritten form of $Y(x_l)$ for angle count sampling that conforms to the definition used in the BWI3 algorithms \citep{bwi3_ausw}:
+Eq. \ref{eq:locdens_plot_2} in Eq. \ref{eq:locdens_plot} yields the rewritten form of $Y(x_l)$ for angle count sampling that conforms to the definition used in the BWI3 algorithms \citep{bwi3_ausw}:
 
@@
 
-where $nha_i$ is the number of trees per hectare represented by tree $i$.
-The local densities on cluster level can then be used to derive the estimated spatial mean $\hat{\bar{Y}}_c$ and its estimated variance $\hat{\var}(\hat{Y}_c)$ for any given spatial unit for which $n_2 \geq 2$ ($n_2$ denoting the number of sample units, i.e.
-clusters):
+\noindent where $nha_i$ is the number of trees per hectare represented by tree $i$.
+The local densities on cluster level can then be used to derive the estimated spatial mean $\hat{\bar{Y}}_c$ and its estimated variance $\hat{\var}(\hat{\bar{Y}}_c)$ for any given spatial unit for which $n_2 \geq 2$ ($n_2$ denoting the number of clusters):
 
@@
 
+with $\bar{M_2}=\frac{\sum_{x \in s_{2}}M(x)}{n_{2}}$.
+
 % \newpage
@@
 
-All three considered small area estimators have in common that they use ordinary least square (OLS) regression models to produce the predictions of the local density $Y_{c}(x)$ directly on the cluster level $c$.
-We consider the \textit{internal model approach}, where the vector of estimated regression coefficients on the cluster level is found by "borrowing strength" from the entire terrestrial sample $s_2$ of the current inventory:
+All three considered small area estimators use ordinary least square (OLS) regression models to produce predictions of the local density $Y_{c}(x)$ directly on the cluster level $c$.
+We consider the internal model approach, where the estimators take into account that the regression coefficients on the cluster level were fitted using the same sample used for estimation.
+To apply this to small area estimation, the vector of estimated regression coefficients on the cluster level is found by "borrowing strength" from the entire terrestrial sample $s_2$ of the current inventory:
 
@@
 
-\noindent The estimated design-based variance-covariance matrix $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}$ accounts for the fact that the regression model is internal by reflecting the dependency of the estimated regression coefficients on the realized sample $s_2$.
+\noindent The estimated design-based variance-covariance matrix $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}$ accounts for the fact that the regression model is internal and reflects the sampling variability that occurs when estimating the regression coefficients on the realized sample $s_2$.
 It is defined as
@@
 \begin{equation}\label{eq:varcovarbeta}
-\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}=\pmb{A}_{c,s_2}^{-1}
+\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}=\pmb{A}_{c,s_2}^{-1}
 \Big(\frac{1}{n_2^2}\sum_{x\in{s_2}}M^{2}(x)\hat{R}_{c}^2(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)\Big)
@@
 
-with
+\noindent with
 
@@
 The second term then corrects for a potential bias of the regression model predictions in the small area $G$ by adding the mean of the empirical residuals $\bar{\hat{R}}_{2,G}$ in $G$.
-This correction insures that the \textit{zero mean residual property} in $F$ also holds within the small area $G$, which is per se not ensured by fitting the regression coefficients with data outside $G$.
+This correction is necessary because the zero mean residual property that holds in $F$ is not guaranteed to hold in small area $G$ under this construction.
 
@@
 	& + \frac{1}{n_{2,G}(n_{2,G}-1)}\sum_{x \in s_{2,G}}\Big(\frac{M_{G}(x)}{\bar{M}_{2,G}}\Big)^2(\hat{R}_{c,G}(x) - \bar{\hat{R}}_{2,G})^2
-	\label{eq:psmall_var}
+	\label{eq:psmallvar}
 	\end{align}
 \end{subequations}
-
-The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Eq.
-\ref{eq:psmall_var}.
-Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean in $G$ using a non-exhaustive sample $s_{1,G}$.
-The third term is the variance of the model residuals and thus accounts for the inaccuracies of the model predictions.
-Note that the first term can also be rewritten using g-weights \cite[pg.14]{mandallaz2016} which ensure calibration properties of the auxiliary variables on the terrestrial sample.\\
 
@@
 with $\bar{M}_{1,G}=\frac{\sum_{x \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.\\
+
+The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Eq.
+\ref{eq:psmall_var}.
+Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean in $G$ using a non-exhaustive sample $s_{1,G}$.
+The third term is the variance of the model residuals and thus accounts for the inaccuracies of the model predictions.
+Note that the first term can also be rewritten using g-weights \cite[pg.14]{mandallaz2016} which ensures some beneficial calibration of the auxiliary variables to the first-phase sample.\\
 
@@
 
-The uncertainty of the model predictions can also no longer be considered in the variance estimation (Eq.
+The contribution to the variance by the model residuals in small area $G$ can also no longer be considered (Eq.
 \ref{eq:psynth_var}).
-The synthetic estimator will therefore usually have a smaller variance than estimators incorporating the model uncertainties, but at the cost of a potential bias.
+As a result, the synthetic estimator will usually have a smaller variance than estimators that consider the model residuals, but at the cost of a potential bias.
 Note that the \psynth{} estimator is still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.\\
@@
 
-The estimation accuracies were quantified by the \textit{estimation error}, which is the ratio of the standard error and the point estimate:
+The estimation precision was quantified by the estimation error, which is the ratio of the standard error and the point estimate:
 
 \begin{equation}\label{eq:error}
-error(\hat{Y})_{[\%]}=\frac{\sqrt{\var(\hat{Y})}}{\hat{Y}}*100
+error(\hat{Y})_{[\%]}=\frac{\sqrt{\hat{\var}(\hat{Y})}}{\hat{Y}}*100
 \end{equation}
 
-We further calculated the 95\% confidence interval for each estimate for visualization purpose.
-The confidence intervals can also be used for hypothesis testing whether the point estimates of the three estimators for a given small area are statistically different.
+We further calculated the 95\% confidence interval for each estimate for visualization purposes.
+The confidence intervals can also be used heuristically for hypothesis testing to determine whether the point estimates of the three estimators for a given small area are statistically different.
 The confidence intervals under SRS can be obtained as:
@@
 \end{equation}
+
+\noindent with $p$ being the number of parameters used in the regression model including the intercept term.\\
 
@@
 8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}.
-The forests of RLP are further characterized by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterized by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a.
+The forests of RLP are further characterised by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterised by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a.
 Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech.
@@
 On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 405 Forstreviere (\textit{FR}).
-The next level are the forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5- to 10 year period in order to set up management strategies for the upcoming 10 years.
-The FAs and FRs constituted the small area (SA) units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}.
+The next level are the forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5 to 10 year period in order to set up management strategies for the upcoming 10 years.
+The FAs and FRs constituted the SA units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}.
 The average area of the SA units were 43'777 ha on the FA-level, and 4624 ha on the FR level.
@@
 Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI.
-In the last inventory (BWI3) conducted in the year 2013, timber volume information was derived for 2810 cluster (8092 plots) in the field survey.
+In the last inventory (BWI3) conducted in the year 2013, timber volume information was derived for 2810 clusters (8092 plots) in the field survey.
 The local timber volume density on the plot and cluster level for this sample was consequently calculated according to Section \ref{sec:srs_estimator}.
-In the frame of this survey, the plot center coordinates were re-measured with differential global satellite navigation system (DGPS) technique.
-Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrially observations and the information derived from the auxiliary information.
+In the framework of this survey, the plot center coordinates were re-measured with the differential global satellite navigation system (DGPS) technique.
+Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrial observations and the information derived from the auxiliary information.
 A comparison of the DGPS coordinates with the so-far used target coordinates revealed that 90\% of all horizontal deviations lay in the range of 25 meters.
@@
 For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.
-The terrestrial sample size $n_{2,G}$ within the FA units was 46 cluster on average and ranged between 11 and 64.
+The terrestrial sample size $n_{2,G}$ within the FA units was 46 clusters on average and ranged between 11 and 64.
 Within the FR units, $n_{2,G}$ was considerably smaller with an average of 5 cluster and a range between 0 and 13.
@@
 
-In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 kilometer grid to a grid size of 500x500 meters that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}).
-The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ cluster by the terrestrially measured DGPS coordinates.
+In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}).
+The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ clusters by the terrestrially measured DGPS coordinates.
 For our study, we restricted the \textit{sampling frame} to the communal and state forest.
@@
 Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.
-The terrestrial sample size $n_2$ was thus reduced to 2055 cluster (5791 plots).
+The terrestrial sample size $n_2$ was thus reduced to 2055 clusters (5791 plots).
 Table \ref{tab:fieldata} provides a short descriptive summary about the volume densities and the main attributes of the NFI plots located in the state and communal forest sampling frame.
-The densification led to an average sample size $n_{1,G}$ of 759  cluster (range: 246 -- 1022) in the FA units, and 88 cluster (range: 1 -- 194) in the FR units.
+The densification led to an average sample size $n_{1,G}$ of 759  clusters (range: 246 -- 1022) in the FA units, and 88 clusters (range: 1 -- 194) in the FR units.
 
@@
 
-A prerequisite for the application of the suggested two-phase small area estimators was the identification of suitable auxiliary data available over the entire study area.
-Between the year 2003 and 2013, the topographic survey institution of RLP conducted an airborne laser scanning (ALS) acquisition over the entire federal state at leaf-off condition in order to derive a countrywide digital terrain and surface model.
-For this study, the recorded LiDAR data was used to create a canopy height model (CHM) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters (Figure \ref{fig:Auxvars}, \textit{top}).
+A prerequisite for the application of the suggested two-phase small area estimators is the identification of suitable auxiliary data available over the entire study area.
+From 2003 and 2013, the topographic survey institution of RLP conducted an airborne laser scanning acquisition over the entire federal state during leaf-off conditions in order to derive a countrywide digital terrain model (DTM) as well as a digital surface model (DSM).
+For this study, the recorded LiDAR data was used to create a canopy height model in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters (Figure \ref{fig:Auxvars}, \textit{top}).
 The CHM (Fig.
-\ref{fig:Auxvars}, \textit{top}) was calculated as the difference between the digital terrain model (DTM) and the digital surface model (DSM) that were derived by a Delauney interpolation of the ground and first ALS pulses respectively.
+\ref{fig:Auxvars}, \textit{top}) was calculated as the difference between the digital terrain model and the digital surface model that were derived by a Delauney interpolation of the ground and first ALS pulses respectively.
 A more detailed description of the procedure can be found in \citet{hill2017a}.
-The CHM was considered to provide the most valuable information to be used in the OLS regression model for predicting the timber volume on sample plot and cluster level.
-However, the extended acquisition period of the ALS campaign led to substantial time gaps to the BWI3 survey of up to 10 years.
-In addition, the CHM exhibited severe quality variations in the CHM du to evolving ALS technology over the years.
-LiDAR acquisition recorded in 2002 and 2003 particularly showed a rather poor quality with about only 0.04 point per m$^2$, while more recently acquired datasets contained more than 5 points per m$^2$.
-Furthermore CHM information was not available at 16 sample locations due to sensor failures.
-These plots were deleted from the sampling frame and its non-available information thus treated as missing at random.
+The CHM provided the most valuable information to be used in the OLS regression model for predicting the timber volume on the plot and cluster level.
+However, it should be noted that the prolonged acquisition period of the ALS campaign led to the possibility of poor temporal alignment with the BWI3 survey, sometimes up to 10 years.
+In addition, the quality of the CHM varied substantially as ALS technology evolved over the years.
+For example, LiDAR acquisition recorded in 2002 and 2003 exhibited particularly poor quality with about only 0.04 point per m$^2$, whereas more recent datasets contained more than 5 points per m$^2$.
+Furthermore, CHM information was not available at 16 sample locations due to sensor failures.
+These plots were deleted from the sampling frame and treated as missing at random.
 This assumption was considered to be reasonable as the respective sample locations did not exclude specific forest structures.
@@
 \ref{fig:Auxvars}, \textit{bottom}).
-The tree species map has a grid size of 5 meters and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) by application of a spatially adaptive classification algorithm \citep{stoffels2012}.
-As timber volume estimations on the tree level are often based on species-specific biomass and volume equations, the use of tree species information has often been stated as a key factor for improving the precision of timber volume estimates \cite{white2016}.
+The tree species map has a grid size of 5x5 m and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) using a spatially adaptive classification algorithm \citep{stoffels2012}.
+As timber volume estimation on the tree level is often based on species-specific biomass and volume equations, the use of tree species information has often been stated as a key factor for improving the precision of timber volume estimates \cite{white2016}.
 In this respect, incorporating the tree species map was particularly attractive as it predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree.
-However, due to unavailable satellite data, the tree species map excluded one large patch with an area of 415 km$^2$ in the south-west part of RLP covering an entire FA unit (10 FR units respectively).
-In 9 additional FR units, the tree species information was also missing for a subset of the sample locations due to two additional patches with an area of 76 km$^2$ and 100 km$^2$ in the northern part of RLP.
+However, due to unavailable satellite data, the tree species map excluded one large patch with an area of 415 km$^2$ in the south-west part of RLP covering an entire FA unit consisting of 10 FR units.
+In 9 additional FR units, the tree species information was also missing for a subset of the sample locations due to two additional patches with areas of 76 km$^2$ and 100 km$^2$ respectively in the northern part of RLP.
 For these 19 FR units, small area estimation was thus restricted to using only the available CHM information in the regression model.
-With respect to fitting the internal model for estimation, the tree species information was missing for 411 (7\%) of the 5791 sample locations.
+Thus, 411 of 5791 sample locations (approximately 7\%) used to fit the regression model were affected by missing tree species information.
 A summary of the sample sizes and missing auxiliary data for both the CHM and the tree species map is provided in Table \ref{tab:ssize}.
@@
 	\begin{center}
-		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plots}$: number of plots. $n_{\{1,2\}}$: number of cluster}
+		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plots}$: number of plots. $n_{\{1,2\}}$: number of clusters. TSPEC: tree species information.}
 		\vspace{0.2cm}
@@
 	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/Auxvars_100dpi.png}}
-	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information.
+	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level.
 Right: Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.}
@@
 
-\subsubsection{ALS canopy height model}
+\subsubsection{Canopy height model}
 
-Continuous explanatory variables derived from the CHM were the mean canopy height (\textit{meanheight}) and the standard deviation (\textit{stddev}).
-The quantities were calculated by evaluating the raster values around each sample location within a predefined circle (\textit{support}) with a radius of 12 meters.
-In order to correct for edge effects at the forest border, each support area was previously intersected with the state and communal forest area, which was defined by a polygon mask provided by the state forest service.
+The continuous explanatory variables derived from the CHM were the mean canopy height (\textit{meanheight}) and the standard deviation (\textit{stddev}).
+The quantities were calculated by evaluating the raster values around each sample location within a circle with a predefined radius of 12 meters, i.e.
+the support.
+In order to correct for edge effects at the forest border, the intersection of each support area to the state and communal forest area was determined using a polygon mask provided by the state forest service.
 The percentage of the support within the forest layer was used as the weight $w(x_l)$ introduced in Eq.
 \ref{eq:Zc(x)} in order to derive the weighted mean of the explanatory variables on the cluster level.
-Restricting the auxiliary data evaluation to the forest area was primarily a means to optimize the coherence between explanatory variables computed at the forest boundary and the corresponding local density, but also supports the consistency with the sampling frame (section \ref{ext_to_2phase}).
-In particular, the BWI3 survey applies an edge correction at the forest border at the individual tree level by intersection of the trees' inclusion circle with the forest border.
-An adjustment for the fact that part of a trees' inclusion circle is outside the forest area is then realized by increasing its counting factor, which would otherwise lead to an underestimation of the local density.
-Since the ALS height values will usually drop to around zero outside the forest area, neglecting the edge correction of the support attenuates the mean canopy height value towards zero and thus increases the discrepancy to the local density.\par
-We further derived the year of the ALS acquisition (\textit{ALSyear}) as an additional categorical variable which was used to account for the time-lag between the CHM information and the terrestrial survey as well as to explain heterogeneity in the data introduced by the varying ALS quality.
-Adjustments were made to the original acquisition years by introducing an additional factor level \textit{2008\_1} for a subset of the 2008 acquisition where the quality turned out to be considerably poor due to a sensor error.
-In addition, the years 2006 and 2007 as well as 2012 and 2013 were pooled in order to increase the number of observations per factor level, resulting in nine categories in total (\textit{2002}, \textit{2003}, \textit{2007}, \textit{2008\_1}, \textit{2008}, \textit{2009}, \textit{2010}, \textit{2011} and \textit{2012}).
+Neglecting the calculation of this weight would deteriorate the coherence between explanatory variables computed at the forest boundary and the corresponding local density that already includes a potential boundary adjustment, thus introducing unnecessary noise to the model.
+The boundary adjustment to the support also makes the sampling frame more consistent for the different data sources (Section \ref{ext_to_2phase}).\par
+The ALS acquisition year (ALSyear) was added as a categorical variable in order to account for the time lag with the terrestrial survey as well as to help explain the heterogeneity in the data introduced by the varying ALS quality.
+In 2008, a sensor error produced particularly poor ALS quality so the year was divided accordingly into two factor levels, denoted \textit{2008\_1} and \textit{2008}.
+Furthermore, in order to increase the number of observations per factor level the years 2006 and 2007 were pooled together and the same was done for 2012 and 2013.
+The result was nine factor levels denoted as \textit{2002}, \textit{2003}, \textit{2007}, \textit{2008\_1}, \textit{2008}, \textit{2009}, \textit{2010}, \textit{2011} and \textit{2012}.
 
@@
 
-The tree species map information was used to predict the main tree species of the sample trees at each sample plot (\textit{treespecies}) as an additional categorical variable.
-This implied two consecutive processing steps.
-In the \textit{first} step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the edge-corrected support were classified as that species.
+The tree species map was used to predict the main tree species at each sample plot which served as an additional categorical variable called \textit{treespecies}.
+This involved two consecutive processing steps.
+In the first step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the edge-corrected support were classified as that species.
 Otherwise, the sample location was assigned the value 'mixed'.
-Likewise for the CHM variables, the support radius was 12 meters although the use of different support sizes for each explanatory variable would be in agreement with the two-phase estimators presented in section \ref{sec:SAestimators}.
-When using the \textit{treespecies} variable in a regression model, the support size and the percentage threshold particularly constitute parameters to be optimized in order to achieve an optimal variance decomposition of the data that subsequently leads to the best possible model accuracy.
-A detailed analysis and description of the optimal processing parameters for the explanatory variables of the present data set is provided in \citet{hill2017a}.
-In this study, the authors also applied a calibration model to the initially derived \textit{treespecies} variable that successfully removed the effects of misclassification errors on the regression model coefficients and increased the model accuracy.
-The calibration model consists of a decision tree from a random forest algorithm \citet{breiman2001} that was trained to predict the actual main plot tree species (known for all terrestrial plots) based on available auxiliary variables.
+Likewise for the CHM variables, the support radius was 12 meters although the use of different support sizes for each explanatory variable would be in agreement with the two-phase estimators presented in Section \ref{sec:SAestimators}.
+When using the \textit{treespecies} variable in a regression model, the support size and the percentage threshold parameters had to be optimized in order to minimize the variance within each level which subsequently leads to improved model precision.
+A detailed analysis and description of the optimal parameter processing for the explanatory variables of the present data set is provided in \citet{hill2017a}.
+In a second step, the \textit{treespecies} variable was also passed through a calibration model in order to reduce the effects of misclassification errors on the regression model coefficients and to increase model accuracy.
+The calibration model consisted of a decision tree from a random forest algorithm \citep{breiman2001} that was trained to predict the actual main plot tree species (known for all terrestrial plots) based on available auxiliary variables.
 These variables were the predicted \textit{treespecies} variable, the mean canopy height and standard deviation of the CHM, as well as the proportion of coniferous trees estimated from the classification map and the growing region derived from a polygon map.
-The algorithm was grown with 2000 trees considering $\sqrt{p} \approx$ 3 of the predictors for each split.
-In a \textit{second} step, we thus applied this calibration model to the \textit{treespecies} variable derived at all sample locations $s_1$.
+The algorithm was grown with 2000 trees considering 3 of the predictors for each split.
+We thus applied this calibration model to the \textit{treespecies} variable derived at all sample locations $s_1$.
 Table \ref{tab:classacc} gives the classification accuracies of the \textit{treespecies} variable after calibration.
@@
 				\hline
-				Main plot species & Producer's accuracy[\%] & User's accuracy[\%] & nref & nclass \\
+				Main plot species & Producer's accuracy[\%] & User's accuracy[\%] & n$_{ref}$ & n$_{class}$ \\
 				\hline \hline	
@@
 
-The model selection constituted a major part of the current study, especially because sophisticated challenges such as a) the heterogeneity in the remote sensing data, b) the identification of the optimal support sizes under angle count sampling and c) the incorporation of tree species information had to be addressed and investigated in order to identify the most accurate regression model realizable under the given data.
-We will here thus only provide a shortened summary of the extensive analysis carried out and refer to the study of \citet{hill2017a} if the reader is interested in more detailed information on the subjects.\par
-
-The model with highest \adjrsq{} and lowest RMSE was achieved with the variables \meanheight{}, \meanheight{}$^2$, \stddev{} and \alsyear{} derived from the ALS data as well as the \treespecies{} variable derived from the classification map as main effect terms.
-Additionally, interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{}, \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{} were included.
-The model yielded an \adjrsq{} of 0.48 and an RMSE of 140.62 \mha{} (46.7\%) on the plot level (table \ref{tab:modacc_modterms}, full model).
-While the study of \citet{hill2017a} only provide the model evaluations on the plot level, the two-phase estimators described in section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level.
-We thus re-evaluated the model as used in the estimators also on the cluster level (formulas given in Appendix) and found the model accuracies to be higher than on the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%).
-A stratification to the ALS acquisition years substantially improved the model accuracy and thus proved to be an effective means in accounting for the artificially introduced noise in the data set due to ALS quality variations and time-gaps between the ALS and the terrestrial survey.
-However, the stratification led to a highly unbalanced dataset when stratifying according to the \treespecies{} variable.
-For this reason, a species individual modeling within each \alsyear{} stratum remained infeasible, but might have further improved the model accuracy.
-An additional evaluation of the model residuals within each ALS acquisition year stratum revealed that the model accuracies substantially varied between the strata (table \ref{tab:adj_r2_within}).
-Values above the overall \adjrsq{} were particularly achieved in ALS acquisition years close to the terrestrial survey date (0.60 to 0.65 on the cluster level).
-This effect was substantially diminished when dropping the \alsyear{} variable from the model term.\par
-
-As depicted in section \ref{sec:tspecclass}, the information of the tree species classification map was missing within 1 FA and 19 FR units.
-For these small area units, we applied the regression model without the \treespecies{} variable (table \ref{tab:modacc_modterms}, reduced model).
-However, the model accuracy of the full and reduced model were found to be very similar on both the plot and cluster level.
-We thus assumed that the application of the reduced model would not cause substantially larger estimation errors as compared to the full model and subsequently performed a joint evaluation of the estimation results in section \ref{sec:Res}.
+The model selection process for this study required a substantial time commitment due to sophisticated challenges such as: a) the heterogeneity of the remote sensing data, b) the identification of the optimal support sizes under angle count sampling, and c) the incorporation of tree species information.
+Here, only a summary of the extensive analysis that was performed is provided but the reader can refer to \citet{hill2017a} if more details are desired\par
+The model with highest \adjrsq{} and lowest RMSE was achieved using \meanheight{}, \meanheight{}$^2$, \stddev{}, \alsyear{} and \treespecies{} as main effects, and including interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{}, \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{}.
+Summary information about the \adjrsq{}, RMSE and RMSE\% of the selected models is provided in Table \ref{tab:modacc_modterms}.
+The two-phase estimators described in Section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level.
+We re-evaluated the model as used in the estimators on the cluster level (formulas given in Appendix) and found improved model fits compared to the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%).
+The stratification by the ALS acquisition year substantially improved the model fit, indicating that it is an effective means in accounting for the noise in the data caused by ALS quality variations and time-gaps between the ALS and the terrestrial survey.
+However, the stratification led to a highly unbalanced data set when a further \treespecies{} stratification was included.
+For this reason, a individual species modeling within each \alsyear{} stratum remained infeasible, but might have further improved the model fit.
+An additional evaluation of the model's performance within each ALS acquisition year stratum revealed that the quality of the model fit substantially varied between the strata (Table \ref{tab:adj_r2_within}).
+In particular, values above the overall \adjrsq{} were higher in ALS acquisition years close to the terrestrial survey date compared to years with larger time gaps.\par
+As described in Section \ref{sec:tspecclass}, the information of the tree species classification map was missing within 1 FA and 19 FR units.
+For these small area units, we applied the regression model without the \treespecies{} variable (Table \ref{tab:modacc_modterms}, reduced model).
+However, the \adjrsq{}s of the full and reduced model were found to be very similar on both the plot and cluster level.
+This implied that the variance reduction of the reduced model when applied to the two-phase estimators would likely be comparable to that of the full model, which is why a joint evaluation of the estimation results is presented in Section \ref{sec:Res}.
 
@@
 
-Concerning the treatment of outliers or leverage points for model fitting, it should be noted that there is a major difference between the external and internal model approach.
+Concerning the existence of outliers or leverage points in the training set for the model, it should be noted that it is more problematic for \psmall{}, \psynth{} and \extpsynth{} to simply remove them as one might be inclined to do in a model-dependent context.
+Strictly speaking, outlier removal in the design-based context essentially means that those plots, and implicitly any potentially similar plots that were not realized in the selected sample, have been removed from the sampling frame and are no longer considered part of the forest area of interest.
+While this may be valid for some obvious typos or measurement errors, it is generally not advisable to manipulate the sampling frame after observing data collected from it, especially when the observation in question lies within the small area of interest.
+However, for sake of completeness, we conducted an analysis of influential observations \citep[pp.
+160--167]{fahrmeir2013} on the plot level for the full regression model.
+We calculated the leverage values and found that 10\% of all observations exceeded a predefined critical threshold, i.e.
+twice the average of the hat matrix diagonal entries.
+Further investigation revealed that several leverage points showed unusually large \meanheight{} values compared to their respective timber volume densities.
+They tended to occur in ALS acquisition years with longer time gaps to the terrestrial survey date and were thus more likely caused by harvesting activities in the sample plot area.
+Although these areas likely affected by harvest should clearly not be removed from the sampling frame, it does provided more justification for the inclusion of the \alsyear{} variable to mitigate these effects.
+
+%Concerning the treatment of outliers or leverage points for model fitting, it should be noted that there is a major difference between the external and internal model approach.
 In order to ensure the zero-mean-residual property of the \psmall{} and \extpsynth{} estimator under the internal model approach (section \ref{sec:psmall} and \ref{sec:extpsynth}), all observations of the terrestrial sample $s_2$ used for estimation must also be included in the modeling frame.

### 2018-02-27 Draft_Form/tex/Results.tex
update 12_02_2018
update 12_02_2018
update 27_02_2018
update 27_02_2018 (Alex review)

@@
 It should be noted that also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 2$.
-Due to substantial larger sample sizes, all estimators could however be applied to all 45 FA units.
-The average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (table \ref{tab:estres}).
+Due to substantially larger sample sizes, all estimators could however be applied to all 45 FA units.
+The average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (Table \ref{tab:estres}).
 An additional pairwise comparison of the 95\% confidence intervals revealed that the four estimators did in fact not produce statistically different point estimates for all FA and FR units.
@@
 				\hlineB{1}
-				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Point estimates} & \multicolumn{3}{c}{Errors [\%]} \\
+				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Point estimates} & \multicolumn{3}{c}{error$_{[\%]}$} \\
 				\cline{4-9} & & & mean & min & max & mean & min & max \\
@@
 % ----------------------------------------------------------------------- %
-\subsection{Estimation errors}
+\subsection{Estimation error}
 \label{sec:esterr}
 
-On both small area levels, the design-unbiased estimators \psmall{} and \extpsynth{} led to a substantial reduction in the estimation errors compared to the SRS estimator (fig.
+On both small area levels, the design-unbiased estimators \psmall{} and \extpsynth{} led to a substantial reduction in the estimation error compared to the SRS estimator (Fig.
 \ref{fig:disterrors}).
-On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under the \extpsynth{} and \psmall{} estimator (table \ref{tab:estres}).
-The cumulative error distribution (fig.
-\ref{fig:disterrors}, left) reveals that under the SRS estimator, errors $\leq$ 5\% were achieved for 17\% of the FA units (8 of 45).
+On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under the \extpsynth{} and \psmall{} respectively (Table \ref{tab:estres}).
+The cumulative error distribution (Fig.
+\ref{fig:disterrors}, left) reveals that under the SRS estimator, errors less than 5\% were achieved for 17\% of the FA units (8 of 45).
 This proportion could be increased to 62\% (28 FA units) and 73\% (33 FA units) by application of the \psmall{} and \extpsynth{} estimator.
-95\% of all estimates exhibited errors $\leq$ 9.5\% under the SRS estimator and $\leq$ 6.6\% when using \psmall{} or \extpsynth{}.
+95\% of all estimates exhibited errors less than 9.5\% under the SRS estimator and less than 6.6\% when using \psmall{} or \extpsynth{}.
 Estimation errors higher than 10\% only appeared twice for each of the three estimators.\par
-The error reduction by the \psmall{} and \extpsynth{} estimator was even more pronounced on the FR level (fig.
-\ref{fig:disterrors}, right), although the overall error niveau was substantially higher than on FA level.
-The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under the \psmall{} and \extpsynth{} estimator (table \ref{tab:estres}).
+Although the estimation errors were substantially larger overall on the FR level compared to the FA level due to smaller sample sizes, the error reduction from SRS by \psmall{} and \extpsynth{} were even more pronounced (Fig.
+\ref{fig:disterrors}, right).
+The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under \psmall{} and \extpsynth{} (Table \ref{tab:estres}).
 Errors smaller than 10\% were achieved for 15\% of the FR units by the SRS estimator, and for 46\% by the \psmall{} and \psynth{} estimator.
-95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors $\leq$ 20\%.
-In comparion, the SRS estimates resulted in errors $\leq$ 36.6\% for 95\% of the 388 FR units.
+95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors less than 20\%.
+In comparion, the SRS estimates resulted in errors less than 36.6\% for 95\% of the 388 FR units.
 
@@
 	\resizebox{1\hsize}{!}{\includegraphics{fig/error_distr_foa_fu.png}}
-	\caption{Cumulative distribution of estimation errors under the simple random sampling (SRS), the pseudo small (\psmall{}), the extended pseudo synthetic (\extpsynth{}) and the pseudo synthetic (\psynth{}) estimator.
+	\caption{Cumulative distribution of estimation errors under SRS, \psmall{}, \extpsynth{} and the \psynth{} estimator.
 \textit{Left}: Results for the 45 FA units.
@@
 This violation was actually observed in 155 of the 321 FR units (48\%).
+
 However, the affected FR units (depicted in red diamonds, fig.
@@
 % ----------------------------------------------------------------------- %
-\subsection{Reduction of SRS variance by \psmall{} and \extpsynth{}}
+\subsection{Variance reduction compared to SRS}
 \label{sec:gain_eval}
 
-A direct comparison of the realized variances within the small area units revealed that the application of the design-unbiased estimators (\psmall{} and \extpsynth{}) led to a reduction of the respective SRS variance in all FA units.
-In 75\% of the FA units, the \extpsynth{} estimator was able to reduce the SRS variance by up to 54.1\% (fig.
-\ref{fig:gain}).
-The reduction in variance was also expressed in the relative efficiency values, which were 2.02 on average and ranged between 1.18 and 4.13 on the FA level.
-On FR-level, the reduction in variance and the relative efficiencies reached even higher values (table \ref{tab:gain} and fig.
+The variance reduction relative to SRS for \psmall{} and \extpsynth{} are described in Figure \ref{fig:gain} and Table \ref{tab:gain}.
+A direct comparison of the variances within the small area units revealed that the application of the design-unbiased estimators (\psmall{}, \extpsynth{}) led to a variance reduction compared to SRS in all FA units.
+In 75\% of the FA units, the \extpsynth{} estimator was able to reduce the variance by up to 54.1\%.
+The reduction in variance can also be expressed in the relative efficiency values, which were 2.02 on average and ranged between 1.18 and 4.13 on the FA level.
+On FR level, the reduction in variance and the relative efficiencies reached even higher values (Table \ref{tab:gain} and Fig.
 \ref{fig:gain}).
@@
 	\centering
-	\resizebox{0.7\hsize}{!}{\includegraphics{fig/compare_onephase_extpsynth_psmall.png}}
+	\resizebox{0.73\hsize}{!}{\includegraphics{fig/compare_onephase_extpsynth_psmall.png}}
 	\caption{Cumulative distribution of variance reduction by the PSMALL and EXTPSYNTH compared to the SRS estimator for the  45 FA and 321 FR units.}
@@
 	\begin{center}
-		\caption{Descriptive summary of SRS variance reduction and relative efficiencies on the two forest district levels. $N_u$: number of evaluated small area units.}
+		\caption{Descriptive summary of variance reduction compared to SRS and relative efficiencies on the two forest district levels. $N_u$: number of evaluated small area units.}
 		\vspace{0.2cm}
@@
 				\hlineB{1}
-				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Reduction of SRS variance [\%]} & \multicolumn{3}{c}{relative efficiency} \\
+				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Variance reduction [\%]} & \multicolumn{3}{c}{relative efficiency} \\
 				\cline{4-9} & & & mean & min & max & mean & min & max \\
@@
 
-However, cases also occurred on the FR level where one or both two-phase estimators produced larger variance values than under the SRS estimator.
-This particularly happened in 19\% (61) of the FR units under the \extpsynth{}, and in 24\% (76) of the FR units under the \psmall{} estimator.
+Cases also occurred on the FR level where one or both two-phase estimators produced larger variance values than under the SRS estimator.
+This happened in 19\% of the FR units under the \extpsynth{}, and in 24\% of the FR units under the \psmall{} estimator.
 One possible reason for this was supposed to be a large residual variance due to a poor performance of the regression model within the small area unit.
 In order to investigate this hypothesis, we analyzed the three variance terms of the \psmall{} estimator (eq.
-\ref{eq:psmall_var}), i.e.
+\ref{eq:psmallvar}), i.e.
 the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residual (term 3).
-The latter particularly expresses the model performance within the small area unit.
-Figure \ref{fig:fail} illustrates the percentage reduction or increase of the SRS variance when compared to the \psmall{} variance for all FR units in dependence on a) the impact of residual variance on the g-weight variance, and b) the terrestrial sample size $n_{2,G}$.\par
+In general, the residual term is expected to make the largest contribution to the overall variance since it's sample size is based on $n_{2,G}$ whereas the auxiliary term and the coefficient term are based on larger sample sizes, i.e.
+$n_{1,G}$ and $n_2$ respectively.
+Figure \ref{fig:fail} illustrates the share of the overall variance by the residual term of the \psmall{} estimator scaled by the overall percentage reduction or increase of the variance compared to SRS for various small area sample sizes $n_{2,G}$.\par
 
-Obviously, the residual term generally constitutes the dominating part of the \psmall{} g-weight variance (around 84\% on average).
+The residual term generally constitutes the dominating part of the \psmall{} variance (around 84\% on average).
+Although high residual term dominance does not necessary indicate that the \psmall{} variance will be disproportionately large, as apparent from Figure \ref{fig:fail} (\textit{right}), the vast majority of the small areas where the \psmall{} variance was larger than the SRS variance had residual terms contributing over 75\% to the overall \psmall{} variance.
+Furthermore, the magnitudes of the worst cases tended to occur in lower sample sizes.
+For example, of the FR units that saw variance increases where $n_{2,G}=4$, the average increase was 272\%, compared to 62\% for FR units with $n_{2,G} > 4$ (Fig.
+\ref{fig:fail}, \textit{left}).
+In comparison, the magnitude of the variance decreases were far more homogeneous than for the variance increases regardless of terrestrial sample size.
+Since $n_{2,G}$ is the same for \psmall{} and SRS, this implies that the sum of square residuals for the model are likely larger than the sum of square local densities for the clusters in $s_{2,G}$ indicating the presence of outliers with large residuals in the problematic small areas.
+This situation is likely to arise when there was forest loss after the ALS scanning but before the terrestrial survey year.
+% [check that]
+
+%As expected, the residual term generally constitutes the dominating part of the \psmall{} variance (around 84\% on average).
 However, a high proportion of the residual variance term seems not to be the driver for large \psmall{} variances, as apparent from Fig.

### 2018-02-28 Draft_Form/tex/Abstract.tex
update 27_02_2018
update 27_02_2018 (Alex review)
update 28_02_2018
update 28_02_2018

@@
 We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (45 and 405 forest district units respectively) in the federal German state of Rhineland-Palatinate.
-An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions on the plot level.
+An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions.
 The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the SRS estimator by 43\% and 25\% on average for the two management levels respectively.
 
-%The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval.
-However, the data have yet been scarcely used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors.
-In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area estimation procedures that try to overcome the restriction in terrestrial sample size by enlarging the sample by a large set of model predictions.
-We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (42 and 392 forest district units respectively) in the federal German state of Rhineland-Palatinate.
-A LiDAR derived canopy height model and a tree species classification map based on satellite data were used as auxiliary information in an ordinary least square regression model to produce the timber volume predictions on the plot level.
-The results indicate that the suggested double-sampling procedure can significantly increase estimation precision on both management levels compared to estimates based on the simple random sampling (SRS) estimator: on Forstamt-level, the proportion of estimation errors below 6\% could be increased from 10\% to 60\% (90\% were below 7\% estimation error).
-The increase of estimation precision was even more pronounced on the Revier-level, although the errors were generally higher than on the Forstamt-level: here, the proportion of estimation errors below 10\% could be increased from 15\% to 40\%.
-The average decrease in variance was ...
-and ..., and the relative efficiency was ...
-and ...
-on Forstamt and Revier-level respectively.
-
-% gain
-% relative efficiency
-% limiting factors (--> to be solved for the future?)
+%The German National Forest Inventory (NFI) consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests in a 10 year interval.
+Although the inventory data have proved to be satisfactory on national and federal state levels, estimation on smaller management levels, such as forest districts, has been prone to large estimation errors due to insufficient sample sizes.
+In this study, we present a double-sampling extension to the existing German NFI that illustrates the implementation of recently developed design-based small area regression estimators and evaluate their potential via timber volume estimation on two small scale management levels (45 and 405 forest district units respectively) in the federal German state of Rhineland-Palatinate.
+An airborne laser scanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least squares regression model to produce the timber volume predictions on the plot level.
+The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels, reducing the variance compared to the standard one-phase estimator on average by 43\% and 25\% respectively.
 
 % Keywords:
-\vspace{0.2cm} \noindent \textbf{Keywords.} National forest inventory, small area estimation, double sampling for regression within strata, cluster sampling, LiDAR canopy height model, tree species classification \vspace{-1cm}
-
-% NOTE
-% - Problem statement: Large scale inventories, such as the German NFI, provide high accuracies on national as well as federal state level.
-However, the uncertainty of estimations on smaller scale management levels (destricts) often turns out be unaccepably large.
-% - Multi-phase sampling procedures try to overcome the lack of terrestrial information by using an additional large sample of predictions based on remote sensing data.
-These techniques can particularly be efficient for domains where the terrestrial sample size is considerably small (small area estimation problem).
-% - The aim of this article was to 
-%
-%
-%
+\vspace{0.2cm} \noindent \textbf{Keywords.} National forest inventory, small area estimation, double sampling for regression within strata, cluster sampling, canopy height model, tree species classification \vspace{-1cm}

### 2018-02-28 Draft_Form/tex/Discussion.tex
update 28_02_2018
update 28_02_2018

@@
 The same level of precision could not be achieved on the lower management level (FR districts) primarily due to substantially smaller terrestrial sample sizes.
-The reason for this were primarily the substantially smaller terrestrial sample sizes.
 However, in 95\% of the FR units, the estimation errors could be limited to 20\% compared to 40\% under SRS.
@@
 We were also able to empirically confirm that the \extpsynth{} estimator generally produces slightly smaller variances and estimation errors than the \psmall{}.
-This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero-mean-residual property of the \extpsynth{}.
+This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero mean residual property of the \extpsynth{}.
 However, our analysis indicated that the difference between the two estimators is negligible for sample sizes $\geq$ 10 due to their asymptotic equivalency.
@@
 Whereas a post-stratification to the ALS acquisition years was an effective means to counteract the implied residual inflation, several leverage points were unambiguously caused by the temporal asynchronicity.
+Undetectable forest loss during the gap between the ALS acquisition and the NFI was also likely a cause for high residual variance in some small areas compared to the terrestrial data variance, which subsequently led to higher variances than the SRS estimator.
 As opposed to the ALS data, the availability of a country-wide tree species classification map has yet been unique among all German federal states.
@@
 We consider these alternative auxiliary data sources to also solve the problem of missing explanatory variables at inventory plots.
-One could also make use of the exhaustive information within the two-phase estimators by using the true the auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which could further decrease of the estimation errors.
+One could also make use of the exhaustive information within the two-phase estimators by using the true the auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which could further decrease estimation errors.
 Previous studies of \citet{mandallaz2013b} however showed that given a reasonable large sample size of the first phase, the differences in the estimation error are usually small.

### 2018-02-28 Draft_Form/tex/Introduction(2).tex
update 28_02_2018
update 28_02_2018

@@
 One method which has proven to be efficient is double- or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}.
-Double sampling incorporates less expensive auxiliary information and can be used to either increase estimation precision under a fixed terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size.
+Double-sampling incorporates less expensive auxiliary information and can be used to either increase estimation precision under a fixed terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size.
 Double-sampling procedures have already been used for stratification in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs.
@@
 We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 45 and 405 forest districts respectively.
-The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a, mandallaz2013b}.
+The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a} and \citet{ mandallaz2013b}.
 Auxiliary data consisted of a canopy height model (CHM) obtained from a countrywide airborne laser scanning (ALS) and a tree species classification map to be used for regression within tree species strata.

### 2018-02-28 Draft_Form/tex/Materials_and_Methods(2).tex
update 28_02_2018
update 28_02_2018

@@
 While information was originally gathered on a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid.
-The German NFI uses a cluster sampling design, which means that a sample unit consists of at most four sample locations (also referred to as \textit{sample plots}) that are arranged in a square, called \textit{cluster}), with a side length of 150 metres.
+The German NFI uses a cluster sampling design, which means that a sample unit consists of at most four sample locations (also referred to as \textit{sample plots}) that are arranged in a square, called \textit{cluster}, with a side length of 150 metres.
 The number of plots per cluster can vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}.
-In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the tree-individual inclusion circle \citep{bwi3_aufn}.
+In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the individual tree's inclusion circle \citep{bwi3_aufn}.
 A further inventory threshold for a tree to be recorded is a diameter at breast height ($DBH$) of at least 7 cm.
@@
 
-The estimators used in this study have been proposed by \citep{mandallaz2013a,mandallaz2013b} and derive their mathematical properties under the so-called infinite population approach (IPA).
+The estimators used in this study have been proposed by \citep{mandallaz2013a,mandallaz2013b} and derive their mathematical properties under the so-called infinite population approach.
 Therefore, we shall first provide a short introduction into this general estimation framework.
@@
 
-The local density on cluster level $Y_{c}(x)$, which in our case the timber volume per hectare, is then defined as the average of the individual sample plot densities $Y(x_l)$:
+The local density on cluster level $Y_{c}(x)$, which is in our case the timber volume per hectare, is then defined as the average of the individual sample plot densities $Y(x_l)$:
 
@@
 
-\noindent being the empirical model residuals at the cluster level, which by construction of OLS satisfy the important \textit{zero mean residual property}, i.e.
+\noindent being the empirical model residuals at the cluster level, which by construction of OLS satisfy the important zero mean residual property, i.e.
 $\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$.\\
@@
 The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Eq.
-\ref{eq:psmall_var}.
+\ref{eq:psmallvar}.
 Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean in $G$ using a non-exhaustive sample $s_{1,G}$.
@@
 \begin{equation}\label{eq:error}
-error(\hat{Y})_{[\%]}=\frac{\sqrt{\hat{\var}(\hat{Y})}}{\hat{Y}}*100
+error_{[\%]}=\frac{\sqrt{\hat{\var}(\hat{Y})}}{\hat{Y}}*100
 \end{equation}
@@
 The confidence intervals can also be used heuristically for hypothesis testing to determine whether the point estimates of the three estimators for a given small area are statistically different.
-The confidence intervals under SRS can be obtained as:
+The confidence intervals for the SRS estimator can be obtained as:
 
@@
 The FAs and FRs constituted the SA units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}.
-The average area of the SA units were 43'777 ha on the FA-level, and 4624 ha on the FR level.
+The average area of the SA units was 43'777 ha on the FA-level, and 4624 ha on the FR level.
 
@@
 The terrestrial sample size $n_{2,G}$ within the FA units was 46 clusters on average and ranged between 11 and 64.
-Within the FR units, $n_{2,G}$ was considerably smaller with an average of 5 cluster and a range between 0 and 13.
+Within the FR units, $n_{2,G}$ was considerably smaller with an average of 5 clusters and a range between 0 and 13.
 
@@
 	\resizebox{0.85\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
-	\caption{\textit{Left}: Study Area with delineated FA forest management units.
-\textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit with overlayed the extended double sampling cluster design.
+	\caption{\textit{Left}: Study area with delineated FA forest management units.
+\textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit overlayed with the extended double-sampling cluster design.
 \textit{Green}: Forest stand polygon layer defining the forest area of this study.}
@@
 % ----------------------------------------------------------------------- %
-\subsection{Extension to double sampling design}
+\subsection{Extension to double-sampling design}
 \label{ext_to_2phase}
 
-In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}).
+In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double-sampling design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}).
 The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ clusters by the terrestrially measured DGPS coordinates.
-For our study, we restricted the \textit{sampling frame} to the communal and state forest.
+For our study, we restricted the sampling frame to the communal and state forest.
 The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service.
@@
 A prerequisite for the application of the suggested two-phase small area estimators is the identification of suitable auxiliary data available over the entire study area.
-From 2003 and 2013, the topographic survey institution of RLP conducted an airborne laser scanning acquisition over the entire federal state during leaf-off conditions in order to derive a countrywide digital terrain model (DTM) as well as a digital surface model (DSM).
-For this study, the recorded LiDAR data was used to create a canopy height model in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters (Figure \ref{fig:Auxvars}, \textit{top}).
-The CHM (Fig.
-\ref{fig:Auxvars}, \textit{top}) was calculated as the difference between the digital terrain model and the digital surface model that were derived by a Delauney interpolation of the ground and first ALS pulses respectively.
+From 2003 to 2013, the topographic survey institution of RLP conducted an airborne laserscanning acquisition over the entire federal state during leaf-off conditions in order to derive a countrywide digital terrain model (DTM) as well as a digital surface model (DSM).
+For this study, the recorded ALS data was used to create a canopy height model (CHM) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters (Fig.
+\ref{fig:Auxvars}, \textit{top}).
+The CHM was calculated as the difference between the digital terrain model and the digital surface model that were derived by a Delauney interpolation of the ground and first ALS pulses respectively.
 A more detailed description of the procedure can be found in \citet{hill2017a}.
@@
 In addition, the quality of the CHM varied substantially as ALS technology evolved over the years.
-For example, LiDAR acquisition recorded in 2002 and 2003 exhibited particularly poor quality with about only 0.04 point per m$^2$, whereas more recent datasets contained more than 5 points per m$^2$.
+For example, the ALS acquisitions recorded in 2002 and 2003 exhibited particularly poor quality with about only 0.04 point per m$^2$, whereas more recent datasets contained more than 5 points per m$^2$.
 Furthermore, CHM information was not available at 16 sample locations due to sensor failures.
@@
 The tree species map has a grid size of 5x5 m and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) using a spatially adaptive classification algorithm \citep{stoffels2012}.
-As timber volume estimation on the tree level is often based on species-specific biomass and volume equations, the use of tree species information has often been stated as a key factor for improving the precision of timber volume estimates \cite{white2016}.
+As timber volume estimation on the tree level is often based on species-specific biomass and volume equations, the use of tree species information has often been stated as a key factor for improving the precision of timber volume estimates \citep{white2016}.
 In this respect, incorporating the tree species map was particularly attractive as it predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree.
@@
 	\begin{center}
-		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plots}$: number of plots. $n_{\{1,2\}}$: number of clusters. TSPEC: tree species information.}
+		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plots}$: number of plots. $n_{\{1,2\}}$: number of clusters. TSPEC: tree species map information.}
 		\vspace{0.2cm}
@@
 \ref{eq:Zc(x)} in order to derive the weighted mean of the explanatory variables on the cluster level.
-Neglecting the calculation of this weight would deteriorate the coherence between explanatory variables computed at the forest boundary and the corresponding local density that already includes a potential boundary adjustment, thus introducing unnecessary noise to the model.
+Neglecting the support adjustment would deteriorate the coherence between explanatory variables computed at the forest boundary and the corresponding local density that already includes a potential boundary adjustment, thus introducing unnecessary noise to the model.
 The boundary adjustment to the support also makes the sampling frame more consistent for the different data sources (Section \ref{ext_to_2phase}).\par
-The ALS acquisition year (ALSyear) was added as a categorical variable in order to account for the time lag with the terrestrial survey as well as to help explain the heterogeneity in the data introduced by the varying ALS quality.
+The ALS acquisition year (\textit{ALSyear}) was added as a categorical variable in order to account for the time lag with the terrestrial survey as well as to help explain the heterogeneity in the data introduced by the varying ALS quality.
 In 2008, a sensor error produced particularly poor ALS quality so the year was divided accordingly into two factor levels, denoted \textit{2008\_1} and \textit{2008}.
@@
 However, the \adjrsq{}s of the full and reduced model were found to be very similar on both the plot and cluster level.
-This implied that the variance reduction of the reduced model when applied to the two-phase estimators would likely be comparable to that of the full model, which is why a joint evaluation of the estimation results is presented in Section \ref{sec:Res}.
+This implied that the variance reduction of the reduced model when applied to the two-phase estimators would likely be comparable to that of the full model, which is why a joint evaluation of the estimation results was performed (Section \ref{sec:Res}).
 
@@
 160--167]{fahrmeir2013} on the plot level for the full regression model.
-We calculated the leverage values and found that 10\% of all observations exceeded a predefined critical threshold, i.e.
+We calculated the leverage values and found that 10\% of all observations exceeding a predefined critical threshold, i.e.
 twice the average of the hat matrix diagonal entries.

### 2018-02-28 Draft_Form/tex/Results.tex
update 28_02_2018
update 28_02_2018

@@
 \ref{fig:disterrors}).
-On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under the \extpsynth{} and \psmall{} respectively (Table \ref{tab:estres}).
+On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under \extpsynth{} and \psmall{} respectively (Table \ref{tab:estres}).
 The cumulative error distribution (Fig.
@@
 \textit{Left}: Results for the 45 FA units.
-\textit{Right}: Results for the 388 (SRS), 321 (\psmall{} / \extpsynth{}) and 403 (\psynth{}) FR units.}
+\textit{Right}: Results for the 388 (SRS), 321 (\psmall{}, \extpsynth{}) and 403 (\psynth{}) FR units.}
 	\label{fig:disterrors}
@@
 On both small area levels, the \psynth{} estimator resulted in much smaller estimation errors compared to \psmall{} and \extpsynth{}.
-This was as expected, since the \psynth{} variance estimate does not take the residual variation in each small area unit into account (section \ref{sec:psynth}).
+This was as expected, since the \psynth{} variance estimate does not take the residual variation in each small area unit into account (Section \ref{sec:psynth}).
 Compared to the asymptotically design-unbiased estimators \psmall{} and \extpsynth{}, the estimation errors produced by \psynth{} thus seem to be too optimistic.
@@
 Figure \ref{fig:disterrors} reveals that the error distribution of \psmall{} and \extpsynth{} are very similar, with \psmall{} showing marginally higher estimation errors.
-In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (fig.
+In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (Fig.
 \ref{fig:compvar}, left).
 As obvious, \psmall{} yielded slightly larger variances for the vast majority of the estimates.
-As addressed in section \ref{sec:extpsynth}, one possible explanation for such differences was the effect of one or more cluster not entirely being included in a small area unit, as this would constitute a violation of the \extpsynth{} estimator.
+As addressed in Section \ref{sec:extpsynth}, one possible explanation for differences was the effect of one or more cluster not entirely being included in a small area unit, as this would constitute a violation of the \extpsynth{} estimator.
 This violation was actually observed in 155 of the 321 FR units (48\%).
+We compared the variances of \psmall{} and \extpsynth{} for all small areas that did not have the violations using a Wilcoxon Rank-Sum Test \citep{wilcoxon1970}.
+This test was also performed for groups $n_{2,G} \leq 6$, $n_{2,G} > 6$ and $n_{2,G} > 10$.
+The distribution of variances from \extpsynth{} were found to be significantly lower than that of \psmall{} (p-values of 1.2*10$^{-13}$, 3.4*10$^{-8}$) except for the group of $n_{2,G} > 10$ (p-value of 0.125).
+The latter was expected since the variances of both estimators are asymptotically equivalent under large terrestrial sample sizes $n_{2,G}$ within the small area \citep[pp.17--18]{mandallaz2016}.
+This was also confirmed by a comparison of the absolute differences in the variances (Fig.
+\ref{fig:compvar}, right) which decreased with increasing terrestrial sample size.
+The Wilcoxon Rank-Sum Test was also used to compare the \extpsynth{} variances of those small areas with violation (depicted in red diamonds, Fig.
+\ref{fig:compvar}) to the \psmall{} variances without violations.
+Overall as well as for $n_{2,G} \leq 6$ there was a significant difference, but not for $n_{2,G} > 6$.
+This provided some evidence that the violations created a statistically significant influence on the \extpsynth{} variance that makes it appear to be slightly over-optimistic.
+However, a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.\par
 
-However, the affected FR units (depicted in red diamonds, fig.
+%However, the affected FR units (depicted in red diamonds, Fig.
 \ref{fig:compvar}) did not show a significant divergence from the \psmall{} variances with respect to the remaining unaffected FR units.
 The variance differences between the two estimators were thus due to the mathematical formulations of the \psmall{} and \extpsynth{} estimator, which are asymptotically equivalent only under large terrestrial sample sizes $n_{2,G}$ within the small area \citep[pp.17--18]{mandallaz2016}.
-An additional comparison of the absolute differences in the g-weight variance (fig.
+An additional comparison of the absolute differences in the g-weight variance (Fig.
 \ref{fig:compvar}, right) revealed that large divergences did in fact particularly occur for small area units with small terrestrial sample sizes ($n_{2,G} \leq 5$).
@@
 	\caption{\textit{Left}: Comparison of the g-weight variance between the PSMALL and the EXTPSYNTH estimator for the 321 FR units.
-		\textit{Right}: Difference in g-weight variance between the PSMALL and the EXTPSYNTH estimator in dependence of the terrestrial data ($n2G$) in the FR unit.}
+		\textit{Right}: Difference in g-weight variance between the PSMALL and the EXTPSYNTH estimator in dependence of the terrestrial data ($n_{2,G}$) in the FR unit.}
 	\label{fig:compvar}
@@
 The reduction in variance can also be expressed in the relative efficiency values, which were 2.02 on average and ranged between 1.18 and 4.13 on the FA level.
-On FR level, the reduction in variance and the relative efficiencies reached even higher values (Table \ref{tab:gain} and Fig.
+On FR level, the reduction in variance even reached values of 90\% and relative efficiencies of 30 (Table \ref{tab:gain} and Fig.
 \ref{fig:gain}).
-The \psmall{} estimator again yielded slightly lower variance reductions and relative efficiencies due to the generally smaller variances of the \extpsynth{} estimator (section \ref{sec:comp}).
+The \psmall{} estimator again yielded slightly lower variance reductions and relative efficiencies due to the generally smaller variances of the \extpsynth{} estimator (Section \ref{sec:comp}).
 
@@
 \ref{eq:psmallvar}), i.e.
-the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residual (term 3).
+the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residuals (term 3).
 In general, the residual term is expected to make the largest contribution to the overall variance since it's sample size is based on $n_{2,G}$ whereas the auxiliary term and the coefficient term are based on larger sample sizes, i.e.
 $n_{1,G}$ and $n_2$ respectively.
-Figure \ref{fig:fail} illustrates the share of the overall variance by the residual term of the \psmall{} estimator scaled by the overall percentage reduction or increase of the variance compared to SRS for various small area sample sizes $n_{2,G}$.\par
-
+Figure \ref{fig:fail} illustrates the share of the overall variance by the residual term of the \psmall{} estimator scaled by the overall percentage reduction or increase of the variance compared to SRS for various small area sample sizes $n_{2,G}$.
 The residual term generally constitutes the dominating part of the \psmall{} variance (around 84\% on average).
@@
 	\resizebox{1\hsize}{!}{\includegraphics{fig/eval_2phase_fail_11.png}}
-	\caption{Increase or reduction of the SRS variance by application of the \psmall{} estimator for all 321 FR units in dependence of a) the terrestrial sample size in the FR units (\textit{x-axis}) and b) the residual term proportion of the \psmall{} g-weight variance (\textit{y-axis}).}
+	\caption{Share of the overall variance by the residual term of the \psmall{} estimator for various small area sample sizes.
+Points are scaled by the overall percentage reduction/increase of the variance compared to SRS.}
 	\label{fig:fail}

### 2018-03-01 Draft_Form/tex/Discussion.tex
update 01_03_2018
update 01_03_2018

@@
 
-The aim of this study was to investigate the performance of design-based estimators for small area estimation of mean standing timber volume on two spatial forest management levels in Germany.
+The aim of this study was to investigate the performance of model-assisted design-based estimators for small area estimation of mean standing timber volume on two spatial forest management levels in Germany.
 It was of particular interest to gather information about the estimation error levels that can be attained using German NFI data that is characterized by low sampling intensities in the area of interests.

### 2018-03-01 Draft_Form/tex/Introduction(2).tex
update 01_03_2018
update 01_03_2018

@@
 One example is \citet{breidenbach2012} who used data from the Norwegian NFI to make small area estimation for standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35.
-The estimation errors under the applied model-based and design-based small area estimators turned to be markedly smaller than under the standard one-phase estimator.
+The estimation errors under the applied model-dependent and design-based small area estimators turned to be markedly smaller than under the standard one-phase estimator.
 Another example is \citet{magnussen2014} who recently used the Swiss NFI data to estimate timber volume within 108 Swiss forest districts with sample sizes between 9 and 206.
@@
 The chosen double-sampling estimators were selected for several reasons: \textbf{(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can be used with \textit{non-exhaustive}, i.e.
-non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals.
+non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust under heteroscedasticity of the model residuals.
 The results from this study were considered to provide valuable information whether the suggested procedure might be a cost-saving alternative to a regional FDI.\par

### 2018-03-01 Draft_Form/tex/Materials_and_Methods(2).tex
update 01_03_2018
update 01_03_2018

@@
 The basic idea of this method is to boost the sample size by providing a large sample of less precise but cheaper predictions of $Y(x)$ in $s_1$ and to correct any possible model bias, i.e., $\EX{(Y(x)-\hat{Y}(x))}$, using the subsample of terrestrial inventory units where the value of $Y(x)$ is observed.
+In this context, it is also important to note that the response and auxiliary variables are assumed to be error-free and the resulting errors for the point estimates reflect only the uncertainty due to sampling.
 
@@
 
+\noindent with $\bar{M}_{2,G}=\frac{\sum_{x \in s_{2,G}}M_{G}(x)}{n_{2,G}}$.\\
+
 The variance-covariance matrix of the auxiliary vector $\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}$ is thereby defined as
@@
 
-with $\bar{M}_{1,G}=\frac{\sum_{x \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.\\
+\noindent with $\bar{M}_{1,G}=\frac{\sum_{x \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.\\
 
@@
 
+%\begin{equation}\label{ci_1phase}
+%CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
+%\hat{Y}+t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
+%\end{equation}
+
 \begin{equation}\label{ci_1phase}
-CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
-\hat{Y}+t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
+CI_{1-\alpha}(\hat{\bar{Y}}_c)=\hat{\bar{Y}}_c \pm t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{\bar{Y}}_c)}
 \end{equation}
@@
 
-\begin{equation}\label{ci_2phase_sae}
-CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
-\hat{Y}+t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
-\end{equation}
+%\begin{equation}\label{ci_2phase_sae}
+%CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
+%\hat{Y}+t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
+%\end{equation}
+
+\begin{subequations}\label{ci_2phase_sae}
+	\begin{align}
+CI_{1-\alpha}(\hat{Y}_{c,G,EXTPSYNTH})&=\hat{Y}_{c,G,EXTPSYNTH} \pm t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y}_{c,G,EXTPSYNTH})} \\
+CI_{1-\alpha}(\hat{Y}_{c,G,PSMALL})&=\hat{Y}_{c,G,PSMALL} \pm t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y}_{c,G,PSMALL})}
+	\end{align}
+\end{subequations}
 
@@
 
-\begin{equation}\label{ci_2phase_global}
-CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
-\hat{Y}+t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
+%\begin{equation}\label{ci_2phase_global}
+%CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
+%\hat{Y}+t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
+%\end{equation}
+
+\begin{equation}\label{ci_2phase_psynth}
+CI_{1-\alpha}(\hat{Y}_{c,G,PSYNTH})=\hat{Y}_{c,G,PSYNTH} \pm t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y}_{c,G,PSYNTH})}
 \end{equation}
@@
 In order to address the potential benefits of the small area estimators compared with the SRS approach, we calculated the \textit{relative efficiency} (Eq.
-\ref{eq:releff}) which can be interpreted as the relative sample size under SRS needed to achieve the variance under the double sampling estimators.
+\ref{eq:releff}) which can be interpreted as the relative sample size under SRS needed to achieve the variance under the double-sampling (DS) estimators.
 
 \begin{equation}\label{eq:releff}
-rel.eff=\frac{\hat{\var}_{SRS}(\hat{Y})}{\hat{\var}_{SAE_{2phase}}(\hat{Y})}
+rel.eff=\frac{\hat{\var}_{SRS}(\hat{Y})}{\hat{\var}_{DS}(\hat{Y})}
 \end{equation}
@@
 	\centering
-	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/Auxvars_100dpi.png}}
+	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/Auxvars_400dpi.png}}
 	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level.
@@
 We thus applied this calibration model to the \textit{treespecies} variable derived at all sample locations $s_1$.
-Table \ref{tab:classacc} gives the classification accuracies of the \textit{treespecies} variable after calibration.
+Table \ref{tab:classacc} gives the classification accuracies \citep{congalton2008} of the \textit{treespecies} variable after calibration.
 

### 2018-05-09 MDPI_template/MDPI_template/template.tex
update 09_05_2018
update 09_05_2018

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.

%=================================================================
\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g. \documentclass[preprints,article,accept,moreauthors,pdftex,10pt,a4paper]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%
%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% actuators, addictions, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, ceramics, challenges, chemengineering, chemosensors, children, chromatography, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cybersecurity, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electrochem, electrochemistry, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, j, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, joitmc, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, mti, medsci, medicina, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, neuroglia, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, plasma, polymers, polysaccharides, preprints, proceedings, processes, proteomes, publications, quaternary, qubs, reactions, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, sinusitis, socsci, societies, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem
%---------
% article
%---------
% The default type of manuscript is article, but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials
% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g. the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{1}
\pubyear{2018}
\copyrightyear{2018}
\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}

%\updates{yes} % If there is an update available, un-comment this line

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz, siunitx

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

% Simple summary
%\simplesumm{}

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for the journal Gels: Please place the Experimental Section after the Conclusions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}
The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g. the positioning of the Materials and Methods section). Please check the instructions for authors page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. And now citing a book reference \cite{ref-book}. Please use the command \citep{ref-journal} for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\begin{quote}
This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsection}

\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}[leftmargin=*,labelsep=5.8mm]
\item	First bullet
\item	Second bullet
\item	Third bullet
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
\item	First item 
\item	Second item
\item	Third item
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=2 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

\subsection{Formatting of Mathematical Components}

This is an example of an equation:

\begin{equation}
a + b = c
\end{equation}
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}
This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; Methodology, X.X.; Software, X.X.; Validation, X.X., Y.Y. and Z.Z.; Formal Analysis, X.X.; Investigation, X.X.; Resources, X.X.; Data Curation, X.X.; Writing—Original Draft Preparation, X.X.; Writing—Review \& Editing, X.X.; Visualization, X.X.; Supervision, X.X.; Project Administration, X.X.; Funding Acquisition, Y.Y.'', please turn to the \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work reported. }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{Please add: ``This research received no external funding'' or ``This research was funded by [name of funder] grant number [xxx].'' Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g. materials used for experiments).}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixsections{multiple} %Leave argument "multiple" if there are multiple sections. Then a counter is printed ("Appendix A"). If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
\appendix
\section{}
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: internal bibliography
%=====================================
\reftitle{References}
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149, DOI.
% Reference 2
\bibitem[Author2(year)]{ref-book}
Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58, ISBN.
\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%=====================================
% References, variant B: external bibliography
%=====================================
%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds ...... are available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2018-05-09 article MDPI/hill et al 2018.tex
update 09_05_2018
update 09_05_2018

--- 2018-03-01 Draft_Form/tex/Materials_and_Methods(2).tex
@@
-% ----------------------------------------------------------------------- %
-% ----------------------------------------------------------------------- %
+%  LaTeX support: latex@mdpi.com 
+%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+
+% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
+
+%=================================================================
+\documentclass[remotesensing,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi} 
+%
+%--------------------
+% Class Options:
+%--------------------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% actuators, addictions, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, ceramics, challenges, chemengineering, chemosensors, children, chromatography, climate, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cybersecurity, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electrochemistry, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, j, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, plasma, polymers, preprints, proceedings, processes, proteomes, publications, quaternary, qubs, recycling, religions, remotesensing, resources, risks, robotics, safety, scipharm, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vetsci, vibration, viruses, vision, water, wem
+%---------
+% article
+%---------
+% The default type of manuscript is article, but can be replaced by: 
+% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
+% supfile = supplementary materials
+% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g.
+the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
+
+%=================================================================
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother 
+\articlenumber{x}
+\doinum{10.3390/------}
+\pubvolume{xx}
+\pubyear{2017}
+\copyrightyear{2017}
+\externaleditor{Academic Editor: name}
+\history{Received: date; Accepted: date; Published: date}
+
+\usepackage{gensymb}
+\usepackage{natbib}
+\usepackage{tabulary}
+\usepackage{multirow}
+\usepackage{boldline}
+
+\usepackage[british]{babel}
+
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+
+\usepackage{booktabs}
+\usepackage{tabularx}
+\usepackage{multirow}
+\usepackage{graphicx}
+
+\usepackage[font=footnotesize]{caption}
+\usepackage[font=footnotesize]{subcaption}
+
+\definecolor{mygreen}{rgb}{0.1, 0.6, 0.4}
+\newcommand{\added}[1]{\color{mygreen}{#1} \color{black}}
+\newcommand{\changed}[1]{\color{red}{#1} \color{black}}
+
+\newcommand{\adjrsq}{adjusted $R^2$}
+\newcommand{\rmsecv}{RMSE$_{cv}$}
+\newcommand{\mha}{m$^3$/ha}
+\newcommand{\bwi}{BWI3}
+\newcommand{\psynth}{PSYNTH}
+\newcommand{\psmall}{PSMALL}
+\newcommand{\extpsynth}{EXTPSYNTH}
+\newcommand{\meanheight}{\textit{meanheight}}
+\newcommand{\stddev}{\textit{stddev}}
+\newcommand{\treespecies}{\textit{treespecies}}
+\newcommand{\alsyear}{\textit{ALSyear}}
+\newcommand{\var}{\mathbb{V}}
+\newcommand{\EX}{\mathbb{E}}
+
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
+
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
+
+%=================================================================
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels}
+
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0002-6367-2256} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name
+
+% Authors, for the paper (add full first names)
+\Author{Andreas Hill $^{1,}$*\orcidA{}, Daniel Mandallaz $^{1}$ and Joachim Langshausen $^{2}$}
+
+% Authors, for metadata in PDF
+\AuthorNames{Andreas Hill, Daniel Mandallaz and Joachim Langshausen}
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+	$^{1}$ \quad Department of Environmental Systems Science, ETH Zurich, 8092 Zurich, Switzerland; mdaniel@retired.ethz.ch (D.M.)\\
+	$^{2}$ \quad State Forest Service Rhineland-Palatinate, 56281 Emmelshausen, Germany; Joachim.Langshausen@wald-rlp.de}
+
+% Contact information of the corresponding author
+\corres{Correspondence: andreas.hill@usys.ethz.ch; Tel.: +x-xxx-xxx-xxxx}
+
+% Abstract (Do not insert blank lines, i.e. \\) 
+\abstract{The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval.
+However, the data have yet been scarcely used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors.
+In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area regression estimators.
+We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (45 and 405 forest district units respectively) in the federal German state of Rhineland-Palatinate.
+An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions.
+The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the SRS estimator by 43\% and 25\% on average for the two management levels respectively.}
+
+% Keywords
+\keyword{National forest inventory, small area estimation, forest districts, double sampling for regression within strata, cluster sampling, canopy height model, tree species classification}
+
+% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
+%\PACS{J0101}
+%\MSC{}
+%\JEL{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Applied Sciences:
+%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Data:
+%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
+If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
+In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
+
+%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+
+%\setcounter{secnumdepth}{4}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Only for the journal Gels: Please place the Experimental Section after the Conclusions
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\setcounter{section}{-1} %% Remove this when starting to work on the template.
+%\section{How to Use this Template}
+%The template details the sections that can be used in a manuscript.
+Note that the order and names of article sections may differ from the requirements of the journal (e.g.
+the positioning of the Materials and Methods section).
+Please check the instructions for authors page of the journal to verify the correct order and names.
+For any questions, please contact the editorial office of the journal or support@mdpi.com.
+For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
+
+\section{Introduction}
+\label{sec:intro}
+
+The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germany's forest over time.
+The NFI thereby has the responsibility to satisfy various information needs including reporting to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and to the United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}.
+The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany.
+In order to cover a large area of 114'191 ha \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels.
+However, sample sizes often drop dramatically when entering spatial units below the federal state level.
+This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out to be unacceptably large due to the very limited number of sample plots within these units.
+For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels.
+In most German federal states, management strategies are thus still based on expert judgments from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par
+
+Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}.
+However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonluepke2013}.
+One method which has proven to be efficient is double- or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}.
+Double-sampling incorporates less expensive auxiliary information and can be used to either increase estimation precision under a fixed terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size.
+Double-sampling procedures have already been used for stratification in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs.
+Recent studies have extended double-sampling to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities.
+An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI of Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories.
+Another example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par
+
+Two-phase and three-phase samplings techniques have also been applied to small area estimation (SAE).
+SAE techniques address the situation where the number of samples within a subunit, or small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit.
+A broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics.
+One such method that is commonly applied is known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not observed in the small area.
+These models are trained using data from outside the small area in order to "borrow strength" from areas where information is available.
+Of numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, most use unit-level models, i.e.
+the inventory plot is the unit of the response variable in the training data used for the model fit.
+Such unit-level models have been intensively investigated for timber volume estimation using various remote sensing auxiliary data \citep{koch2010, naesset2014inmaltamo}.
+Other studies have investigated area-level models, where the auxiliary information is only provided on the SA level \citep{magnussen2017}.
+Some studies have illustrated that even NFI data derived under low sampling densities can still be used to provide acceptable precision of small area estimates on much smaller management levels.
+One example is \citet{breidenbach2012} who used data from the Norwegian NFI to make small area estimation for standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35.
+The estimation errors under the applied model-dependent and design-based small area estimators turned to be markedly smaller than under the standard one-phase estimator.
+Another example is \citet{magnussen2014} who recently used the Swiss NFI data to estimate timber volume within 108 Swiss forest districts with sample sizes between 9 and 206.
+Similar studies using German NFI data for small area estimation have been lacking.\par
+
+The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels using the latest small area estimation procedures.
+We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 45 and 405 forest districts respectively.
+The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a} and \citet{ mandallaz2013b}.
+Auxiliary data consisted of a canopy height model (CHM) obtained from a countrywide airborne laser scanning (ALS) and a tree species classification map to be used for regression within tree species strata.
+The estimation precisions were compared to those obtained by the standard one-phase estimator for cluster sampling under simple random sampling.
+The chosen double-sampling estimators were selected for several reasons: \textbf{(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can be used with \textit{non-exhaustive}, i.e.
+non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust under heteroscedasticity of the model residuals.
+The results from this study were considered to provide valuable information whether the suggested procedure might be a cost-saving alternative to a regional FDI.\par
+
+%---------------------------------------------------------------------------------------------------------%
+% ---------------------------------- Materials and Methods ---------------------------------------------- %
 
@@
 
-% \subsubsection{One- and Two-Phase Sampling in the Infinite Population Approach}
+ \subsubsection{One- and Two-Phase Sampling in the Infinite Population Approach}
 
@@
 In this context, it is also important to note that the response and auxiliary variables are assumed to be error-free and the resulting errors for the point estimates reflect only the uncertainty due to sampling.
-
-% which in \pkg{forestinventory} is always a linear model fit in $s_2$ using ordinary least squares (OLS).
-%The one-phase and two-phase estimators applied in this study have been implemented in the software-package \textit{forestinventory} \cite{forestinventory} 
-% The local density $Y(x)$ is in practice derived by ...
-% extend the approach to collecting auxiliary information ...
-% say that we also assume that the forest area is well-defined ...
 
@@
 \begin{equation}\label{eq:releff}
-rel.eff=\frac{\hat{\var}_{SRS}(\hat{Y})}{\hat{\var}_{DS}(\hat{Y})}
+rel.eff=\frac{\hat{\var}(\hat{Y}_{SRS})}{\hat{\var}(\hat{Y}_{DS})}
 \end{equation}
-
-\newpage
 
@@
 \label{sec:CaseStudy}
-
-%This section describes the actual implementation of the proposed small area estimators (Section \ref{sec:estimators}) under the cluster design of the German NFI (Section \ref{sec:germanNFI}) in the federal state Rhineland-Palatinate.
 
@@
 The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}.
-For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArea}).
+For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArean}).
 On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 405 Forstreviere (\textit{FR}).
@@
 The average area of the SA units was 43'777 ha on the FA-level, and 4624 ha on the FR level.
-
-% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
-%   FA                43'777 ha  (17367 - 125423)     46 (128)                            11 (36)            64 (198)
-%   FR                4624 ha   (0.68 - 43284)         5  (14)                            0 (0)             13 (34)
-%   stand level       6 ha     (0.03 ha - 73)          0 (0)                              0 (0)             2 (4)
-
-% Add Graphic 1:
-% - Graphic of RLP with "zoom" in the 3 managament units (or later all together in Graphic
-
-% Add in text:
-% - add information on the (average) spatial area of each sae-level
-
-% Notes to myself:
-% - in the original forstrevier layer, we have 427 FR units but 21 of them are not covered by woefis-layer (so no state- and communal forest), and 1 is the "Bundesforstamt" not considered by us
 
@@
 \textit{Green}: Forest stand polygon layer defining the forest area of this study.}
-	\label{fig:StudyArea}
+	\label{fig:StudyArean}
 \end{figure}
@@
 
-In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double-sampling design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}).
+In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double-sampling design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArean}, \textit{right}).
 The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ clusters by the terrestrially measured DGPS coordinates.
@@
 \input{tab/table_fieldmeasuredvals.tex}
-
-% NOTES:
-%
-% Add Table:
-% provide table of "forest characteristics" in RLP
-% adress sample sizes before and after extension (table?)
-%
-% move this to discussion:
-% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$.
-This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer.
-For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$.
-The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e.
-by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par
-%
-%  "This extension led to a considerable increase of the sample size $n_{1,G}$ in the small area units of both, the FA and FR level."
-% - Show (theoretical) increase in sample sizes by extension to 2phase scheme 
-%   --> these sample sizes are in the following reduced by missing rs-info
-%
-
-% ----------------------------------------------------------------------- %
-% Table xx provides an overview of the terrestrial sample sizes on these management levels for the state and communal forest areas.
-
-% \input{terrSamplsizeFoaFuWa.tex}
-
-% average no. plots / clusters; average area of all three units (divided by state + communal forest & entire forest area)
-
-% --> this is only for communal & state forest area:
-% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
-%   FA                43'777 ha  (17367 - 125423)     46 (128)         11 (36)            64 (198)
-%   FR                4624 ha   (0.68 - 43284)         5  (14)          0 (0)             13 (34)
-%   stand level       6 ha     (0.03 ha - 73)          0 (0)            0 (0)             2 (4)
-
-% - Verwaltungsebenen: management levels (Forstamt, Revier, Bestände) -> durschnittliche Flächengrössen (für die sollen die sae schätzungen gemacht werden)
-% - evtl bereits Stichprobenzahlen generell und innerhalb der Managementenheiten nennen (das ginge dirket hinsichltich des eigentlichen Themas)
-%   (das generelle Problem der Stichprobenanzahl in diesen Einheiten wurde ja schon in der Einleitung angesprochen, also könnte man
-%    hier direkt ein Beispiel geben) --> hier noch getrennt nach gesamter Wald und nur Woefis-Wald (Tabelle, Grpahik)
-% - warum RLP ? (neues Informationssystem, Interesse an effizienteren Methoden)
-% wir nennen Fortamt einfach 'FA-level' und Forstrevier einfach 'FR-level' :-)
-% Info: 45 Forstämter without Bundesforstamt; 426 Reviere without Bundesforstamt
-% mention that the boundaries of all these management units are well-defined by polygon masks (that were used to extract the sampling
-% frame)
-% ----------------------------------------------------------------------- %
 
@@
 
-% Graphik:
-\begin{figure}[H]
-	\centering
-	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/Auxvars_400dpi.png}}
-	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level.
-Right: Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.}
-	\label{fig:Auxvars}
-\end{figure}
-
 % ---------------------------------------------- %
@@
 The result was nine factor levels denoted as \textit{2002}, \textit{2003}, \textit{2007}, \textit{2008\_1}, \textit{2008}, \textit{2009}, \textit{2010}, \textit{2011} and \textit{2012}.
+
+% Graphik:
+\begin{figure}[H]
+	\centering
+	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/Auxvars_400dpi.png}}
+	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level.
+Right: Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.}
+	\label{fig:Auxvars}
+\end{figure}
 
@@
 
-%% Here is the table with calibrated and uncalibrated values:
-%\begin{table}[H]
-%	\begin{center}
-%	\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
-%	\vspace{0.2cm}
-%	\label{tab:classacc}
-% {\small %
-%	\begin{tabular}{l|c c|c c|c|c c} %8cols
-%		\hlineB{1}
-%		\multirow{2}{*}{Main plot species} & \multicolumn{2}{c|}{Producer's accuracy[\%]} & \multicolumn{2}{c|}{User's accuracy[\%]} & \multirow{2}{*}{nref} & \multicolumn{2}{c}{nclass} \\ 
-%		\cline{2-3} \cline{4-5} \cline{7-8} & uncalib & calib & uncalib & calib & & uncalib & calib \\
-%		\hline \hline	
-%		 Beech       & 29.56 & 22.31 & 46.11 & 47.02 & 883 & 566 & 419 \\
-%		 Douglas Fir & 33.04 & 24.78 & 47.50 & 48.72 & 230 & 160 & 117 \\
-%		 Oak         & 47.75 & 11.07 & 24.34 & 48.48 & 289 & 567 & 66 \\
-%		 Spruce      & 43.63 & 53.15 & 60.81 & 61.13 & 651 & 467 & 566 \\
-%		 Scots Pine  & 55.87 & 22.91 & 29.59 & 46.07 & 179 & 338 & 89 \\
-%		 Mixed       & 66.40 & 84.49 & 63.69 & 64.53 & 3152 & 3286 & 4127 \\
-%		\hline
-%		 & \multicolumn{4}{l|}{Overall accuracy: 54.83\% (61.96\%)} & 5384 & \multicolumn{2}{c}{5384} \\
-%		 \hline \hline
-%	\end{tabular}
-%}%
-%	\end{center}
-%\end{table}
-
 % ---------------------------------------------- %
@@
 The model selection process for this study required a substantial time commitment due to sophisticated challenges such as: a) the heterogeneity of the remote sensing data, b) the identification of the optimal support sizes under angle count sampling, and c) the incorporation of tree species information.
-Here, only a summary of the extensive analysis that was performed is provided but the reader can refer to \citet{hill2017a} if more details are desired\par
+Here, only a summary of the extensive analysis that was performed is provided but the reader can refer to \citet{hill2017a} if more details are desired.\par
 The model with highest \adjrsq{} and lowest RMSE was achieved using \meanheight{}, \meanheight{}$^2$, \stddev{}, \alsyear{} and \treespecies{} as main effects, and including interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{}, \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{}.
 Summary information about the \adjrsq{}, RMSE and RMSE\% of the selected models is provided in Table \ref{tab:modacc_modterms}.
-The two-phase estimators described in Section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level.
-We re-evaluated the model as used in the estimators on the cluster level (formulas given in Appendix) and found improved model fits compared to the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%).
+As the two-phase estimators described in Section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level, we re-evaluated the model as used in the estimators on the cluster level (formulas given in Appendix) and found improved model fits compared to the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%).
 The stratification by the ALS acquisition year substantially improved the model fit, indicating that it is an effective means in accounting for the noise in the data caused by ALS quality variations and time-gaps between the ALS and the terrestrial survey.
@@
 
+% Table 2:
+\input{tab/mod_r2_lyearstrata_table.tex}
+
 Concerning the existence of outliers or leverage points in the training set for the model, it should be noted that it is more problematic for \psmall{}, \psynth{} and \extpsynth{} to simply remove them as one might be inclined to do in a model-dependent context.
@@
 
-%Concerning the treatment of outliers or leverage points for model fitting, it should be noted that there is a major difference between the external and internal model approach.
-In order to ensure the zero-mean-residual property of the \psmall{} and \extpsynth{} estimator under the internal model approach (section \ref{sec:psmall} and \ref{sec:extpsynth}), all observations of the terrestrial sample $s_2$ used for estimation must also be included in the modeling frame.
-Thus, excluding an observation from the model fit does also require its deletion from the sampling frame, which has to be regarded as an interference with the random sampling process the design-based inference relies on.
-For this reason, a removal of potential outliers or leverage points is, strictly speaking, only justified if the terrestrial response value or the explanatory variable value turns out to be truly erroneous (e.g.
-typos or measurement errors).
-If this is not the case, the removal of outliers or influential data points might increase the model fit, but to the cost of possible bias for the estimates.
-With respect to these considerations, we conducted an analysis of influential observations \citep[pp.
-160--167]{fahrmeir2013} on the plot level for the full regression model.
-In order to identify implausible observations in the explanatory data, we calculated the \textit{leverage} values and found that the critical threshold of $2p/n$ (i.e.
-twice the average of the hat matrix' diagonal entries) was exceeded by 10\% of all observations.
-Further investigation revealed that several leverage points showed unusually large \meanheight{} values associated to their respective timber volume density values.
-These implausible height values particularly occured in ALSyear acquisition years differing from the terrestrial survey date and were thus much more likely caused by harvesting activities in the sample plot area than erroneous ALS data.
-A deletion of these plots from the sampling frame was thus not justified due to the reasons given before.
-Also the remaining leverage points could not be definitely attributed to erroneous auxiliary data and were kept in the data set.
-The same was true for 10 observation with exceptionally large local density values that were identified as \textit{outliers}.
+%-------------------------------------------------------------------------------------------%
+% ---------------------------------- Results ---------------------------------------------- %
+\section{Results}
+\label{sec:Res}
 
-% Table 2:
-\input{tab/mod_r2_lyearstrata_table.tex}
+\subsection{General estimation results}
+\label{sec:feasest}
 
-%\begin{equation}\label{eq:R_squared_clust}
-%R^2 =  \frac{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(\hat{Y}_{c}(x)-\bar{Y}_c(x)\Big)^2}{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(Y_{c}(x)-\bar{Y}_c(x)\Big)^2}
-%\end{equation}
+An application of the SRS, \psmall{} and \extpsynth{} estimator was not feasible for 17 of all 405 FR-units due to an insufficient terrestrial sample size of $n_{2,G} < 2$.
+We further restricted the calculation of the \psmall{} and \extpsynth{} estimator to small area units with a minimum terrestrial sample size of $n_{2,G} \geq 4$ to avoid unstable estimates.
+This affected 65 additional FR units and limited unbiased two-phase estimations to 321 (79\%) of the 405 FR units.
+It should be noted that also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 2$.
+Due to substantially larger sample sizes, all estimators could however be applied to all 45 FA units.
+The average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (Table \ref{tab:estres}).
+An additional pairwise comparison of the 95\% confidence intervals revealed that the four estimators did in fact not produce statistically different point estimates for all FA and FR units.
+This confirmed that the differences between the estimators are solely found in the precision which they provide for the point estimates.
 
-%% Notes on leverages:
-%
-% - 568 plots exceed the critical threshold of 2p/n
-% - 1/5 (20\%) 
-% - leverages that can indeed be assumed to have a significant influence on the regression coefficients particularly were 
-%   a) per se small \meanheight{} values associated to small timber volume densities
-%   b) unusually large \meanheight{} values associated to small timber volume values.
-These implausible height values particularly occured in ALSyear acquisition years differing from the terrestrial survey.
-These leverage points were thus much more likely caused by harvesting activities in the sample plot area than erroneous ALS data.
-A deletion of these plots from the sampling / modelling frame was thus not justified due to the reasons given before.
-However, fitting the model without these plots turned out not to have any influence on the regression coefficients and the overall model accuracy.
+\begin{table}[H]
+	\begin{center}
+		\caption{Descriptive summary of point estimates and estimation errors on the two forest district levels. $N_u$: number of evaluated small area units.}
+		\vspace{0.2cm}
+		\label{tab:estres}
+		{\small %
+			\begin{tabular}{c|l c|c c c|c c c} %8cols
+				\hlineB{1}
+				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Point estimates} & \multicolumn{3}{c}{error$_{[\%]}$} \\
+				\cline{4-9} & & & mean & min & max & mean & min & max \\
+				\hline \hline
+				\multirow{4}{*}{FA} & SRS       & ($N_u$=45)  & 300.16 & 215.91 & 392.84 &  6.69 & 3.87 & 13.21 \\
+				& PSMALL    & ($N_u$=45)  & 307.29 & 209.26 & 417.10 &  5.16 & 3.46 & 14.33 \\
+				& EXTPSYNTH & ($N_u$=45)  & 307.27 & 209.01 & 415.02 &  4.78 & 3.25 & 13.88 \\
+				& PSYNTH    & ($N_u$=45)  & 306.90 & 223.51 & 409.92 &  2.34 & 1.54 &  3.95 \\
+				\hlineB{2}          
+				\multirow{4}{*}{FR} & SRS       & ($N_u$=388) & 301.83 &  99.89 & 612.13 & 18.32 & 0.34 & 104.97 \\
+				& PSMALL    & ($N_u$=321) & 308.15 & 159.64 & 568.67 & 12.24 & 3.48 &  44.94 \\
+				& EXTPSYNTH & ($N_u$=321) & 308.38 & 154.07 & 544.34 & 11.34 & 3.60 &  40.91 \\
+				& PSYNTH    & ($N_u$=403) & 307.82 & 166.01 & 444.29 & 4.65  & 2.56 &  62.51 \\
+				\hline \hline
+			\end{tabular}
+		}%
+	\end{center}
+\end{table}
 
-% x-values at the boundaries (small and large values) usually have a high leverage. It does not mean that they are invalid / erroneous.
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+\subsection{Estimation error}
+\label{sec:esterr}
 
-%% NOTES:
-%
-% - differences: zero-plots included !!! (basically, we here HAVE to use ALL plots for the regression model calibration --> because we use an internal model)
-%   --> comment on the (non) removal of outliers / leverage plots: see review-answers --> plots stay in dataset with exception of truly erroneous local density variables
-%       'plots kept in the sampling frame (i.e. they are used as x e s2 in the estimators) MUST also be kept in the modelling frame --> to insure the zero-mean-residual assumption'
-%       (important: also leverage plots or "outliers" might have a good reason to be kept in the sampling / modelling frame --> think of sherman tree)
-%
-% for discussion: better than removing plots would be the the use of disturbance classes (Massey --> change estimation) in order to decrease the impact on plots where major cuttings took place
-% between the ALS acquisition and the terrestrial survey. However, this is not possible if one height acquisition is available
+On both small area levels, the design-unbiased estimators \psmall{} and \extpsynth{} led to a substantial reduction in the estimation error compared to the SRS estimator (Fig.
+\ref{fig:disterrors}).
+On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under \extpsynth{} and \psmall{} respectively (Table \ref{tab:estres}).
+The cumulative error distribution (Fig.
+\ref{fig:disterrors}, left) reveals that under the SRS estimator, errors less than 5\% were achieved for 17\% of the FA units (8 of 45).
+This proportion could be increased to 62\% (28 FA units) and 73\% (33 FA units) by application of the \psmall{} and \extpsynth{} estimator.
+95\% of all estimates exhibited errors less than 9.5\% under the SRS estimator and less than 6.6\% when using \psmall{} or \extpsynth{}.
+Estimation errors higher than 10\% only appeared twice for each of the three estimators.\par
+Although the estimation errors were substantially larger overall on the FR level compared to the FA level due to smaller sample sizes, the error reduction from SRS by \psmall{} and \extpsynth{} were even more pronounced (Fig.
+\ref{fig:disterrors}, right).
+The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under \psmall{} and \extpsynth{} (Table \ref{tab:estres}).
+Errors smaller than 10\% were achieved for 15\% of the FR units by the SRS estimator, and for 46\% by the \psmall{} and \psynth{} estimator.
+95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors less than 20\%.
+In comparion, the SRS estimates resulted in errors less than 36.6\% for 95\% of the 388 FR units.
 
-\newpage
-% ======================================================================================================================== %
-% NOTES:
-% - Study Area **
-%   o characteristics of forests, e.g. structural & species diversity
-%   o introduce forest districts, show example and quickly mention their reasoning  
-% 
-% - The German NFI *
-%   o cluster sampling, angle-cound sampling, CF-correction at the forest border
-%     no. of plots (clusters) original according to BWI-survey
-%   o plot locations by DGPS, and expected accuracy and pre-processing (plausibility analyses
-%     and replacing by old coordinates if necessary)
-%
-% - Estimators **
-%   o one-phase estimator: write down estimator in HT-style (evtl. Derivation of CF-correction in
-%     Appendix)
-%   o two-phase psmall cluster
-%   o two-phase psynth extended cluster
-%   o two-phase psynth cluster
-%   (briefly explain:
-%    o the estimator like in jss-article, pronounce difference between psmall
-%      and psynthext in case of cluster sampling --> special case and research question:
-%      how often does it occur and does it make a difference?
-%    o explain difference between external and internal model --> this can be the reasoning for
-%      using Daniels estimators for our objective: a) "db" --> we do not depent on the model which
-%      is a huge advantage if we have medium-level quality data; b) "cluster" --> provided by Daniels
-%      estimators in combination with c) "iternal" model building --> g-weight property and
-%      considering dependency of regression coefs on the sample 
-%
-% - Extension of terrestrial sample grid **
-%   o rules (?), new sample sizes globally and within saes
+\begin{figure}[H]
+	\centering
+	\resizebox{1\hsize}{!}{\includegraphics{fig/error_distr_foa_fu.png}}
+	\caption{Cumulative distribution of estimation errors under SRS, \psmall{}, \extpsynth{} and the \psynth{} estimator.
+\textit{Left}: Results for the 45 FA units.
+\textit{Right}: Results for the 388 (SRS), 321 (\psmall{}, \extpsynth{}) and 403 (\psynth{}) FR units.}
+	\label{fig:disterrors}
+\end{figure}
+
+On both small area levels, the \psynth{} estimator resulted in much smaller estimation errors compared to \psmall{} and \extpsynth{}.
+This was as expected, since the \psynth{} variance estimate does not take the residual variation in each small area unit into account (Section \ref{sec:psynth}).
+Compared to the asymptotically design-unbiased estimators \psmall{} and \extpsynth{}, the estimation errors produced by \psynth{} thus seem to be too optimistic.
+One should also recall that the estimates of the \psynth{} estimator are potentially design-biased.
+
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+\subsection{Comparison of \psmall{} and \extpsynth{}}
+\label{sec:comp}
+
+Figure \ref{fig:disterrors} reveals that the error distribution of \psmall{} and \extpsynth{} are very similar, with \psmall{} showing marginally higher estimation errors.
+In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (Fig.
+\ref{fig:compvar}, left).
+As obvious, \psmall{} yielded slightly larger variances for the vast majority of the estimates.
+As addressed in Section \ref{sec:extpsynth}, one possible explanation for differences was the effect of one or more clusters not entirely being included in a small area unit, as this would constitute an assumption violation of the \extpsynth{} estimator.
+This violation was actually observed in 155 of the 321 FR units (48\%).
+We compared the variances of \psmall{} and \extpsynth{} for all small areas that did not have the violations using a Wilcoxon Signed-Rank Test \citep{wilcoxon1970} on a 5\% significance level.
+This test was also performed pairwise for groups $n_{2,G} \leq 6$, $n_{2,G} > 6$ and $n_{2,G} > 10$.
+The distribution of variances from \extpsynth{} was found to be highly significantly lower than that of \psmall{} except for the group of $n_{2,G} > 10$.
+The latter was expected since the variances of both estimators are asymptotically equivalent under large terrestrial sample sizes $n_{2,G}$ within the small area \citep[pp.17--18]{mandallaz2016}.
+This was also confirmed by a visual comparison of the absolute differences in the variances (Fig.
+\ref{fig:compvar}, right) which decreased with increasing terrestrial sample size.
+Performing the same comparison for small areas with violations also revealed the \extpsynth{} variances to be significantly smaller than the respective \psmall{} variances until sample sizes $n_{2,G} > 10$.
+Based on these investigations, it was not possible to determine whether the differences for sample sizes smaller than 10 were caused by the violations or just reflect the general tendency of \extpsynth{} to produce smaller variances than \psmall{} under small sample sizes.
+However, a visual inspection provided some evidence that the violations created a statistically significant influence on the \extpsynth{} variance (Fig.
+\ref{fig:compvar}, left, red diamonds) that makes it appear to be slightly over-optimistic.
+For sample sizes of $n_{2,G} < 6$, a weakly significant difference between the \extpsynth{} variances of those small areas with violations and the \extpsynth{} variances without violation was also indicated by an unpaired Wilcoxon Rank-Sum Test.
+However, the differences were still marginal and a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.
+
+\begin{figure}[H]
+	\centering
+	\resizebox{1\hsize}{!}{\includegraphics{fig/psmall_vs_extpsynth_fu.png}}
+	\caption{\textit{Left}: Comparison of the g-weight variance between the PSMALL and the EXTPSYNTH estimator for the 321 FR units.
+		\textit{Right}: Difference in g-weight variance between the PSMALL and the EXTPSYNTH estimator in dependence of the terrestrial data ($n_{2,G}$) in the FR unit.}
+	\label{fig:compvar}
+\end{figure}
+
+% ----------------------------------------------------------------------- %
+% ----------------------------------------------------------------------- %
+\subsection{Variance reduction compared to SRS}
+\label{sec:gain_eval}
+
+The variance reduction relative to SRS for \psmall{} and \extpsynth{} are described in Figure \ref{fig:gain} and Table \ref{tab:gain}.
+A direct comparison of the variances within the small area units revealed that the application of the design-unbiased estimators (\psmall{}, \extpsynth{}) led to a variance reduction compared to SRS in all FA units.
+In 75\% of the FA units, the \extpsynth{} estimator was able to reduce the variance by up to 54.1\%.
+The reduction in variance can also be expressed in the relative efficiency values, which were 2.02 on average and ranged between 1.18 and 4.13 on the FA level.
+On FR level, the reduction in variance even reached values of 90\% and relative efficiencies of 30 (Table \ref{tab:gain} and Fig.
+\ref{fig:gain}).
+The \psmall{} estimator again yielded slightly lower variance reductions and relative efficiencies due to the generally smaller variances of the \extpsynth{} estimator (Section \ref{sec:comp}).
+
+\begin{figure}[H]
+	\centering
+	\resizebox{0.73\hsize}{!}{\includegraphics{fig/compare_onephase_extpsynth_psmall.png}}
+	\caption{Cumulative distribution of variance reduction by the PSMALL and EXTPSYNTH compared to the SRS estimator for the  45 FA and 321 FR units.}
+	\label{fig:gain}
+\end{figure}
+
+\begin{table}[H]
+	\begin{center}
+		\caption{Descriptive summary of variance reduction compared to SRS and relative efficiencies on the two forest district levels. $N_u$: number of evaluated small area units.}
+		\vspace{0.2cm}
+		\label{tab:gain}
+		{\small %
+			\begin{tabular}{c|l c|c c c|c c c} %8cols
+				\hlineB{1}
+				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Variance reduction [\%]} & \multicolumn{3}{c}{relative efficiency} \\
+				\cline{4-9} & & & mean & min & max & mean & min & max \\
+				\hline \hline
+				\multirow{2}{*}{FA} & PSMALL    & ($N_u$=45)  & 33.51 &  2.6 & 72.5 & 1.74 & 1.03 & 3.64 \\
+				& EXTPSYNTH & ($N_u$=45)  & 43.30 & 15.7 & 75.8 & 2.03  & 1.18 & 4.13 \\
+				\hlineB{2}          
+				\multirow{2}{*}{FR} & PSMALL    & ($N_u$=321) & 12.48 & -1203.9 & 96.8 & 2.54 & 0.08 & 31.61  \\
+				& EXTPSYNTH & ($N_u$=321) & 24.75 & -892.7  & 97.0 & 2.95 & 0.10 & 33.70 \\
+				\hline \hline
+			\end{tabular}
+		}%
+	\end{center}
+\end{table}
+
+Cases also occurred on the FR level where one or both two-phase estimators produced larger variance values than under the SRS estimator.
+This happened in 19\% of the FR units under the \extpsynth{}, and in 24\% of the FR units under the \psmall{} estimator.
+One possible reason for this was supposed to be a large residual variance due to a poor performance of the regression model within the small area unit.
+In order to investigate this hypothesis, we analyzed the three variance terms of the \psmall{} estimator (eq.
+\ref{eq:psmallvar}), i.e.
+the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residuals (term 3).
+In general, the residual term is expected to make the largest contribution to the overall variance since it's sample size is based on $n_{2,G}$ whereas the auxiliary term and the coefficient term are based on larger sample sizes, i.e.
+$n_{1,G}$ and $n_2$ respectively.
+Figure \ref{fig:fail} illustrates the share of the overall variance by the residual term of the \psmall{} estimator scaled by the overall percentage reduction or increase of the variance compared to SRS for various small area sample sizes $n_{2,G}$.
+The residual term generally constitutes the dominating part of the \psmall{} variance (around 84\% on average).
+Although high residual term dominance does not necessary indicate that the \psmall{} variance will be disproportionately large, as apparent from Figure \ref{fig:fail} (\textit{right}), the vast majority of the small areas where the \psmall{} variance was larger than the SRS variance had residual terms contributing over 75\% to the overall \psmall{} variance.
+Furthermore, the magnitudes of the worst cases tended to occur in lower sample sizes.
+For example, of the FR units that saw variance increases where $n_{2,G}=4$, the average increase was 272\%, compared to 62\% for FR units with $n_{2,G} > 4$ (Fig.
+\ref{fig:fail}, \textit{left}).
+In comparison, the magnitude of the variance decreases were far more homogeneous than for the variance increases regardless of terrestrial sample size.
+Since $n_{2,G}$ is the same for \psmall{} and SRS, this implies that the sum of square residuals for the model are likely larger than the sum of square local densities for the clusters in $s_{2,G}$ indicating the presence of outliers with large residuals in the problematic small areas.
+This situation is likely to arise when there was forest loss after the ALS scanning but before the terrestrial survey year.
+% [check that]
+
+\begin{figure}[H]
+	\centering
+	\resizebox{1\hsize}{!}{\includegraphics{fig/eval_2phase_fail_11.png}}
+	\caption{Share of the overall variance by the residual term of the \psmall{} estimator for various small area sample sizes.
+Points are scaled by the overall percentage reduction/increase of the variance compared to SRS.}
+	\label{fig:fail}
+\end{figure}
+
+%----------------------------------------------------------------------------------------------%
+% ---------------------------------- Discussion ---------------------------------------------- %
+
+\section{Discussion}
+\label{sec:Dis}
+
+% ------------------------ %
+\subsection{Performance of estimators}
+
+The aim of this study was to investigate the performance of model-assisted design-based estimators for small area estimation of mean standing timber volume on two spatial forest management levels in Germany.
+It was of particular interest to gather information about the estimation error levels that can be attained using German NFI data that is characterized by low sampling intensities in the area of interests.
+To address these research questions, we applied the SRS, the \psmall{} and the \extpsynth{} estimators for cluster sampling to two forest management levels consisting of 45 and 405 small area units respectively in the German federal state of Rhineland-Palatinate.\par
+
+Our study showed that on both small area levels, the \psmall{} and the \extpsynth{} estimators generally led to a substantial reduction in estimation error compared to the standard one-phase SRS estimator.
+On the upper management level (FA districts), \psmall{} and \extpsynth{} produced estimation errors smaller than 5\% for 73\% of the small areas compared to only 17\% under the one-phase SRS estimator.
+The same level of precision could not be achieved on the lower management level (FR districts) primarily due to substantially smaller terrestrial sample sizes.
+However, in 95\% of the FR units, the estimation errors could be limited to 20\% compared to 40\% under SRS.
+A pairwise comparison of the confidence intervals revealed that the estimators did not produce significantly different point estimates.
+The much smaller estimation errors of the \psynth{} estimator reflected the fact that it does not try to correct for potential bias in the point estimate which can lead to overly optimistic estimation errors and confidence intervals.
+One should thus prefer the unbiased estimates of \psmall{} or \extpsynth{}.\par
+
+For several FR units, it was observed that the \psmall{} and the \extpsynth{} estimator can occasionally produce larger variances than the SRS estimator.
+It is important to note that this is in perfect agreement with the theory of both two-phase estimators and can theoretically appear if the residual variance in the small area, which generally constitutes the dominating part of the two-phase variance, turns out to be much higher than the variance of the terrestrial data in the small area.
+The empirical findings of our study suggest that such cases can particularly occur if moderate or poor model fits within a small area are combined with small terrestrial sample sizes ($\leq 5$) in the small area.
+A closer look on these small areas thus might reveal the reason for the poor prediction performance and help to improve the model fit.
+Nonetheless, it should be kept in mind that small terrestrial sample sizes can also cause the SRS estimator to not reflect the actual variation of the local density within a small area.
+In this case, the two-phase variance estimate might be larger but more realistic.
+Whereas a visual analysis of aerial images, remote sensing data or stand maps might give some further evidence for or against this hypothesis, a definite proof is practically infeasible.\par
+
+We were also able to empirically confirm that the \extpsynth{} estimator generally produces slightly smaller variances and estimation errors than the \psmall{} estimator.
+This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero mean residual property of the \extpsynth{} estimator.
+However, our analysis indicated that the difference between the two estimators is negligible for sample sizes $\geq$ 10 due to their asymptotic equivalency.
+We further investigated a potential impact on the \extpsynth{} variance caused by the assumption violation that one or more clusters are not entirely included in the small area unit and found a slight but statistically significant tendency to be over-optimistic for sample sizes smaller than 6.
+More empirical evidence must be gathered before generalizing this as a rule of thumb for the application of the \extpsynth{} under cluster sampling.
+It thus seems recommendable to prefer the \extpsynth{} to the \psmall{} estimator if its assumptions are not violated since it yields slightly smaller variances under mathematically soundness.
+Even if the differences between both estimators were marginal and did not lead to significantly different point estimates, \psmall{} can serve as a safe alternative if the \extpsynth{} assumption is violated.
+Aside from this, calculating both \psmall{} and \extpsynth{} and subsequently compare their results is always recommended to reveal suspicious deviations.\par
+
+% ------------------------ %
+\subsection{Auxiliary data}
+
+The auxiliary data used in our study were derived from two remote sensing sources, i.e.
+an ALS canopy height model and a tree species classification map.
+Likewise in many similar studies, the ALS mean canopy height proved to be the explanatory variable with highest predictive power.
+However, the large time-gaps of up to 10 years between the ALS acquisition and the terrestrial survey date caused the substantial introduction of artificial noise in the data.
+Whereas a post-stratification to the ALS acquisition years was an effective means to counteract the implied residual inflation, several leverage points were unambiguously caused by the temporal asynchronicity.
+Undetectable forest loss during the gap between the ALS acquisition and the NFI was also likely a cause for high residual variance in some small areas compared to the terrestrial data variance, which subsequently led to higher variances than the SRS estimator.
+As opposed to the ALS data, the availability of a country-wide tree species classification map has yet been unique among all German federal states.
+Whereas the study of \citet{hill2017a} already showed that the tree species information was able to improve the model fit, it has yet not been used to its full potential.
+One reason for this was the impossibility of modeling individual tree species within each ALS acquisition year, which would add further explanatory power.
+Another reason was the lack of available satellite data for classification in some parts of the country, which led to missing values in the inventory data and restricted 19 FR units to a simpler regression model.
+Promising steps with respect to more up-to-date canopy height information have already been made, as the topographic survey institution of RLP will from this year on provide a country-wide canopy height model derived from aerial imagery acquisitions.
+These campaigns will in the future be conducted in a two-year period and allow to derive canopy height information matching the dates of terrestrial forest inventories.
+A study of \citet{kirchhoefer2017} recently indicated that similar model performance for German NFI data can be achieved using such imagery-based canopy height models.
+Due to the improved coverage and repetition rate of the Sentinel-2 satellite \citep{sentinel2}, the tree species classification map will in the future be updated each year.
+We consider these alternative auxiliary data sources to also solve the problem of missing explanatory variables at inventory plots.
+One could also make use of the exhaustive information within the two-phase estimators by using the true the auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which could further decrease estimation errors.
+Previous studies of \citet{mandallaz2013b} however showed that given a reasonable large sample size of the first phase, the differences in the estimation error are usually small.
+With respect to the substantial improvements in the temporal synchronicity between auxiliary and terrestrial inventory data, we consider the demonstrated double-sampling approach also to be very efficient for change estimation \citep{massey2015b}.\par
+
+%----------------------------------------------------------------------------------------------%
+% ---------------------------------- Conclusion ---------------------------------------------- %
+
+\section{Conclusion}
+\label{sec:concl}
+
+The study led to two major conclusions: (1) the \extpsynth{} and \psmall{} estimator generally achieved substantially smaller estimation errors on the two investigated forest district levels compared to the SRS estimator.
+The demonstrated double-sampling procedure thus constitutes a major contribution to an increase in value of the existing German NFI data on the federal state level.
+However, it is not possible to conclude from our study results alone whether the realized error levels are already sufficient enough in order to support forest planning decisions.
+Thus, further investigations are necessary in close cooperation with the forest authorities.
+A first study will concentrate on testing the \extpsynth{} and \psmall{} confidence intervals as a validation source for the stand-wise inventories.
+(2) Despite the quality restrictions in the ALS data and the tree species map, the two data sources were found to be well suited to model the mean timber volume on plot and cluster levels.
+With respect to frequently updated aerial canopy height models and tree species maps, it will thus be of interest to investigate the model and estimation performances that can be expected for future applications.
+In this framework, the incorporation of additional auxiliary data and the extension to change estimation seem the reasonable next steps to be explored towards an operational implementation of the demonstrated double-sampling procedure.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{6pt} 
 %
 %
-% - Auxililary information and variable derivation **
-%   o document missing data at 1-phase grid (separate into s1 and s2) 
-%   o maybe: "due to missing remote sensing information at some sample points, the original sample sizes (s2, s1) 
-%             were shrinked down to the numbers shwn in table XX" (-> table showing the actual sample sizes)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\acknowledgments{We want to express our gratitude to Prof.
+H.
+Heinimann (Chair of Land Use Engineering, ETH Zurich) for supporting this study.
+We also want to explicitly thank Dr.
+Johannes Stoffels and Dr.
+Henning Buddenbaum from the Environmental Sensing and Geoinformatic Group of University of Trier for providing the ALS data and tree species classification map, and Dr.
+Kai Husmann and Dr.
+Christoph Fischer from the Northwest German Forest Research Institution G{\"o}ttingen for their advice in processing the terrestrial inventory data.
+Special gratitude is also owed to Dr.
+Thomas Riedel from the Th{\"u}nen Institute for providing the densified NFI sample grid, and Dr.
+Alexander Massey for proofreading.}
 %
-% - Model building **
-%   o refer to calibration method in previous article
-%   o refer to comprehensice model evaluations in previous article
-%   o present final model
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{Andreas Hill conducted the study and wrote the manuscript.
+Daniel Mandallaz developed the design-based estimators and supported the statistical analysis.
+Joachim Langshausen supported the study on the part of the State Forest Service Rhineland-Palatinate and cross-checked the analysis and the manuscript.}
 %
-%
-% 1) Preprocessing of terrestrial inventory data
-% 2) Preprocessing of auxiliary information
-% 3) Extention to 2-phase sample grid
-% 4) Model building
-%
-%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\conflictsofinterest{The authors declare no conflict of interest.}
 
-% NOTES:
-% - model formulation was based on the following considerations: a) The mean canopy height has the heighest explanatory power.
-Since the strength of correlation between meanheight and the timber volume on plot level showed high variation according to the time-lag of up to 10 years between the LiDAR acquisition and the BWI3 terrestrial inventory.
-and the varying LiDAR quality, the
-%
-%
-%
-%
-%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+\appendixsections{one} %Leave argument "multiple" if there are multiple sections.
+Then a counter is printed ("Appendix A").
+If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
 
-% MENTION:
-% - objective: find regression model (formula) to be applied in the sae estimators
-% - Specialty here: in the sae estimators, the predictions are generated on the cluster level (thus the regression coefficients are found on the cluster level)
-%   (--> and even more important: the residuals considered in the variance est. are also on the cluster level)
-%  ==> so for model selection, we looked at the global model performance on the plot as well as the cluster level
-%  ==> we also performed individual paramater t-test for each variable on the plot and cluster level. In order to  
-%
-% - important to recall that the design-based estimators, in which the regression model is used, do not impose any assumptions on the regression model as is the case in the model-dependent estimation framework.
-%
-% - no terrestrial data removed from the dataset for modelling, as all terrestrial data are used in the internal model (no choice, its specified by the estimators) 
-%
-% - mention sample sizes here: Due to missingness in the rs-data, the auxiliary variables were calculated for 89'930 sample plots (5384 terrestrial ...)
-%
-% - Model Validation (compare several models in table --> Alex)
-%
-% - Design-based Model Inference (new, use design-based var-covar-matrix)
-%
-% - idea: make a design-based inference of the regression coefficients on cluster level on the robust reg.coef-matrix
-%   "whereas the regression analysis in hill et al. 2017a" was carried out on the sample plot level, we here extend
-%    the analysis to the cluster level, as this is actually the level the estimators use the regression model predictions"
-%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
 
-% Feasibility: 
-% FA-level: for 44 out of 45 FA-units, the full model could be applied. For one remaining, only the model without tree species was applied.
-% FR-level: for xx out of the 405 FR-units, the full model could be applied. For one remaining, only the model without tree species was applied.
-%
-% ==> show specs for both regression models
+%=====================================
+% References, variant A: internal bibliography
+%=====================================
+\reftitle{References}
+\externalbibliography{yes}
+\bibliography{bib/literaturerRLPsae}
+
+\end{document}

### 2018-05-09 article MDPI/hill et al 2018.tex
update 09_05_2018(3)
update 09_05_2018(3)

@@
 If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
+\appendix
+
+\section{}
+% -------------------------------------- %
+\subsection*{R-squared on cluster level}
+
+The R$^2$ on the cluster level is calculated using the number of plots $M(x)$ of each cluster in order to weight for the varying number of plots on which $Y_c(x)$ and $\hat{Y}_{c}(x)$ are based on.
+
+\begin{equation*}\label{eq:R_squared_clust}
+R^2 =  \frac{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(\hat{Y}_{c}(x)-\hat{\bar{Y}}_c\Big)^2}{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(Y_{c}(x)-\hat{\bar{Y}}_c\Big)^2}
+\end{equation*}
+
+\noindent $Y_c(x)$ and $\hat{Y}_{c}(x)$ are the predicted and observed local densities on the cluster level calculated according to Equations \ref{eq:locdens_clust} and \ref{eq:globresids}.
+$\hat{\bar{Y}}_c$ is the estimated sample mean corresponding to the weighted mean over all observed local densities on the cluster level (Eq.
+\ref{eq:srs_est_clusters}).\par
+
+% -------------------------------------- %
+\subsection*{RMSE on cluster level}
+
+The same weights $M(x)$ are also applied to calculate the RMSE on the cluster level. $n_2$ is the number of clusters used in the modeling frame.
+
+\begin{equation*}\label{eq:RMSE_clust}
+RMSE= \sqrt{\frac{1}{n_{2}}  \sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M}_2}\Big)^2 \Big(\hat{Y}_{c}(x)-Y_c(x)\Big)^2}
+\end{equation*}
+
+\noindent The \textit{relative} or \textit{normalized} RMSE is calculated by dividing the RMSE by the estimated sample mean $\hat{\bar{Y}}_c$:
+
+\begin{equation*}\label{eq:NRMSE_clust}
+RMSE[\%] = \frac{RMSE}{\hat{\bar{Y}}_c}
+\end{equation*}
+
+\noindent Note that the weights $\frac{M(x)}{\bar{M_2}} \equiv 1$ if the number of plots per cluster is constant.
 

### 2018-05-10 article MDPI/hill et al 2018.tex
update 10_05_2018
update 10_05_2018

@@
 In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area regression estimators.
-We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (45 and 405 forest district units respectively) in the federal German state of Rhineland-Palatinate.
+We illustrate the implementation of the estimation procedure and evaluate its potential for future large scale operational application by the example of timber volume estimation on two small scale management levels (45 and 405 forest district units respectively) over the entire area of the federal German state of Rhineland-Palatinate.
 An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions.
@@
 
-The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels using the latest small area estimation procedures.
-We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 45 and 405 forest districts respectively.
+The objective of this study was to investigate whether the application of latest design-based small area estimation methods allow to use the German NFI data to produce estimates of acceptable precision on two forest district levels.
+The methods were tested in the German federal state Rhineland-Palatinate.
+Three types of model-assisted design-based small area regression estimators were used to derive point and variance estimates of mean standing timber volume for 45 and 405 forest management units on the two respective district levels.
 The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a} and \citet{ mandallaz2013b}.
@@
 The chosen double-sampling estimators were selected for several reasons: \textbf{(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can be used with \textit{non-exhaustive}, i.e.
-non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust under heteroscedasticity of the model residuals.
-The results from this study were considered to provide valuable information whether the suggested procedure might be a cost-saving alternative to a regional FDI.\par
+non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance partially accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust under heteroscedasticity of the model residuals.
+The results from this study were considered to provide valuable information about the potential of the suggested small area estimation procedure and the incorporated auxiliary information for future operational large scale application.\par
 
@@
 The one-phase estimator for cluster sampling (SRS) constitutes the \textit{status quo} that is currently applied under the existing one-phase sampling design of the German NFI in order to obtain point and variance estimates for the mean timber volume of a given estimation unit.
-In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator that is applied in the BWI3 algorithms \citep{bwi3_ausw} in the form given in \citet{mandallaz2008, mandallaz2016}.\par
+In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator that is applied in the BWI3 algorithms \citep{bwi3_ausw} in the form given in \citet{mandallaz2008} and \citet{mandallaz2016}.\par
 In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M=4$ ) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$.
@@
 \noindent $\pmb{Z}_{c}(x)$ is the vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Eq.\ref{eq:Zc(x)}).
-The weight $w(x_l)$ is the proportion of the support-area within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.
+The weight $w(x_l)$ is the proportion of the extraction area (support) within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.
 
@@
 	\hat{\bar{\pmb{Z}}}_{c,G} &= \frac{\sum_{x \in s_{1,G}} M_{G}(x) \pmb{Z}_{c,G}(x)}{\sum_{x \in s_{1,G}} M_{G}(x)} \label{eq:meanZcG} \hspace{3ex} &\text{where} \hspace{3ex}
-	\pmb{Z}_{c,G}(x) =  \frac{\sum_{l=1}^{L} I_{G}(x_l)\pmb{Z}(x_l)}{M_{G}(x)}\\		
-	Y_{c,G}(x) &= \frac{\sum_{l=1}^{L} I_{G}(x_l)Y(x_l)}{M_{G}(x)}  &\text{and} \hspace{3ex}
+	\pmb{Z}_{c,G}(x) =  \frac{\sum_{l=1}^{M} I_{G}(x_l)\pmb{Z}(x_l)}{M_{G}(x)}\\		
+	Y_{c,G}(x) &= \frac{\sum_{l=1}^{M} I_{G}(x_l)Y(x_l)}{M_{G}(x)}  &\text{and} \hspace{3ex}
 	\hat{Y}_{c,G}(x)=\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2}\\
@@
 Note that the restriction to $G$, i.e.
-$I_{G}(x_l)=\{0,1\}$, is made on the individual sample plot level $x_l$, and $M_{G}(x) = \sum_{l=1}^{L}I_{G}(x_l)$ thus is the number of sample plots per cluster within the small area.
+$I_{G}(x_l)=\{0,1\}$, is made on the individual sample plot level $x_l$, and $M_{G}(x) = \sum_{l=1}^{M}I_{G}(x_l)$ thus is the number of sample plots per cluster within the small area.
 The asymptotically design-unbiased point estimate of \textit{PSMALL} is then defined according to Eq.
@@
 The \extpsynth{} estimator (Eq.
-\ref{eq:extpsynth}) has been proposed by \cite{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased.
+\ref{eq:extpsynth}) has been proposed by \citet{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased.
 It has the advantage that the mean of the empirical model residuals of the OLS regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e.
@@
 \ref{eq:compsG}.
-A decomposition of $\hat{\pmb{\theta}}_{s_2}$ reveals that the residual correction term is now included in the regression coefficient $\hat{\pmb{\theta}}_{s_2}$.
+A decomposition of $\hat{\pmb{\theta}}_{s_2}$ reveals that the residual correction term is now included in the regression coefficient $\hat{\pmb{\theta}}_{s_2}$ \citep{mandallaz2016}.
 
@@
 \citet{mandallaz2016} assumed that the effects on the estimates should be negligible as the number of occasions where $M_{G}(x) < M(x)$ was considered to be small in practical implementations.
-It was thus a further objective of this study to investigate the actual occurrences and effects of this phenomenon by comparing the estimates of \extpsynth{} to those of \psmall{}.
+It was thus a further objective of this study to investigate the actual number of occurrences as well as effects of this phenomenon by comparing the estimates of \extpsynth{} to those of \psmall{}.
 % where the estimates stay unaffected
@@
 
-The estimation precision was quantified by the estimation error, which is the ratio of the standard error and the point estimate:
+The estimation precision was quantified by the estimation error, which is the ratio of the standard error and the point estimate (here $\hat{Y}$ stands for the point estimate produced under the various estimators):
 
@@
 
-We further calculated the 95\% confidence interval for each estimate for visualization purposes.
-The confidence intervals can also be used heuristically for hypothesis testing to determine whether the point estimates of the three estimators for a given small area are statistically different.
+We further calculated the 95\% confidence interval for each estimate.
+The confidence intervals were used heuristically for hypothesis testing to determine whether the point estimates of the three estimators for a given small area were statistically different.
 The confidence intervals for the SRS estimator can be obtained as:
@@
 
-In order to address the potential benefits of the small area estimators compared with the SRS approach, we calculated the \textit{relative efficiency} (Eq.
+In order to address the potential benefits of the small area estimators compared with the SRS approach, we calculated the \textit{relative efficiency} (\textit{RE}, Eq.
 \ref{eq:releff}) which can be interpreted as the relative sample size under SRS needed to achieve the variance under the double-sampling (DS) estimators.
@@
 \begin{equation}\label{eq:releff}
-rel.eff=\frac{\hat{\var}(\hat{Y}_{SRS})}{\hat{\var}(\hat{Y}_{DS})}
-\end{equation}
+RE=\frac{\hat{\var}(\hat{Y}_{SRS})}{\hat{\var}(\hat{Y}_{DS})}
+\end{equation}
+
+where $\hat{Y}$ stands for the point estimate produced under the respective estimator.
 
@@
 Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI.
-In the last inventory (BWI3) conducted in the year 2013, timber volume information was derived for 2810 clusters (8092 plots) in the field survey.
+In the last inventory (BWI3) conducted in the year 2011 and 2012, timber volume information was derived for 2810 clusters (8092 plots) in the field survey.
 The local timber volume density on the plot and cluster level for this sample was consequently calculated according to Section \ref{sec:srs_estimator}.
@@
 \textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit overlayed with the extended double-sampling cluster design.
-\textit{Green}: Forest stand polygon layer defining the forest area of this study.}
+\textit{Green}: Forest stand polygon layer defining the state and communal forest area of this study.}
 	\label{fig:StudyArean}
@@
 
-In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double-sampling design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArean}, \textit{right}).
-The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ clusters by the terrestrially measured DGPS coordinates.
-For our study, we restricted the sampling frame to the communal and state forest.
-The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service.
+In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double-sampling cluster design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ (Figure \ref{fig:StudyArean}, \textit{right}).
+The existing terrestrial phase $s_2$ was integrated by replacing the target coordinates of the respective $s_1$ clusters by the terrestrially measured DGPS coordinates.
+The sampling frame was further restricted to the communal and state forest area.
+The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stand layer provided by the forest service.
 Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.
@@
 These plots were deleted from the sampling frame and treated as missing at random.
-This assumption was considered to be reasonable as the respective sample locations did not exclude specific forest structures.
+This assumption was considered to be reasonable as the respective sample locations did not systematically exclude specific forest structures.
 
@@
 	\begin{center}
-		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plots}$: number of plots. $n_{\{1,2\}}$: number of clusters. TSPEC: tree species map information.}
+		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plot}$: number of plots. $n_{\{1,2\}}$: number of clusters. TSPEC: tree species map information.}
 		\vspace{0.2cm}
@@
 	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level.
-Right: Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.}
+Right: Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.
+From top to bottom: CHM, aerial image, tree species classification.}
 	\label{fig:Auxvars}
@@
 
-The tree species map was used to predict the main tree species at each sample plot which served as an additional categorical variable called \textit{treespecies}.
-This involved two consecutive processing steps.
+The tree species map was used to predict the main tree species at each sample plot which served as an additional categorical variable \textit{treespecies} in the regression model.
 In the first step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the edge-corrected support were classified as that species.
@@
 Likewise for the CHM variables, the support radius was 12 meters although the use of different support sizes for each explanatory variable would be in agreement with the two-phase estimators presented in Section \ref{sec:SAestimators}.
-When using the \textit{treespecies} variable in a regression model, the support size and the percentage threshold parameters had to be optimized in order to minimize the variance within each level which subsequently leads to improved model precision.
-A detailed analysis and description of the optimal parameter processing for the explanatory variables of the present data set is provided in \citet{hill2017a}.
+The specific setting for the support size and the percentage threshold was found to be optimal in order to yield the best possible regression model precision when incorporating the \textit{treespecies} variable as an additional predictor.
 In a second step, the \textit{treespecies} variable was also passed through a calibration model in order to reduce the effects of misclassification errors on the regression model coefficients and to increase model accuracy.
@@
 Table \ref{tab:classacc} gives the classification accuracies \citep{congalton2008} of the \textit{treespecies} variable after calibration.
+More details on the processing of the explanatory variables and identification of optimal parameter settings for their calculation are described in \citet{hill2017a}.
 
@@
 However, the \adjrsq{}s of the full and reduced model were found to be very similar on both the plot and cluster level.
-This implied that the variance reduction of the reduced model when applied to the two-phase estimators would likely be comparable to that of the full model, which is why a joint evaluation of the estimation results was performed (Section \ref{sec:Res}).
+This implied that the variance reduction of the reduced model when applied to the two-phase estimators would likely be comparable to that of the full model.
+For this reason, a joint evaluation of the estimation results is performed in Section \ref{sec:Res}.
 
@@
 They tended to occur in ALS acquisition years with longer time gaps to the terrestrial survey date and were thus more likely caused by harvesting activities in the sample plot area.
-Although these areas likely affected by harvest should clearly not be removed from the sampling frame, it does provided more justification for the inclusion of the \alsyear{} variable to mitigate these effects.
+Although these areas likely affected by harvest should clearly not be removed from the sampling frame, it does provide more justification for the inclusion of the \alsyear{} variable to mitigate the implied effects.
 
@@
 % ----------------------------------------------------------------------- %
-\subsection{Estimation error}
+\subsection{Estimation errors}
 \label{sec:esterr}
@@
 The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under \psmall{} and \extpsynth{} (Table \ref{tab:estres}).
-Errors smaller than 10\% were achieved for 15\% of the FR units by the SRS estimator, and for 46\% by the \psmall{} and \psynth{} estimator.
+Errors smaller than 10\% were achieved for 15\% of the FR units by the SRS estimator, and for 46\% by the \psmall{} and \extpsynth{} estimator.
 95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors less than 20\%.
@@
 One possible reason for this was supposed to be a large residual variance due to a poor performance of the regression model within the small area unit.
-In order to investigate this hypothesis, we analyzed the three variance terms of the \psmall{} estimator (eq.
+In order to investigate this hypothesis, we analyzed the three variance terms of the \psmall{} estimator (Eq.
 \ref{eq:psmallvar}), i.e.
@@
 Figure \ref{fig:fail} illustrates the share of the overall variance by the residual term of the \psmall{} estimator scaled by the overall percentage reduction or increase of the variance compared to SRS for various small area sample sizes $n_{2,G}$.
-The residual term generally constitutes the dominating part of the \psmall{} variance (around 84\% on average).
-Although high residual term dominance does not necessary indicate that the \psmall{} variance will be disproportionately large, as apparent from Figure \ref{fig:fail} (\textit{right}), the vast majority of the small areas where the \psmall{} variance was larger than the SRS variance had residual terms contributing over 75\% to the overall \psmall{} variance.
-Furthermore, the magnitudes of the worst cases tended to occur in lower sample sizes.
-For example, of the FR units that saw variance increases where $n_{2,G}=4$, the average increase was 272\%, compared to 62\% for FR units with $n_{2,G} > 4$ (Fig.
-\ref{fig:fail}, \textit{left}).
-In comparison, the magnitude of the variance decreases were far more homogeneous than for the variance increases regardless of terrestrial sample size.
-Since $n_{2,G}$ is the same for \psmall{} and SRS, this implies that the sum of square residuals for the model are likely larger than the sum of square local densities for the clusters in $s_{2,G}$ indicating the presence of outliers with large residuals in the problematic small areas.
-This situation is likely to arise when there was forest loss after the ALS scanning but before the terrestrial survey year.
+Not surprisingly, the residual term generally constitutes the dominating part of the \psmall{} variance (around 84\% on average).
+It has to be noted that such high residual term dominance does not necessary indicate that the \psmall{} variance will be disproportionately large (Figure \ref{fig:fail}, \textit{right}).
+However, the vast majority of cases where the \psmall{} variance was considerably larger than the SRS variance occurred where the residual term contributed over 75\% to the overall \psmall{} variance (Figure \ref{fig:fail}, \textit{left}).
+Among those cases, the most pronounced were observed under small sample sizes $n_{2,G} < 5$.
+Here, the average increase in variance compared to SRS of those FR units with $n_{2,G}=4$ was 272\%, compared to 62\% for FR units with $n_{2,G} > 4$.
+In contrast, the decreases in variance compared to SRS (Figure \ref{fig:fail}, \textit{right}) were much more homogeneous in magnitude and also independent of the terrestrial sample size.
+Since $n_{2,G}$ is the same for \psmall{} and SRS, these observations imply that in the problematic small areas, the sum of square residuals for the regression model are likely larger than the sum of square local densities for the clusters in $s_{2,G}$.
+This indicates the presence of outliers with large residuals, which likely arise when there was forest loss after the ALS scanning but before the terrestrial survey year.
 % [check that]
@@
 
-The aim of this study was to investigate the performance of model-assisted design-based estimators for small area estimation of mean standing timber volume on two spatial forest management levels in Germany.
-It was of particular interest to gather information about the estimation error levels that can be attained using German NFI data that is characterized by low sampling intensities in the area of interests.
-To address these research questions, we applied the SRS, the \psmall{} and the \extpsynth{} estimators for cluster sampling to two forest management levels consisting of 45 and 405 small area units respectively in the German federal state of Rhineland-Palatinate.\par
+With the objective of extending the use of the German NFI data to additional estimation on small scale management levels, we evaluated the performance of design-based small area regression estimators with respect to their suitability for future operational large scale application.
+For this reason, we conducted a case study in the German federal state of Rhineland-Palatinate where we applied the SRS, the \psmall{} and the \extpsynth{} estimators to produce estimates of the mean timber volume on two forest management levels over the entire federal state area, comprising 45 and 405 small area units respectively.
+In order to assess and compare the performance of the estimators, it was of particular interest to gather information about the magnitudes of estimation precision they can provide.\par
+
+%Important criteria were considered to be:
+%
+%- the magnitude of estimation precision on the respective management level
+%- the ability of the small area estimators to be
+%   a) applied for large scale application, and 
+%   b) frequently repeated
+%   c) transferred / applicable to numerous forest attributes under comparable low effort
+%- the identification of suitable auxiliary information, especially remote sensing data, with respect to their predictive power and their future availability
 
@@
 The much smaller estimation errors of the \psynth{} estimator reflected the fact that it does not try to correct for potential bias in the point estimate which can lead to overly optimistic estimation errors and confidence intervals.
-One should thus prefer the unbiased estimates of \psmall{} or \extpsynth{}.\par
+One should thus prefer the unbiased estimates of \psmall{} or \extpsynth{} whenever their calculation is possible.\par
 
@@
 Whereas a post-stratification to the ALS acquisition years was an effective means to counteract the implied residual inflation, several leverage points were unambiguously caused by the temporal asynchronicity.
-Undetectable forest loss during the gap between the ALS acquisition and the NFI was also likely a cause for high residual variance in some small areas compared to the terrestrial data variance, which subsequently led to higher variances than the SRS estimator.
+Undetectable forest loss during the gap between the ALS acquisition and the NFI was also likely a cause for high residual variance in some small area units compared to the terrestrial data variance, which subsequently led to higher variances than the SRS estimator.
 As opposed to the ALS data, the availability of a country-wide tree species classification map has yet been unique among all German federal states.
@@
 A study of \citet{kirchhoefer2017} recently indicated that similar model performance for German NFI data can be achieved using such imagery-based canopy height models.
-Due to the improved coverage and repetition rate of the Sentinel-2 satellite \citep{sentinel2}, the tree species classification map will in the future be updated each year.
+Additionally, the improved coverage and repetition rate of the Sentinel-2 satellite \citep{sentinel2} will allow to produce annually updated tree species classification maps.
 We consider these alternative auxiliary data sources to also solve the problem of missing explanatory variables at inventory plots.
-One could also make use of the exhaustive information within the two-phase estimators by using the true the auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which could further decrease estimation errors.
+One could also make use of the exhaustive information within the two-phase estimators by using the true auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which could further decrease estimation errors.
 Previous studies of \citet{mandallaz2013b} however showed that given a reasonable large sample size of the first phase, the differences in the estimation error are usually small.
-With respect to the substantial improvements in the temporal synchronicity between auxiliary and terrestrial inventory data, we consider the demonstrated double-sampling approach also to be very efficient for change estimation \citep{massey2015b}.\par
+With respect to the substantial improvements in the temporal synchronicity between auxiliary and terrestrial inventory data, we consider the demonstrated double-sampling approach also to be very efficient for the estimation of change \citep{massey2015b}.\par
 
@@
 The study led to two major conclusions: (1) the \extpsynth{} and \psmall{} estimator generally achieved substantially smaller estimation errors on the two investigated forest district levels compared to the SRS estimator.
-The demonstrated double-sampling procedure thus constitutes a major contribution to an increase in value of the existing German NFI data on the federal state level.
-However, it is not possible to conclude from our study results alone whether the realized error levels are already sufficient enough in order to support forest planning decisions.
-Thus, further investigations are necessary in close cooperation with the forest authorities.
+Thus, the demonstrated small area estimation procedure constitutes a major contribution to an additional use of the German NFI data for estimation below the federal state level.
+Further close cooperation with the forest authorities is crucial to evaluate whether the achieved error levels are already sufficient enough in order to support forest planning decisions.
 A first study will concentrate on testing the \extpsynth{} and \psmall{} confidence intervals as a validation source for the stand-wise inventories.
-(2) Despite the quality restrictions in the ALS data and the tree species map, the two data sources were found to be well suited to model the mean timber volume on plot and cluster levels.
-With respect to frequently updated aerial canopy height models and tree species maps, it will thus be of interest to investigate the model and estimation performances that can be expected for future applications.
-In this framework, the incorporation of additional auxiliary data and the extension to change estimation seem the reasonable next steps to be explored towards an operational implementation of the demonstrated double-sampling procedure.
+(2) Despite the quality restrictions, the ALS data and the tree species map were found to be well suited to model the mean timber volume on the plot and cluster level.
+With the prospect of more frequently updated aerial canopy height models and tree species maps, the two data sources will become even more attractive to be used as an integral part of future operational applications.
+The improving availability of remote sensing data will also allow to extent the demonstrated estimation procedure to the estimation of change.
+We consider this to be one of the next milestones towards a future operational use of the demonstrated small area estimation procedure.
 

### 2018-05-14 article MDPI/hill et al 2018.tex
update 14_05_2018
update 14_05_2018

@@
 
-With the objective of extending the use of the German NFI data to additional estimation on small scale management levels, we evaluated the performance of design-based small area regression estimators with respect to their suitability for future operational large scale application.
+With the objective of extending the use of the German NFI data to additional estimation on small-scale management levels, we evaluated the performance of design-based small area regression estimators with respect to their suitability for future operational large scale application.
 For this reason, we conducted a case study in the German federal state of Rhineland-Palatinate where we applied the SRS, the \psmall{} and the \extpsynth{} estimators to produce estimates of the mean timber volume on two forest management levels over the entire federal state area, comprising 45 and 405 small area units respectively.
@@
 %- the magnitude of estimation precision on the respective management level
-%- the ability of the small area estimators to be
-%   a) applied for large scale application, and 
-%   b) frequently repeated
-%   c) transferred / applicable to numerous forest attributes under comparable low effort
+%- the ability of the small area estimators to
+%   a) be applied for large scale application, and 
+%   b) be frequently repeated
+%   c) be transferred / applicable to numerous forest attributes under comparable low effort
+%   d) provide reliable specification of their estimation errors (uncertainties / precisions)
 %- the identification of suitable auxiliary information, especially remote sensing data, with respect to their predictive power and their future availability

### 2018-05-17 hill et al 2018/hill et al 2018.tex
update 17_05_2018
update 17_05_2018

--- 2018-05-14 article MDPI/hill et al 2018.tex
@@
 In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area regression estimators.
-We illustrate the implementation of the estimation procedure and evaluate its potential for future large scale operational application by the example of timber volume estimation on two small scale management levels (45 and 405 forest district units respectively) over the entire area of the federal German state of Rhineland-Palatinate.
+We illustrate the implementation of the estimation procedure and evaluate its potential for future large-scale operational application by the example of timber volume estimation on two small-scale management levels (45 and 405 forest district units respectively) over the entire area of the federal German state of Rhineland-Palatinate.
 An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions.
-The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the SRS estimator by 43\% and 25\% on average for the two management levels respectively.}
+The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the one-phase simple random sampling estimator by 43\% and 25\% on average for the two management levels respectively.}
 
@@
 % ---------------------------------------------- %
-\subsubsection{Tree species map}
+\subsubsection{Tree species classification map}
 \label{sec:tspecclass}
@@
 
-\subsubsection{Tree species map}
+\subsubsection{Tree species classification map}
 

### 2018-08-06 Reviews/answer_reviewers.tex
update 06_08_2018
final version of published article

\documentclass{article}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage[normalem]{ulem}

%============================================ Define Titlepage & packages =============================================%

\title{Review - revision}

\author{A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels\\
Andreas Hill, Daniel Mandallaz, Joachim Langshausen}

\usepackage{fancyhdr}     
\usepackage{amsmath} %Paket für erweiterte math. Formeln
\usepackage[labelfont=bf]{caption}
\usepackage[font=footnotesize]{caption}
\usepackage[font=footnotesize]{subcaption}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[final]{pdfpages}
\usepackage{color}

\usepackage{geometry}
\geometry{
	a4paper,
	left=25mm,
	right=25mm,
	top=30mm,
	bottom=30mm
}

\setlength{\parindent}{0em} % Einzug bei neuen Absätzen

%------------------------------------------------------------------------------------------------%
% -------------------------------------- Main Document------------------------------------------ %

\begin{document}

%------------------------------------------------------------------------------------------------%
% -------------------------------------- Tex Settings ------------------------------------------ %

\maketitle
\thispagestyle{empty}
\newpage

\pagenumbering{arabic}
\setcounter{page}{1}

\pagestyle{fancy} %Kopfzeile und Fusszeile
\fancyfoot[C]{\thepage}
\setlength{\headsep}{15mm}

\definecolor{mybrown}{rgb}{0.6, 0.15, 0.1}
\definecolor{amaranth}{rgb}{0.9, 0.17, 0.31}
\definecolor{mygreen}{rgb}{0.1, 0.4, 0.4}
\newcommand{\answer}[1]{\small \color{mybrown}{#1} \color{black}}
\newcommand{\note}[1]{\textit{\small \color{amaranth} \textbf{Note:} #1} \color{black}}
\newcommand{\todo}[1]{\color{red}{#1} \color{black}}
\newcommand{\answerfin}[1]{\small \color{mygreen}{#1} \color{black}}

%------------------------------------------------------------------------------------------------%
% ---------------------------------- Reviewer 1 ------------------------------------------------ %

\section*{Reviewer 1:}

I have only a single marginal question, and probably I am wrong: $Z_{c}(x)$ is introduced as a row vector in line 183 and Eqs. 9a and 9b, but it is used as column vector in Eqs. 12, 13 and 14. I would appreciate much if the authors could check whether this inconsistency really exists with respect to notation of $Z_{c}(x)$.\\

Answer:\\

\answerfin{Vectors are always column vectors, i.e $Z(x)$ and $Z_{c}(x)$ are column vectors.	When they are used for predictions they have to be transposed in order to get a scalar product written as a matrix multiplication, i.e. $\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2}$. We added the information that $Z_{c}(x)$ is a column vector in line 183 to make this more clear for the reader.}

%------------------------------------------------------------------------------------------------%
% ---------------------------------- Reviewer 2 ------------------------------------------------ %

\section*{Reviewer 2:}

General comment on publishing the article in Remote Sensing:

We decided to hand in our article to be published in the \textit{Remote Sensing} special issue \textit{Remote sensing based Forest Inventories from Landscape to Global Scale}, since multiple of the mentioned topics for articles of the special issue are covered by our article (such as 'Application of remote-sensing techniques for monitoring forest attributes at the forest enterprise level', 'Application of remote-sensing techniques for monitoring forest attributes for national forest inventories', 'Large scale in-situ data requirement and sampling design for monitoring forest ecosystems with remote-sensing techniques').  Additionally, of course, not all readers of \textit{Remote Sensing} are specialists in forest inventory, but most of the latter frequently read \textit{Remote Sensing}.

\begin{enumerate}

  % 01) ++++++++++++++++++++++++++ %
  \item \textit{L28: “entire forest state area of Germany” I understand what you mean, but it may be misleading as readers might think about the area owned by the German state forest enterprise (Bundesforst). I would suggest to rephrase “forested area of Germany”.}

  \answerfin{Has been changed accordingly.}
  % --------------------------- %

  % 02) ++++++++++++++++++++++++++ %
  \item \textit{L29: 114'191 ha – A wrong unit was used here, its 114 191 km$^2$ (or 11 419 124 ha)..}

  \answerfin{Has been corrected accordingly.}  
  % --------------------------- %

   % 03) ++++++++++++++++++++++++++ %
  \item \textit{L36: “standwise forest inventories (SFI)”?}

  \answerfin{Has been changed accordingly.}  
  % --------------------------- %

  % 04) ++++++++++++++++++++++++++ %
  \item \textit{L38-41: Please add the information that the FDI of Lower-Saxony (Betriebsinventur, BI) is only done for forests owned by the state forest enterprise (Lower Saxony State Forests = Niedersächsische Landesforsten, NLF)}

  \answerfin{The information has been added.}  
  % --------------------------- %

  % 05) ++++++++++++++++++++++++++ %
  \item \textit{L41 As far as I remember, [4] is an article written in German. If so, please indicate in the reference list – it is annoying for readers to search for papers that turn out to be written in a language they possibly do not understand.}

  \answerfin{We now give the original title in German.}  
  % --------------------------- %

  % 06) ++++++++++++++++++++++++++ %
  \item \textit{L42: As far as I remember, v.Lüpke’s dissertation [5] is a cumulative work. If so, please cite the original articles and not the compilation.}

  \answerfin{Has been changed accordingly.}  
  % --------------------------- %

  % 07) ++++++++++++++++++++++++++ %
  \item \textit{L43: I would suggest to cite the classic textbooks of Cochran (1977) and de Vries (1986) beside the modern literature [6-9] }

  \answerfin{The respective citations have been added.}  
  % --------------------------- %

  % 08) ++++++++++++++++++++++++++ %
  \item \textit{L43-48: I would suggest to add some words (here or in the discussion) addressing the problems arising with multi-purpose forest inventories (e.g. Corona and Marchetti 2007): The stratification is optimized for a single target variable (in most cases the volume of the growing stock) and the introduction of additional target variables becomes challenging (e.g. Ritter and Saborowski, 2014).}

  \answerfin{We think that the reviewer might mix up \textit{stratification} (where the sample sizes are optimized for strata \textit{prior} to the actual conduction of the inventory based on auxiliary data) with \textit{post-stratification} (where the categorical auxiliary data are used in the regression model \textit{after} the inventory has been conducted). The latter, which is the case applied in our article, does not impose any of the mentioned problems of multi-objective optimization. We thus think that including this topic does not fit well into our article since it is not affecting the methods that we are demonstrating.}

%  \note{I don't think this issue concerns the work presented in our study, since optimization was not part of the study. One could mention the anticipated variance treated in the book of Mandallaz (2008). Multi-objective optimization would implies a weighting of the objectives, which is a highly political issue and probably unsolvable in my opinion. Separate investigation are probably simpler and better. Worth emphasizing that the method presented is valid for any response variable which can be used to define a local density. I also think that the reviewer exchanges stratification (where the sample sizes are optimized prior to the actual conduction of the inventory based on auxiliary data) and post-stratification (where the categorical auxiliary data are used in the regression model after the inventory has been conducted). The latter, which is the case applied in our article, does not impose any of the mentioned problems of multi-objective optimization. We thus think that including this topic does not fit well into our article since it is not affecting the methods we suggest.}
  % --------------------------- %

  % 09) ++++++++++++++++++++++++++ %
  \item \textit{L46-47: Double-sample procedures have not only been used in the FDI of Lower Saxony, but also in the NFIs of Canada (Gillis et al., 2010) and Switzerland (Lanz et al. 2010), and in different other inventories (e.g. Chojnacky, 1998 or  Gasparini et al., 2010).}

  \answerfin{We rephrased the sentence and added the suggested references.}  
  % --------------------------- %

  % 10) ++++++++++++++++++++++++++ %
  \item \textit{L99 “The German NFI (Bundeswaldinventur, BWI)“  I think, the abbreviation introduced in the next line becomes more meaningful when giving the German name here.}

  \answerfin{Has been changed.}  
  % --------------------------- %

  % 11) ++++++++++++++++++++++++++ %
  \item \textit{L100 “The third and most recent” }

  \answerfin{Has been changed.}  
  % --------------------------- %

  % 12) ++++++++++++++++++++++++++ %
  \item \textit{L101 '4x4km' I would prefer '4km ' 4km'}

  \answerfin{We would like to stick to the given notation in accordance with our previously published article (Hill et. al 2018: Combining canopy height and tree species map information for large-scale timber volume estimations under strong heterogeneity of auxiliary data and variable sample plot sizes, \textit{European Journal of Forest Research}).}  
  % --------------------------- %

  % 13) ++++++++++++++++++++++++++ %
  \item \textit{L102 '2x2km' same as above (2km ' 2km)}

  \answerfin{Same as above.}  
  % --------------------------- %

  % 14) ++++++++++++++++++++++++++ %
  \item \textit{L107: A short explanation of the angle count sampling concept would be helpful for readers who aren't foresters, maybe here or in a corresponding appendix.}

  \answerfin{We added an explanation of angle count sampling in Section 2.}  
  % --------------------------- %

  % 15) ++++++++++++++++++++++++++ %
  \item \textit{L110/111 “DBH” and “DBH” Please decide whether or not to use italics. Please also add the information that this refers to a height of 1.3 m, Remote Sensing has a lot of readers who are not foresters.}

  \answerfin{We added the information about the height. Concerning italics, we decided to use italics when first introducing a notation/term and use normal formatting when using the term afterwards.}  
  % --------------------------- %

  % 17) ++++++++++++++++++++++++++ %
  \item \textit{L196 Please also provide reference to the R software itself, and not only to the package. }

  \answerfin{The reference has been added.}  
  % --------------------------- %

  % 18) ++++++++++++++++++++++++++ %
  \item \textit{L273: I think this is the only occasion you use italics for "RLP".}

  \answerfin{We use italics when introducing a term for the first time and use normal formatting when using the term afterwards.}  
  % --------------------------- %

  % 19) ++++++++++++++++++++++++++ %
  \item \textit{L283: “communal forests” is most often used as a synonym for “community forests” in context of rural development policy. I think here it is rather an odd translation of the German word “Kommunalwald”. Maybe, “municipal forests” is the better translation.}

  \answerfin{We changed 'communal' to 'municipal' throughout the entire article.}  
  % --------------------------- %

  % 20) ++++++++++++++++++++++++++ %
  \item \textit{L295 "RLP" was already introduced as an abbreviation}

  \answerfin{'RLP' has been deleted.}  
  % --------------------------- %

  % 21) ++++++++++++++++++++++++++ %
  \item \textit{L287: Instead of “45 Forstämter (FA)” I would use “45 forest districts (Forstämter, FA)” }

  \answerfin{Has been changed, and likewise for the Forstreviere which we now call sub-districts.}  
  % --------------------------- %

  % 22) ++++++++++++++++++++++++++ %
  \item \textit{L289-290: If the SFI is conducted in a five year cycle, shouldn’t the management strategy be also set up for five years, instead of ten years?}

  \answerfin{The cycle of the stand wise inventories actually varies between 5 and 10 years and can in some cases even exceed 10 years. The stand wise inventories and the date of their conduction are planned by the state forest service. The management strategy for the stands is, however, always made for the upcoming 10 years ('mittelfristige Planung').}  
  % --------------------------- %

  % 23) ++++++++++++++++++++++++++ %
  \item \textit{L295 "2x2km" (see above)}

  \answerfin{We would like to keep the '2x2km' notation.}  
  % --------------------------- %

  % 24) ++++++++++++++++++++++++++ %
  \item \textit{Figure 1: "communal forests" (see above)}

  \answerfin{Has been corrected.}  
  % --------------------------- %

  % 25) ++++++++++++++++++++++++++ %
  \item \textit{Table 1: Please remove the digits (or at least reduce the number of digits). Giving values with an “accuracy” of 1/100th of a mm (i.e. 10 mm) for DBH, as an example, really does not make much sense. }

  \answerfin{We limited the number of digits for timber volume, DBH and height to one digit and removed the digits for stem number.}  
  % --------------------------- %

  % 26) ++++++++++++++++++++++++++ %
  \item \textit{Table 3: I think one digit for the percentage values should be enough.}

  \answerfin{Has been changed accordingly.}  
  % --------------------------- %

  % 27) ++++++++++++++++++++++++++ %
  \item \textit{Table 6: Please indicate for what variable point estimates are. I suppose it is volume of growing stock per area unit [m$^3$ha-1]? And again, check the number of digits.}

  \answerfin{Yes! We added the missing information accordingly.}  
  % --------------------------- %

 % 28) ++++++++++++++++++++++++++ %
  \item \textit{L454-458 I understand your intention and the necessity of removing FR-units. However, when comparing the performance of the estimators you should use the same population for all estimators. Removing the "difficult" FR-units (i.e. those with a low sampling density) only for PSMALL and EXTPSYNTH is somewhat unfair against the other estimators, and may bias the results. So, my advice is to recalculate SRS and PSYNTH for the same 321 FRs that were used for PSMALL and EXTPSYNTH. Edit: I noticed you confined your analyses to those 321 FRs later on (Fig 5 and Tab. 7), another reason to also do it here.}

  \answerfin{We changed the evaluation according to your suggestion and added a sentence in the paragraph above the table. The descriptive summary statistics for the one-phase SRS and the PSYNTH estimator did only differ marginally, with exception of the maximal errors which logically turned out to be lower. We also adjusted the numbers given in Section 6.2 and the graphic of Figure 3 respectively.}

  % --------------------------- %

 % 29) ++++++++++++++++++++++++++ %
  \item \textit{L517: Please use the same scaling for both x- and y-axis on the left plot. It is irritating that the 1:1 line does not cross the grid-corners.}

  \answerfin{Has been changed accordingly.}  
  % --------------------------- %

   % 30) ++++++++++++++++++++++++++ %
  \item \textit{L655-656: "Northwest German Forest Research Institution" It should be "Institute" instead of "Institution"}

  \answerfin{Has been corrected.}  
  % --------------------------- %

\end{enumerate}

%------------------------------------------------------------------------------------------------%
% ---------------------------------- Reviewer 3 ------------------------------------------------ %

\section*{Reviewer 3:}

\begin{enumerate}

    % 01) ++++++++++++++++++++++++++ %
  	\item \textit{Under the design-based inferential framework, invoking the asymptotical properties of a small-area estimator is a contradiction in terms; the asymptotic properties are based on large-sample assumptions, while SAE estimators are used when the sample size is (too) small. If the sample size for the entire population is very large, then the small-area estimation becomes a common domain estimation problem, and there is no need for tailored SA estimators because the direct estimators are probably the most efficient -  see Estevao and Särndal (2004) 'Borrowing strength is not the best technique within a wide class of design-consistent domain estimators.  Journal of Official Statistics, 20, 645-669' for details. This is an important aspect that it’s been often ignored in the model-assisted SA studies. The authors put a great deal of effort in assessing the results by the realized sample sizes in various SAs, however, such comparisons have limited relevance if the asymptotic results cannot be invoked. This is not criticism, personally I do not have a solution, and there is probably no analytical solution to derive the small-sample properties of these estimators. However, I think that rising this issue would add value to the manuscript, by informing the readers of potential drawbacks of the estimation methods.}

%  	\note{ the populations are domains (i.e. a continuum of infinitely many points) of the plane F, also known as the Monte Carlo approach: the objective is to estimate the integral $\int_{G} Y(x)dx$, $G \in F$ a function $Y(x)$ which is essentially the Horwitz-Thompson estimator for a response variable for the population of trees. This is the main difference with standard survey sampling. Another important difference is that instead of having a single large sample we have $n_2$ points $x$	each one with a sample of trees (terrestrial sample). The sample size $n_2$ can be large over the entire domain, but small over sub-domains, and too small to fit models using auxiliary data available at a much larger number of points $n_1$. You do not have to borrow strength if you are strong, which is obvious. We do not propose to fit models over extremely large areas with very different forest structures (say all Europe) but to rely on predictions based on remote sensing data to provide better estimates for smaller management units. Asymptotic results for the variances are, given the complexity of the problem, the only available ones. When are asymptotic results approximately valid? Take for instance n=6 (not a very large number), then the distribution of the mean of n=6 uniformly distributed random variables is practically undistinguishable from the normal distribution, so that in this case n=6 is the asymptotic validity range. On the other hand with extreme values statistics, n=100 can be far to small to reach a normal distribution. Some simulations performed on the artificial examples (see our articles published in the Canadian Journal of Forest Research - Source) and on a unique data set (Zurichberg data, see book of Mandallaz for examples) show that for SA problems, $n$ > 12 or even 6 is acceptable. All the variance estimates are based on the asumption of i.i.d uniformly distributed points (or clusters origins) for remote sensing for remote sensing followed by SRS selection for terrestrial observations, whereas in practice systematic grids are used. Simulation and past experience with alternative model-dependent Kriging procedure (Source) show that the variance estimates are usually to pessimistic. On the other hand, only sampling errors are taken into account and not measurement errors (e.g. on bole volume).}

  	\answerfin{Asymptotic results for the variances are, given the complexity of the problem, the only available ones. When are asymptotic results approximately valid? If one takes for instance n=6 (not a very large number), then the distribution of the mean of n=6 uniformly distributed random variables is practically undistinguishable from the normal distribution, so that in this case n=6 is the asymptotic validity range. On the other hand with extreme values statistics, n=100 can be far to small to reach e.g. the Gumbel distribution. Transferring this to the case of forest inventory, it is actually impossible to define a minimal sample size that always ensures the validity of the central limit theorem for the particular case. However, simulations performed for an artificial example in Mandallaz et al. (2013). New regression estimators in forest inventories with two-phase sampling and partially exhaustive information: a design-based monte carlo approach with applications to small-area estimation. \textit{Canadian Journal of Forest Research}, 43(11), 1023-1031, suggested that for SA problems, a sample size in a small area of $n$ > 6 is acceptable to reach the nominal coverage rates of the confidence intervals. Whereas these simulations where performed for simple sampling, re-evaluating the simulation example recently confirmed the same results for cluster sampling. We added a respective remark in the discussion, Section 7.1, line 638-645.}

    % 02) ++++++++++++++++++++++++++ %
    \item \textit{The authors argue that some PSYNTH and the EXTPSYNTH estimators may not always be design-unbiased for the SAs that do not contain field sampling units. I assume that the authors are well aware that the sample sizes within the SAs are random variables. Under SAE there is always a risk that a some SAs will not be represented in a particular sample, but every SA will contain field observations under unconditional estimation over all possible samples, otherwise a coverage bias will occur. Thus, for statements such as 'The PSYNTH estimator thus has a potential unobservable design-based bias' (lines 228-229), the authors should clarify if they are considering the properties of the estimators conditioning on the realized sample, or unconditionally. One could also argue that, if the asymptotic arguments are	invoked (although they should probably not be), then the PSYNTH estimator is still design-consistent for SAs, even in the absence of field observations. See Firth and Bennett (1998) 'Robust models in probability sampling. Journal of the Royal Statistical Society, 60, 3-21'.}

    \answerfin{It is, of course, conditioned on the realized sample. We added this information in the respective line 248/249.}

    % 03) ++++++++++++++++++++++++++ %
    \item \textit{Regarding the case study, I understand the motivation for using SAE at FR level, where the average number of field sampling units (clusters) is about 5 (0 to 13) per SA. However, using SAE at FA level - where the average sample size contains about 46 clusters (11 to 64)- has to be better justified because, least for some FAs, a direct estimator would have been more efficient (Estevao and Saerndal 2004). However, it is perfectly understandable that constructing domain specific (FA-level) models is a time consuming endeavor and simplifying the regression modeling is a pragmatic solution for statistical production, but a discussion on this topic should be provided to inform the readers of the possible choices.}

    \answerfin{Thank you for this valuable hint! We added a discussion of this question in the discussion, Section 7.1., line 590-600. We point out that the main reason we did not consider direct estimation on the FA-level was the large number of parameters (39 coefficients for the full model, see also Hill et al. 2018*) to be fitted for each FA-unit model due to the pronounced heterogeneity of the auxiliary data (multiple tree species and ALS acquisition years per FA-unit). In this case, the strategy to 'borrow strength' from the entire inventory domain was preferred to direct estimation in order to avoid overfitting and the implied risk of unstable global estimation.\\

    * Hill, A., Buddenbaum, H., \& Mandallaz, D. (2018). Combining canopy height and tree species map information for large-scale timber volume estimations under strong heterogeneity of auxiliary data and variable sample plot sizes. \textit{European Journal of Forest Research}, 1-17.}

%    \note{the situation is even more complicated because we treat a systematic sample (grid) as a random sample of uniformly distributed points (or cluster origins). Consequently all sample sizes (i.e. number of plots or cluster in the forest or sub-domains of it) clusters are random. Treating such a systematic sample as a random will as afore mentioned lead to an over-estimations of the the sampling variance. The resulting variances are conditional on the observed sample sizes. In model-assisted design-based inference models do not have to be true (as in model-dependent survey inference), they only have to be useful. In the external approach (asymptotically valid also for internal models) you must correct the estimator with the residuals. (PSMALL does that and EXTPSYNTH also but in a indirect way). It can happen, by chance, that	the PSYNTH is indeed closer to the truth (example in the book). 
%    	
%    The crucial	point is to use remote sensing data and direct estimation (still using auxiliary information) can be unstable because of the large number of parameters in the prediction model. The synthetic estimator can be severely biased (take the model with only the intercept term, it is unbiased globally but not locally, unless the forest looks much the same everywhere, this has been confirmed by simulations with more complex model). In the model-dependent approach it can happen (we have such a case study ) that the synthetic estimator is closer to the known true value than all other estimates (included the sample mean of the observations in the small area). It is not clear what direct estimation mean: a model relying on auxiliary information built especially for the SA under consideration (which can be expected to be better than a global model, provided we have enough observations for model-building) or estimates based only on the sampled response variable in the SA. If you have unlimited resources it is clearly better. National forest inventory are time consuming and expensive and local management want this data to be useful for their own use, so that ideally that do not have to perform local inventories.}
    % --------------------------- %

    % 04) ++++++++++++++++++++++++++ %
    \item \textit{Regarding the terminology used (especially) in Section 4, expressions like “design-based small area regression estimator” are not very accurate, since the same estimator (i.e., the same mathematical expression) can be used (appropriately or not) in different contexts. For instance, one could use the PSYNTH estimator (based on an internal model) as an external estimator for another population in a	model-dependent framework. Instead, I would rather use the formulation “design-based small area regression estimation”, to avoid confusions.}

    \answerfin{When using the terms '... estimators' as titles in Section 4, they refer explicitly to the estimators which we decided to apply in our article. In accordance to the various articles published on the used estimators by Mandallaz (see selected references below), we would prefer to maintain the terminology as given in our article. Additionally, up to our knowledge the terms 'design-based estimator', 'model-based estimators' are also frequently used in the literature, e.g.:

    	\begin{itemize}

    		\item Mandallaz, D. (2013). A three-phase sampling extension of the generalized regression estimator with partially exhaustive information. \textit{Canadian Journal of Forest Research}, 44(4), 383-388.

    		\item Mandallaz, D., Breschan, J., \& Hill, A. (2013). New regression estimators in forest inventories with two-phase sampling and partially exhaustive information: a design-based monte carlo approach with applications to small-area estimation. \textit{Canadian Journal of Forest Research}, 43(11), 1023-1031.

    		\item Massey, A., \& Mandallaz, D. (2015). Comparison of classical, kernel-based, and nearest neighbors regression estimators using the design-based Monte Carlo approach for two-phase forest inventories. \textit{Canadian Journal of Forest Research}, 45(11), 1480-1488.

    		\item Breidenbach, J., McRoberts, R. E., \& Astrup, R. (2016). Empirical coverage of model-based variance estimators for remote sensing assisted estimation of stand-level timber volume. \textit{Remote Sensing of Environment}, 173, 274-281

    		\item Ghosh, M., \& Kumar Sinha, B. (1990). On the consistency between model-and design-based estimators in survey sampling. \textit{Communications in Statistics-Theory and Methods}, 19(2), 689-702

    		\item Magnussen, S. (2015). Arguments for a model-dependent inference?. \textit{Forestry: An International Journal of Forest Research}, 88(3), 317-325

    	\end{itemize}

    and many more.}

    % --------------------------- %

    % 05) ++++++++++++++++++++++++++ %
   \item \textit{Please elaborate on the importance of the zero-mean residual property (lines 191-192). This is an important issue that can be tracked down to the definition of the internally bias-calibrated models in Firth and Bennett (1998) “Robust models in probability sampling. Journal of the Royal Statistical Society, 60, 3-21”. }

   \answerfin{We rephrased this part. We added some sentences to emphasize the difference between the OLS residuals being zero on average (this is of course the case for any OLS fitted model) and the consequence for the theoretical residuals in the inventory domain $F$ if they model is fitted internally (then, we have the \textit{zero mean residual property} according to the works of Mandallaz). We also mention the importance of this property for deriving the g-weight variance in the framework of small area estimation, a technique that was introduced by Mandallaz in 2012/2013. In case a reader is interested in more mathematical details, we give the respective references. We would like to emphasize that the objective of our article was to illustrate the application of the already extensively mathematically described estimators by Mandallaz to large inventory areas and investigate their suitability for future operational use in NFIs. Consequently, the article explicitly targets at an audience of practitioners. For this reason, we strongly believe that discussing more mathematical details which have already been given in various peer-reviewed articles in the Canadian Journal of forest research and technical reports (references given in the article) is beyond the scope of the article's objective.}

   % --------------------------- %

   % 06) ++++++++++++++++++++++++++ %
   \item \textit{Line 231-232: See the general comments with regard to design-unbiasedness.}

   \answerfin{We added that it is conditional on the realized sample.}
  % --------------------------- %

  % 07) ++++++++++++++++++++++++++ %
  \item \textit{Line 233: The PSYNTH estimator is not design-based, the estimation is design based.}

  \answerfin{Has been changed respectively.}

%  \answerfin{The PSYNTH estimator as well as its estimations are design-based. To our knowledge, the terms 'design-based estimator', 'model-based estimators' are perfectly valid and frequently used in the literature (see, e.g., Breidenbach, J., McRoberts, R. E., \& Astrup, R. (2016). Empirical coverage of model-based variance estimators for remote sensing assisted estimation of stand-level timber volume. \textit{Remote Sensing of Environment}, 173, 274-281.; Ghosh, M., \& Kumar Sinha, B. (1990). On the consistency between model-and design-based estimators in survey sampling. \textit{Communications in Statistics-Theory and Methods}, 19(2), 689-702., Magnussen, S. (2015). Arguments for a model-dependent inference?. \textit{Forestry: An International Journal of Forest Research}, 88(3), 317-325, and many more. We thus think that it is justified to leave the terminology as is.)}

  % --------------------------- %

  % 08) ++++++++++++++++++++++++++ %
  \item \textit{Line 418-419: Is it real stratification of post-stratification by the ALS acquisition year?}

  \answerfin{We referred to using a categorical variable in a regression model in a classical model-dependent framework as 'stratification'. Using this model in a regression estimator is indeed referred to as 'post-stratification'. The entire paragraph which the reviewer refers to, however, exclusively deals with the model building part. In order to avoid misunderstandings, we rephrased the sentences and avoided the term 'stratification'.}

  % --------------------------- %

  % 09) ++++++++++++++++++++++++++ %
  \item \textit{Lines 435-442: Removing observation during the regression model process is perfectly valid, as long as the regression residuals are estimated on the full sample. Of course, the zero-mean residual property doesn’t hold anymore, which in turn restricts the use of some estimators. Please reformulate.}

  \answerfin{You are absolutely right. We rephrased the paragraph respectively.}

  % --------------------------- %

  % 10) ++++++++++++++++++++++++++ %
  \item \textit{Line 593-594: If the asymptotic argument is raised, then there is no need for small-area estimators, I would say, because the sample would sufficiently large to support a direct estimators.}

  \answerfin{We think the reviewer misunderstood the sentence. We here refer to the asymptotic equivalency of the two design-unbiased small area estimators PSMALL and EXTPSYNTH (firstly mentioned in Mandallaz, D.; Hill, A.; Massey, A. (2016) Design-based properties of some small-area estimators in forest inventory with two-phase sampling - revised version. \textit{Technical report}, Department of Environmental Systems Science, ETH Zurich, and empirically observed in our study).}

  % --------------------------- %

%  the extended model (extended by the indicator variable of the small area under consideration) is a mathematical trick to ensure zero mean residual over the small area, which enables to derive better variance estimates based on the g-weights estimates adapted from Sarndal’s work. The technical details and proofs are available in the references. In (Mandallaz D., Massey A., 2015, e-collection-. Regression and non-parametric estimators for two-phase forest inventories in the design-based Monte-Carlo approach, Appendix C) we also consider a model-calibration approach (according to Wu,C. and Sitter R., JASA (2001, pp.185-193) and translated the results into the Monte Carlo approach and found out that it is asymptotically equivalent to the two-phase regression estimator.

\end{enumerate}

%------------------------------------------------------------------------------------------------%
\end{document}

### 2018-08-06 Reviews/answer_to reviewer1.tex
update 06_08_2018
final version of published article

--- 2018-08-06 Reviews/answer_reviewers.tex
@@
 %------------------------------------------------------------------------------------------------%
-% ---------------------------------- Reviewer 2 ------------------------------------------------ %
-
-\section*{Reviewer 2:}
-
-General comment on publishing the article in Remote Sensing:
-
-We decided to hand in our article to be published in the \textit{Remote Sensing} special issue \textit{Remote sensing based Forest Inventories from Landscape to Global Scale}, since multiple of the mentioned topics for articles of the special issue are covered by our article (such as 'Application of remote-sensing techniques for monitoring forest attributes at the forest enterprise level', 'Application of remote-sensing techniques for monitoring forest attributes for national forest inventories', 'Large scale in-situ data requirement and sampling design for monitoring forest ecosystems with remote-sensing techniques').
-Additionally, of course, not all readers of \textit{Remote Sensing} are specialists in forest inventory, but most of the latter frequently read \textit{Remote Sensing}.
-
-\begin{enumerate}
-
-  % 01) ++++++++++++++++++++++++++ %
-  \item \textit{L28: “entire forest state area of Germany” I understand what you mean, but it may be misleading as readers might think about the area owned by the German state forest enterprise (Bundesforst).
-I would suggest to rephrase “forested area of Germany”.}
-
-  \answerfin{Has been changed accordingly.}
-  % --------------------------- %
-
-  % 02) ++++++++++++++++++++++++++ %
-  \item \textit{L29: 114'191 ha – A wrong unit was used here, its 114 191 km$^2$ (or 11 419 124 ha)..}
-
-  \answerfin{Has been corrected accordingly.}  
-  % --------------------------- %
-
-   % 03) ++++++++++++++++++++++++++ %
-  \item \textit{L36: “standwise forest inventories (SFI)”?}
-
-  \answerfin{Has been changed accordingly.}  
-  % --------------------------- %
-
-  % 04) ++++++++++++++++++++++++++ %
-  \item \textit{L38-41: Please add the information that the FDI of Lower-Saxony (Betriebsinventur, BI) is only done for forests owned by the state forest enterprise (Lower Saxony State Forests = Niedersächsische Landesforsten, NLF)}
-
-  \answerfin{The information has been added.}  
-  % --------------------------- %
-
-  % 05) ++++++++++++++++++++++++++ %
-  \item \textit{L41 As far as I remember, [4] is an article written in German.
-If so, please indicate in the reference list – it is annoying for readers to search for papers that turn out to be written in a language they possibly do not understand.}
-
-  \answerfin{We now give the original title in German.}  
-  % --------------------------- %
-
-  % 06) ++++++++++++++++++++++++++ %
-  \item \textit{L42: As far as I remember, v.Lüpke’s dissertation [5] is a cumulative work. If so, please cite the original articles and not the compilation.}
-
-  \answerfin{Has been changed accordingly.}  
-  % --------------------------- %
-
-  % 07) ++++++++++++++++++++++++++ %
-  \item \textit{L43: I would suggest to cite the classic textbooks of Cochran (1977) and de Vries (1986) beside the modern literature [6-9] }
-
-  \answerfin{The respective citations have been added.}  
-  % --------------------------- %
-
-  % 08) ++++++++++++++++++++++++++ %
-  \item \textit{L43-48: I would suggest to add some words (here or in the discussion) addressing the problems arising with multi-purpose forest inventories (e.g.
-Corona and Marchetti 2007): The stratification is optimized for a single target variable (in most cases the volume of the growing stock) and the introduction of additional target variables becomes challenging (e.g.
-Ritter and Saborowski, 2014).}
-
-  \answerfin{We think that the reviewer might mix up \textit{stratification} (where the sample sizes are optimized for strata \textit{prior} to the actual conduction of the inventory based on auxiliary data) with \textit{post-stratification} (where the categorical auxiliary data are used in the regression model \textit{after} the inventory has been conducted).
-The latter, which is the case applied in our article, does not impose any of the mentioned problems of multi-objective optimization.
-We thus think that including this topic does not fit well into our article since it is not affecting the methods that we are demonstrating.}
-
-%  \note{I don't think this issue concerns the work presented in our study, since optimization was not part of the study.
-One could mention the anticipated variance treated in the book of Mandallaz (2008).
-Multi-objective optimization would implies a weighting of the objectives, which is a highly political issue and probably unsolvable in my opinion.
-Separate investigation are probably simpler and better.
-Worth emphasizing that the method presented is valid for any response variable which can be used to define a local density.
-I also think that the reviewer exchanges stratification (where the sample sizes are optimized prior to the actual conduction of the inventory based on auxiliary data) and post-stratification (where the categorical auxiliary data are used in the regression model after the inventory has been conducted).
-The latter, which is the case applied in our article, does not impose any of the mentioned problems of multi-objective optimization.
-We thus think that including this topic does not fit well into our article since it is not affecting the methods we suggest.}
-  % --------------------------- %
-
-  % 09) ++++++++++++++++++++++++++ %
-  \item \textit{L46-47: Double-sample procedures have not only been used in the FDI of Lower Saxony, but also in the NFIs of Canada (Gillis et al., 2010) and Switzerland (Lanz et al.
-2010), and in different other inventories (e.g.
-Chojnacky, 1998 or  Gasparini et al., 2010).}
-
-  \answerfin{We rephrased the sentence and added the suggested references.}  
-  % --------------------------- %
-
-  % 10) ++++++++++++++++++++++++++ %
-  \item \textit{L99 “The German NFI (Bundeswaldinventur, BWI)“  I think, the abbreviation introduced in the next line becomes more meaningful when giving the German name here.}
-
-  \answerfin{Has been changed.}  
-  % --------------------------- %
-
-  % 11) ++++++++++++++++++++++++++ %
-  \item \textit{L100 “The third and most recent” }
-
-  \answerfin{Has been changed.}  
-  % --------------------------- %
-
-  % 12) ++++++++++++++++++++++++++ %
-  \item \textit{L101 '4x4km' I would prefer '4km ' 4km'}
-
-  \answerfin{We would like to stick to the given notation in accordance with our previously published article (Hill et.
-al 2018: Combining canopy height and tree species map information for large-scale timber volume estimations under strong heterogeneity of auxiliary data and variable sample plot sizes, \textit{European Journal of Forest Research}).}
-  % --------------------------- %
-
-  % 13) ++++++++++++++++++++++++++ %
-  \item \textit{L102 '2x2km' same as above (2km ' 2km)}
-
-  \answerfin{Same as above.}  
-  % --------------------------- %
-
-  % 14) ++++++++++++++++++++++++++ %
-  \item \textit{L107: A short explanation of the angle count sampling concept would be helpful for readers who aren't foresters, maybe here or in a corresponding appendix.}
-
-  \answerfin{We added an explanation of angle count sampling in Section 2.}  
-  % --------------------------- %
-
-  % 15) ++++++++++++++++++++++++++ %
-  \item \textit{L110/111 “DBH” and “DBH” Please decide whether or not to use italics.
-Please also add the information that this refers to a height of 1.3 m, Remote Sensing has a lot of readers who are not foresters.}
-
-  \answerfin{We added the information about the height.
-Concerning italics, we decided to use italics when first introducing a notation/term and use normal formatting when using the term afterwards.}
-  % --------------------------- %
-
-  % 17) ++++++++++++++++++++++++++ %
-  \item \textit{L196 Please also provide reference to the R software itself, and not only to the package. }
-
-  \answerfin{The reference has been added.}  
-  % --------------------------- %
-
-  % 18) ++++++++++++++++++++++++++ %
-  \item \textit{L273: I think this is the only occasion you use italics for "RLP".}
-
-  \answerfin{We use italics when introducing a term for the first time and use normal formatting when using the term afterwards.}  
-  % --------------------------- %
-
-  % 19) ++++++++++++++++++++++++++ %
-  \item \textit{L283: “communal forests” is most often used as a synonym for “community forests” in context of rural development policy.
-I think here it is rather an odd translation of the German word “Kommunalwald”.
-Maybe, “municipal forests” is the better translation.}
-
-  \answerfin{We changed 'communal' to 'municipal' throughout the entire article.}  
-  % --------------------------- %
-
-  % 20) ++++++++++++++++++++++++++ %
-  \item \textit{L295 "RLP" was already introduced as an abbreviation}
-
-  \answerfin{'RLP' has been deleted.}  
-  % --------------------------- %
-
-  % 21) ++++++++++++++++++++++++++ %
-  \item \textit{L287: Instead of “45 Forstämter (FA)” I would use “45 forest districts (Forstämter, FA)” }
-
-  \answerfin{Has been changed, and likewise for the Forstreviere which we now call sub-districts.}  
-  % --------------------------- %
-
-  % 22) ++++++++++++++++++++++++++ %
-  \item \textit{L289-290: If the SFI is conducted in a five year cycle, shouldn’t the management strategy be also set up for five years, instead of ten years?}
-
-  \answerfin{The cycle of the stand wise inventories actually varies between 5 and 10 years and can in some cases even exceed 10 years.
-The stand wise inventories and the date of their conduction are planned by the state forest service.
-The management strategy for the stands is, however, always made for the upcoming 10 years ('mittelfristige Planung').}
-  % --------------------------- %
-
-  % 23) ++++++++++++++++++++++++++ %
-  \item \textit{L295 "2x2km" (see above)}
-
-  \answerfin{We would like to keep the '2x2km' notation.}  
-  % --------------------------- %
-
-  % 24) ++++++++++++++++++++++++++ %
-  \item \textit{Figure 1: "communal forests" (see above)}
-
-  \answerfin{Has been corrected.}  
-  % --------------------------- %
-
-  % 25) ++++++++++++++++++++++++++ %
-  \item \textit{Table 1: Please remove the digits (or at least reduce the number of digits).
-Giving values with an “accuracy” of 1/100th of a mm (i.e.
-10 mm) for DBH, as an example, really does not make much sense.
-}
-
-  \answerfin{We limited the number of digits for timber volume, DBH and height to one digit and removed the digits for stem number.}  
-  % --------------------------- %
-
-  % 26) ++++++++++++++++++++++++++ %
-  \item \textit{Table 3: I think one digit for the percentage values should be enough.}
-
-  \answerfin{Has been changed accordingly.}  
-  % --------------------------- %
-
-  % 27) ++++++++++++++++++++++++++ %
-  \item \textit{Table 6: Please indicate for what variable point estimates are. I suppose it is volume of growing stock per area unit [m$^3$ha-1]? And again, check the number of digits.}
-
-  \answerfin{Yes! We added the missing information accordingly.}  
-  % --------------------------- %
-
- % 28) ++++++++++++++++++++++++++ %
-  \item \textit{L454-458 I understand your intention and the necessity of removing FR-units.
-However, when comparing the performance of the estimators you should use the same population for all estimators.
-Removing the "difficult" FR-units (i.e.
-those with a low sampling density) only for PSMALL and EXTPSYNTH is somewhat unfair against the other estimators, and may bias the results.
-So, my advice is to recalculate SRS and PSYNTH for the same 321 FRs that were used for PSMALL and EXTPSYNTH.
-Edit: I noticed you confined your analyses to those 321 FRs later on (Fig 5 and Tab.
-7), another reason to also do it here.}
-
-  \answerfin{We changed the evaluation according to your suggestion and added a sentence in the paragraph above the table.
-The descriptive summary statistics for the one-phase SRS and the PSYNTH estimator did only differ marginally, with exception of the maximal errors which logically turned out to be lower.
-We also adjusted the numbers given in Section 6.2 and the graphic of Figure 3 respectively.}
-
-  % --------------------------- %
-
- % 29) ++++++++++++++++++++++++++ %
-  \item \textit{L517: Please use the same scaling for both x- and y-axis on the left plot. It is irritating that the 1:1 line does not cross the grid-corners.}
-
-  \answerfin{Has been changed accordingly.}  
-  % --------------------------- %
-
-   % 30) ++++++++++++++++++++++++++ %
-  \item \textit{L655-656: "Northwest German Forest Research Institution" It should be "Institute" instead of "Institution"}
-
-  \answerfin{Has been corrected.}  
-  % --------------------------- %
-
-\end{enumerate}
-
-%------------------------------------------------------------------------------------------------%
-% ---------------------------------- Reviewer 3 ------------------------------------------------ %
-
-\section*{Reviewer 3:}
-
-\begin{enumerate}
-
-    % 01) ++++++++++++++++++++++++++ %
-  	\item \textit{Under the design-based inferential framework, invoking the asymptotical properties of a small-area estimator is a contradiction in terms; the asymptotic properties are based on large-sample assumptions, while SAE estimators are used when the sample size is (too) small.
-If the sample size for the entire population is very large, then the small-area estimation becomes a common domain estimation problem, and there is no need for tailored SA estimators because the direct estimators are probably the most efficient -  see Estevao and Särndal (2004) 'Borrowing strength is not the best technique within a wide class of design-consistent domain estimators.
-Journal of Official Statistics, 20, 645-669' for details.
-This is an important aspect that it’s been often ignored in the model-assisted SA studies.
-The authors put a great deal of effort in assessing the results by the realized sample sizes in various SAs, however, such comparisons have limited relevance if the asymptotic results cannot be invoked.
-This is not criticism, personally I do not have a solution, and there is probably no analytical solution to derive the small-sample properties of these estimators.
-However, I think that rising this issue would add value to the manuscript, by informing the readers of potential drawbacks of the estimation methods.}
-
-%  	\note{ the populations are domains (i.e.
-a continuum of infinitely many points) of the plane F, also known as the Monte Carlo approach: the objective is to estimate the integral $\int_{G} Y(x)dx$, $G \in F$ a function $Y(x)$ which is essentially the Horwitz-Thompson estimator for a response variable for the population of trees.
-This is the main difference with standard survey sampling.
-Another important difference is that instead of having a single large sample we have $n_2$ points $x$	each one with a sample of trees (terrestrial sample).
-The sample size $n_2$ can be large over the entire domain, but small over sub-domains, and too small to fit models using auxiliary data available at a much larger number of points $n_1$.
-You do not have to borrow strength if you are strong, which is obvious.
-We do not propose to fit models over extremely large areas with very different forest structures (say all Europe) but to rely on predictions based on remote sensing data to provide better estimates for smaller management units.
-Asymptotic results for the variances are, given the complexity of the problem, the only available ones.
-When are asymptotic results approximately valid?
-Take for instance n=6 (not a very large number), then the distribution of the mean of n=6 uniformly distributed random variables is practically undistinguishable from the normal distribution, so that in this case n=6 is the asymptotic validity range.
-On the other hand with extreme values statistics, n=100 can be far to small to reach a normal distribution.
-Some simulations performed on the artificial examples (see our articles published in the Canadian Journal of Forest Research - Source) and on a unique data set (Zurichberg data, see book of Mandallaz for examples) show that for SA problems, $n$ > 12 or even 6 is acceptable.
-All the variance estimates are based on the asumption of i.i.d uniformly distributed points (or clusters origins) for remote sensing for remote sensing followed by SRS selection for terrestrial observations, whereas in practice systematic grids are used.
-Simulation and past experience with alternative model-dependent Kriging procedure (Source) show that the variance estimates are usually to pessimistic.
-On the other hand, only sampling errors are taken into account and not measurement errors (e.g.
-on bole volume).}
-
-  	\answerfin{Asymptotic results for the variances are, given the complexity of the problem, the only available ones.
-When are asymptotic results approximately valid?
-If one takes for instance n=6 (not a very large number), then the distribution of the mean of n=6 uniformly distributed random variables is practically undistinguishable from the normal distribution, so that in this case n=6 is the asymptotic validity range.
-On the other hand with extreme values statistics, n=100 can be far to small to reach e.g.
-the Gumbel distribution.
-Transferring this to the case of forest inventory, it is actually impossible to define a minimal sample size that always ensures the validity of the central limit theorem for the particular case.
-However, simulations performed for an artificial example in Mandallaz et al.
-(2013).
-New regression estimators in forest inventories with two-phase sampling and partially exhaustive information: a design-based monte carlo approach with applications to small-area estimation.
-\textit{Canadian Journal of Forest Research}, 43(11), 1023-1031, suggested that for SA problems, a sample size in a small area of $n$ > 6 is acceptable to reach the nominal coverage rates of the confidence intervals.
-Whereas these simulations where performed for simple sampling, re-evaluating the simulation example recently confirmed the same results for cluster sampling.
-We added a respective remark in the discussion, Section 7.1, line 638-645.}
-
-    % 02) ++++++++++++++++++++++++++ %
-    \item \textit{The authors argue that some PSYNTH and the EXTPSYNTH estimators may not always be design-unbiased for the SAs that do not contain field sampling units.
-I assume that the authors are well aware that the sample sizes within the SAs are random variables.
-Under SAE there is always a risk that a some SAs will not be represented in a particular sample, but every SA will contain field observations under unconditional estimation over all possible samples, otherwise a coverage bias will occur.
-Thus, for statements such as 'The PSYNTH estimator thus has a potential unobservable design-based bias' (lines 228-229), the authors should clarify if they are considering the properties of the estimators conditioning on the realized sample, or unconditionally.
-One could also argue that, if the asymptotic arguments are	invoked (although they should probably not be), then the PSYNTH estimator is still design-consistent for SAs, even in the absence of field observations.
-See Firth and Bennett (1998) 'Robust models in probability sampling.
-Journal of the Royal Statistical Society, 60, 3-21'.}
-
-    \answerfin{It is, of course, conditioned on the realized sample. We added this information in the respective line 248/249.}
-
-    % 03) ++++++++++++++++++++++++++ %
-    \item \textit{Regarding the case study, I understand the motivation for using SAE at FR level, where the average number of field sampling units (clusters) is about 5 (0 to 13) per SA.
-However, using SAE at FA level - where the average sample size contains about 46 clusters (11 to 64)- has to be better justified because, least for some FAs, a direct estimator would have been more efficient (Estevao and Saerndal 2004).
-However, it is perfectly understandable that constructing domain specific (FA-level) models is a time consuming endeavor and simplifying the regression modeling is a pragmatic solution for statistical production, but a discussion on this topic should be provided to inform the readers of the possible choices.}
-
-    \answerfin{Thank you for this valuable hint!
-We added a discussion of this question in the discussion, Section 7.1., line 590-600.
-We point out that the main reason we did not consider direct estimation on the FA-level was the large number of parameters (39 coefficients for the full model, see also Hill et al.
-2018*) to be fitted for each FA-unit model due to the pronounced heterogeneity of the auxiliary data (multiple tree species and ALS acquisition years per FA-unit).
-In this case, the strategy to 'borrow strength' from the entire inventory domain was preferred to direct estimation in order to avoid overfitting and the implied risk of unstable global estimation.\\
-
-    * Hill, A., Buddenbaum, H., \& Mandallaz, D.
-(2018).
-Combining canopy height and tree species map information for large-scale timber volume estimations under strong heterogeneity of auxiliary data and variable sample plot sizes.
-\textit{European Journal of Forest Research}, 1-17.}
-
-%    \note{the situation is even more complicated because we treat a systematic sample (grid) as a random sample of uniformly distributed points (or cluster origins).
-Consequently all sample sizes (i.e.
-number of plots or cluster in the forest or sub-domains of it) clusters are random.
-Treating such a systematic sample as a random will as afore mentioned lead to an over-estimations of the the sampling variance.
-The resulting variances are conditional on the observed sample sizes.
-In model-assisted design-based inference models do not have to be true (as in model-dependent survey inference), they only have to be useful.
-In the external approach (asymptotically valid also for internal models) you must correct the estimator with the residuals.
-(PSMALL does that and EXTPSYNTH also but in a indirect way).
-It can happen, by chance, that	the PSYNTH is indeed closer to the truth (example in the book).
-%    	
-%    The crucial	point is to use remote sensing data and direct estimation (still using auxiliary information) can be unstable because of the large number of parameters in the prediction model.
-The synthetic estimator can be severely biased (take the model with only the intercept term, it is unbiased globally but not locally, unless the forest looks much the same everywhere, this has been confirmed by simulations with more complex model).
-In the model-dependent approach it can happen (we have such a case study ) that the synthetic estimator is closer to the known true value than all other estimates (included the sample mean of the observations in the small area).
-It is not clear what direct estimation mean: a model relying on auxiliary information built especially for the SA under consideration (which can be expected to be better than a global model, provided we have enough observations for model-building) or estimates based only on the sampled response variable in the SA.
-If you have unlimited resources it is clearly better.
-National forest inventory are time consuming and expensive and local management want this data to be useful for their own use, so that ideally that do not have to perform local inventories.}
-    % --------------------------- %
-
-    % 04) ++++++++++++++++++++++++++ %
-    \item \textit{Regarding the terminology used (especially) in Section 4, expressions like “design-based small area regression estimator” are not very accurate, since the same estimator (i.e., the same mathematical expression) can be used (appropriately or not) in different contexts.
-For instance, one could use the PSYNTH estimator (based on an internal model) as an external estimator for another population in a	model-dependent framework.
-Instead, I would rather use the formulation “design-based small area regression estimation”, to avoid confusions.}
-
-    \answerfin{When using the terms '...
-estimators' as titles in Section 4, they refer explicitly to the estimators which we decided to apply in our article.
-In accordance to the various articles published on the used estimators by Mandallaz (see selected references below), we would prefer to maintain the terminology as given in our article.
-Additionally, up to our knowledge the terms 'design-based estimator', 'model-based estimators' are also frequently used in the literature, e.g.:
-
-    	\begin{itemize}
-
-    		\item Mandallaz, D.
-(2013).
-A three-phase sampling extension of the generalized regression estimator with partially exhaustive information.
-\textit{Canadian Journal of Forest Research}, 44(4), 383-388.
-
-    		\item Mandallaz, D., Breschan, J., \& Hill, A.
-(2013).
-New regression estimators in forest inventories with two-phase sampling and partially exhaustive information: a design-based monte carlo approach with applications to small-area estimation.
-\textit{Canadian Journal of Forest Research}, 43(11), 1023-1031.
-
-    		\item Massey, A., \& Mandallaz, D.
-(2015).
-Comparison of classical, kernel-based, and nearest neighbors regression estimators using the design-based Monte Carlo approach for two-phase forest inventories.
-\textit{Canadian Journal of Forest Research}, 45(11), 1480-1488.
-
-    		\item Breidenbach, J., McRoberts, R.
-E., \& Astrup, R.
-(2016).
-Empirical coverage of model-based variance estimators for remote sensing assisted estimation of stand-level timber volume.
-\textit{Remote Sensing of Environment}, 173, 274-281
-
-    		\item Ghosh, M., \& Kumar Sinha, B.
-(1990).
-On the consistency between model-and design-based estimators in survey sampling.
-\textit{Communications in Statistics-Theory and Methods}, 19(2), 689-702
-
-    		\item Magnussen, S. (2015). Arguments for a model-dependent inference?. \textit{Forestry: An International Journal of Forest Research}, 88(3), 317-325
-
-    	\end{itemize}
-
-    and many more.}
-
-    % --------------------------- %
-
-    % 05) ++++++++++++++++++++++++++ %
-   \item \textit{Please elaborate on the importance of the zero-mean residual property (lines 191-192).
-This is an important issue that can be tracked down to the definition of the internally bias-calibrated models in Firth and Bennett (1998) “Robust models in probability sampling.
-Journal of the Royal Statistical Society, 60, 3-21”.
-}
-
-   \answerfin{We rephrased this part.
-We added some sentences to emphasize the difference between the OLS residuals being zero on average (this is of course the case for any OLS fitted model) and the consequence for the theoretical residuals in the inventory domain $F$ if they model is fitted internally (then, we have the \textit{zero mean residual property} according to the works of Mandallaz).
-We also mention the importance of this property for deriving the g-weight variance in the framework of small area estimation, a technique that was introduced by Mandallaz in 2012/2013.
-In case a reader is interested in more mathematical details, we give the respective references.
-We would like to emphasize that the objective of our article was to illustrate the application of the already extensively mathematically described estimators by Mandallaz to large inventory areas and investigate their suitability for future operational use in NFIs.
-Consequently, the article explicitly targets at an audience of practitioners.
-For this reason, we strongly believe that discussing more mathematical details which have already been given in various peer-reviewed articles in the Canadian Journal of forest research and technical reports (references given in the article) is beyond the scope of the article's objective.}
-
-   % --------------------------- %
-
-   % 06) ++++++++++++++++++++++++++ %
-   \item \textit{Line 231-232: See the general comments with regard to design-unbiasedness.}
-
-   \answerfin{We added that it is conditional on the realized sample.}
-  % --------------------------- %
-
-  % 07) ++++++++++++++++++++++++++ %
-  \item \textit{Line 233: The PSYNTH estimator is not design-based, the estimation is design based.}
-
-  \answerfin{Has been changed respectively.}
-
-%  \answerfin{The PSYNTH estimator as well as its estimations are design-based.
-To our knowledge, the terms 'design-based estimator', 'model-based estimators' are perfectly valid and frequently used in the literature (see, e.g., Breidenbach, J., McRoberts, R.
-E., \& Astrup, R.
-(2016).
-Empirical coverage of model-based variance estimators for remote sensing assisted estimation of stand-level timber volume.
-\textit{Remote Sensing of Environment}, 173, 274-281.; Ghosh, M., \& Kumar Sinha, B.
-(1990).
-On the consistency between model-and design-based estimators in survey sampling.
-\textit{Communications in Statistics-Theory and Methods}, 19(2), 689-702., Magnussen, S.
-(2015).
-Arguments for a model-dependent inference?.
-\textit{Forestry: An International Journal of Forest Research}, 88(3), 317-325, and many more.
-We thus think that it is justified to leave the terminology as is.)}
-
-  % --------------------------- %
-
-  % 08) ++++++++++++++++++++++++++ %
-  \item \textit{Line 418-419: Is it real stratification of post-stratification by the ALS acquisition year?}
-
-  \answerfin{We referred to using a categorical variable in a regression model in a classical model-dependent framework as 'stratification'.
-Using this model in a regression estimator is indeed referred to as 'post-stratification'.
-The entire paragraph which the reviewer refers to, however, exclusively deals with the model building part.
-In order to avoid misunderstandings, we rephrased the sentences and avoided the term 'stratification'.}
-
-  % --------------------------- %
-
-  % 09) ++++++++++++++++++++++++++ %
-  \item \textit{Lines 435-442: Removing observation during the regression model process is perfectly valid, as long as the regression residuals are estimated on the full sample.
-Of course, the zero-mean residual property doesn’t hold anymore, which in turn restricts the use of some estimators.
-Please reformulate.}
-
-  \answerfin{You are absolutely right. We rephrased the paragraph respectively.}
-
-  % --------------------------- %
-
-  % 10) ++++++++++++++++++++++++++ %
-  \item \textit{Line 593-594: If the asymptotic argument is raised, then there is no need for small-area estimators, I would say, because the sample would sufficiently large to support a direct estimators.}
-
-  \answerfin{We think the reviewer misunderstood the sentence.
-We here refer to the asymptotic equivalency of the two design-unbiased small area estimators PSMALL and EXTPSYNTH (firstly mentioned in Mandallaz, D.; Hill, A.; Massey, A.
-(2016) Design-based properties of some small-area estimators in forest inventory with two-phase sampling - revised version.
-\textit{Technical report}, Department of Environmental Systems Science, ETH Zurich, and empirically observed in our study).}
-
-  % --------------------------- %
-
-%  the extended model (extended by the indicator variable of the small area under consideration) is a mathematical trick to ensure zero mean residual over the small area, which enables to derive better variance estimates based on the g-weights estimates adapted from Sarndal’s work.
-The technical details and proofs are available in the references.
-In (Mandallaz D., Massey A., 2015, e-collection-.
-Regression and non-parametric estimators for two-phase forest inventories in the design-based Monte-Carlo approach, Appendix C) we also consider a model-calibration approach (according to Wu,C.
-and Sitter R., JASA (2001, pp.185-193) and translated the results into the Monte Carlo approach and found out that it is asymptotically equivalent to the two-phase regression estimator.
-
-\end{enumerate}
-
-%------------------------------------------------------------------------------------------------%
 \end{document}

### 2018-08-06 Reviews/answer_to reviewer2.tex
update 06_08_2018
final version of published article

--- 2018-08-06 Reviews/answer_reviewers.tex
@@
 %------------------------------------------------------------------------------------------------%
-% ---------------------------------- Reviewer 1 ------------------------------------------------ %
-
-\section*{Reviewer 1:}
-
-I have only a single marginal question, and probably I am wrong: $Z_{c}(x)$ is introduced as a row vector in line 183 and Eqs.
-9a and 9b, but it is used as column vector in Eqs.
-12, 13 and 14.
-I would appreciate much if the authors could check whether this inconsistency really exists with respect to notation of $Z_{c}(x)$.\\
-
-Answer:\\
-
-\answerfin{Vectors are always column vectors, i.e $Z(x)$ and $Z_{c}(x)$ are column vectors.	When they are used for predictions they have to be transposed in order to get a scalar product written as a matrix multiplication, i.e.
-$\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2}$.
-We added the information that $Z_{c}(x)$ is a column vector in line 183 to make this more clear for the reader.}
-
-%------------------------------------------------------------------------------------------------%
 % ---------------------------------- Reviewer 2 ------------------------------------------------ %
@@
 We decided to hand in our article to be published in the \textit{Remote Sensing} special issue \textit{Remote sensing based Forest Inventories from Landscape to Global Scale}, since multiple of the mentioned topics for articles of the special issue are covered by our article (such as 'Application of remote-sensing techniques for monitoring forest attributes at the forest enterprise level', 'Application of remote-sensing techniques for monitoring forest attributes for national forest inventories', 'Large scale in-situ data requirement and sampling design for monitoring forest ecosystems with remote-sensing techniques').
-Additionally, of course, not all readers of \textit{Remote Sensing} are specialists in forest inventory, but most of the latter frequently read \textit{Remote Sensing}.
 
@@
 %------------------------------------------------------------------------------------------------%
-% ---------------------------------- Reviewer 3 ------------------------------------------------ %
-
-\section*{Reviewer 3:}
-
-\begin{enumerate}
-
-    % 01) ++++++++++++++++++++++++++ %
-  	\item \textit{Under the design-based inferential framework, invoking the asymptotical properties of a small-area estimator is a contradiction in terms; the asymptotic properties are based on large-sample assumptions, while SAE estimators are used when the sample size is (too) small.
-If the sample size for the entire population is very large, then the small-area estimation becomes a common domain estimation problem, and there is no need for tailored SA estimators because the direct estimators are probably the most efficient -  see Estevao and Särndal (2004) 'Borrowing strength is not the best technique within a wide class of design-consistent domain estimators.
-Journal of Official Statistics, 20, 645-669' for details.
-This is an important aspect that it’s been often ignored in the model-assisted SA studies.
-The authors put a great deal of effort in assessing the results by the realized sample sizes in various SAs, however, such comparisons have limited relevance if the asymptotic results cannot be invoked.
-This is not criticism, personally I do not have a solution, and there is probably no analytical solution to derive the small-sample properties of these estimators.
-However, I think that rising this issue would add value to the manuscript, by informing the readers of potential drawbacks of the estimation methods.}
-
-%  	\note{ the populations are domains (i.e.
-a continuum of infinitely many points) of the plane F, also known as the Monte Carlo approach: the objective is to estimate the integral $\int_{G} Y(x)dx$, $G \in F$ a function $Y(x)$ which is essentially the Horwitz-Thompson estimator for a response variable for the population of trees.
-This is the main difference with standard survey sampling.
-Another important difference is that instead of having a single large sample we have $n_2$ points $x$	each one with a sample of trees (terrestrial sample).
-The sample size $n_2$ can be large over the entire domain, but small over sub-domains, and too small to fit models using auxiliary data available at a much larger number of points $n_1$.
-You do not have to borrow strength if you are strong, which is obvious.
-We do not propose to fit models over extremely large areas with very different forest structures (say all Europe) but to rely on predictions based on remote sensing data to provide better estimates for smaller management units.
-Asymptotic results for the variances are, given the complexity of the problem, the only available ones.
-When are asymptotic results approximately valid?
-Take for instance n=6 (not a very large number), then the distribution of the mean of n=6 uniformly distributed random variables is practically undistinguishable from the normal distribution, so that in this case n=6 is the asymptotic validity range.
-On the other hand with extreme values statistics, n=100 can be far to small to reach a normal distribution.
-Some simulations performed on the artificial examples (see our articles published in the Canadian Journal of Forest Research - Source) and on a unique data set (Zurichberg data, see book of Mandallaz for examples) show that for SA problems, $n$ > 12 or even 6 is acceptable.
-All the variance estimates are based on the asumption of i.i.d uniformly distributed points (or clusters origins) for remote sensing for remote sensing followed by SRS selection for terrestrial observations, whereas in practice systematic grids are used.
-Simulation and past experience with alternative model-dependent Kriging procedure (Source) show that the variance estimates are usually to pessimistic.
-On the other hand, only sampling errors are taken into account and not measurement errors (e.g.
-on bole volume).}
-
-  	\answerfin{Asymptotic results for the variances are, given the complexity of the problem, the only available ones.
-When are asymptotic results approximately valid?
-If one takes for instance n=6 (not a very large number), then the distribution of the mean of n=6 uniformly distributed random variables is practically undistinguishable from the normal distribution, so that in this case n=6 is the asymptotic validity range.
-On the other hand with extreme values statistics, n=100 can be far to small to reach e.g.
-the Gumbel distribution.
-Transferring this to the case of forest inventory, it is actually impossible to define a minimal sample size that always ensures the validity of the central limit theorem for the particular case.
-However, simulations performed for an artificial example in Mandallaz et al.
-(2013).
-New regression estimators in forest inventories with two-phase sampling and partially exhaustive information: a design-based monte carlo approach with applications to small-area estimation.
-\textit{Canadian Journal of Forest Research}, 43(11), 1023-1031, suggested that for SA problems, a sample size in a small area of $n$ > 6 is acceptable to reach the nominal coverage rates of the confidence intervals.
-Whereas these simulations where performed for simple sampling, re-evaluating the simulation example recently confirmed the same results for cluster sampling.
-We added a respective remark in the discussion, Section 7.1, line 638-645.}
-
-    % 02) ++++++++++++++++++++++++++ %
-    \item \textit{The authors argue that some PSYNTH and the EXTPSYNTH estimators may not always be design-unbiased for the SAs that do not contain field sampling units.
-I assume that the authors are well aware that the sample sizes within the SAs are random variables.
-Under SAE there is always a risk that a some SAs will not be represented in a particular sample, but every SA will contain field observations under unconditional estimation over all possible samples, otherwise a coverage bias will occur.
-Thus, for statements such as 'The PSYNTH estimator thus has a potential unobservable design-based bias' (lines 228-229), the authors should clarify if they are considering the properties of the estimators conditioning on the realized sample, or unconditionally.
-One could also argue that, if the asymptotic arguments are	invoked (although they should probably not be), then the PSYNTH estimator is still design-consistent for SAs, even in the absence of field observations.
-See Firth and Bennett (1998) 'Robust models in probability sampling.
-Journal of the Royal Statistical Society, 60, 3-21'.}
-
-    \answerfin{It is, of course, conditioned on the realized sample. We added this information in the respective line 248/249.}
-
-    % 03) ++++++++++++++++++++++++++ %
-    \item \textit{Regarding the case study, I understand the motivation for using SAE at FR level, where the average number of field sampling units (clusters) is about 5 (0 to 13) per SA.
-However, using SAE at FA level - where the average sample size contains about 46 clusters (11 to 64)- has to be better justified because, least for some FAs, a direct estimator would have been more efficient (Estevao and Saerndal 2004).
-However, it is perfectly understandable that constructing domain specific (FA-level) models is a time consuming endeavor and simplifying the regression modeling is a pragmatic solution for statistical production, but a discussion on this topic should be provided to inform the readers of the possible choices.}
-
-    \answerfin{Thank you for this valuable hint!
-We added a discussion of this question in the discussion, Section 7.1., line 590-600.
-We point out that the main reason we did not consider direct estimation on the FA-level was the large number of parameters (39 coefficients for the full model, see also Hill et al.
-2018*) to be fitted for each FA-unit model due to the pronounced heterogeneity of the auxiliary data (multiple tree species and ALS acquisition years per FA-unit).
-In this case, the strategy to 'borrow strength' from the entire inventory domain was preferred to direct estimation in order to avoid overfitting and the implied risk of unstable global estimation.\\
-
-    * Hill, A., Buddenbaum, H., \& Mandallaz, D.
-(2018).
-Combining canopy height and tree species map information for large-scale timber volume estimations under strong heterogeneity of auxiliary data and variable sample plot sizes.
-\textit{European Journal of Forest Research}, 1-17.}
-
-%    \note{the situation is even more complicated because we treat a systematic sample (grid) as a random sample of uniformly distributed points (or cluster origins).
-Consequently all sample sizes (i.e.
-number of plots or cluster in the forest or sub-domains of it) clusters are random.
-Treating such a systematic sample as a random will as afore mentioned lead to an over-estimations of the the sampling variance.
-The resulting variances are conditional on the observed sample sizes.
-In model-assisted design-based inference models do not have to be true (as in model-dependent survey inference), they only have to be useful.
-In the external approach (asymptotically valid also for internal models) you must correct the estimator with the residuals.
-(PSMALL does that and EXTPSYNTH also but in a indirect way).
-It can happen, by chance, that	the PSYNTH is indeed closer to the truth (example in the book).
-%    	
-%    The crucial	point is to use remote sensing data and direct estimation (still using auxiliary information) can be unstable because of the large number of parameters in the prediction model.
-The synthetic estimator can be severely biased (take the model with only the intercept term, it is unbiased globally but not locally, unless the forest looks much the same everywhere, this has been confirmed by simulations with more complex model).
-In the model-dependent approach it can happen (we have such a case study ) that the synthetic estimator is closer to the known true value than all other estimates (included the sample mean of the observations in the small area).
-It is not clear what direct estimation mean: a model relying on auxiliary information built especially for the SA under consideration (which can be expected to be better than a global model, provided we have enough observations for model-building) or estimates based only on the sampled response variable in the SA.
-If you have unlimited resources it is clearly better.
-National forest inventory are time consuming and expensive and local management want this data to be useful for their own use, so that ideally that do not have to perform local inventories.}
-    % --------------------------- %
-
-    % 04) ++++++++++++++++++++++++++ %
-    \item \textit{Regarding the terminology used (especially) in Section 4, expressions like “design-based small area regression estimator” are not very accurate, since the same estimator (i.e., the same mathematical expression) can be used (appropriately or not) in different contexts.
-For instance, one could use the PSYNTH estimator (based on an internal model) as an external estimator for another population in a	model-dependent framework.
-Instead, I would rather use the formulation “design-based small area regression estimation”, to avoid confusions.}
-
-    \answerfin{When using the terms '...
-estimators' as titles in Section 4, they refer explicitly to the estimators which we decided to apply in our article.
-In accordance to the various articles published on the used estimators by Mandallaz (see selected references below), we would prefer to maintain the terminology as given in our article.
-Additionally, up to our knowledge the terms 'design-based estimator', 'model-based estimators' are also frequently used in the literature, e.g.:
-
-    	\begin{itemize}
-
-    		\item Mandallaz, D.
-(2013).
-A three-phase sampling extension of the generalized regression estimator with partially exhaustive information.
-\textit{Canadian Journal of Forest Research}, 44(4), 383-388.
-
-    		\item Mandallaz, D., Breschan, J., \& Hill, A.
-(2013).
-New regression estimators in forest inventories with two-phase sampling and partially exhaustive information: a design-based monte carlo approach with applications to small-area estimation.
-\textit{Canadian Journal of Forest Research}, 43(11), 1023-1031.
-
-    		\item Massey, A., \& Mandallaz, D.
-(2015).
-Comparison of classical, kernel-based, and nearest neighbors regression estimators using the design-based Monte Carlo approach for two-phase forest inventories.
-\textit{Canadian Journal of Forest Research}, 45(11), 1480-1488.
-
-    		\item Breidenbach, J., McRoberts, R.
-E., \& Astrup, R.
-(2016).
-Empirical coverage of model-based variance estimators for remote sensing assisted estimation of stand-level timber volume.
-\textit{Remote Sensing of Environment}, 173, 274-281
-
-    		\item Ghosh, M., \& Kumar Sinha, B.
-(1990).
-On the consistency between model-and design-based estimators in survey sampling.
-\textit{Communications in Statistics-Theory and Methods}, 19(2), 689-702
-
-    		\item Magnussen, S. (2015). Arguments for a model-dependent inference?. \textit{Forestry: An International Journal of Forest Research}, 88(3), 317-325
-
-    	\end{itemize}
-
-    and many more.}
-
-    % --------------------------- %
-
-    % 05) ++++++++++++++++++++++++++ %
-   \item \textit{Please elaborate on the importance of the zero-mean residual property (lines 191-192).
-This is an important issue that can be tracked down to the definition of the internally bias-calibrated models in Firth and Bennett (1998) “Robust models in probability sampling.
-Journal of the Royal Statistical Society, 60, 3-21”.
-}
-
-   \answerfin{We rephrased this part.
-We added some sentences to emphasize the difference between the OLS residuals being zero on average (this is of course the case for any OLS fitted model) and the consequence for the theoretical residuals in the inventory domain $F$ if they model is fitted internally (then, we have the \textit{zero mean residual property} according to the works of Mandallaz).
-We also mention the importance of this property for deriving the g-weight variance in the framework of small area estimation, a technique that was introduced by Mandallaz in 2012/2013.
-In case a reader is interested in more mathematical details, we give the respective references.
-We would like to emphasize that the objective of our article was to illustrate the application of the already extensively mathematically described estimators by Mandallaz to large inventory areas and investigate their suitability for future operational use in NFIs.
-Consequently, the article explicitly targets at an audience of practitioners.
-For this reason, we strongly believe that discussing more mathematical details which have already been given in various peer-reviewed articles in the Canadian Journal of forest research and technical reports (references given in the article) is beyond the scope of the article's objective.}
-
-   % --------------------------- %
-
-   % 06) ++++++++++++++++++++++++++ %
-   \item \textit{Line 231-232: See the general comments with regard to design-unbiasedness.}
-
-   \answerfin{We added that it is conditional on the realized sample.}
-  % --------------------------- %
-
-  % 07) ++++++++++++++++++++++++++ %
-  \item \textit{Line 233: The PSYNTH estimator is not design-based, the estimation is design based.}
-
-  \answerfin{Has been changed respectively.}
-
-%  \answerfin{The PSYNTH estimator as well as its estimations are design-based.
-To our knowledge, the terms 'design-based estimator', 'model-based estimators' are perfectly valid and frequently used in the literature (see, e.g., Breidenbach, J., McRoberts, R.
-E., \& Astrup, R.
-(2016).
-Empirical coverage of model-based variance estimators for remote sensing assisted estimation of stand-level timber volume.
-\textit{Remote Sensing of Environment}, 173, 274-281.; Ghosh, M., \& Kumar Sinha, B.
-(1990).
-On the consistency between model-and design-based estimators in survey sampling.
-\textit{Communications in Statistics-Theory and Methods}, 19(2), 689-702., Magnussen, S.
-(2015).
-Arguments for a model-dependent inference?.
-\textit{Forestry: An International Journal of Forest Research}, 88(3), 317-325, and many more.
-We thus think that it is justified to leave the terminology as is.)}
-
-  % --------------------------- %
-
-  % 08) ++++++++++++++++++++++++++ %
-  \item \textit{Line 418-419: Is it real stratification of post-stratification by the ALS acquisition year?}
-
-  \answerfin{We referred to using a categorical variable in a regression model in a classical model-dependent framework as 'stratification'.
-Using this model in a regression estimator is indeed referred to as 'post-stratification'.
-The entire paragraph which the reviewer refers to, however, exclusively deals with the model building part.
-In order to avoid misunderstandings, we rephrased the sentences and avoided the term 'stratification'.}
-
-  % --------------------------- %
-
-  % 09) ++++++++++++++++++++++++++ %
-  \item \textit{Lines 435-442: Removing observation during the regression model process is perfectly valid, as long as the regression residuals are estimated on the full sample.
-Of course, the zero-mean residual property doesn’t hold anymore, which in turn restricts the use of some estimators.
-Please reformulate.}
-
-  \answerfin{You are absolutely right. We rephrased the paragraph respectively.}
-
-  % --------------------------- %
-
-  % 10) ++++++++++++++++++++++++++ %
-  \item \textit{Line 593-594: If the asymptotic argument is raised, then there is no need for small-area estimators, I would say, because the sample would sufficiently large to support a direct estimators.}
-
-  \answerfin{We think the reviewer misunderstood the sentence.
-We here refer to the asymptotic equivalency of the two design-unbiased small area estimators PSMALL and EXTPSYNTH (firstly mentioned in Mandallaz, D.; Hill, A.; Massey, A.
-(2016) Design-based properties of some small-area estimators in forest inventory with two-phase sampling - revised version.
-\textit{Technical report}, Department of Environmental Systems Science, ETH Zurich, and empirically observed in our study).}
-
-  % --------------------------- %
-
-%  the extended model (extended by the indicator variable of the small area under consideration) is a mathematical trick to ensure zero mean residual over the small area, which enables to derive better variance estimates based on the g-weights estimates adapted from Sarndal’s work.
-The technical details and proofs are available in the references.
-In (Mandallaz D., Massey A., 2015, e-collection-.
-Regression and non-parametric estimators for two-phase forest inventories in the design-based Monte-Carlo approach, Appendix C) we also consider a model-calibration approach (according to Wu,C.
-and Sitter R., JASA (2001, pp.185-193) and translated the results into the Monte Carlo approach and found out that it is asymptotically equivalent to the two-phase regression estimator.
-
-\end{enumerate}
-
-%------------------------------------------------------------------------------------------------%
 \end{document}

### 2018-08-06 Reviews/answer_to reviewer3.tex
update 06_08_2018
final version of published article

--- 2018-08-06 Reviews/answer_reviewers.tex
@@
 \newcommand{\answerfin}[1]{\small \color{mygreen}{#1} \color{black}}
-
-%------------------------------------------------------------------------------------------------%
-% ---------------------------------- Reviewer 1 ------------------------------------------------ %
-
-\section*{Reviewer 1:}
-
-I have only a single marginal question, and probably I am wrong: $Z_{c}(x)$ is introduced as a row vector in line 183 and Eqs.
-9a and 9b, but it is used as column vector in Eqs.
-12, 13 and 14.
-I would appreciate much if the authors could check whether this inconsistency really exists with respect to notation of $Z_{c}(x)$.\\
-
-Answer:\\
-
-\answerfin{Vectors are always column vectors, i.e $Z(x)$ and $Z_{c}(x)$ are column vectors.	When they are used for predictions they have to be transposed in order to get a scalar product written as a matrix multiplication, i.e.
-$\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2}$.
-We added the information that $Z_{c}(x)$ is a column vector in line 183 to make this more clear for the reader.}
-
-%------------------------------------------------------------------------------------------------%
-% ---------------------------------- Reviewer 2 ------------------------------------------------ %
-
-\section*{Reviewer 2:}
-
-General comment on publishing the article in Remote Sensing:
-
-We decided to hand in our article to be published in the \textit{Remote Sensing} special issue \textit{Remote sensing based Forest Inventories from Landscape to Global Scale}, since multiple of the mentioned topics for articles of the special issue are covered by our article (such as 'Application of remote-sensing techniques for monitoring forest attributes at the forest enterprise level', 'Application of remote-sensing techniques for monitoring forest attributes for national forest inventories', 'Large scale in-situ data requirement and sampling design for monitoring forest ecosystems with remote-sensing techniques').
-Additionally, of course, not all readers of \textit{Remote Sensing} are specialists in forest inventory, but most of the latter frequently read \textit{Remote Sensing}.
-
-\begin{enumerate}
-
-  % 01) ++++++++++++++++++++++++++ %
-  \item \textit{L28: “entire forest state area of Germany” I understand what you mean, but it may be misleading as readers might think about the area owned by the German state forest enterprise (Bundesforst).
-I would suggest to rephrase “forested area of Germany”.}
-
-  \answerfin{Has been changed accordingly.}
-  % --------------------------- %
-
-  % 02) ++++++++++++++++++++++++++ %
-  \item \textit{L29: 114'191 ha – A wrong unit was used here, its 114 191 km$^2$ (or 11 419 124 ha)..}
-
-  \answerfin{Has been corrected accordingly.}  
-  % --------------------------- %
-
-   % 03) ++++++++++++++++++++++++++ %
-  \item \textit{L36: “standwise forest inventories (SFI)”?}
-
-  \answerfin{Has been changed accordingly.}  
-  % --------------------------- %
-
-  % 04) ++++++++++++++++++++++++++ %
-  \item \textit{L38-41: Please add the information that the FDI of Lower-Saxony (Betriebsinventur, BI) is only done for forests owned by the state forest enterprise (Lower Saxony State Forests = Niedersächsische Landesforsten, NLF)}
-
-  \answerfin{The information has been added.}  
-  % --------------------------- %
-
-  % 05) ++++++++++++++++++++++++++ %
-  \item \textit{L41 As far as I remember, [4] is an article written in German.
-If so, please indicate in the reference list – it is annoying for readers to search for papers that turn out to be written in a language they possibly do not understand.}
-
-  \answerfin{We now give the original title in German.}  
-  % --------------------------- %
-
-  % 06) ++++++++++++++++++++++++++ %
-  \item \textit{L42: As far as I remember, v.Lüpke’s dissertation [5] is a cumulative work. If so, please cite the original articles and not the compilation.}
-
-  \answerfin{Has been changed accordingly.}  
-  % --------------------------- %
-
-  % 07) ++++++++++++++++++++++++++ %
-  \item \textit{L43: I would suggest to cite the classic textbooks of Cochran (1977) and de Vries (1986) beside the modern literature [6-9] }
-
-  \answerfin{The respective citations have been added.}  
-  % --------------------------- %
-
-  % 08) ++++++++++++++++++++++++++ %
-  \item \textit{L43-48: I would suggest to add some words (here or in the discussion) addressing the problems arising with multi-purpose forest inventories (e.g.
-Corona and Marchetti 2007): The stratification is optimized for a single target variable (in most cases the volume of the growing stock) and the introduction of additional target variables becomes challenging (e.g.
-Ritter and Saborowski, 2014).}
-
-  \answerfin{We think that the reviewer might mix up \textit{stratification} (where the sample sizes are optimized for strata \textit{prior} to the actual conduction of the inventory based on auxiliary data) with \textit{post-stratification} (where the categorical auxiliary data are used in the regression model \textit{after} the inventory has been conducted).
-The latter, which is the case applied in our article, does not impose any of the mentioned problems of multi-objective optimization.
-We thus think that including this topic does not fit well into our article since it is not affecting the methods that we are demonstrating.}
-
-%  \note{I don't think this issue concerns the work presented in our study, since optimization was not part of the study.
-One could mention the anticipated variance treated in the book of Mandallaz (2008).
-Multi-objective optimization would implies a weighting of the objectives, which is a highly political issue and probably unsolvable in my opinion.
-Separate investigation are probably simpler and better.
-Worth emphasizing that the method presented is valid for any response variable which can be used to define a local density.
-I also think that the reviewer exchanges stratification (where the sample sizes are optimized prior to the actual conduction of the inventory based on auxiliary data) and post-stratification (where the categorical auxiliary data are used in the regression model after the inventory has been conducted).
-The latter, which is the case applied in our article, does not impose any of the mentioned problems of multi-objective optimization.
-We thus think that including this topic does not fit well into our article since it is not affecting the methods we suggest.}
-  % --------------------------- %
-
-  % 09) ++++++++++++++++++++++++++ %
-  \item \textit{L46-47: Double-sample procedures have not only been used in the FDI of Lower Saxony, but also in the NFIs of Canada (Gillis et al., 2010) and Switzerland (Lanz et al.
-2010), and in different other inventories (e.g.
-Chojnacky, 1998 or  Gasparini et al., 2010).}
-
-  \answerfin{We rephrased the sentence and added the suggested references.}  
-  % --------------------------- %
-
-  % 10) ++++++++++++++++++++++++++ %
-  \item \textit{L99 “The German NFI (Bundeswaldinventur, BWI)“  I think, the abbreviation introduced in the next line becomes more meaningful when giving the German name here.}
-
-  \answerfin{Has been changed.}  
-  % --------------------------- %
-
-  % 11) ++++++++++++++++++++++++++ %
-  \item \textit{L100 “The third and most recent” }
-
-  \answerfin{Has been changed.}  
-  % --------------------------- %
-
-  % 12) ++++++++++++++++++++++++++ %
-  \item \textit{L101 '4x4km' I would prefer '4km ' 4km'}
-
-  \answerfin{We would like to stick to the given notation in accordance with our previously published article (Hill et.
-al 2018: Combining canopy height and tree species map information for large-scale timber volume estimations under strong heterogeneity of auxiliary data and variable sample plot sizes, \textit{European Journal of Forest Research}).}
-  % --------------------------- %
-
-  % 13) ++++++++++++++++++++++++++ %
-  \item \textit{L102 '2x2km' same as above (2km ' 2km)}
-
-  \answerfin{Same as above.}  
-  % --------------------------- %
-
-  % 14) ++++++++++++++++++++++++++ %
-  \item \textit{L107: A short explanation of the angle count sampling concept would be helpful for readers who aren't foresters, maybe here or in a corresponding appendix.}
-
-  \answerfin{We added an explanation of angle count sampling in Section 2.}  
-  % --------------------------- %
-
-  % 15) ++++++++++++++++++++++++++ %
-  \item \textit{L110/111 “DBH” and “DBH” Please decide whether or not to use italics.
-Please also add the information that this refers to a height of 1.3 m, Remote Sensing has a lot of readers who are not foresters.}
-
-  \answerfin{We added the information about the height.
-Concerning italics, we decided to use italics when first introducing a notation/term and use normal formatting when using the term afterwards.}
-  % --------------------------- %
-
-  % 17) ++++++++++++++++++++++++++ %
-  \item \textit{L196 Please also provide reference to the R software itself, and not only to the package. }
-
-  \answerfin{The reference has been added.}  
-  % --------------------------- %
-
-  % 18) ++++++++++++++++++++++++++ %
-  \item \textit{L273: I think this is the only occasion you use italics for "RLP".}
-
-  \answerfin{We use italics when introducing a term for the first time and use normal formatting when using the term afterwards.}  
-  % --------------------------- %
-
-  % 19) ++++++++++++++++++++++++++ %
-  \item \textit{L283: “communal forests” is most often used as a synonym for “community forests” in context of rural development policy.
-I think here it is rather an odd translation of the German word “Kommunalwald”.
-Maybe, “municipal forests” is the better translation.}
-
-  \answerfin{We changed 'communal' to 'municipal' throughout the entire article.}  
-  % --------------------------- %
-
-  % 20) ++++++++++++++++++++++++++ %
-  \item \textit{L295 "RLP" was already introduced as an abbreviation}
-
-  \answerfin{'RLP' has been deleted.}  
-  % --------------------------- %
-
-  % 21) ++++++++++++++++++++++++++ %
-  \item \textit{L287: Instead of “45 Forstämter (FA)” I would use “45 forest districts (Forstämter, FA)” }
-
-  \answerfin{Has been changed, and likewise for the Forstreviere which we now call sub-districts.}  
-  % --------------------------- %
-
-  % 22) ++++++++++++++++++++++++++ %
-  \item \textit{L289-290: If the SFI is conducted in a five year cycle, shouldn’t the management strategy be also set up for five years, instead of ten years?}
-
-  \answerfin{The cycle of the stand wise inventories actually varies between 5 and 10 years and can in some cases even exceed 10 years.
-The stand wise inventories and the date of their conduction are planned by the state forest service.
-The management strategy for the stands is, however, always made for the upcoming 10 years ('mittelfristige Planung').}
-  % --------------------------- %
-
-  % 23) ++++++++++++++++++++++++++ %
-  \item \textit{L295 "2x2km" (see above)}
-
-  \answerfin{We would like to keep the '2x2km' notation.}  
-  % --------------------------- %
-
-  % 24) ++++++++++++++++++++++++++ %
-  \item \textit{Figure 1: "communal forests" (see above)}
-
-  \answerfin{Has been corrected.}  
-  % --------------------------- %
-
-  % 25) ++++++++++++++++++++++++++ %
-  \item \textit{Table 1: Please remove the digits (or at least reduce the number of digits).
-Giving values with an “accuracy” of 1/100th of a mm (i.e.
-10 mm) for DBH, as an example, really does not make much sense.
-}
-
-  \answerfin{We limited the number of digits for timber volume, DBH and height to one digit and removed the digits for stem number.}  
-  % --------------------------- %
-
-  % 26) ++++++++++++++++++++++++++ %
-  \item \textit{Table 3: I think one digit for the percentage values should be enough.}
-
-  \answerfin{Has been changed accordingly.}  
-  % --------------------------- %
-
-  % 27) ++++++++++++++++++++++++++ %
-  \item \textit{Table 6: Please indicate for what variable point estimates are. I suppose it is volume of growing stock per area unit [m$^3$ha-1]? And again, check the number of digits.}
-
-  \answerfin{Yes! We added the missing information accordingly.}  
-  % --------------------------- %
-
- % 28) ++++++++++++++++++++++++++ %
-  \item \textit{L454-458 I understand your intention and the necessity of removing FR-units.
-However, when comparing the performance of the estimators you should use the same population for all estimators.
-Removing the "difficult" FR-units (i.e.
-those with a low sampling density) only for PSMALL and EXTPSYNTH is somewhat unfair against the other estimators, and may bias the results.
-So, my advice is to recalculate SRS and PSYNTH for the same 321 FRs that were used for PSMALL and EXTPSYNTH.
-Edit: I noticed you confined your analyses to those 321 FRs later on (Fig 5 and Tab.
-7), another reason to also do it here.}
-
-  \answerfin{We changed the evaluation according to your suggestion and added a sentence in the paragraph above the table.
-The descriptive summary statistics for the one-phase SRS and the PSYNTH estimator did only differ marginally, with exception of the maximal errors which logically turned out to be lower.
-We also adjusted the numbers given in Section 6.2 and the graphic of Figure 3 respectively.}
-
-  % --------------------------- %
-
- % 29) ++++++++++++++++++++++++++ %
-  \item \textit{L517: Please use the same scaling for both x- and y-axis on the left plot. It is irritating that the 1:1 line does not cross the grid-corners.}
-
-  \answerfin{Has been changed accordingly.}  
-  % --------------------------- %
-
-   % 30) ++++++++++++++++++++++++++ %
-  \item \textit{L655-656: "Northwest German Forest Research Institution" It should be "Institute" instead of "Institution"}
-
-  \answerfin{Has been corrected.}  
-  % --------------------------- %
-
-\end{enumerate}
-
-%------------------------------------------------------------------------------------------------%
-% ---------------------------------- Reviewer 3 ------------------------------------------------ %
 

### 2018-08-06 Reviews/coverletter.tex
update 06_08_2018
final version of published article

\documentclass{article}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

%============================================ Define Titlepage & packages =============================================%

\title{Coverletter}

\author{A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels\\
Andreas Hill, Daniel Mandallaz, Joachim Langshausen}

\usepackage{fancyhdr}     
\usepackage{amsmath} %Paket für erweiterte math. Formeln
\usepackage[labelfont=bf]{caption}
\usepackage[font=footnotesize]{caption}
\usepackage[font=footnotesize]{subcaption}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[final]{pdfpages}
\usepackage{color}

\usepackage{natbib}
\usepackage{apalike}

\usepackage{geometry}
\geometry{
	a4paper,
	left=25mm,
	right=25mm,
	top=30mm,
	bottom=30mm
}

\setlength{\parindent}{0em} % Einzug bei neuen Absätzen

%------------------------------------------------------------------------------------------------%
% -------------------------------------- Main Document------------------------------------------ %

\begin{document}

%------------------------------------------------------------------------------------------------%
% -------------------------------------- Tex Settings ------------------------------------------ %

\maketitle
\thispagestyle{empty}
\newpage
\thispagestyle{empty}

\setlength{\headsep}{15mm}

%------------------------------------------------------------------------------------------------%

Dear Editors,\\

National forest inventories (NFIs) have a long tradition of providing reliable and accurate information of the state and development of forests on the national scale. However, the operational use of NFI data on spatially smaller forest management units such as forest enterprises or districts has been scarce due to the low sample frequencies and the implied insufficiently large estimation errors. The objective of our study was to develop a double-sampling estimation procedure for the German NFI that increases the value of the NFI data for forest authorities by extending their applicability to estimation on two forest district levels (i.e., \textit{Forst{\"a}mter} and \textit{Forstreviere}). As the integral part of this double-sampling estimation procedure, we tested two model-assisted design-based regression estimators that have been suggested by \citet{mandallaz2013a} and \citet{mandallaz2013b} under the infinite population approach. The potential of these estimators to be integrated in existing national forest inventories for \textit{global} estimation has recently been demonstrated by \cite{massey2014a} and \citet{massey2015b}. Our study continues to explore the suitability of these estimators for the special case of small area estimation. In this framework, it was of particular interest to evaluate the performance of the estimators with respect to their future large-scale operational use in NFIs, which is why we implemented and applied the procedure over the entire forest area of the German federal state Rhineland-Palatinate (appr. 8400 km$^2$). Up to our knowledge, there has not yet been a comparable large-scale application within either Germany or the neighboring countries. Our submitted article also constitutes the follow-up study of our recently published article in the \textit{European Journal of Forest Research} \citep{hill2017a}, which addressed the building of a regression model that is integrated in the small area estimators in order to predict the timber volume density on NFI plot level over the entire federal state area. This regression model includes the novelty of combining ALS-derived information with predictor variables derived from a satellite-based tree species classification map.\\

We believe that sharing our results on an international level via publication in \textit{Remote Sensing} is a valuable contribution to the field for the following main reasons: Firstly, the suggested small area estimators show great potential to use NFI data for estimation of various forest attributes on small-scale management levels. They are able to substantially reduce the estimation errors that are achieved under one-phase sampling (in the presented study, they achieved 5\% and 11\% on average on the two forest district levels, respectively). At the same time, they provide the advantage of the design-based framework, i.e., their design-unbiasedness does not depend on any model assumptions, which makes them very attractive to be used operationally. Secondly, the estimators are also well suited since explicitly formulated for cluster sampling designs such as used in the German NFI, which has not yet been the case for frequently used model-dependent estimators. Thirdly, our study complements the already existing literature about the considered estimators by providing new empirical insights about their performance and characteristics, leading to valuable recommendations with respect to their future operational application. And fourthly, the transferability of our method to other inventories is also supported by their recent implementation in an open-source statistical software package \citep{forestinventory} that has been optimized for large-scale application.\\

We would very much appreciate if the editors would consider our article for publication in their special issue.\\

With best regards,\\

The authors\\ \\

\newpage
\thispagestyle{empty}

\bibliographystyle{apalike2}
%\bibliographystyle{spbasic} 
\bibliography{bib/literaturerRLPsae}

%------------------------------------------------------------------------------------------------%
\end{document}

### 2018-08-06 Reviews/hill et al 2018.tex
update 06_08_2018
final version of published article

--- 2018-05-17 hill et al 2018/hill et al 2018.tex
@@
 The NFI thereby has the responsibility to satisfy various information needs including reporting to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and to the United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}.
-The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany.
-In order to cover a large area of 114'191 ha \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels.
+The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forested area of Germany.
+In order to cover a large area of 114'191 km$^2$ \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels.
 However, sample sizes often drop dramatically when entering spatial units below the federal state level.
@@
 For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels.
-In most German federal states, management strategies are thus still based on expert judgments from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par
-
-Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}.
-However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonluepke2013}.
-One method which has proven to be efficient is double- or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}.
+In most German federal states, management strategies are thus still based on expert judgements from time-consuming standwise forest inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par
+
+Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) carried out for forests owned by the state forest enterprise with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}.
+However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonLuepke2012, vonluepke2013}.
+One method which has proven to be efficient is double- or two-phase sampling \citep{devries1986, cochran1977, sarndal2003, gregoire2007, kohl2006, mandallaz2008}.
 Double-sampling incorporates less expensive auxiliary information and can be used to either increase estimation precision under a fixed terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size.
-Double-sampling procedures have already been used for stratification in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs.
-Recent studies have extended double-sampling to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities.
+
+Double-sampling procedures have already been used in various countries such as Canada \citep{gillis2010intomppo}, the USA \citep{chojnacky1998}, Switzerland \citep{lanz2010intomppo}, Italy \citep{gasparini2010intomppo} and Germany \citep{saborowski2010}.
+Recent studies from \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs.
+Double-sampling has also been extended to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities.
 An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI of Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories.
@@
 
-The German NFI is a periodic inventory that is carried out every 10 years over the entire forest area of Germany.
-The most recent inventory (BWI3) was conducted in 2011 and 2012.
+The German NFI (Bundeswaldinventur, BWI )is a periodic inventory that is carried out every 10 years over the entire forest area of Germany.
+The third and most recent inventory (BWI3) was conducted in 2011 and 2012.
 While information was originally gathered on a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid.
@@
 The number of plots per cluster can vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}.
-In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the individual tree's inclusion circle \citep{bwi3_aufn}.
-A further inventory threshold for a tree to be recorded is a diameter at breast height ($DBH$) of at least 7 cm.
+In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}.
+Angle count sampling is a visual selection procedure conducted via an optical instrument (\textit{Relascope}).
+At a sample point $x$, a tree is selected as a sample tree if its apparent diameter at the height of 1.3 m ($DBH$) and the associated angle $\alpha_i$ (in radiant) appears larger than a limit angle $\alpha$ when viewed through the Relascope \citep{mandallaz2008}.
+The limit angle $\alpha{}$ can be expressed by the so-called basal area factor ($BAF$), i.e.
+$BAF = 10^{2}sin^{2}(\frac{\alpha}{2})$.
+Consequently, each tree $i$ is assigned with an individual radius $R_{i}=\frac{DBH_{i}}{2\sqrt{BAF}}$ which is the distance between the tree location and the sample plot center.
+A tree is selected if $R_{i}$ is equal to or smaller than the so-called limiting distance $R$ that results from chosen BAF (i.e., $\alpha$).
+One characteristic of angle count sampling is that a sample plot does no longer has a fixed radius in which sample trees are selected, but each tree creates its individual radius $R_i$ that is - likewise the associated inclusion probability - proportional to its basal area.
+For this reason, the angle count method is also referred to as \textit{variable radius plot sampling} and implements the \textit{probability proportional to size (PPS)} concept.
+The BWI3 uses a basal area factor of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the individual tree's inclusion circle \citep{bwi3_aufn}.
+A further inventory threshold for a tree to be recorded is a DBH of at least 7 cm.
 For each sample tree that is selected by this procedure, the DBH, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to estimate the volume at the tree level.
@@
 
-\noindent $\pmb{Z}_{c}(x)$ is the vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Eq.\ref{eq:Zc(x)}).
+\noindent $\pmb{Z}_{c}(x)$ is the column vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Eq.\ref{eq:Zc(x)}).
 The weight $w(x_l)$ is the proportion of the extraction area (support) within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.
@@
 
-\noindent being the empirical model residuals at the cluster level, which by construction of OLS satisfy the important zero mean residual property, i.e.
-$\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$.\\
-
-In the following, we will give a short description of each small area estimator and refer to \citet{mandallaz2013a, mandallaz2016, mandallaz2013b} if the reader requires additional details or proofs.
-The estimators have also been implemented in the R-package \textit{forestinventory} \citep{forestinventory} which was used to compute all estimates in this study.\\
+\noindent being the empirical model residuals at the cluster level.
+By construction of OLS, the empirical model residuals satisfy that they average to zero, i.e.
+$\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$, if $\pmb{Z}_{c}(x)$ contains the intercept term 1.
+Because the model is fitted internally, i.e.
+using the terrestrial sample $s_2$ of the inventory area, this leads to the important \textit{zero mean residual property} of the theoretical model residuals over the inventory domain $F$, i.e.
+$\int_{F} R_{c}(x)dx$.
+\citet{mandallaz2013a} and \citet{mandallaz2013b} used this property particular for the case of small area estimation to derive better variance estimates based on the g-weight technique adapted from the works of \citet{sarndal2003}.\\
+
+In the following, we will give a short description of each small area estimator and refer to \citet{mandallaz2013a, mandallaz2016, mandallaz2013b} if the reader requires additional mathematical details or proofs.
+The estimators have also been implemented in the open-source software-package \textit{forestinventory} \citep{forestinventory} in the statistical software \textit{R} \citep{R} which was used to compute all estimates in this study.\\
 
@@
 \ref{eq:psmall_pest}) can no longer be applied.
-The \psynth{} estimator thus has a potential unobservable design-based bias.
+Conditioned on the realized sample, the \psynth{} estimator can thus potentially have an unobservable design-based bias.
 
@@
 As a result, the synthetic estimator will usually have a smaller variance than estimators that consider the model residuals, but at the cost of a potential bias.
-Note that the \psynth{} estimator is still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.\\
+Note that the \psynth{} estimations are still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.\\
 
@@
 The forest area of RLP are divided into 3 ownership classes, i.e.
-state forest (27\%), communal forest (46\%) and privately owned forest (27\%).
-The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}.
+state forest (27\%), municipal forest (46\%) and privately owned forest (27\%).
+The forest service of RLP has the legal mandate to sustainably manage the state and municipal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}.
 For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArean}).
-On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 405 Forstreviere (\textit{FR}).
+On the upper level, RLP has been divided into 45 forest districts (Forst{\"a}mter, \textit{FA}), which are further divided into a total number of 405 sub-districts (Forstreviere, \textit{FR}).
 The next level are the forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5 to 10 year period in order to set up management strategies for the upcoming 10 years.
@@
 
-Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI.
+Rhineland-Palatinate is covered by a 2x2 km inventory grid of the German NFI.
 In the last inventory (BWI3) conducted in the year 2011 and 2012, timber volume information was derived for 2810 clusters (8092 plots) in the field survey.
@@
 \textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit overlayed with the extended double-sampling cluster design.
-\textit{Green}: Forest stand polygon layer defining the state and communal forest area of this study.}
+\textit{Green}: Forest stand polygon layer defining the state and municipal forest area of this study.}
 	\label{fig:StudyArean}
@@
 The existing terrestrial phase $s_2$ was integrated by replacing the target coordinates of the respective $s_1$ clusters by the terrestrially measured DGPS coordinates.
-The sampling frame was further restricted to the communal and state forest area.
-The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stand layer provided by the forest service.
+The sampling frame was further restricted to the municipal and state forest area.
+The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the municipal and state forest stand layer provided by the forest service.
 Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.
 The terrestrial sample size $n_2$ was thus reduced to 2055 clusters (5791 plots).
-Table \ref{tab:fieldata} provides a short descriptive summary about the volume densities and the main attributes of the NFI plots located in the state and communal forest sampling frame.
+Table \ref{tab:fieldata} provides a short descriptive summary about the volume densities and the main attributes of the NFI plots located in the state and municipal forest sampling frame.
 The densification led to an average sample size $n_{1,G}$ of 759  clusters (range: 246 -- 1022) in the FA units, and 88 clusters (range: 1 -- 194) in the FR units.
@@
 				\hline \hline
-				communal and state forest & 96'854 & 33'365 & 5791 & 2055\\
+				municipal and state forest & 96'854 & 33'365 & 5791 & 2055\\
 				\hspace{5mm} \footnotesize missing CHM & \footnotesize 18 & \footnotesize 10 & \footnotesize 0 & \footnotesize 0\\ % <--
@@
 the support.
-In order to correct for edge effects at the forest border, the intersection of each support area to the state and communal forest area was determined using a polygon mask provided by the state forest service.
+In order to correct for edge effects at the forest border, the intersection of each support area to the state and municipal forest area was determined using a polygon mask provided by the state forest service.
 The percentage of the support within the forest layer was used as the weight $w(x_l)$ introduced in Eq.
@@
 				\hline \hline	
-				Beech       & 22.31 & 47.02 & 883 & 419 \\
-				Douglas Fir & 24.78 & 48.72 & 230 & 117 \\
-				Oak         & 11.07 & 48.48 & 289 & 66 \\
-				Spruce      & 53.15 & 61.13 & 651 & 566 \\
-				Scots Pine  & 22.91 & 46.07 & 179 & 89 \\
-				Mixed       & 84.49 & 64.53 & 3152 & 4127 \\
+				Beech       & 22.3 & 47.0 & 883 & 419 \\
+				Douglas Fir & 24.8 & 48.7 & 230 & 117 \\
+				Oak         & 11.1 & 48.5 & 289 & 66 \\
+				Spruce      & 53.2 & 61.1 & 651 & 566 \\
+				Scots Pine  & 22.9 & 46.1 & 179 & 89 \\
+				Mixed       & 84.5 & 64.5 & 3152 & 4127 \\
 				\hlineB{2}
-				& \multicolumn{2}{l|}{Overall accuracy: 61.96\%} & 5384 & 5384 \\
+				& \multicolumn{2}{l|}{Overall accuracy: 62.0 \%} & 5384 & 5384 \\
 				\hline \hline
@@
 As the two-phase estimators described in Section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level, we re-evaluated the model as used in the estimators on the cluster level (formulas given in Appendix) and found improved model fits compared to the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%).
-The stratification by the ALS acquisition year substantially improved the model fit, indicating that it is an effective means in accounting for the noise in the data caused by ALS quality variations and time-gaps between the ALS and the terrestrial survey.
-However, the stratification led to a highly unbalanced data set when a further \treespecies{} stratification was included.
+Using the ALS acquisition year as a categorical variable substantially improved the model fit, indicating that it is an effective means in accounting for the noise in the data caused by ALS quality variations and time-gaps between the ALS and the terrestrial survey.
+However, this also led to a highly unbalanced data set when introducing the \treespecies{} variable as an additional categorical predictor.
 For this reason, a individual species modeling within each \alsyear{} stratum remained infeasible, but might have further improved the model fit.
@@
 
-Concerning the existence of outliers or leverage points in the training set for the model, it should be noted that it is more problematic for \psmall{}, \psynth{} and \extpsynth{} to simply remove them as one might be inclined to do in a model-dependent context.
+%Concerning the existence of outliers or leverage points in the training set for the model, it should be noted that it is more problematic for \psmall{}, \psynth{} and \extpsynth{} to simply remove them as one might be inclined to do in a model-dependent context.
 Strictly speaking, outlier removal in the design-based context essentially means that those plots, and implicitly any potentially similar plots that were not realized in the selected sample, have been removed from the sampling frame and are no longer considered part of the forest area of interest.
 While this may be valid for some obvious typos or measurement errors, it is generally not advisable to manipulate the sampling frame after observing data collected from it, especially when the observation in question lies within the small area of interest.
-However, for sake of completeness, we conducted an analysis of influential observations \citep[pp.
+
+% new: 
+Concerning the treatment of outliers or leverage points, it can be advisable to remove such observations from the training data set that is used to determine the regression coefficients (Section \ref{sec:SAestimators}) in order to minimize the residual variance for the entire terrestrial sample.
+However, it should be noted that such removal of observations does restrict the calculation of design-unbiased estimation to the \psmall{} estimator, because the residuals still have to be derived for the full terrestrial sample in order to ensure unbiased estimation.
+This would no longer be satisfied when using the \extpsynth{} estimator, where the residual correction term is included in the regression coefficient (Section \ref{sec:extpsynth}).
+For our particular case, we conducted an analysis of influential observations \citep[pp.
 160--167]{fahrmeir2013} on the plot level for the full regression model.
@@
 This affected 65 additional FR units and limited unbiased two-phase estimations to 321 (79\%) of the 405 FR units.
-It should be noted that also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 2$.
-Due to substantially larger sample sizes, all estimators could however be applied to all 45 FA units.
+Also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 2$.
+For better comparison, the descriptive summaries of point estimates and estimation errors for each estimator presented in Table \ref{tab:estres} are always based on the same population of small area units, i.e.
+the 321 districts for which unbiased two-phase estimations were possible.\\
+All estimators could however be applied to all 45 FA units due to substantially larger sample sizes.
 The average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (Table \ref{tab:estres}).
@@
 	\begin{center}
-		\caption{Descriptive summary of point estimates and estimation errors on the two forest district levels. $N_u$: number of evaluated small area units.}
+		\caption{Descriptive summary of point estimates and estimation errors for the volume of growing stock per area unit [m$^3$/ha] on the two forest district levels.
+$N_u$: number of evaluated small area units.}
 		\vspace{0.2cm}
@@
 				\hlineB{2}          
-				\multirow{4}{*}{FR} & SRS       & ($N_u$=388) & 301.83 &  99.89 & 612.13 & 18.32 & 0.34 & 104.97 \\
+				\multirow{4}{*}{FR} & SRS       & ($N_u$=321) & 302.77 &  99.89 & 552.87 & 16.94 & 2.76 & 55.51 \\
 				& PSMALL    & ($N_u$=321) & 308.15 & 159.64 & 568.67 & 12.24 & 3.48 &  44.94 \\
 				& EXTPSYNTH & ($N_u$=321) & 308.38 & 154.07 & 544.34 & 11.34 & 3.60 &  40.91 \\
-				& PSYNTH    & ($N_u$=403) & 307.82 & 166.01 & 444.29 & 4.65  & 2.56 &  62.51 \\
+				& PSYNTH    & ($N_u$=321) & 305.56 & 197.47 & 444.29 & 4.13  & 2.56 &  18.07 \\
 				\hline \hline
@@
 \ref{fig:disterrors}, right).
-The average error under the SRS estimator was 18.3\%, while it was 11.3\% and 12.2\% under \psmall{} and \extpsynth{} (Table \ref{tab:estres}).
+The average error under the SRS estimator was 16.9\%, while it was 11.3\% and 12.2\% under \psmall{} and \extpsynth{} (Table \ref{tab:estres}).
 Errors smaller than 10\% were achieved for 15\% of the FR units by the SRS estimator, and for 46\% by the \psmall{} and \extpsynth{} estimator.
 95\% of the 321 FR units where \psmall{} and \extpsynth{} could be applied exhibited errors less than 20\%.
-In comparion, the SRS estimates resulted in errors less than 36.6\% for 95\% of the 388 FR units.
+In comparion, the SRS estimates resulted in errors less than 32.3\% for 95\% of the 321 evaluated FR units.
 
@@
 \textit{Left}: Results for the 45 FA units.
-\textit{Right}: Results for the 388 (SRS), 321 (\psmall{}, \extpsynth{}) and 403 (\psynth{}) FR units.}
+\textit{Right}: Results for the 321 FR units.}
 	\label{fig:disterrors}
@@
 On the upper management level (FA districts), \psmall{} and \extpsynth{} produced estimation errors smaller than 5\% for 73\% of the small areas compared to only 17\% under the one-phase SRS estimator.
-The same level of precision could not be achieved on the lower management level (FR districts) primarily due to substantially smaller terrestrial sample sizes.
+It could be argued that the majority of the FA units comprised a sample size (46 clusters on average) that would also have allowed to build an individual prediction model for each FA unit and apply direct estimation, which can be more efficient.
+The main reason why this was not considered in the present study was the large number of parameters that would have to be fitted in the individual prediction models resulting from the pronounced heterogeneity in the auxiliary data (multiple tree species and ALS acquisition years in each FA unit).
+In this case, the strategy to 'borrow strength' from the entire inventory domain was preferred to direct estimation in order to avoid overfitting and the implied risk of unstable global estimation.
+Even in case the above mentioned problem of overfitting is not raised, individual model building for a large number of small area units can be time-consuming and small area estimation can be a cost-saving alternative - however, possibly the cost of more efficient global estimation.\par
+
+The level of precision of the FA-level could not be achieved on the lower management level (FR districts) primarily due to substantially smaller terrestrial sample sizes.
 However, in 95\% of the FR units, the estimation errors could be limited to 20\% compared to 40\% under SRS.
@@
 Aside from this, calculating both \psmall{} and \extpsynth{} and subsequently compare their results is always recommended to reveal suspicious deviations.\par
+
+%new
+A commonly raised critic on the proposed design-unbiased estimators are their asymptotic properties, i.e.
+the validity of the confidence coverage rates is only ensured if the sample size in a small area is sufficiently large.
+Giving a generally valid sample size for the asymptotic validity range is, unfortunately, infeasible due to the dependency on the heterogeneity of the underlying population which is per se unknown.
+However, simulation studies for simple random sampling presented in \citet{mandallaz2013b} suggested that a minimum sample size of 6 within a small area is sufficient to ensure the nominal coverage rates of the confidence intervals for \psmall{} and \extpsynth{}.
+Re-evaluating the same simulation example recently confirmed the same results for cluster sampling.
 
@@
 Kai Husmann and Dr.
-Christoph Fischer from the Northwest German Forest Research Institution G{\"o}ttingen for their advice in processing the terrestrial inventory data.
+Christoph Fischer from the Northwest German Forest Research Institute G{\"o}ttingen for their advice in processing the terrestrial inventory data.
 Special gratitude is also owed to Dr.

### 2018-08-06 hill et al 2018 revised version/tab/table_fieldmeasuredvals.tex
update 06_08_2018
final version of published article

\begin{table}[ht]
	\begin{center}
	\caption{Descriptive statistics of the forest observed on NFI sample plots located within communal and state forest area ($n_2$=5791).}
	\label{tab:fieldata}
	{\small %
	\begin{tabular}{lllrrr}
		\hline
		Variable & Mean & SD & Maximum \\ 
		\hline \hline
Timber Volume (m$^3$/ha) & 300.9 & 195.6 & 1375.3 \\
Mean DBH (mm) & 354.9 & 137.2 & 1123.2 \\
Mean height (dm) & 239.6 & 72.4 & 497.4 \\
Mean stem density per hectare & 101  & 114 & 1010 \\
\hline
\hline
\end{tabular}
}%
\end{center}
\end{table}

### 2018-08-06 hill et al 2018/hill et al 2018.tex
update 06_08_2018
final version of published article

@@
 For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels.
-In most German federal states, management strategies are thus still based on expert judgments from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par
-
-Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}.
+In most German federal states, management strategies are thus still based on expert judgements from time-consuming standwise forest inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par
+
+Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) carried out for forests owned by the state forest enterprise with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}.
 However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonluepke2013}.

### 2018-08-06 manuscript.v4/remotesensing-311343-proofreading/remotesensing-311343-proofreading.tex
update 06_08_2018
final version of published article

--- 2018-08-06 Reviews/hill et al 2018.tex
@@
 
-%=================================================================
-\documentclass[remotesensing,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi} 
+% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
+\documentclass[remotesensing,article,accept,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi} 
 %
@@
 
-%=================================================================
+% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
 \firstpage{1} 
@@
 \makeatother
-\articlenumber{x}
-\doinum{10.3390/------}
 \pubvolume{xx}
-\pubyear{2017}
-\copyrightyear{2017}
-\externaleditor{Academic Editor: name}
-\history{Received: date; Accepted: date; Published: date}
+\issuenum{1}
+\articlenumber{1}
+\pubyear{2018}
+\copyrightyear{2018}
+%\externaleditor{Academic Editor: name}
+\history{Received: 17 May 2018; Accepted: 26 June 2018; Published: date}
 
@@
 
-\usepackage[font=footnotesize]{caption}
-\usepackage[font=footnotesize]{subcaption}
+\usepackage[font = footnotesize]{caption}
+\usepackage[font = footnotesize]{subcaption}
 
@@
 % The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
-
-%=================================================================
+%\pdfoutput = 1
+
+% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
 % Add packages and commands here.
@@
 
-%=================================================================
+% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
 %% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
@@
 
-%=================================================================
+% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
 % Full title of the paper (Capitalized)
-\Title{A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels}
+\Title{A Double-Sampling Extension of the German National Forest Inventory for Design-Based Small Area Estimation on Forest District Levels}
 
@@
 \address{%
-	$^{1}$ \quad Department of Environmental Systems Science, ETH Zurich, 8092 Zurich, Switzerland; mdaniel@retired.ethz.ch (D.M.)\\
+	$^{1}$ \quad Department of Environmental Systems Science, ETH Zurich, 8092 Zurich, Switzerland; mdaniel@retired.ethz.ch\\
 	$^{2}$ \quad State Forest Service Rhineland-Palatinate, 56281 Emmelshausen, Germany; Joachim.Langshausen@wald-rlp.de}
@@
 % Contact information of the corresponding author
-\corres{Correspondence: andreas.hill@usys.ethz.ch; Tel.: +x-xxx-xxx-xxxx}
-
-% Abstract (Do not insert blank lines, i.e. \\) 
+\corres{Correspondence: andreas.hill@usys.ethz.ch}
+
+% Abstract (Do not insert blank lines, i.e.,~\\) 
 \abstract{The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval.
@@
 An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions.
-The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the one-phase simple random sampling estimator by 43\% and 25\% on average for the two management levels respectively.}
+The~results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the one-phase simple random sampling estimator by 43\% and 25\% on average for the two management levels~respectively.}
 
 % Keywords
-\keyword{National forest inventory, small area estimation, forest districts, double sampling for regression within strata, cluster sampling, canopy height model, tree species classification}
+\keyword{National Forest Inventory; small area estimation; forest districts; double sampling for regression within strata; cluster sampling; canopy height model; tree species classification}
 
@@
 The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forested area of Germany.
-In order to cover a large area of 114'191 km$^2$ \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels.
+In order to cover a large area of 114,191 km$^2$ \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels.
 However, sample sizes often drop dramatically when entering spatial units below the federal state level.
@@
 Double-sampling procedures have already been used in various countries such as Canada \citep{gillis2010intomppo}, the USA \citep{chojnacky1998}, Switzerland \citep{lanz2010intomppo}, Italy \citep{gasparini2010intomppo} and Germany \citep{saborowski2010}.
-Recent studies from \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs.
+Recent studies \mbox{from \citet{grafstrom2017a}} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs.
 Double-sampling has also been extended to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities.
@@
 SAE techniques address the situation where the number of samples within a subunit, or small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit.
-A broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics.
-One such method that is commonly applied is known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not observed in the small area.
-These models are trained using data from outside the small area in order to "borrow strength" from areas where information is available.
-Of numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, most use unit-level models, i.e.
-the inventory plot is the unit of the response variable in the training data used for the model fit.
+A~broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics.
+One~such method that is commonly applied is known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not observed in the small area.
+These models are trained using data from outside the small area in order to ``borrow strength'' from areas where information is available.
+Of numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, most use unit-level models, i.e.,~the inventory plot is the unit of the response variable in the training data used for the model fit.
 Such unit-level models have been intensively investigated for timber volume estimation using various remote sensing auxiliary data \citep{koch2010, naesset2014inmaltamo}.
@@
 Some studies have illustrated that even NFI data derived under low sampling densities can still be used to provide acceptable precision of small area estimates on much smaller management levels.
-One example is \citet{breidenbach2012} who used data from the Norwegian NFI to make small area estimation for standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35.
+One~example is \citet{breidenbach2012} who used data from the Norwegian NFI to make small area estimation for standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35.
 The estimation errors under the applied model-dependent and design-based small area estimators turned to be markedly smaller than under the standard one-phase estimator.
@@
 Three types of model-assisted design-based small area regression estimators were used to derive point and variance estimates of mean standing timber volume for 45 and 405 forest management units on the two respective district levels.
-The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a} and \citet{ mandallaz2013b}.
+The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested \mbox{by \citet{mandallaz2013a}} and \citet{ mandallaz2013b}.
 Auxiliary data consisted of a canopy height model (CHM) obtained from a countrywide airborne laser scanning (ALS) and a tree species classification map to be used for regression within tree species strata.
 The estimation precisions were compared to those obtained by the standard one-phase estimator for cluster sampling under simple random sampling.
-The chosen double-sampling estimators were selected for several reasons: \textbf{(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can be used with \textit{non-exhaustive}, i.e.
-non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance partially accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust under heteroscedasticity of the model residuals.
+The chosen double-sampling estimators were selected for several reasons: {(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; {(ii)} the estimators can be used with \textit{non-exhaustive}, i.e.,~non wall-to-wall, auxiliary information; {(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators and {(iv)} the asymptotically unbiased g-weight variance partially accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust under heteroscedasticity of the model residuals.
 The results from this study were considered to provide valuable information about the potential of the suggested small area estimation procedure and the incorporated auxiliary information for future operational large scale application.\par
@@
 
-\section{Terrestrial sampling design of the German NFI}
+\section{Terrestrial Sampling Design of the German NFI}
 \label{sec:germanNFI}
 
-The German NFI (Bundeswaldinventur, BWI )is a periodic inventory that is carried out every 10 years over the entire forest area of Germany.
+The German NFI (Bundeswaldinventur, BWI) is a periodic inventory that is carried out every 10 years over the entire forest area of Germany.
 The third and most recent inventory (BWI3) was conducted in 2011 and 2012.
-While information was originally gathered on a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid.
+While information was originally gathered on a systematic 4 $\times$ 4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2 $\times$ 2 km grid.
 The German NFI uses a cluster sampling design, which means that a sample unit consists of at most four sample locations (also referred to as \textit{sample plots}) that are arranged in a square, called \textit{cluster}, with a side length of 150 metres.
@@
 At a sample point $x$, a tree is selected as a sample tree if its apparent diameter at the height of 1.3 m ($DBH$) and the associated angle $\alpha_i$ (in radiant) appears larger than a limit angle $\alpha$ when viewed through the Relascope \citep{mandallaz2008}.
-The limit angle $\alpha{}$ can be expressed by the so-called basal area factor ($BAF$), i.e.
-$BAF = 10^{2}sin^{2}(\frac{\alpha}{2})$.
-Consequently, each tree $i$ is assigned with an individual radius $R_{i}=\frac{DBH_{i}}{2\sqrt{BAF}}$ which is the distance between the tree location and the sample plot center.
+The limit angle $\alpha{}$ can be expressed by the so-called basal area factor ($BAF$), i.e.,~$BAF  =  10^{2}sin^{2}(\frac{\alpha}{2})$.
+Consequently, each tree $i$ is assigned with an individual radius $R_{i} = \frac{DBH_{i}}{2\sqrt{BAF}}$ which is the distance between the tree location and the sample plot center.
 A tree is selected if $R_{i}$ is equal to or smaller than the so-called limiting distance $R$ that results from chosen BAF (i.e., $\alpha$).
@@
 A further inventory threshold for a tree to be recorded is a DBH of at least 7 cm.
-For each sample tree that is selected by this procedure, the DBH, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to estimate the volume at the tree level.
+For each sample tree that is selected by this procedure, the DBH, the absolute tree height, the~tree diameter at 7 m ($D7$) and the tree species is measured and used to estimate the volume at the tree level.
 These volume estimates are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.
@@
 % ++++++++++++ %
-\section{Double sampling in the infinite population approach}
+\section{Double Sampling in the Infinite Population Approach}
 \label{sec:inf_pop}
-
- \subsubsection{One- and Two-Phase Sampling in the Infinite Population Approach}
+\vspace{-6pt}
+
+% \subsection*{One- and Two-Phase Sampling in the Infinite Population Approach} [Please remove this header if possible (redundant with main section title)]
 
@@
 Therefore, we shall first provide a short introduction into this general estimation framework.
-We start by assuming that the population $P$ of trees $i \in 1,2, ..., N$ within a forest of interest $F$ is exactly defined, and each tree $i$ has a response variable $Y_i$ (e.g.
-its timber volume) that can be used to define the population mean $Y$ (e.g., the average timber volume per unit area) over $F$.
+We start by assuming that the population $P$ of trees $i \in 1,2, ..., N$ within a forest of interest $F$ is exactly defined, and each tree $i$ has a response variable $Y_i$ (e.g., its timber volume) that can be used to define the population mean $Y$ (e.g., the average timber volume per unit area) over $F$.
 Since a full census of all tree population individuals is almost never feasible, $Y$ has to be estimated based on a sample.
 In the infinite population approach this sample is a set of points or locations $x$ distributed independently and uniformly over the set of all possible points in $F$.
-Each point $x$ has an associated local density $Y(x)$ (e.g., the timber volume per unit area) whose spatial distribution is given by a fixed (i.e.
-non stochastic) piecewise constant function.
-The population mean $Y$ is mathematically equivalent to the integral of the local density function surface divided by the surface area of $F$, $\lambda(F)$, i.e.
-$Y=\frac{1}{N} \sum_{i=1}^{N}Y_i=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$, and thus the population mean $Y$ corresponds to a spatial mean.
+Each point $x$ has an associated local density $Y(x)$ (e.g., the timber volume per unit area) whose spatial distribution is given by a fixed (i.e.,~non stochastic) piecewise constant function.
+The population mean $Y$ is mathematically equivalent to the integral of the local density function surface divided by the surface area of $F$, $\lambda(F)$, i.e.,~$Y = \frac{1}{N} \sum_{i = 1}^{N}Y_i = \frac{1}{\lambda(F)}\int_{F}Y(x)dx$, and thus the population mean $Y$ corresponds to a spatial mean.
 Since the actual local density function is unobserved in its entirety, one estimates $Y$ by taking a sample $s_2$ consisting of $n_2$ points and measuring each of their respective local densities.
@@
 In contrast to the one-phase approach, \textit{two-phase} or \textit{double-sampling} procedures use information from two nested samples (phases).
-Practically speaking, the terrestrial inventory $s_2$ is embedded in a large phase $s_1$ comprising $n_1$ sample locations that each provide a set of explanatory variables described by the column vector $\pmb{Z}(x)=(z(x)_1, z(x)_2,...,z(x)_p)^{\top}$ at each point $x \in s_1$.
+Practically speaking, the terrestrial inventory $s_2$ is embedded in a large phase $s_1$ comprising $n_1$ sample locations that each provide a set of explanatory variables described by the column vector $\pmb{Z}(x) = (z(x)_1, z(x)_2,...,z(x)_p)^{\top}$ at each point $x \in s_1$.
 These explanatory variables are derived from auxiliary information that is available in high quantity within the forest $F$.
 For every $x \in s_1$, $\pmb{Z}(x)$ is transformed into a prediction $\hat{Y}(x)$ of $Y(x)$ using the choice of some prediction model.
-The basic idea of this method is to boost the sample size by providing a large sample of less precise but cheaper predictions of $Y(x)$ in $s_1$ and to correct any possible model bias, i.e., $\EX{(Y(x)-\hat{Y}(x))}$, using the subsample of terrestrial inventory units where the value of $Y(x)$ is observed.
+The basic idea of this method is to boost the sample size by providing a large sample of less precise but cheaper predictions of $Y(x)$ in $s_1$ and to correct any possible model bias, i.e.,~$\EX{(Y(x)-\hat{Y}(x))}$, using the subsample of terrestrial inventory units where the value of $Y(x)$ is observed.
 In this context, it is also important to note that the response and auxiliary variables are assumed to be error-free and the resulting errors for the point estimates reflect only the uncertainty due to sampling.
@@
 
+\vspace{-6pt}
 % ++++++++++++ %
-\subsection{Design-based one-phase estimator for cluster sampling (SRS)}
+\subsection{Design-Based One-Phase Estimator for Cluster Sampling (SRS)}
 \label{sec:srs_estimator}
@@
 In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator that is applied in the BWI3 algorithms \citep{bwi3_ausw} in the form given in \citet{mandallaz2008} and \citet{mandallaz2016}.\par
-In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M=4$ ) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$.
-The actual number of plots per cluster, $M(x)$, is a random variable due to the uniform distribution of $x_l$ ($l=1, ..., M$) in the forest $F$ and to the forest/non-forest decision for each sample location $x_l$:
-
+In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M = 4$) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$.
+The actual number of plots per cluster, $M(x)$, is a random variable due to the uniform distribution of $x_l$ ($l = 1, ..., M$) in the forest $F$ and to the forest/non-forest decision for each sample location $x_l$:
 \begin{equation}\label{eq:Mx}
-M(x)=\sum_{l=1}^{M}I_{F}(x_l) \hspace{3ex} \text{where} \hspace{3ex} I_F(x_l)=\begin{cases}&1 \text{ if $x_l \in F$}\\
+M(x) = \sum_{l = 1}^{M}I_{F}(x_l) \hspace{3ex} \text{where} \hspace{3ex} I_F(x_l) = \begin{cases}&1 \text{ if $x_l \in F$}\\
 &0 \text{ if $x_l\not\in F$}
@@
 The local density on cluster level $Y_{c}(x)$, which is in our case the timber volume per hectare, is then defined as the average of the individual sample plot densities $Y(x_l)$:
-
 \begin{equation}\label{eq:locdens_clust}
-Y_{c}(x) = \frac{\sum_{l=1}^{M} I_{F}(x_{l}) Y(x_l)}{M(x)}
+Y_{c}(x)  =  \frac{\sum_{l = 1}^{M} I_{F}(x_{l}) Y(x_l)}{M(x)}
 \end{equation}
@@
 The general form of $Y(x)$ in \citet{mandallaz2008} is given as the Horwitz-Thompson estimator
-
 %\begin{equation}\label{locdens_plot}
-%Y(x)= \sum_{i=1}^{F}\frac{I_{i}(x)Y_i}{\varPi_{i}\lambda(F)} = \sum_{i \in s_{2}(x)}\frac{Y_i}{\varPi_{i}\lambda(F)}
+%Y(x) =  \sum_{i = 1}^{F}\frac{I_{i}(x)Y_i}{\varPi_{i}\lambda(F)}  =  \sum_{i \in s_{2}(x)}\frac{Y_i}{\varPi_{i}\lambda(F)}
 %\end{equation}
-
 \begin{equation}\label{eq:locdens_plot}
-Y(x_l)=\sum_{i \in s_{2}(x_l)}\frac{Y_i}{\pi_{i}\lambda(F)}
+Y(x_l) = \sum_{i \in s_{2}(x_l)}\frac{Y_i}{\pi_{i}\lambda(F)}
 \end{equation}
-
-\noindent where $Y_i$ is in our case the timber volume of the tree $i$ recorded at sample location $x$ in m$^3$.
-Each tree has an inclusion probability $\pi_{i}$ that is well defined as the proportion of its inclusion circle area $\lambda(K_i)$ within the forest area $\lambda(F)$, i.e.
-via their geometric intersection:
-
+where $Y_i$ is in our case the timber volume of the tree $i$ recorded at sample location $x$ in m$^3$.
+Each tree has an inclusion probability $\pi_{i}$ that is well defined as the proportion of its inclusion circle area $\lambda(K_i)$ within the forest area $\lambda(F)$, i.e.,~via their geometric intersection:
 %with the binary indicator variable $Ii$ for the $i$th tree defined as
@@
 %\begin{equation}\label{1stage}
-%I_i(x)=\begin{cases}&1 \text{ if $x \in K_i$}\\
+%I_i(x) = \begin{cases}&1 \text{ if $x \in K_i$}\\
 %&0 \text{ if $x\not\in K_i$}
@@
 %\end{equation}
-
 \begin{equation}\label{locdens_plot_1}
@@
 In case of angle-count sampling, we can rewrite $\pi_{i}$ as
-
 \begin{equation}\label{eq:locdens_plot_2}
@@
 
-\noindent since the intersection area $\lambda(K_i \cap F)/\lambda(F)$ can be expressed using the trees basal area $G_i$ (in m$^2$) and the corrected counting factor:
-
+since the intersection area $\lambda(K_i \cap F)/\lambda(F)$ can be expressed using the trees basal area $G_i$ (in m$^2$) and the corrected counting factor:
 \begin{equation}\label{eq:locdens_plot_3}
@@
 
-Eq. \ref{eq:locdens_plot_2} in Eq. \ref{eq:locdens_plot} yields the rewritten form of $Y(x_l)$ for angle count sampling that conforms to the definition used in the BWI3 algorithms \citep{bwi3_ausw}:
-
+Equation~(\ref{eq:locdens_plot_2}) in Equation~(\ref{eq:locdens_plot}) yields the rewritten form of $Y(x_l)$ for angle count sampling that conforms to the definition used in the BWI3 algorithms \citep{bwi3_ausw}:
 \begin{equation}\label{eq:locdens_plot_4}
-Y(x_l)= \sum_{i \in s_{2}(x_l)} \frac{cf_{i, corr}Y_i}{G_i} = \sum_{i \in s_{2}(x_l)} nha_{i}{Y_i}
+Y(x_l) =  \sum_{i \in s_{2}(x_l)} \frac{cf_{i, corr}Y_i}{G_i}  =  \sum_{i \in s_{2}(x_l)} nha_{i}{Y_i}
 \end{equation}
-
-\noindent where $nha_i$ is the number of trees per hectare represented by tree $i$.
+where $nha_i$ is the number of trees per hectare represented by tree $i$.
 The local densities on cluster level can then be used to derive the estimated spatial mean $\hat{\bar{Y}}_c$ and its estimated variance $\hat{\var}(\hat{\bar{Y}}_c)$ for any given spatial unit for which $n_2 \geq 2$ ($n_2$ denoting the number of clusters):
-
 \begin{subequations}\label{eq:srs_est_clusters}
 	\begin{align}
-	\hat{\bar{Y}}_c &= \frac{\sum_{x \in s_2} M(x) Y_{c}(x)}{\sum_{x \in s_2} M(x)} \\
-	\hat{\var}(\hat{\bar{Y}}_c) &= \frac{1}{n_2(n_2 - 1)}\sum_{x \in s_2}\Big(\frac{M(x)}{\bar{M_2}}\Big)^2(Y_{c}(x) - \hat{\bar{Y}}_c)^2
+	\hat{\bar{Y}}_c & =  \frac{\sum_{x \in s_2} M(x) Y_{c}(x)}{\sum_{x \in s_2} M(x)} \\
+	\hat{\var}(\hat{\bar{Y}}_c) & =  \frac{1}{n_2(n_2 - 1)}\sum_{x \in s_2}\Big(\frac{M(x)}{\bar{M_2}}\Big)^2(Y_{c}(x) - \hat{\bar{Y}}_c)^2
 	\end{align}
 \end{subequations}
-
-with $\bar{M_2}=\frac{\sum_{x \in s_{2}}M(x)}{n_{2}}$.
+with $\bar{M_2} = \frac{\sum_{x \in s_{2}}M(x)}{n_{2}}$.
 
@@
 % +++++++++++++++++++++++++++++ %
-\subsection{Design-based small area regression estimators for cluster sampling}
+\subsection{Design-Based Small Area Regression Estimators for Cluster Sampling}
 \label{sec:SAestimators}
@@
 We consider the internal model approach, where the estimators take into account that the regression coefficients on the cluster level were fitted using the same sample used for estimation.
-To apply this to small area estimation, the vector of estimated regression coefficients on the cluster level is found by "borrowing strength" from the entire terrestrial sample $s_2$ of the current inventory:
-
+To apply this to small area estimation, the~vector of estimated regression coefficients on the cluster level is found by ``borrowing strength'' from the entire terrestrial sample $s_2$ of the current inventory:
 \begin{subequations}\label{normequ_simple_cluster}
 	\begin{align}
-	\hat{\pmb{\beta}}_{c,s_2} &= \pmb{A}_{c,s_2}^{-1} \Big(\frac{1}{n_2}\sum_{x\in{s_2}}M(x)Y_{c}(x)\pmb{Z}_{c}(x)\Big) \\
-	\pmb{A}_{c,s_2} &=\frac{1}{n_2}\sum_{x\in{s_2}}M(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)
+	\hat{\pmb{\beta}}_{c,s_2} & =  \pmb{A}_{c,s_2}^{-1} \Big(\frac{1}{n_2}\sum_{x\in{s_2}}M(x)Y_{c}(x)\pmb{Z}_{c}(x)\Big) \\
+	\pmb{A}_{c,s_2} & = \frac{1}{n_2}\sum_{x\in{s_2}}M(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)
 	\end{align}
@@
 
-\noindent $\pmb{Z}_{c}(x)$ is the column vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Eq.\ref{eq:Zc(x)}).
-The weight $w(x_l)$ is the proportion of the extraction area (support) within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.
-
+$\pmb{Z}_{c}(x)$ is the column vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Equation~(\ref{eq:Zc(x)})).
+The~weight $w(x_l)$ is the proportion of the extraction area (support) within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.
 \begin{equation}\label{eq:Zc(x)}
-\pmb{Z}_{c}(x)=\frac{\sum_{l=1}^{M}I_{F}(x_l)w(x_l)\pmb{Z}(x_l)}{\sum_{l=1}^{M}I_{F}(x_l)w(x_l)}
+\pmb{Z}_{c}(x) = \frac{\sum_{l = 1}^{M}I_{F}(x_l)w(x_l)\pmb{Z}(x_l)}{\sum_{l = 1}^{M}I_{F}(x_l)w(x_l)}
 \end{equation}
 
-\noindent The estimated design-based variance-covariance matrix $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}$ accounts for the fact that the regression model is internal and reflects the sampling variability that occurs when estimating the regression coefficients on the realized sample $s_2$.
+The estimated design-based variance-covariance matrix $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}$ accounts for the fact that the regression model is internal and reflects the sampling variability that occurs when estimating the regression coefficients on the realized sample $s_2$.
 It is defined as
-
 \begin{equation}\label{eq:varcovarbeta}
-\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}=\pmb{A}_{c,s_2}^{-1}
+\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}} = \pmb{A}_{c,s_2}^{-1}
 \Big(\frac{1}{n_2^2}\sum_{x\in{s_2}}M^{2}(x)\hat{R}_{c}^2(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)\Big)
@@
 \end{equation}
-
-\noindent with
-
+with 
 \begin{equation}\label{eq:globresids}
-\hat{R}_{c}=Y_{c}(x)-\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2} = Y_{c}(x) - \hat{Y}_{c}(x)
+\hat{R}_{c} = Y_{c}(x)-\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2}  =  Y_{c}(x) - \hat{Y}_{c}(x)
 \end{equation}
-
-\noindent being the empirical model residuals at the cluster level.
-By construction of OLS, the empirical model residuals satisfy that they average to zero, i.e.
-$\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$, if $\pmb{Z}_{c}(x)$ contains the intercept term 1.
-Because the model is fitted internally, i.e.
-using the terrestrial sample $s_2$ of the inventory area, this leads to the important \textit{zero mean residual property} of the theoretical model residuals over the inventory domain $F$, i.e.
-$\int_{F} R_{c}(x)dx$.
-\citet{mandallaz2013a} and \citet{mandallaz2013b} used this property particular for the case of small area estimation to derive better variance estimates based on the g-weight technique adapted from the works of \citet{sarndal2003}.\\
+being the empirical model residuals at the cluster level.
+By construction of OLS, the empirical model residuals satisfy that they average to zero, i.e.,~$\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)} = 0$, if $\pmb{Z}_{c}(x)$ contains the intercept term~1.
+Because the model is fitted internally, i.e.,~using the terrestrial sample $s_2$ of the inventory area, this~leads to the important \textit{zero mean residual property} of the theoretical model residuals over the inventory domain $F$, i.e.,~$\int_{F} R_{c}(x)dx$.
+\citet{mandallaz2013a} and \citet{mandallaz2013b} used this property particular for the case of small area estimation to derive better variance estimates based on the g-weight technique adapted from the works of \citet{sarndal2003}.
 
@@
 	\begin{align}
-	\hat{\bar{\pmb{Z}}}_{c,G} &= \frac{\sum_{x \in s_{1,G}} M_{G}(x) \pmb{Z}_{c,G}(x)}{\sum_{x \in s_{1,G}} M_{G}(x)} \label{eq:meanZcG} \hspace{3ex} &\text{where} \hspace{3ex}
-	\pmb{Z}_{c,G}(x) =  \frac{\sum_{l=1}^{M} I_{G}(x_l)\pmb{Z}(x_l)}{M_{G}(x)}\\		
-	Y_{c,G}(x) &= \frac{\sum_{l=1}^{M} I_{G}(x_l)Y(x_l)}{M_{G}(x)}  &\text{and} \hspace{3ex}
-	\hat{Y}_{c,G}(x)=\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2}\\
-	\bar{\hat{R}}_{2,G} &= \frac{\sum_{x \in s_{2,G}} M_{G}(x) \hat{R}_{c,G}(x)}{\sum_{x \in s_{2,G}} M_{G}(x)} \hspace{3ex} &\text{where} \hspace{3ex}
+	\hat{\bar{\pmb{Z}}}_{c,G} & =  \frac{\sum_{x \in s_{1,G}} M_{G}(x) \pmb{Z}_{c,G}(x)}{\sum_{x \in s_{1,G}} M_{G}(x)} \label{eq:meanZcG} \hspace{3ex} &\text{where} \hspace{3ex}
+	\pmb{Z}_{c,G}(x)  =   \frac{\sum_{l = 1}^{M} I_{G}(x_l)\pmb{Z}(x_l)}{M_{G}(x)}\\		
+	Y_{c,G}(x) & =  \frac{\sum_{l = 1}^{M} I_{G}(x_l)Y(x_l)}{M_{G}(x)}  &\text{and} \hspace{3ex}
+	\hat{Y}_{c,G}(x) = \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2}\\
+	\bar{\hat{R}}_{2,G} & =  \frac{\sum_{x \in s_{2,G}} M_{G}(x) \hat{R}_{c,G}(x)}{\sum_{x \in s_{2,G}} M_{G}(x)} \hspace{3ex} &\text{where} \hspace{3ex}
 	\hat{R}_{c,G}(x)  =  Y_{c,G}(x)-\hat{Y}_{c,G}(x)
@@
 
-Note that the restriction to $G$, i.e.
-$I_{G}(x_l)=\{0,1\}$, is made on the individual sample plot level $x_l$, and $M_{G}(x) = \sum_{l=1}^{M}I_{G}(x_l)$ thus is the number of sample plots per cluster within the small area.
-The asymptotically design-unbiased point estimate of \textit{PSMALL} is then defined according to Eq.
-\ref{eq:psmall_pest}.
+Note that the restriction to $G$,i.e.,~$I_{G}(x_l) = \{0,1\}$, is made on the individual sample plot level $x_l$, and $M_{G}(x)  =  \sum_{l = 1}^{M}I_{G}(x_l)$ thus is the number of sample plots per cluster within the small area.
+The~asymptotically design-unbiased point estimate of \textit{PSMALL} is then defined according to Equation~(\ref{eq:psmall_pest}).
 The first term estimates the small area population mean of $G$ by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$.
-The second term then corrects for a potential bias of the regression model predictions in the small area $G$ by adding the mean of the empirical residuals $\bar{\hat{R}}_{2,G}$ in $G$.
+The~second term then corrects for a potential bias of the regression model predictions in the small area $G$ by adding the mean of the empirical residuals $\bar{\hat{R}}_{2,G}$ in $G$.
 This correction is necessary because the zero mean residual property that holds in $F$ is not guaranteed to hold in small area $G$ under this construction.
@@
 	\begin{align}
-	\hat{Y}_{c,G,PSMALL} &= \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} + \bar{\hat{R}}_{2,G} \label{eq:psmall_pest} \\
+	\hat{Y}_{c,G,PSMALL} & =  \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} + \bar{\hat{R}}_{2,G} \label{eq:psmall_pest} \\
 	\hat{\var}(\hat{Y}_{c,G,PSMALL}) &  =  \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}\hat{\bar{\pmb{Z}}}_{c,G}
@@
 \end{subequations}
-
-\noindent with $\bar{M}_{2,G}=\frac{\sum_{x \in s_{2,G}}M_{G}(x)}{n_{2,G}}$.\\
+with $\bar{M}_{2,G} = \frac{\sum_{x \in s_{2,G}}M_{G}(x)}{n_{2,G}}$.\\
 
 The variance-covariance matrix of the auxiliary vector $\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}$ is thereby defined as
-
 \begin{equation}\label{estvarcovaux_G}
@@
 \end{equation}
-
-\noindent with $\bar{M}_{1,G}=\frac{\sum_{x \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.\\
-
-The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Eq.
-\ref{eq:psmallvar}.
+with $\bar{M}_{1,G} = \frac{\sum_{x \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.
+
+The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Equation~(\ref{eq:psmallvar}).
 Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean in $G$ using a non-exhaustive sample $s_{1,G}$.
 The third term is the variance of the model residuals and thus accounts for the inaccuracies of the model predictions.
-Note that the first term can also be rewritten using g-weights \cite[pg.14]{mandallaz2016} which ensures some beneficial calibration of the auxiliary variables to the first-phase sample.\\
+Note that the first term can also be rewritten using g-weights~\cite{mandallaz2016}~(pp.14) which ensures some beneficial calibration of the auxiliary variables to the first-phase~sample.
 
@@
 
-The \psynth{} estimator is commonly applied when no terrestrial sample is available within the small area $G$ (i.e.
-$n_{2,G}=0$).
-The point estimate (Eq.
-\ref{eq:psynth_pest}) is thus only based on the predictions generated by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$.
-Note that the bias correction term using the empirical residuals (Eq.
-\ref{eq:psmall_pest}) can no longer be applied.
+The \psynth{} estimator is commonly applied when no terrestrial sample is available within the small area $G$ (i.e.,~$n_{2,G} = 0$).
+The point estimate (Equation~(\ref{eq:psynth_pest})) is thus only based on the predictions generated by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$.
+Note that the bias correction term using the empirical residuals (Equation~(\ref{eq:psmall_pest})) can no longer be applied.
 Conditioned on the realized sample, the \psynth{} estimator can thus potentially have an unobservable design-based bias.
@@
 	\begin{align}
-	\hat{Y}_{c,G,PSYNTH} & =\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} \label{eq:psynth_pest} \\
+	\hat{Y}_{c,G,PSYNTH} &  = \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} \label{eq:psynth_pest} \\
 	\hat{\var}(\hat{Y}_{c,G,PSYNTH})&  = 
@@
 
-The contribution to the variance by the model residuals in small area $G$ can also no longer be considered (Eq.
-\ref{eq:psynth_var}).
+The contribution to the variance by the model residuals in small area $G$ can also no longer be considered (Equation~(\ref{eq:psynth_var})).
 As a result, the synthetic estimator will usually have a smaller variance than estimators that consider the model residuals, but at the cost of a potential bias.
-Note that the \psynth{} estimations are still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.\\
+Note that the \psynth{} estimations are still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.
 
@@
 
-The \extpsynth{} estimator (Eq.
-\ref{eq:extpsynth}) has been proposed by \citet{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased.
-It has the advantage that the mean of the empirical model residuals of the OLS regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e.
-$\bar{\hat{R}}_{c} = \bar{\hat{R}}_{c,G} = 0$.
-This is realized by \textit{extending} the auxiliary vector $\pmb{Z}_{c}(x)$ by the indicator variable $I_{c,G}$ which takes the value 1 if the entire cluster lies within the small area $G$ and 0 if the entire cluster is outside $G$, i.e.
-$I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$.
-The extended auxiliary vector thus becomes $\pmb{\mathbb{Z}}_{c}^{\top}(x)= (\pmb{Z}_{c}^{\top}(x),I_{c,G}(x))$ and the new regression coefficient using $\pmb{\mathbb{Z}}_{c}(x)$ instead of $\pmb{Z}_{c}(x)$ in Eq.
-\ref{normequ_simple_cluster} is denoted as $\hat{\pmb{\theta}}_{s_2}$.
-All remaining components are calculated by plugging in $\pmb{\mathbb{Z}}_{c}(x)$ in Eq.
-\ref{eq:compsG}.
+The \extpsynth{} estimator (Equation~(\ref{eq:extpsynth})) has been proposed by \citet{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased.
+It has the advantage that the mean of the empirical model residuals of the OLS regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e.,~$\bar{\hat{R}}_{c}  =  \bar{\hat{R}}_{c,G}  =  0$.
+This is realized by \textit{extending} the auxiliary vector $\pmb{Z}_{c}(x)$ by the indicator variable $I_{c,G}$ which takes the value 1 if the entire cluster lies within the small area $G$ and 0 if the entire cluster is outside $G$, i.e.,~$I_{c,G}(x) = \frac{M_{G}(x)}{M(x)}$.
+The extended auxiliary vector thus becomes $\pmb{\mathbb{Z}}_{c}^{\top}(x) =  (\pmb{Z}_{c}^{\top}(x),I_{c,G}(x))$ and the new regression coefficient using $\pmb{\mathbb{Z}}_{c}(x)$ instead of $\pmb{Z}_{c}(x)$ in Equation~(\ref{normequ_simple_cluster}) is denoted as $\hat{\pmb{\theta}}_{s_2}$.
+All remaining components are calculated by plugging in $\pmb{\mathbb{Z}}_{c}(x)$ in Equation~(\ref{eq:compsG}).
 A decomposition of $\hat{\pmb{\theta}}_{s_2}$ reveals that the residual correction term is now included in the regression coefficient $\hat{\pmb{\theta}}_{s_2}$ \citep{mandallaz2016}.
@@
 	\begin{align}
-	\hat{Y}_{c,G,EXTPSYNTH} & =\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}^{\top}\hat{\pmb{\theta}}_{c,s_2} \label{eq:extpsynth_pest} \\
+	\hat{Y}_{c,G,EXTPSYNTH} &  = \hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}^{\top}\hat{\pmb{\theta}}_{c,s_2} \label{eq:extpsynth_pest} \\
 	\hat{\var}(\hat{Y}_{c,G,EXTPSYNTH})&  = 
@@
 
-However, it is important to note that $\bar{\hat{R}}_{c,G} = 0$ under the extended regression model only holds if the sample plots $x_1, ..., x_l$ of a cluster are \textit{all} either inside our outside the small area, i.e.
-$M_G(x)\equiv M(x)$, and thus $I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$ can only take the values 1 or 0.
+However, it is important to note that $\bar{\hat{R}}_{c,G}  =  0$ under the extended regression model only holds if the sample plots $x_1, ..., x_l$ of a cluster are \textit{all} either inside our outside the small area, i.e.,~$M_G(x)\equiv M(x)$, and thus $I_{c,G}(x) = \frac{M_{G}(x)}{M(x)}$ can only take the values 1 or 0.
 \citet{mandallaz2016} assumed that the effects on the estimates should be negligible as the number of occasions where $M_{G}(x) < M(x)$ was considered to be small in practical implementations.
@@
 % ----------------------------- %
-\subsection{Measures of estimation accuracy}
-
-The estimation precision was quantified by the estimation error, which is the ratio of the standard error and the point estimate (here $\hat{Y}$ stands for the point estimate produced under the various estimators):
-
+\subsection{Measures of Estimation Accuracy}
+
+The estimation precision was quantified by the estimation error, which is the ratio of the standard error and the point estimate (here $\hat{Y}$ stands for the point estimate produced under the various~estimators):
 \begin{equation}\label{eq:error}
-error_{[\%]}=\frac{\sqrt{\hat{\var}(\hat{Y})}}{\hat{Y}}*100
+error_{[\%]} = \frac{\sqrt{\hat{\var}(\hat{Y})}}{\hat{Y}} \times 100
 \end{equation}
@@
 The confidence intervals for the SRS estimator can be obtained as:
-
 %\begin{equation}\label{ci_1phase}
-%CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
+%CI_{1-\alpha}(\hat{Y}) = \bigg{\lbrack}\hat{Y}-t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
 %\hat{Y}+t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
 %\end{equation}
-
 \begin{equation}\label{ci_1phase}
-CI_{1-\alpha}(\hat{\bar{Y}}_c)=\hat{\bar{Y}}_c \pm t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{\bar{Y}}_c)}
+CI_{1-\alpha}(\hat{\bar{Y}}_c) = \hat{\bar{Y}}_c \pm t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{\bar{Y}}_c)}
 \end{equation}
@@
 The confidence intervals for the \psmall{} and \extpsynth{} estimates are calculated as:
-
 %\begin{equation}\label{ci_2phase_sae}
-%CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
+%CI_{1-\alpha}(\hat{Y}) = \bigg{\lbrack}\hat{Y}-t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
 %\hat{Y}+t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
 %\end{equation}
-
 \begin{subequations}\label{ci_2phase_sae}
 	\begin{align}
-	CI_{1-\alpha}(\hat{Y}_{c,G,EXTPSYNTH})&=\hat{Y}_{c,G,EXTPSYNTH} \pm t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y}_{c,G,EXTPSYNTH})} \\
-	CI_{1-\alpha}(\hat{Y}_{c,G,PSMALL})&=\hat{Y}_{c,G,PSMALL} \pm t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y}_{c,G,PSMALL})}
+	CI_{1-\alpha}(\hat{Y}_{c,G,EXTPSYNTH})& = \hat{Y}_{c,G,EXTPSYNTH} \pm t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y}_{c,G,EXTPSYNTH})} \\
+	CI_{1-\alpha}(\hat{Y}_{c,G,PSMALL})& = \hat{Y}_{c,G,PSMALL} \pm t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y}_{c,G,PSMALL})}
 	\end{align}
@@
 For the \psynth{} estimates, the confidence intervals are
-
 %\begin{equation}\label{ci_2phase_global}
-%CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
+%CI_{1-\alpha}(\hat{Y}) = \bigg{\lbrack}\hat{Y}-t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
 %\hat{Y}+t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
 %\end{equation}
-
 \begin{equation}\label{ci_2phase_psynth}
-CI_{1-\alpha}(\hat{Y}_{c,G,PSYNTH})=\hat{Y}_{c,G,PSYNTH} \pm t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y}_{c,G,PSYNTH})}
+CI_{1-\alpha}(\hat{Y}_{c,G,PSYNTH}) = \hat{Y}_{c,G,PSYNTH} \pm t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y}_{c,G,PSYNTH})}
 \end{equation}
-
-\noindent with $p$ being the number of parameters used in the regression model including the intercept term.\\
-
-In order to address the potential benefits of the small area estimators compared with the SRS approach, we calculated the \textit{relative efficiency} (\textit{RE}, Eq.
-\ref{eq:releff}) which can be interpreted as the relative sample size under SRS needed to achieve the variance under the double-sampling (DS) estimators.
-
+with $p$ being the number of parameters used in the regression model including the intercept term.
+
+In order to address the potential benefits of the small area estimators compared with the SRS approach, we calculated the \textit{relative efficiency} (\textit{RE}, Equation~(\ref{eq:releff})) which can be interpreted as the relative sample size under SRS needed to achieve the variance under the double-sampling (DS) estimators.
 \begin{equation}\label{eq:releff}
-RE=\frac{\hat{\var}(\hat{Y}_{SRS})}{\hat{\var}(\hat{Y}_{DS})}
+RE = \frac{\hat{\var}(\hat{Y}_{SRS})}{\hat{\var}(\hat{Y}_{DS})}
 \end{equation}
-
 where $\hat{Y}$ stands for the point estimate produced under the respective estimator.
@@
 % ----------------------------------------------------------------------- %
-\section{Case study}
+\section{Case Study}
 \label{sec:CaseStudy}
-
-\subsection{Study area and small area units}
+\vspace{-6pt}
+
+\subsection{Study Area and Small Area Units}
 \label{sec:studyarea}
@@
 With 42.3\% (appr.
-8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}.
+8400 km$^2$) of the entire state area (19,850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}.
 The forests of RLP are further characterised by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterised by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a.
@@
 Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure.
-The forest area of RLP are divided into 3 ownership classes, i.e.
-state forest (27\%), municipal forest (46\%) and privately owned forest (27\%).
+The forest area of RLP are divided into 3 ownership classes, i.e.,~state forest (27\%), municipal forest (46\%) and privately owned forest (27\%).
 The forest service of RLP has the legal mandate to sustainably manage the state and municipal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}.
@@
 On the upper level, RLP has been divided into 45 forest districts (Forst{\"a}mter, \textit{FA}), which are further divided into a total number of 405 sub-districts (Forstreviere, \textit{FR}).
-The next level are the forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5 to 10 year period in order to set up management strategies for the upcoming 10 years.
+The next level are the forest stands (104,184 in total) for which expert judgements are conducted by SFIs in a 5 to 10 year period in order to set up management strategies for the upcoming 10 years.
 The FAs and FRs constituted the SA units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}.
-The average area of the SA units was 43'777 ha on the FA-level, and 4624 ha on the FR level.
-
+The average area of the SA units was 43,777 ha on the FA-level, and 4624 ha on the FR level.
+
+\begin{figure}[H]
+	\centering
+	\resizebox{0.85\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
+	\caption{({\textbf{Left}}): Study area with delineated FA forest management units.
+{(\textbf{Right}}): Example for each of the three management units (from top to bottom): FA, FR and forest stand unit overlayed with the extended double-sampling cluster design.
+{Green}: Forest stand polygon layer defining the state and municipal forest area of this study.}
+	\label{fig:StudyArean}
+\end{figure}
 % ----------------------------------------------------------------------- %
-\subsection{Terrestrial sample}
-
-Rhineland-Palatinate is covered by a 2x2 km inventory grid of the German NFI.
+\subsection{Terrestrial Sample}
+
+Rhineland-Palatinate is covered by a 2 $\times$ 2 km inventory grid of the German NFI.
 In the last inventory (BWI3) conducted in the year 2011 and 2012, timber volume information was derived for 2810 clusters (8092 plots) in the field survey.
@@
 Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrial observations and the information derived from the auxiliary information.
-A comparison of the DGPS coordinates with the so-far used target coordinates revealed that 90\% of all horizontal deviations lay in the range of 25 meters.
-A detailed analysis of horizontal DGPS errors in RLP by \citet{lambrecht2017} indicated that 80\% of the plots should not exceed horizontal DGPS errors of 8 meters.
+A comparison of the DGPS coordinates with the so-far used target coordinates revealed that 90\% of all horizontal deviations lay in the range of 25 m.
+A detailed analysis of horizontal DGPS errors in RLP by \citet{lambrecht2017} indicated that 80\% of the plots should not exceed horizontal DGPS errors of 8 m.
 For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.
@@
 
-\begin{figure}[H]
-	\centering
-	\resizebox{0.85\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
-	\caption{\textit{Left}: Study area with delineated FA forest management units.
-\textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit overlayed with the extended double-sampling cluster design.
-\textit{Green}: Forest stand polygon layer defining the state and municipal forest area of this study.}
-	\label{fig:StudyArean}
-\end{figure}
-
 % ----------------------------------------------------------------------- %
-\subsection{Extension to double-sampling design}
+\subsection{Extension to Double-Sampling Design}
 \label{ext_to_2phase}
 
-In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double-sampling cluster design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ (Figure \ref{fig:StudyArean}, \textit{right}).
+In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double-sampling cluster design by densifying the existing systematic 2 $\times$ 2 km grid to a grid size of 500 $\times$ 500 m that constituted the large first phase $s_1$ (Figure \ref{fig:StudyArean}, {right}).
 The existing terrestrial phase $s_2$ was integrated by replacing the target coordinates of the respective $s_1$ clusters by the terrestrially measured DGPS coordinates.
@@
 Table \ref{tab:fieldata} provides a short descriptive summary about the volume densities and the main attributes of the NFI plots located in the state and municipal forest sampling frame.
-The densification led to an average sample size $n_{1,G}$ of 759  clusters (range: 246 -- 1022) in the FA units, and 88 clusters (range: 1 -- 194) in the FR units.
-
-\input{tab/table_fieldmeasuredvals.tex}
+The densification led to an average sample size $n_{1,G}$ of 759  clusters (range: 246--1022) in the FA units, and 88 clusters (range: 1--194) in the FR units.
+
+\begin{table}[H]
+	\begin{center}
+	\caption{Descriptive statistics of the forest observed on NFI sample plots located within communal and state forest area ($n_2$  =  5791).}
+	\label{tab:fieldata}
+	{\small %
+	\begin{tabular}{cccc}
+		\toprule
+		\textbf{Variable} & \textbf{Mean} & \textbf{SD} & \textbf{Maximum} \\ 
+		\midrule
+Timber Volume (m$^3$/ha) & 300.9 & 195.6 & 1375.3 \\
+Mean DBH (mm) & 354.9 & 137.2 & 1123.2 \\
+Mean height (dm) & 239.6 & 72.4 & 497.4 \\
+Mean stem density per hectare & 101  & 114 & 1010 \\
+\bottomrule
+\end{tabular}
+}%
+\end{center}
+\end{table}
 
@@
 % ----------------------------------------------------------------------- %
-\subsection{Auxiliary data}
+\subsection{Auxiliary Data}
 \label{sec:auxinfo}
-
+\vspace{-6pt}
 % ----------------------------------------- %
-\subsubsection{LiDAR canopy height model}
+\subsubsection{LiDAR Canopy Height Model}
 \label{sec:chm}
@@
 From 2003 to 2013, the topographic survey institution of RLP conducted an airborne laserscanning acquisition over the entire federal state during leaf-off conditions in order to derive a countrywide digital terrain model (DTM) as well as a digital surface model (DSM).
-For this study, the recorded ALS data was used to create a canopy height model (CHM) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 meters (Fig.
-\ref{fig:Auxvars}, \textit{top}).
+For this study, the recorded ALS data was used to create a canopy height model (CHM) in raster format, providing discrete information about the canopy surface height of the forest area in a spatial resolution of 5 m (Figure~\ref{fig:Auxvars}, {top}).
 The CHM was calculated as the difference between the digital terrain model and the digital surface model that were derived by a Delauney interpolation of the ground and first ALS pulses respectively.
@@
 In addition, the quality of the CHM varied substantially as ALS technology evolved over the years.
-For example, the ALS acquisitions recorded in 2002 and 2003 exhibited particularly poor quality with about only 0.04 point per m$^2$, whereas more recent datasets contained more than 5 points per m$^2$.
+For example, the ALS acquisitions recorded in 2002 and 2003 exhibited particularly poor quality with about only 0.04~points per m$^2$, whereas more recent datasets contained more than 5 points per m$^2$.
 Furthermore, CHM information was not available at 16 sample locations due to sensor failures.
@@
 
+% Graphik:
+\begin{figure}[H]
+	\centering
+	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/Auxvars_400dpi.png}}
+	\caption{(\textbf{Left}): CHM (top) and tree species classification map (bottom) available on the federal state level.
+(\textbf{Right}): Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.
+From top to bottom: CHM, aerial image, tree species classification.}
+	\label{fig:Auxvars}
+\end{figure}
+
 % ---------------------------------------------- %
-\subsubsection{Tree species classification map}
+\subsubsection{Tree Species Classification Map}
 \label{sec:tspecclass}
 
-Additional auxiliary data was derived from a countrywide satellite-based classification map predicting the five main tree species \citep{stoffels2015}, i.e.
-European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir and Scots pine (Fig.
-\ref{fig:Auxvars}, \textit{bottom}).
-The tree species map has a grid size of 5x5 m and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) using a spatially adaptive classification algorithm \citep{stoffels2012}.
+Additional auxiliary data was derived from a countrywide satellite-based classification map predicting the five main tree species \citep{stoffels2015}, i.e.,~European beech, Sessile and Pedunculate oak, Norway spruce, Douglas fir and Scots pine (Figure~\ref{fig:Auxvars}, {bottom}).
+The tree species map has a grid size of \mbox{5 $\times$ 5 m} and was calculated from 22 bi-temporal satellite images (SPOT5 and RapidEye) using a spatially adaptive classification algorithm \citep{stoffels2012}.
 As timber volume estimation on the tree level is often based on species-specific biomass and volume equations, the use of tree species information has often been stated as a key factor for improving the precision of timber volume estimates \citep{white2016}.
 In this respect, incorporating the tree species map was particularly attractive as it predicts five of the seven tree species that are used in the BWI3 taper functions \citep{kublin2013} to calculate the timber volume of a sample tree.
-However, due to unavailable satellite data, the tree species map excluded one large patch with an area of 415 km$^2$ in the south-west part of RLP covering an entire FA unit consisting of 10 FR units.
+However, due to unavailable satellite data, the tree species map excluded one large patch with an area of 415~km$^2$ in the south-west part of RLP covering an entire FA unit consisting of 10 FR units.
 In 9 additional FR units, the tree species information was also missing for a subset of the sample locations due to two additional patches with areas of 76 km$^2$ and 100 km$^2$ respectively in the northern part of RLP.
@@
 		\caption{Sample size for each phase in entire study area. $n_{\{1,2\},plot}$: number of plots. $n_{\{1,2\}}$: number of clusters. TSPEC: tree species map information.}
-		\vspace{0.2cm}
+
 		\label{tab:ssize}
 		{\small %
-			\begin{tabular}{l|r|r|r|r}
-				\hline
-				\multicolumn{1}{c|}{\textit{Sampling frame}} & \multicolumn{1}{c|}{\textbf{$n_{1,plot}$}}  & \multicolumn{1}{c|}{\textbf{$n_1$}}  & \multicolumn{1}{c|}{\textbf{$n_{2,plot}$}}  & \multicolumn{1}{c}{\textbf{$n_2$}} \\ % <-- added & and content for each column
-				\hline \hline
-				municipal and state forest & 96'854 & 33'365 & 5791 & 2055\\
-				\hspace{5mm} \footnotesize missing CHM & \footnotesize 18 & \footnotesize 10 & \footnotesize 0 & \footnotesize 0\\ % <--
-				\hspace{5mm} \footnotesize missing TSPEC & \footnotesize 7060  & \footnotesize 3587 & \footnotesize 414 & \footnotesize 385\\ % <--
-				\hspace{5mm} \footnotesize missing CHM \textit{and} TSPEC & \footnotesize 3 & \footnotesize 2 & \footnotesize 0 & \footnotesize 0\\ % <--
-				\hspace{5mm} \footnotesize missing CHM \textit{or} TSPEC & \footnotesize 7075 & \footnotesize 3595 & \footnotesize 414 & \footnotesize 385\\ % <--
-				\hline \hline
+			\begin{tabular}{lrrrr}%{ccccc}
+				\toprule
+				\multicolumn{1}{c}{\textit{\textbf{Sampling Frame}}} & \multicolumn{1}{c}{\boldmath\textbf{$n_{1,plot}$}}  & \multicolumn{1}{c}{\boldmath\textbf{$n_1$}}  & \multicolumn{1}{c}{\boldmath\textbf{$n_{2,plot}$}}  & \multicolumn{1}{c}{\boldmath\textbf{$n_2$}} \\ % <-- added & and content for each column
+				\midrule
+				municipal and state forest & 96,854 & 33,365 & 5791 & 2055\\
+				\hspace{5mm}  missing CHM &18 &  10 &  0 &  0\\ % <--
+				\hspace{5mm}  missing TSPEC &7060  &  3587 &  414 &  385\\ % <--
+				\hspace{5mm}  missing CHM \textit{and} TSPEC &  3 & 2 &  0 & 0\\ % <--
+				\hspace{5mm}  missing CHM \textit{or} TSPEC &  7075 &  3595 &  414 &  385\\ % <--
+				\bottomrule
 			\end{tabular}
@@
 % ---------------------------------------------- %
-\subsection{Calculation of the explanatory variables}
+\subsection{Calculation of the Explanatory Variables}
 \label{sec:expvarcalc}
-
-\subsubsection{Canopy height model}
+\vspace{-6pt}
+\subsubsection{Canopy Height Model}
 
 The continuous explanatory variables derived from the CHM were the mean canopy height (\textit{meanheight}) and the standard deviation (\textit{stddev}).
-The quantities were calculated by evaluating the raster values around each sample location within a circle with a predefined radius of 12 meters, i.e.
-the support.
+The quantities were calculated by evaluating the raster values around each sample location within a circle with a predefined radius of 12 m, i.e.,~the~support.
 In order to correct for edge effects at the forest border, the intersection of each support area to the state and municipal forest area was determined using a polygon mask provided by the state forest service.
-The percentage of the support within the forest layer was used as the weight $w(x_l)$ introduced in Eq.
-\ref{eq:Zc(x)} in order to derive the weighted mean of the explanatory variables on the cluster level.
+The percentage of the support within the forest layer was used as the weight $w(x_l)$ introduced in Equation~(\ref{eq:Zc(x)}) in order to derive the weighted mean of the explanatory variables on the cluster level.
 Neglecting the support adjustment would deteriorate the coherence between explanatory variables computed at the forest boundary and the corresponding local density that already includes a potential boundary adjustment, thus introducing unnecessary noise to the model.
@@
 
-% Graphik:
-\begin{figure}[H]
-	\centering
-	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/Auxvars_400dpi.png}}
-	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level.
-Right: Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.
-From top to bottom: CHM, aerial image, tree species classification.}
-	\label{fig:Auxvars}
-\end{figure}
-
-\subsubsection{Tree species classification map}
+\subsubsection{Tree Species Classification Map}
 
@@
 Otherwise, the sample location was assigned the value 'mixed'.
-Likewise for the CHM variables, the support radius was 12 meters although the use of different support sizes for each explanatory variable would be in agreement with the two-phase estimators presented in Section \ref{sec:SAestimators}.
+Likewise for the CHM variables, the support radius was 12 m although the use of different support sizes for each explanatory variable would be in agreement with the two-phase estimators presented in Section \ref{sec:SAestimators}.
 The specific setting for the support size and the percentage threshold was found to be optimal in order to yield the best possible regression model precision when incorporating the \textit{treespecies} variable as an additional predictor.
@@
 We thus applied this calibration model to the \textit{treespecies} variable derived at all sample locations $s_1$.
-Table \ref{tab:classacc} gives the classification accuracies \citep{congalton2008} of the \textit{treespecies} variable after calibration.
+Table~\ref{tab:classacc} gives the classification accuracies \citep{congalton2008} of the \textit{treespecies} variable after calibration.
 More details on the processing of the explanatory variables and identification of optimal parameter settings for their calculation are described in \citet{hill2017a}.
@@
 		\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
-		\vspace{0.2cm}
+
 		\label{tab:classacc}
 		{\small %
-			\begin{tabular}{l|c|c|c|c} %8cols
-				\hline
-				Main plot species & Producer's accuracy[\%] & User's accuracy[\%] & n$_{ref}$ & n$_{class}$ \\
-				\hline \hline	
+			\begin{tabular}{ccccc} %8cols
+				\toprule
+				\textbf{Main Plot Species} & \textbf{Producer's Accuracy} \textbf{[\%] }& \textbf{User's Accuracy} \textbf{[\%]} & \boldmath$n_{ref}$ &\boldmath $n_{class}$ \\
+				\midrule
 				Beech       & 22.3 & 47.0 & 883 & 419 \\
@@
 				Mixed       & 84.5 & 64.5 & 3152 & 4127 \\
-				\hlineB{2}
-				& \multicolumn{2}{l|}{Overall accuracy: 62.0 \%} & 5384 & 5384 \\
-				\hline \hline
+				\midrule
+				\multicolumn{3}{c}{Overall accuracy: 62.0\%} & 5384 & 5384 \\
+				\bottomrule
 			\end{tabular}
@@
 \end{table}
+\vspace{-15pt}
 
@@
 
-The model selection process for this study required a substantial time commitment due to sophisticated challenges such as: a) the heterogeneity of the remote sensing data, b) the identification of the optimal support sizes under angle count sampling, and c) the incorporation of tree species information.
+The model selection process for this study required a substantial time commitment due to sophisticated challenges such as: (a) the heterogeneity of the remote sensing data; (b) the identification of the optimal support sizes under angle count sampling and (c) the incorporation of tree species information.
 Here, only a summary of the extensive analysis that was performed is provided but the reader can refer to \citet{hill2017a} if more details are desired.\par
@@
 For this reason, a individual species modeling within each \alsyear{} stratum remained infeasible, but might have further improved the model fit.
-An additional evaluation of the model's performance within each ALS acquisition year stratum revealed that the quality of the model fit substantially varied between the strata (Table \ref{tab:adj_r2_within}).
+An~additional evaluation of the model's performance within each ALS acquisition year stratum revealed that the quality of the model fit substantially varied between the strata (Table \ref{tab:adj_r2_within}).
 In particular, values above the overall \adjrsq{} were higher in ALS acquisition years close to the terrestrial survey date compared to years with larger time gaps.\par
@@
 % Table 1:
-\input{tab/modacc_modterms.tex}
-
-% Table 2:
-\input{tab/mod_r2_lyearstrata_table.tex}
+% latex table generated in R 3.4.2 by xtable 1.8-2 package
+% Sun Jan 07 17:11:26 2018
+
+\begin{table}[H]
+	\begin{center}
+	\caption{Model fit specifications for the two OLS regression models on the cluster level. Interaction terms are indicated by ':'. () give the respective values on the plot level.} 
+	\label{tab:modacc_modterms}
+    {\small %
+	\begin{tabular}{ccccc}
+\toprule
+\textbf{Model Terms} & \textbf{Model} & \boldmath$R^2_{adj}$ & \textbf{RMSE} & \textbf{RMSE}\% \\ 
+\midrule
+meanheight + stddev + meanheight$^2$ +  & full model &  0.58 & 90.11  & 29.76 \\
+treespecies + ALSyear + & & (0.48) &  (139.22) & (45.98) \\ 
+meanheight:treespecies + \\ meanheight:ALSyear + meanheight:stddev + \\ stddev:ALSyear &&& \\ \midrule
+meanheight + stddev + meanheight$^2$ + & reduced model  & 0.55  & 95.23 & 31.65 \\
+ALSyear + meanheight:ALSyear + & & (0.45) & (144.13) & (47.60) \\
+meanheight:stddev + stddev:ALSyear &&& \\  
+\bottomrule
+\end{tabular}
+}%
+\end{center}
+\end{table}
+\vspace{-12pt}
+
+\begin{table}[H]
+	\begin{center}
+		\caption{$R^2$, RMSE and RMSE\% on the cluster level of the full regression model within ALS acquisition year strata (\textit{ALSyear}).
+$Area_{ALSyear}$: Area covered by ALS acquisition given in km$^2$.
+\textit{n}: sample size of validation data.
+() give the respective values on the plot level.}
+		\label{tab:adj_r2_within}
+		{\small %
+			\begin{tabular}{cccccc}
+				\toprule
+				\textit{\textbf{ALSyear}} & \boldmath$Area_{ALSyear}$ & \boldmath$R^2$ & \textbf{RMSE} &\textbf{ RMSE\%} &\emph{\textbf{ n}} \\ 
+				\midrule
+				\multirow{2}{*}{2012}  & \multirow{2}{*}{2807}  &  0.65  &  98.52  &  29.62 &  156  \\ 
+				&&             (0.61) & (135.84) & (44.87) & (408) \\ \midrule
+
+				\multirow{2}{*}{2011}  & \multirow{2}{*}{4361}  &  0.60   & 96.89   &  29.66 & 354  \\ 
+				&&             (0.57)  & (146.21) & (48.29) & (883) \\ \midrule
+
+				\multirow{2}{*}{2010} & \multirow{2}{*}{4182}     & 0.64  & 76.38   & 27.57 & 420 \\ 
+				&&             (0.51)  & (120.90) & (39.93) & (1171) \\\midrule
+
+				\multirow{2}{*}{2009} & \multirow{2}{*}{2100}     & 0.53  & 92.22  & 33.31 & 218  \\   
+				&&             (0.42)  & (133.42) & (44.07) & (559) \\ \midrule
+
+				\multirow{2}{*}{2008} & \multirow{2}{*}{2968}     & 0.61  & 87.10   & 32.20 & 247  \\        
+				&&             (0.48)  & (130.38) & (43.06) & (701) \\ \midrule
+
+				\multirow{2}{*}{2008\_1} & \multirow{2}{*}{2116}  & 0.43  & 117.99  & 33.64 & 157  \\      
+				&&             (0.33)  & (175.43) & (57.94) & (394) \\ \midrule
+
+				\multirow{2}{*}{2007} & \multirow{2}{*}{3498}     & 0.56  & 82.43  & 26.57 & 135 \\ 
+				&&             (0.46)  & (136.47)  & (45.08) & (418) \\\midrule
+
+				\multirow{2}{*}{2003} & \multirow{2}{*}{602}      & 0.34  & 85.92  & 27.31 & 145  \\ 
+				&&             (0.27)  & (154.48) & (51.02) & (529) \\\midrule
+
+				\multirow{2}{*}{2002} & \multirow{2}{*}{775}      & 0.52  & 87.25  & 27.22 & 97  \\ 
+				&&             (0.44) & (141.55) & (46.75) & (314) \\
+				\bottomrule
+			\end{tabular}
+		}%
+	\end{center}
+\end{table}
+
+%\begin{table}[H]
+%	\begin{center}
+%		\caption{$R^2$, RMSE and RMSE\% of the full regression model within ALS acquisition year strata (\textit{ALSyear}).
+$Area_{ALSyear}$: Area covered by ALS acquisition given in km$^2$.
+\textit{n}: number of validation data.
+() give the respective values on the cluster level.}
+%		\label{tab:adj_r2_within}
+%		{\small %
+%			\begin{tabular}{llcccc}
+%				\hline
+%				\textit{ALSyear} & $Area_{ALSyear}$ & $R^2$ & RMSE & RMSE\% & n \\ 
+%				\hline
+%				2012  & 2807  &  0.61  &  135.84  &  44.87  &  408  \\ 
+%				&&             (0.66) & (101.99) & (30.61) & (156) \\[0.2cm]
+%				
+%				2011  & 4361  &  0.57   & 146.21   &  48.29  & 883  \\ 
+%				&&             (0.59)  & (109.78) & (34.23) & (354) \\[0.2cm]
+%				
+%				2010 & 4182     & 0.51  & 120.90   & 39.93  & 1171 \\ 
+%				&&             (0.58)  & (86.88) & (31.44) & (420) \\[0.2cm]
+%				
+%				2009 & 2100     & 0.42  & 133.42  & 44.07  & 559  \\   
+%				&&             (0.45)  & (102.07) & (36.63) & (218) \\[0.2cm]
+%				
+%				2008 & 2968     & 0.48  & 130.38   & 43.06  & 701  \\        
+%				&&             (0.53)  & (95.16) & (35.53) & (247) \\[0.2cm]
+%				
+%				2008\_1 & 2116  & 0.33  & 175.43  & 57.94  & 394  \\      
+%				&&             (0.33)  & (135.90) & (38.43) & (157) \\[0.2cm]
+%				
+%				2007 & 3498     & 0.46  & 136.47   & 45.08   & 418  \\ 
+%				&&             (0.48)  & (94.42)  & (30.41) & (135] \\[0.2cm]
+%				
+%				2003 & 602      & 0.27  & 154.48   & 51.02  & 529  \\ 
+%				&&             (0.29)  & (98.96) & (30.57) & (145) \\[0.2cm]
+%				
+%				2002 & 775      & 0.44  & 141.55   & 46.75   & 314   \\ 
+%				&&             (0.61) & (85.4) & (26.76) & (97) \\
+%				\hline
+%				\hline
+%			\end{tabular}
+%		}%
+%	\end{center}
+%\end{table}
 
@@
 
-% new: 
-Concerning the treatment of outliers or leverage points, it can be advisable to remove such observations from the training data set that is used to determine the regression coefficients (Section \ref{sec:SAestimators}) in order to minimize the residual variance for the entire terrestrial sample.
+\vspace{-12pt}
+Concerning the treatment of outliers or leverage points, it can be advisable to remove such observations from the training data set that is used to determine the regression coefficients (Section~\ref{sec:SAestimators}) in order to minimize the residual variance for the entire terrestrial sample.
 However, it should be noted that such removal of observations does restrict the calculation of design-unbiased estimation to the \psmall{} estimator, because the residuals still have to be derived for the full terrestrial sample in order to ensure unbiased estimation.
 This would no longer be satisfied when using the \extpsynth{} estimator, where the residual correction term is included in the regression coefficient (Section \ref{sec:extpsynth}).
-For our particular case, we conducted an analysis of influential observations \citep[pp.
-160--167]{fahrmeir2013} on the plot level for the full regression model.
-We calculated the leverage values and found that 10\% of all observations exceeding a predefined critical threshold, i.e.
-twice the average of the hat matrix diagonal entries.
+For our particular case, we conducted an analysis of influential observations \citep{fahrmeir2013} (pp.
+160--167) on the plot level for the full regression model.
+We calculated the leverage values and found that 10\% of all observations exceeding a predefined critical threshold, i.e.,~twice the average of the hat matrix diagonal entries.
 Further investigation revealed that several leverage points showed unusually large \meanheight{} values compared to their respective timber volume densities.
@@
 
-\subsection{General estimation results}
+\vspace{-6pt}
+\subsection{General Estimation Results}
 \label{sec:feasest}
@@
 Also the \psynth{} estimator could not be applied for 2 FR-units since $n_{1,G} < 2$.
-For better comparison, the descriptive summaries of point estimates and estimation errors for each estimator presented in Table \ref{tab:estres} are always based on the same population of small area units, i.e.
-the 321 districts for which unbiased two-phase estimations were possible.\\
+For better comparison, the descriptive summaries of point estimates and estimation errors for each estimator presented in Table \ref{tab:estres} are always based on the same population of small area units, i.e.,~the 321 districts for which unbiased two-phase estimations were~possible.
+
 All estimators could however be applied to all 45 FA units due to substantially larger sample sizes.
-The average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (Table \ref{tab:estres}).
+The~average value and the range of the mean timber volume estimates over the evaluated FA and FR units turned out to be very similar between all estimators (Table \ref{tab:estres}).
 An additional pairwise comparison of the 95\% confidence intervals revealed that the four estimators did in fact not produce statistically different point estimates for all FA and FR units.
@@
 $N_u$: number of evaluated small area units.}
-		\vspace{0.2cm}
+
 		\label{tab:estres}
 		{\small %
-			\begin{tabular}{c|l c|c c c|c c c} %8cols
-				\hlineB{1}
-				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Point estimates} & \multicolumn{3}{c}{error$_{[\%]}$} \\
-				\cline{4-9} & & & mean & min & max & mean & min & max \\
-				\hline \hline
-				\multirow{4}{*}{FA} & SRS       & ($N_u$=45)  & 300.16 & 215.91 & 392.84 &  6.69 & 3.87 & 13.21 \\
-				& PSMALL    & ($N_u$=45)  & 307.29 & 209.26 & 417.10 &  5.16 & 3.46 & 14.33 \\
-				& EXTPSYNTH & ($N_u$=45)  & 307.27 & 209.01 & 415.02 &  4.78 & 3.25 & 13.88 \\
-				& PSYNTH    & ($N_u$=45)  & 306.90 & 223.51 & 409.92 &  2.34 & 1.54 &  3.95 \\
-				\hlineB{2}          
-				\multirow{4}{*}{FR} & SRS       & ($N_u$=321) & 302.77 &  99.89 & 552.87 & 16.94 & 2.76 & 55.51 \\
-				& PSMALL    & ($N_u$=321) & 308.15 & 159.64 & 568.67 & 12.24 & 3.48 &  44.94 \\
-				& EXTPSYNTH & ($N_u$=321) & 308.38 & 154.07 & 544.34 & 11.34 & 3.60 &  40.91 \\
-				& PSYNTH    & ($N_u$=321) & 305.56 & 197.47 & 444.29 & 4.13  & 2.56 &  18.07 \\
-				\hline \hline
+			\begin{tabular}{ccccccccc} %8cols
+				\toprule
+				\multirow{2}{*}{\textbf{\vspace{-3PT}
+ District Level}} & \multicolumn{2}{c}{\multirow{2}{*}{\vspace{-3PT}\textbf{Estimator}}} & \multicolumn{3}{c}{\textbf{Point Estimates}} & \multicolumn{3}{c}{\textbf{Error}\boldmath$_{[\%]}$} \\
+				\cmidrule{4-9} & & & \textbf{Mean} & \textbf{Min} & \textbf{Max} & \textbf{Mean} & \textbf{Min} & \textbf{Max} \\
+			\midrule
+				\multirow{4}{*}{FA} & SRS       & ($N_u$ = 45)  & 300.16 & 215.91 & 392.84 &  6.69 & 3.87 & 13.21 \\
+				& PSMALL    & ($N_u$ = 45)  & 307.29 & 209.26 & 417.10 &  5.16 & 3.46 & 14.33 \\
+				& EXTPSYNTH & ($N_u$ = 45)  & 307.27 & 209.01 & 415.02 &  4.78 & 3.25 & 13.88 \\
+				& PSYNTH    & ($N_u$ = 45)  & 306.90 & 223.51 & 409.92 &  2.34 & 1.54 &  3.95 \\
+				\midrule
+				\multirow{4}{*}{FR} & SRS       & ($N_u$ = 321) & 302.77 &  99.89 & 552.87 & 16.94 & 2.76 & 55.51 \\
+				& PSMALL    & ($N_u$ = 321) & 308.15 & 159.64 & 568.67 & 12.24 & 3.48 &  44.94 \\
+				& EXTPSYNTH & ($N_u$ = 321) & 308.38 & 154.07 & 544.34 & 11.34 & 3.60 &  40.91 \\
+				& PSYNTH    & ($N_u$ = 321) & 305.56 & 197.47 & 444.29 & 4.13  & 2.56 &  18.07 \\
+			\bottomrule
 			\end{tabular}
@@
 
+\vspace{-12pt}
+
 % ----------------------------------------------------------------------- %
 % ----------------------------------------------------------------------- %
-\subsection{Estimation errors}
+\subsection{Estimation Errors}
 \label{sec:esterr}
 
-On both small area levels, the design-unbiased estimators \psmall{} and \extpsynth{} led to a substantial reduction in the estimation error compared to the SRS estimator (Fig.
-\ref{fig:disterrors}).
+On both small area levels, the design-unbiased estimators \psmall{} and \extpsynth{} led to a substantial reduction in the estimation error compared to the SRS estimator (Figure~\ref{fig:disterrors}).
 On the FA level, the SRS estimator yielded an estimation error of 6.7\% on average compared to 5.2\% and 4.8\% under \extpsynth{} and \psmall{} respectively (Table \ref{tab:estres}).
-The cumulative error distribution (Fig.
-\ref{fig:disterrors}, left) reveals that under the SRS estimator, errors less than 5\% were achieved for 17\% of the FA units (8 of 45).
+The cumulative error distribution (Figure~\ref{fig:disterrors}, left) reveals that under the SRS estimator, errors less than 5\% were achieved for 17\% of the FA units \mbox{(8 of 45}).
 This proportion could be increased to 62\% (28 FA units) and 73\% (33 FA units) by application of the \psmall{} and \extpsynth{} estimator.
@@
 Estimation errors higher than 10\% only appeared twice for each of the three estimators.\par
-Although the estimation errors were substantially larger overall on the FR level compared to the FA level due to smaller sample sizes, the error reduction from SRS by \psmall{} and \extpsynth{} were even more pronounced (Fig.
-\ref{fig:disterrors}, right).
+Although the estimation errors were substantially larger overall on the FR level compared to the FA level due to smaller sample sizes, the error reduction from SRS by \psmall{} and \extpsynth{} were even more pronounced (Figure~\ref{fig:disterrors}, right).
 The average error under the SRS estimator was 16.9\%, while it was 11.3\% and 12.2\% under \psmall{} and \extpsynth{} (Table \ref{tab:estres}).
@@
 	\caption{Cumulative distribution of estimation errors under SRS, \psmall{}, \extpsynth{} and the \psynth{} estimator.
-\textit{Left}: Results for the 45 FA units.
-\textit{Right}: Results for the 321 FR units.}
+({\textbf{Left}}): Results for the 45 FA units.
+({\textbf{Right}}): Results for the 321 FR units.}
 	\label{fig:disterrors}
@@
 Figure \ref{fig:disterrors} reveals that the error distribution of \psmall{} and \extpsynth{} are very similar, with \psmall{} showing marginally higher estimation errors.
-In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (Fig.
-\ref{fig:compvar}, left).
+In order to investigate the differences between \psmall{} and \extpsynth{}, we compared the g-weight variances of both estimators for all 321 FR units (Figure~\ref{fig:compvar}, left).
 As obvious, \psmall{} yielded slightly larger variances for the vast majority of the estimates.
@@
 The distribution of variances from \extpsynth{} was found to be highly significantly lower than that of \psmall{} except for the group of $n_{2,G} > 10$.
-The latter was expected since the variances of both estimators are asymptotically equivalent under large terrestrial sample sizes $n_{2,G}$ within the small area \citep[pp.17--18]{mandallaz2016}.
-This was also confirmed by a visual comparison of the absolute differences in the variances (Fig.
-\ref{fig:compvar}, right) which decreased with increasing terrestrial sample size.
+The latter was expected since the variances of both estimators are asymptotically equivalent under large terrestrial sample sizes $n_{2,G}$ within the small area \citep{mandallaz2016} (pp.17--18).
+This was also confirmed by a visual comparison of the absolute differences in the variances (Figure~\ref{fig:compvar}, right) which decreased with increasing terrestrial sample size.
 Performing the same comparison for small areas with violations also revealed the \extpsynth{} variances to be significantly smaller than the respective \psmall{} variances until sample sizes $n_{2,G} > 10$.
 Based on these investigations, it was not possible to determine whether the differences for sample sizes smaller than 10 were caused by the violations or just reflect the general tendency of \extpsynth{} to produce smaller variances than \psmall{} under small sample sizes.
-However, a visual inspection provided some evidence that the violations created a statistically significant influence on the \extpsynth{} variance (Fig.
-\ref{fig:compvar}, left, red diamonds) that makes it appear to be slightly over-optimistic.
+However, a visual inspection provided some evidence that the violations created a statistically significant influence on the \extpsynth{} variance (Figure~\ref{fig:compvar}, left, red diamonds) that makes it appear to be slightly over-optimistic.
 For sample sizes of $n_{2,G} < 6$, a weakly significant difference between the \extpsynth{} variances of those small areas with violations and the \extpsynth{} variances without violation was also indicated by an unpaired Wilcoxon Rank-Sum Test.
-However, the differences were still marginal and a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point estimates.
+However, the differences were still marginal and a comparison of the confidence intervals of \psmall{} and \extpsynth{} revealed that the variance differences did not lead to statistically significant point~estimates.
 
@@
 	\resizebox{1\hsize}{!}{\includegraphics{fig/psmall_vs_extpsynth_fu.png}}
-	\caption{\textit{Left}: Comparison of the g-weight variance between the PSMALL and the EXTPSYNTH estimator for the 321 FR units.
-		\textit{Right}: Difference in g-weight variance between the PSMALL and the EXTPSYNTH estimator in dependence of the terrestrial data ($n_{2,G}$) in the FR unit.}
+	\caption{({\textbf{Left}}): Comparison of the g-weight variance between the PSMALL and the EXTPSYNTH estimator for the 321 FR units.
+		({\textbf{Right}}): Difference in g-weight variance between the PSMALL and the EXTPSYNTH estimator in dependence of the terrestrial data ($n_{2,G}$) in the FR unit.}
 	\label{fig:compvar}
@@
 % ----------------------------------------------------------------------- %
-\subsection{Variance reduction compared to SRS}
+\subsection{Variance Reduction Compared to SRS}
 \label{sec:gain_eval}
 
-The variance reduction relative to SRS for \psmall{} and \extpsynth{} are described in Figure \ref{fig:gain} and Table \ref{tab:gain}.
+The variance reduction relative to SRS for \psmall{} and \extpsynth{} are described in Figure~\ref{fig:gain} and Table \ref{tab:gain}.
 A direct comparison of the variances within the small area units revealed that the application of the design-unbiased estimators (\psmall{}, \extpsynth{}) led to a variance reduction compared to SRS in all FA units.
@@
 The reduction in variance can also be expressed in the relative efficiency values, which were 2.02 on average and ranged between 1.18 and 4.13 on the FA level.
-On FR level, the reduction in variance even reached values of 90\% and relative efficiencies of 30 (Table \ref{tab:gain} and Fig.
-\ref{fig:gain}).
+On FR level, the reduction in variance even reached values of 90\% and relative efficiencies of 30 (Table \ref{tab:gain} and Figure~\ref{fig:gain}).
 The \psmall{} estimator again yielded slightly lower variance reductions and relative efficiencies due to the generally smaller variances of the \extpsynth{} estimator (Section \ref{sec:comp}).
@@
 \end{figure}
-
+\vspace{-12pt}
 \begin{table}[H]
@@
 		\caption{Descriptive summary of variance reduction compared to SRS and relative efficiencies on the two forest district levels. $N_u$: number of evaluated small area units.}
-		\vspace{0.2cm}
 		\label{tab:gain}
 		{\small %
-			\begin{tabular}{c|l c|c c c|c c c} %8cols
-				\hlineB{1}
-				\multirow{2}{*}{District level} & \multicolumn{2}{c|}{\multirow{2}{*}{Estimator}} & \multicolumn{3}{c|}{Variance reduction [\%]} & \multicolumn{3}{c}{relative efficiency} \\
-				\cline{4-9} & & & mean & min & max & mean & min & max \\
-				\hline \hline
-				\multirow{2}{*}{FA} & PSMALL    & ($N_u$=45)  & 33.51 &  2.6 & 72.5 & 1.74 & 1.03 & 3.64 \\
-				& EXTPSYNTH & ($N_u$=45)  & 43.30 & 15.7 & 75.8 & 2.03  & 1.18 & 4.13 \\
-				\hlineB{2}          
-				\multirow{2}{*}{FR} & PSMALL    & ($N_u$=321) & 12.48 & -1203.9 & 96.8 & 2.54 & 0.08 & 31.61  \\
-				& EXTPSYNTH & ($N_u$=321) & 24.75 & -892.7  & 97.0 & 2.95 & 0.10 & 33.70 \\
-				\hline \hline
+			\begin{tabular}{ccccccccc} %8cols
+				\toprule
+				\multirow{2}{*}{\vspace{-3PT}\textbf{District Level}} & \multicolumn{2}{c}{\multirow{2}{*}{\vspace{-3PT}\textbf{Estimator}}} & \multicolumn{3}{c}{\textbf{Variance Reduction [\%]}} & \multicolumn{3}{c}{\textbf{Relative Efficiency}} \\
+				\cmidrule{4-9} & & & \textbf{Mean} & \textbf{Min} & \textbf{Max} & \textbf{Mean} & \textbf{Min} & \textbf{Max} \\
+				\midrule
+				\multirow{2}{*}{FA} & PSMALL    & ($N_u$ = 45)  & 33.51 &  2.6 & 72.5 & 1.74 & 1.03 & 3.64 \\
+				& EXTPSYNTH & ($N_u$ = 45)  & 43.30 & 15.7 & 75.8 & 2.03  & 1.18 & 4.13 \\
+			\midrule
+				\multirow{2}{*}{FR} & PSMALL    & ($N_u$ = 321) & 12.48 & $-1203.9$ & 96.8 & 2.54 & 0.08 & 31.61  \\
+				& EXTPSYNTH & ($N_u$ = 321) & 24.75 & $-892.7$  & 97.0 & 2.95 & 0.10 & 33.70 \\
+				\bottomrule
 			\end{tabular}
@@
 \end{table}
-
+\vspace{-6pt}
 Cases also occurred on the FR level where one or both two-phase estimators produced larger variance values than under the SRS estimator.
@@
 One possible reason for this was supposed to be a large residual variance due to a poor performance of the regression model within the small area unit.
-In order to investigate this hypothesis, we analyzed the three variance terms of the \psmall{} estimator (Eq.
-\ref{eq:psmallvar}), i.e.
-the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residuals (term 3).
-In general, the residual term is expected to make the largest contribution to the overall variance since it's sample size is based on $n_{2,G}$ whereas the auxiliary term and the coefficient term are based on larger sample sizes, i.e.
-$n_{1,G}$ and $n_2$ respectively.
+In order to investigate this hypothesis, we analyzed the three variance terms of the \psmall{} estimator (Equation~(\ref{eq:psmallvar})), i.e.,~the variance introduced by the uncertainty of the regression coefficients (term 1), the variance caused by estimating the auxiliary means (term 2), and the variance of the model residuals (term 3).
+In general, the residual term is expected to make the largest contribution to the overall variance since it's sample size is based on $n_{2,G}$ whereas the auxiliary term and the coefficient term are based on larger sample sizes, i.e.,~$n_{1,G}$ and $n_2$ respectively.
 Figure \ref{fig:fail} illustrates the share of the overall variance by the residual term of the \psmall{} estimator scaled by the overall percentage reduction or increase of the variance compared to SRS for various small area sample sizes $n_{2,G}$.
 Not surprisingly, the residual term generally constitutes the dominating part of the \psmall{} variance (around 84\% on average).
-It has to be noted that such high residual term dominance does not necessary indicate that the \psmall{} variance will be disproportionately large (Figure \ref{fig:fail}, \textit{right}).
-However, the vast majority of cases where the \psmall{} variance was considerably larger than the SRS variance occurred where the residual term contributed over 75\% to the overall \psmall{} variance (Figure \ref{fig:fail}, \textit{left}).
+It has to be noted that such high residual term dominance does not necessary indicate that the \psmall{} variance will be disproportionately large (Figure \ref{fig:fail}, {right}).
+However, the vast majority of cases where the \psmall{} variance was considerably larger than the SRS variance occurred where the residual term contributed over 75\% to the overall \psmall{} variance (Figure \ref{fig:fail}, {left}).
 Among those cases, the most pronounced were observed under small sample sizes $n_{2,G} < 5$.
-Here, the average increase in variance compared to SRS of those FR units with $n_{2,G}=4$ was 272\%, compared to 62\% for FR units with $n_{2,G} > 4$.
-In contrast, the decreases in variance compared to SRS (Figure \ref{fig:fail}, \textit{right}) were much more homogeneous in magnitude and also independent of the terrestrial sample size.
+Here, the average increase in variance compared to SRS of those FR units with $n_{2,G} = 4$ was 272\%, compared to 62\% for FR units with $n_{2,G} > 4$.
+In contrast, the decreases in variance compared to SRS (Figure \ref{fig:fail}, {right}) were much more homogeneous in magnitude and also independent of the terrestrial sample size.
 Since $n_{2,G}$ is the same for \psmall{} and SRS, these observations imply that in the problematic small areas, the sum of square residuals for the regression model are likely larger than the sum of square local densities for the clusters in $s_{2,G}$.
@@
 \label{sec:Dis}
-
+\vspace{-6pt}
 % ------------------------ %
-\subsection{Performance of estimators}
+\subsection{Performance of Estimators}
 
@@
 The main reason why this was not considered in the present study was the large number of parameters that would have to be fitted in the individual prediction models resulting from the pronounced heterogeneity in the auxiliary data (multiple tree species and ALS acquisition years in each FA unit).
-In this case, the strategy to 'borrow strength' from the entire inventory domain was preferred to direct estimation in order to avoid overfitting and the implied risk of unstable global estimation.
-Even in case the above mentioned problem of overfitting is not raised, individual model building for a large number of small area units can be time-consuming and small area estimation can be a cost-saving alternative - however, possibly the cost of more efficient global estimation.\par
+In this case, the strategy to `borrow strength' from the entire inventory domain was preferred to direct estimation in order to avoid overfitting and the implied risk of unstable global estimation.
+Even in case the above mentioned problem of overfitting is not raised, individual model building for a large number of small area units can be time-consuming and small area estimation can be a cost-saving alternative- however, possibly the cost of more efficient global estimation.\par
 
@@
 The much smaller estimation errors of the \psynth{} estimator reflected the fact that it does not try to correct for potential bias in the point estimate which can lead to overly optimistic estimation errors and confidence intervals.
-One should thus prefer the unbiased estimates of \psmall{} or \extpsynth{} whenever their calculation is possible.\par
+One should thus prefer the unbiased estimates of \psmall{} or \extpsynth{} whenever their calculation is possible.
 
@@
 It is important to note that this is in perfect agreement with the theory of both two-phase estimators and can theoretically appear if the residual variance in the small area, which generally constitutes the dominating part of the two-phase variance, turns out to be much higher than the variance of the terrestrial data in the small area.
-The empirical findings of our study suggest that such cases can particularly occur if moderate or poor model fits within a small area are combined with small terrestrial sample sizes ($\leq 5$) in the small area.
+The~empirical findings of our study suggest that such cases can particularly occur if moderate or poor model fits within a small area are combined with small terrestrial sample sizes ($\leq$5) in the small area.
 A closer look on these small areas thus might reveal the reason for the poor prediction performance and help to improve the model fit.
@@
 This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero mean residual property of the \extpsynth{} estimator.
-However, our analysis indicated that the difference between the two estimators is negligible for sample sizes $\geq$ 10 due to their asymptotic equivalency.
+However, our analysis indicated that the difference between the two estimators is negligible for sample sizes $\geq$10 due to their asymptotic equivalency.
 We further investigated a potential impact on the \extpsynth{} variance caused by the assumption violation that one or more clusters are not entirely included in the small area unit and found a slight but statistically significant tendency to be over-optimistic for sample sizes smaller than 6.
@@
 %new
-A commonly raised critic on the proposed design-unbiased estimators are their asymptotic properties, i.e.
-the validity of the confidence coverage rates is only ensured if the sample size in a small area is sufficiently large.
+A commonly raised critic on the proposed design-unbiased estimators are their asymptotic properties, i.e.,~the validity of the confidence coverage rates is only ensured if the sample size in a small area is sufficiently large.
 Giving a generally valid sample size for the asymptotic validity range is, unfortunately, infeasible due to the dependency on the heterogeneity of the underlying population which is per se unknown.
@@
 % ------------------------ %
-\subsection{Auxiliary data}
-
-The auxiliary data used in our study were derived from two remote sensing sources, i.e.
-an ALS canopy height model and a tree species classification map.
+\subsection{Auxiliary Data}
+
+The auxiliary data used in our study were derived from two remote sensing sources, i.e.,~an~ALS canopy height model and a tree species classification map.
 Likewise in many similar studies, the ALS mean canopy height proved to be the explanatory variable with highest predictive power.
@@
 One reason for this was the impossibility of modeling individual tree species within each ALS acquisition year, which would add further explanatory power.
-Another reason was the lack of available satellite data for classification in some parts of the country, which led to missing values in the inventory data and restricted 19 FR units to a simpler regression model.
+Another reason was the lack of available satellite data for classification in some parts of the country, which~led to missing values in the inventory data and restricted 19 FR units to a simpler regression model.
 Promising steps with respect to more up-to-date canopy height information have already been made, as the topographic survey institution of RLP will from this year on provide a country-wide canopy height model derived from aerial imagery acquisitions.
@@
 A study of \citet{kirchhoefer2017} recently indicated that similar model performance for German NFI data can be achieved using such imagery-based canopy height models.
-Additionally, the improved coverage and repetition rate of the Sentinel-2 satellite \citep{sentinel2} will allow to produce annually updated tree species classification maps.
+Additionally, the~improved coverage and repetition rate of the Sentinel-2 satellite \citep{sentinel2} will allow to produce annually updated tree species classification maps.
 We consider these alternative auxiliary data sources to also solve the problem of missing explanatory variables at inventory plots.
@@
 
-\section{Conclusion}
+\section{Conclusions}
 \label{sec:concl}
@@
 %
-%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{A.H.
+conducted the study and wrote the manuscript.
+D.M.
+developed the design-based estimators and supported the statistical analysis.
+J.L.
+supported the study on the part of the State Forest Service Rhineland-Palatinate and cross-checked the analysis and the manuscript.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\funding{This research received no external funding.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Andreas Hill conducted the study and wrote the manuscript.
-Daniel Mandallaz developed the design-based estimators and supported the statistical analysis.
-Joachim Langshausen supported the study on the part of the State Forest Service Rhineland-Palatinate and cross-checked the analysis and the manuscript.}
+
 %
@@
 \appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendixsections{one} %Leave argument "multiple" if there are multiple sections.
+\appendixsections{multiple} %Leave argument "multiple" if there are multiple sections.
 Then a counter is printed ("Appendix A").
@@
 \section{}
+\vspace{-6pt}
 % -------------------------------------- %
-\subsection*{R-squared on cluster level}
-
-The R$^2$ on the cluster level is calculated using the number of plots $M(x)$ of each cluster in order to weight for the varying number of plots on which $Y_c(x)$ and $\hat{Y}_{c}(x)$ are based on.
-
+\appendixtitles{yes} 
+\subsection{R-Squared on Cluster Level}
+
+The \emph{R}$^2$ on the cluster level is calculated using the number of plots $M(x)$ of each cluster in order to weight for the varying number of plots on which $Y_c(x)$ and $\hat{Y}_{c}(x)$ are based on.
 \begin{equation*}\label{eq:R_squared_clust}
@@
 
-\noindent $Y_c(x)$ and $\hat{Y}_{c}(x)$ are the predicted and observed local densities on the cluster level calculated according to Equations \ref{eq:locdens_clust} and \ref{eq:globresids}.
-$\hat{\bar{Y}}_c$ is the estimated sample mean corresponding to the weighted mean over all observed local densities on the cluster level (Eq.
-\ref{eq:srs_est_clusters}).\par
+ $Y_c(x)$ and $\hat{Y}_{c}(x)$ are the predicted and observed local densities on the cluster level calculated according to Equations (\ref{eq:locdens_clust}) and (\ref{eq:globresids}).
+$\hat{\bar{Y}}_c$ is the estimated sample mean corresponding to the weighted mean over all observed local densities on the cluster level (Equation~(\ref{eq:srs_est_clusters})).
 
 % -------------------------------------- %
-\subsection*{RMSE on cluster level}
+\appendixtitles{yes} 
+\subsection{RMSE on Cluster Level}
 
 The same weights $M(x)$ are also applied to calculate the RMSE on the cluster level. $n_2$ is the number of clusters used in the modeling frame.
-
 \begin{equation*}\label{eq:RMSE_clust}
-RMSE= \sqrt{\frac{1}{n_{2}}  \sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M}_2}\Big)^2 \Big(\hat{Y}_{c}(x)-Y_c(x)\Big)^2}
+RMSE =  \sqrt{\frac{1}{n_{2}}  \sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M}_2}\Big)^2 \Big(\hat{Y}_{c}(x)-Y_c(x)\Big)^2}
 \end{equation*}
 
-\noindent The \textit{relative} or \textit{normalized} RMSE is calculated by dividing the RMSE by the estimated sample mean $\hat{\bar{Y}}_c$:
-
+The \textit{relative} or \textit{normalized} RMSE is calculated by dividing the RMSE by the estimated sample mean~$\hat{\bar{Y}}_c$:
 \begin{equation*}\label{eq:NRMSE_clust}
@@
 
-\noindent Note that the weights $\frac{M(x)}{\bar{M_2}} \equiv 1$ if the number of plots per cluster is constant.
+Note that the weights $\frac{M(x)}{\bar{M_2}} \equiv 1$ if the number of plots per cluster is constant.
 
@@
 
-%=====================================
+% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
 % References, variant A: internal bibliography
-%=====================================
+% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
 \reftitle{References}
 \externalbibliography{yes}
-\bibliography{bib/literaturerRLPsae}
+\begin{thebibliography}{999}
+\providecommand{\natexlab}[1]{#1}
+
+\bibitem[Polley {et~al.}(2010)Polley, Schmitz, Hennig, and
+  Kroiher]{polley2010intomppo}
+Polley, H.; Schmitz, F.; Hennig, P.; Kroiher, F.
+\newblock {\em National Forest Inventories---Pathways for Common
+  Reporting}; Springer: Heidelberg/Berlin, Germany, 2010; Chapter~13, pp. 223--243.
+
+\bibitem[Th{\"u}nen-Institut(2014)]{bwi3}
+Th{\"u}nen-Institut.
+\newblock Dritte {B}undeswaldinventur 2012,  2014. Available online: \url{https://bwi.info} (accessed on 3 February 2012).
+
+\bibitem[Kulie{\v{s}}is {et~al.}(2016)Kulie{\v{s}}is, Tomter, Vidal, and
+  Lanz]{kulievsis2016}
+Kulie{\v{s}}is, A.; Tomter, S.M.; Vidal, C.; Lanz, A.
+\newblock Estimates of stem wood increments in forest resources: comparison of
+  different approaches in forest inventory: Consequences for international
+  reporting: case studyof European forests.
+\newblock {\em Ann. For. Sci.} {\bf 2016}, {\em 73},~857--869.
+
+\bibitem[B{\"o}ckmann {et~al.}(1998)B{\"o}ckmann, Saborowski, Dahm, Nagel,
+  and Spellmann]{bockmann1998}
+B{\"o}ckmann, T.; Saborowski, J.; Dahm, S.; Nagel, J.; Spellmann, H.
+\newblock Neukonzeption und Weiterentwicklung der Forsteinrichtung in
+  Niedersachsen.
+\newblock {\em Forst und Holz (Germany)} {\bf 1998}, {\em 53},~298--302.
+
+\bibitem[von L{\"u}pke {et~al.}(2012)von L{\"u}pke, Hansen, and
+  Saborowski]{vonLuepke2012}
+Von L{\"u}pke, N.; Hansen, J.; Saborowski, J.
+\newblock A Three-Phase Sampling Procedure for Continuous Forest Inventory with
+  Partial Re-measurement and Updating of Terrestrial Sample Plots.
+\newblock {\em Eur. J. For. Res.} {\bf 2012}, {\em
+  131},~1979--1990.
+\newblock
+doi:{\changeurlcolor{black}\href{https://doi.org/10.1007/s10342-012-0648-z}{\detokenize{10.1007/s10342-012-0648-z}}}.
+
+\bibitem[von L{\"u}pke(2013)]{vonluepke2013}
+Von L{\"u}pke, N.
+\newblock Approaches for the Optimisation of Double Sampling for Stratification
+  in Repeated Forest Inventories.
+\newblock Ph.D. Thesis, University of G{\"o}ttingen, Göttingen, Germany, 2013.
+
+\bibitem[De~Vries(1986)]{devries1986}
+De~Vries, P.G.
+\newblock {\em Sampling Theory for Forest Inventory: A Teach-Yourself Course};
+  Springer: Heidelberg/Berlin, Germany, 1986.
+
+\bibitem[Cochran(1977)]{cochran1977}
+Cochran, W.G.
+\newblock {\em Sampling Techniques}; Wiley Series in Probability and
+  Mathematical Statistics; Wiley:  Hoboken, NJ, USA,
+  1977.
+
+\bibitem[S{\"a}rndal {et~al.}(2003)S{\"a}rndal, Swensson, and
+  Wretman]{sarndal2003}
+S{\"a}rndal, C.E.; Swensson, B.; Wretman, J.
+\newblock {\em Model Assisted Survey Sampling}; Springer Science \& Business
+  Media: Heidelberg/Berlin, Germany,  2003.
+
+\bibitem[Gregoire and Valentine(2007)]{gregoire2007}
+Gregoire, T.G.; Valentine, H.T.
+\newblock {\em Sampling Strategies for Natural Resources and the Environment};
+  CRC Press: Boca~Raton, FL, USA, 2007.
+
+\bibitem[K{\"o}hl {et~al.}(2006)K{\"o}hl, Magnussen, and
+  Marchetti]{kohl2006}
+K{\"o}hl, M.; Magnussen, S.S.; Marchetti, M.
+\newblock {\em Sampling Methods, Remote Sensing and GIS Multiresource Forest
+  Inventory}; Springer Science \& Business Media: Heidelberg/Berlin, Germany,  2006.
+
+\bibitem[Mandallaz(2008)]{mandallaz2008}
+Mandallaz, D.
+\newblock {\em Sampling Techniques for Forest Inventories};  CRC Press: Boca Raton, FL, USA,  2008.
+
+\bibitem[Gillis {et~al.}(2010)Gillis, Boudewyn, Power, and
+  Russo]{gillis2010intomppo}
+Gillis, M.; Boudewyn, P.; Power, K.; Russo, G.
+\newblock Canada. In {\em National Forest Inventories---Pathways for Common
+  Reporting}; Springer: Heidelberg/Berlin, Germany,  2010; Chapter~4, pp. 97--111,
+
+\bibitem[Chojnacky(1998)]{chojnacky1998}
+Chojnacky, D.C.
+\newblock \emph{Double Sampling for Stratification: A Forest Inventory Application in
+  the Interior West};
+\newblock Technical Report; US Department of Agriculture, Forest Service, Rocky
+  Mountain Research Station Ogden: Washington, DC, USA, 1998.
+
+\bibitem[Lanz {et~al.}(2010)Lanz, Br{\"a}ndli, Brassel, Ginzler, Kaufmann,
+  and Th{\"u}rig]{lanz2010intomppo}
+Lanz, A.; Br{\"a}ndli, U.B.; Brassel, P.; Ginzler, C.; Kaufmann, E.;
+  Th{\"u}rig, E.
+\newblock Switzerland. In {\em National Forest Inventories--Pathways for
+  Common Reporting}; Springer: Heidelberg/Berlin, Germany,  2010; Chapter~36, pp.~555–565.
+
+\bibitem[Gasparini {et~al.}(2010)Gasparini, Tosi, and
+  DiCosmo]{gasparini2010intomppo}
+Gasparini, P.; Tosi, V.; DiCosmo, L.
+\newblock Italy. In {\em National Forest Inventories---Pathways for Common
+  Reporting}; Springer: Heidelberg/Berlin, Germany, 2010; Chapter~19, pp. 311–331.
+
+\bibitem[Saborowski {et~al.}(2010)Saborowski, Marx, Nagel, and
+  B{\"o}ckmann]{saborowski2010}
+Saborowski, J.; Marx, A.; Nagel, J.; B{\"o}ckmann, T.
+\newblock Double sampling for stratification in periodic inventories—Infinite
+  population approach.
+\newblock {\em For. Ecol. Manag.} {\bf 2010}, {\em
+  260},~1886--1895.
+
+\bibitem[Grafstr{\"o}m {et~al.}(2017)Grafstr{\"o}m, Schnell, Saarela,
+  Hubbell, and Condit]{grafstrom2017a}
+Grafstr{\"o}m, A.; Schnell, S.; Saarela, S.; Hubbell, S.; Condit, R.
+\newblock The continuous population approach to forest inventories and use of
+  information in the design.
+\newblock {\em Environmetrics} {\bf 2017}, \emph{28}, doi:10.1002/env.2480.
+.
+
+\bibitem[Massey {et~al.}(2014)Massey, Mandallaz, and Lanz]{massey2014a}
+Massey, A.; Mandallaz, D.; Lanz, A.
+\newblock Integrating remote sensing and past inventory data under the new
+  annual design of the Swiss National Forest Inventory using three-phase
+  design-based regression estimation.
+\newblock {\em Can. J. For. Res.} {\bf 2014}, {\em
+  44},~1177--1186.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1139/cjfr-2014-0152}{\detokenize{10.1139/cjfr-2014-0152}}}.
+
+\bibitem[Mandallaz(2013)]{mandallaz2013c}
+Mandallaz, D.
+\newblock A three-phase sampling extension of the generalized regression
+  estimator with partially exhaustive information.
+\newblock {\em Can. J. For. Res.} {\bf 2013}, {\em
+  44},~383--388.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1139/cjfr-2013-0449}{\detokenize{10.1139/cjfr-2013-0449}}}.
+
+\bibitem[Rao(2015)]{rao2015}
+Rao, J.N.
+\newblock {\em Small-Area Estimation}; Wiley Online Library: Hoboken, NJ, USA, 2015.
+
+\bibitem[Breidenbach and Astrup(2012)]{breidenbach2012}
+Breidenbach, J.; Astrup, R.
+\newblock Small area estimation of forest attributes in the Norwegian National
+  Forest Inventory.
+\newblock {\em Eur. J. For. Res.} {\bf 2012}, {\em
+  131},~1255--1267.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1007/s10342-012-0596-7}{\detokenize{10.1007/s10342-012-0596-7}}}.
+
+\bibitem[Goerndt {et~al.}(2011)Goerndt, Monleon, and Temesgen]{goerndt2011}
+Goerndt, M.E.; Monleon, V.J.; Temesgen, H.
+\newblock A comparison of small-area estimation techniques to estimate selected
+  stand attributes using LiDAR-derived auxiliary variables.
+\newblock {\em Can. J. For. Res.} {\bf 2011}, {\em
+  41},~1189--1201.
+
+\bibitem[Steinmann {et~al.}(2013)Steinmann, Mandallaz, Ginzler, and
+  Lanz]{steinmann2013}
+Steinmann, K.; Mandallaz, D.; Ginzler, C.; Lanz, A.
+\newblock Small area estimations of proportion of forest and timber volume
+  combining Lidar data and stereo aerial images with terrestrial data.
+\newblock {\em Can. J. For. Res.} {\bf 2013}, {\em
+  28},~373--385.
+
+\bibitem[Mandallaz {et~al.}(2013)Mandallaz, Breschan, and
+  Hill]{mandallaz2013b}
+Mandallaz, D.; Breschan, J.; Hill, A.
+\newblock New regression estimators in forest inventories with two-phase
+  sampling and partially exhaustive information: A design-based monte carlo
+  approach with applications to small-area estimation.
+\newblock {\em Can. J. For. Res.} {\bf 2013}, {\em
+  43},~1023--1031.
+\newblock
+doi:{\changeurlcolor{black}\href{https://doi.org/10.1139/cjfr-2013-0181}{\detokenize{10.1139/cjfr-2013-0181}}}.
+
+\bibitem[Koch(2010)]{koch2010}
+Koch, B.
+\newblock Status and future of laser scanning, synthetic aperture radar and
+  hyperspectral remote sensing data for forest biomass assessment.
+\newblock {\em ISPRS J. Photogramm. Remote Sens.} {\bf 2010},
+  {\em 65},~581--590.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1016/j.isprsjprs.2010.09.001}{\detokenize{10.1016/j.isprsjprs.2010.09.001}}}.
+
+\bibitem[Naesset(2014)]{naesset2014inmaltamo}
+Naesset, E.
+\newblock Area-Based Inventory in Norway---From Innovation to an Operational
+  Reality. In {\em Forest Applications of Airborne Laser Scanning---Concepts
+  and Case Studies}; Springer: Heidelberg/Berlin, Germany,  2014; Chapter~11, pp. 216--240.
+
+\bibitem[Magnussen {et~al.}(2017)Magnussen, Mauro, Breidenbach, Lanz, and
+  K{\"a}ndler]{magnussen2017}
+Magnussen, S.; Mauro, F.; Breidenbach, J.; Lanz, A.; K{\"a}ndler, G.
+\newblock Area-level analysis of forest inventory variables.
+\newblock {\em Eur. J. For. Res.} {\bf 2017}, \emph{136}, 839--855..
+
+\bibitem[Magnussen {et~al.}(2014)Magnussen, Mandallaz, Breidenbach, Lanz,
+  and Ginzler]{magnussen2014}
+Magnussen, S.; Mandallaz, D.; Breidenbach, J.; Lanz, A.; Ginzler, C.
+\newblock National forest inventories in the service of small area estimation
+  of stem volume.
+\newblock {\em Can. J. For. Res.} {\bf 2014}, {\em
+  44},~1079--1090.
+
+\bibitem[Mandallaz(2013)]{mandallaz2013a}
+Mandallaz, D.
+\newblock Design-based properties of some small-area estimators in forest
+  inventory with two-phase sampling.
+\newblock {\em Can. J. For. Res.} {\bf 2013}, {\em
+  43},~441--449.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1139/cjfr-2012-0381}{\detokenize{10.1139/cjfr-2012-0381}}}.
+
+\bibitem[{B}undesministerium~für {E}rn{\"a}hrung(2011)]{bwi3_aufn}
+{B}undesministerium~für {E}rn{\"a}hrung, L.u.V.
+\newblock Aufnahmeanweisung für die Dritte {B}undeswaldinventur {BWI3} (2011--2012); BMELV: Berlin, Germany, 2011.
+
+\bibitem[Bitterlich(1984)]{bitterlich1984}
+Bitterlich, W.
+\newblock {\em The Relascope Idea. Relative Measurements in Forestry};
+  Commonwealth Agricultural Bureaux:  Wallingford, UK,  1984.
+
+\bibitem[Kublin {et~al.}(2013)Kublin, Breidenbach, and
+  K{\"a}ndler]{kublin2013}
+Kublin, E.; Breidenbach, J.; K{\"a}ndler, G.
+\newblock A flexible stem taper and volume prediction method based on
+  mixed-effects B-spline regression.
+\newblock {\em Eur. J. For. Res.} {\bf 2013}, {\em
+  132},~983--997.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1007/s10342-013-0715-0}{\detokenize{10.1007/s10342-013-0715-0}}}.
+
+\bibitem[Schmitz {et~al.}(2008)Schmitz, Polley, Hennig, Dunger, and
+  Schwitzgebel]{bwi3_ausw}
+Schmitz, F.; Polley, H.; Hennig, P.; Dunger, K.; Schwitzgebel, F.
+\newblock \emph{Die Zweite Bundeswaldinventur-BWI2: Inventur- und
+  Auswertmethoden, Bundesministerium fur Ernahrung, Land-Wirtschaft
+  und Verbraucherschutz (Hrsg)};  BMELV: Berlin, Germany, 2008.
+
+\bibitem[Mandallaz {et~al.}(2016)Mandallaz, Hill, and Massey]{mandallaz2016}
+Mandallaz, D.; Hill, A.; Massey, A.
+\newblock \emph{Design-Based Properties of Some Small-Area Estimators in Forest
+  Inventory with Two-Phase Sampling---Revised Version};
+\newblock Technical Report; Department of Environmental Systems Science, ETH
+  Zurich:  Zürich, Switzerland, 2016.
+
+\bibitem[Hill and Massey(2017)]{forestinventory}
+Hill, A.; Massey, A.
+\newblock {\em forestinventory: Design-Based Global and Small-Area Estimations
+  for Multiphase Forest Inventories}; R package version 0.3.1; 2017.
+
+\bibitem[{R Core Team}(2018)]{R}
+{R Core Team}.
+\newblock {\em R: A Language and Environment for Statistical Computing};
+\newblock R Foundation for Statistical Computing: Vienna, Austria,  2018.
+
+\bibitem[Gauer and Aldinger(2005)]{gauer2005}
+Gauer, J.; Aldinger, E.
+\newblock Wald{\"o}kologische Naturr{\"a}ume Deutschlands-Wuchsgebiete.
+\newblock {\em Mitt. Ver. Forstliche Standortskunde
+  Forstpflanzenz{\"u}chtung} {\bf 2005}, {\em 43},~281--288.
+
+\bibitem[LWaldG(2000)]{lwaldg_rlp}
+LWaldG.
+\newblock {\em {L}andeswaldgesetz {R}heinland-{P}falz ({F}orest {Act}
+  {R}hineland-{P}alatinate)};
+\newblock {R}hineland: {P}alatinate, {G}ermany,~2000.
+
+\bibitem[Lamprecht {et~al.}(2017)Lamprecht, Hill, Stoffels, and
+  Udelhoven]{lambrecht2017}
+Lamprecht, S.; Hill, A.; Stoffels, J.; Udelhoven, T.
+\newblock A Machine Learning Method for Co-Registration and Individual Tree
+  Matching of Forest Inventory and Airborne Laser Scanning Data.
+\newblock {\em Remote Sens.} {\bf 2017}, {\em 9}.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.3390/rs9050505}{\detokenize{10.3390/rs9050505}}}.
+
+\bibitem[Hill {et~al.}(2018)Hill, Buddenbaum, and Mandallaz]{hill2017a}
+Hill, A.; Buddenbaum, H.; Mandallaz, D.
+\newblock Combining canopy height and tree species map information for
+  large-scale timber volume estimations under strong heterogeneity of auxiliary
+  data and variable sample plot sizes.
+\newblock {\em Eur. J. For. Res.} {\bf 2018}.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1007/s10342-018-1118-z}{\detokenize{10.1007/s10342-018-1118-z}}}.
+
+\bibitem[Stoffels {et~al.}(2015)Stoffels, Hill, Sachtleber, Mader,
+  Buddenbaum, Stern, Langshausen, Dietz, and Ontrup]{stoffels2015}
+Stoffels, J.; Hill, J.; Sachtleber, T.; Mader, S.; Buddenbaum, H.; Stern, O.;
+  Langshausen, J.; Dietz, J.; Ontrup, G.
+\newblock Satellite-Based Derivation of High-Resolution Forest Information
+  Layers for Operational Forest Management.
+\newblock {\em Forests} {\bf 2015}, {\em 6},~1982--2013.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.3390/f6061982}{\detokenize{10.3390/f6061982}}}.
+
+\bibitem[Stoffels {et~al.}(2012)Stoffels, Mader, Hill, Werner, and
+  Ontrup]{stoffels2012}
+Stoffels, J.; Mader, S.; Hill, J.; Werner, W.; Ontrup, G.
+\newblock Satellite-based stand-wise forest cover type mapping using a
+  spatially adaptive classification approach.
+\newblock {\em Eur. J. For. Res.} {\bf 2012}, {\em
+  131},~1071--1089.
+
+\bibitem[White {et~al.}(2016)White, Coops, Wulder, Vastaranta, Hilker, and
+  Tompalski]{white2016}
+White, J.C.; Coops, N.C.; Wulder, M.A.; Vastaranta, M.; Hilker, T.; Tompalski,
+  P.
+\newblock Remote sensing technologies for enhancing forest inventories: A
+  review.
+\newblock {\em Can. J. Remote Sens.} {\bf 2016}, {\em
+  42},~619--641.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1080/07038992.2016.1207484}{\detokenize{10.1080/07038992.2016.1207484}}}.
+
+\bibitem[Breiman(2001)]{breiman2001}
+Breiman, L.
+\newblock Random forests.
+\newblock {\em Mach. Learn.} {\bf 2001}, {\em 45},~5--32.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1023/A:1010933404324}{\detokenize{10.1023/A:1010933404324}}}.
+
+\bibitem[Congalton and Green(2008)]{congalton2008}
+Congalton, R.G.; Green, K.
+\newblock {\em Assessing the Accuracy of Remotely Sensed Data: Principles and
+  Practices};  CRC Press: Boca Raton, FL, USA,  2008.
+
+\bibitem[Fahrmeir {et~al.}(2013)Fahrmeir, Kneib, Lang, and
+  Marx]{fahrmeir2013}
+Fahrmeir, L.; Kneib, T.; Lang, S.; Marx, B.
+\newblock {\em Regression: Models, Methods and Applications}; Springer Science
+  \& Business Media: Heidelberg/Berlin, Germany, 2013.
+
+\bibitem[Wilcoxon {et~al.}(1970)Wilcoxon, Katti, and Wilcox]{wilcoxon1970}
+Wilcoxon, F.; Katti, S.; Wilcox, R.A.
+\newblock Critical values and probability levels for the Wilcoxon rank sum test
+  and the Wilcoxon signed rank test.
+\newblock {\em Sel. Tables Math. Stat.} {\bf 1970}, {\em
+  1},~171--259.
+
+\bibitem[Kirchhoefer {et~al.}(2017)Kirchhoefer, Schumacher, Adler, and
+  K{\"a}ndler]{kirchhoefer2017}
+Kirchhoefer, M.; Schumacher, J.; Adler, P.; K{\"a}ndler, G.
+\newblock Considerations towards a Novel Approach for Integrating Angle-Count
+  Sampling Data in Remote Sensing Based Forest Inventories.
+\newblock {\em Forests} {\bf 2017}, {\em 8},~239.
+\newpage
+\bibitem[ESA(2017)]{sentinel2}
+ESA.
+\newblock Sentinel-2 Earth Observation Mission, 2017. Available online: \url{https://sentinel.esa.int/web/sentinel/missions/sentinel-2} (accessed on 29 March 2017).
+
+\bibitem[Massey and Mandallaz(2015)]{massey2015b}
+Massey, A.; Mandallaz, D.
+\newblock Design-based regression estimation of net change for forest
+  inventories.
+\newblock {\em Can. J. For. Res.} {\bf 2015}, {\em
+  45},~1775--1784.
+\newblock
+  doi:{\changeurlcolor{black}\href{https://doi.org/10.1139/cjfr-2015-0266}{\detokenize{10.1139/cjfr-2015-0266}}}.
+
+\end{thebibliography}
 
